### 2015-04-01 datapaper.tex
template

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{epstopdf}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

\title{Data Paper%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}
}
%\subtitle{Do you have a subtitle?\\ If so, write it here}

%\titlerunning{Short form of title}        % if too long for running head

\author{First Author         \and
        Second Author %etc.
}

%\authorrunning{Short form of author list} % if too long for running head

\institute{F. Author \at
              first address \\
              Tel.: +123-45-678910\\
              Fax: +123-45-678910\\
              \email{fauthor@example.com}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           S. Author \at
              second address
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

\maketitle

\begin{abstract}
Insert your abstract here. Include keywords, PACS and mathematical
subject classification numbers as needed.
\keywords{First keyword \and Second keyword \and More}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

\section{Introduction}\label{intro}
Text with citations \cite{RefB} and \cite{RefJ}.

\section{Background} \label{sec:1}

\section{Data Collection}\label{sec:2}

\subsection{Hardware Setup}

\subsection{Image Accusation}

\subsection{Image Calibration}

\section{Image Labeling}

\section{Baseline Performance}

\section{Conclusion}

\paragraph{Paragraph headings} Use paragraph headings as needed.
\begin{equation}
a^2+b^2=c^2
\end{equation}

% For one-column wide figures use
\begin{figure}
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics{example.eps}
% figure caption is below the figure
\caption{Please write your figure caption here}
\label{fig:1}       % Give a unique label
\end{figure}
%
% For two-column wide figures use
\begin{figure*}
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[width=0.75\textwidth]{example.eps}
% figure caption is below the figure
\caption{Please write your figure caption here}
\label{fig:2}       % Give a unique label
\end{figure*}
%
% For tables use
\begin{table}
% table caption is above the table
\caption{Please write your table caption here}
\label{tab:1}       % Give a unique label
% For LaTeX tables use
\begin{tabular}{lll}
\hline\noalign{\smallskip}
first & second & third  \\
\noalign{\smallskip}\hline\noalign{\smallskip}
number & number & number \\
number & number & number \\
\noalign{\smallskip}\hline
\end{tabular}
\end{table}

%\begin{acknowledgements}
%If you'd like to thank anyone, place your comments here
%and remove the percent signs.
%\end{acknowledgements}

% BibTeX users please use one of
%\bibliographystyle{spbasic}      % basic style, author-year citations
%\bibliographystyle{spmpsci}      % mathematics and physical sciences
%\bibliographystyle{spphys}       % APS-like style for physics
%\bibliography{}   % name your BibTeX data base

% Non-BibTeX users please use
\begin{thebibliography}{}
%
% and use \bibitem to create references. Consult the Instructions
% for authors for reference list style.
%
\bibitem{RefJ}
% Format for Journal Reference
Author, Article title, Journal, Volume, page numbers (year)
% Format for books
\bibitem{RefB}
Author, Book title, page numbers. Publisher, place (year)
% etc
\end{thebibliography}

\end{document}
% end of file template.tex

### 2015-04-13 labeling.tex
labeling section by Xi

\section{Image Labeling}

Part of the dataset is manually annotated to provide ground truth tip locations, leaf segmentation results and leaf consistency overtime. 
Tip locations are saved in TXT file \textcolor{red}{(TBD)}.
Leaf segmentation results are stored in PNG images with one color for each leaf.
The same color is used to represent the same leaf over a sequence of frames.

We use RGB images for labeling because of better visualization. 
All plants are cropped out from the background and saved as JPG files. 
For Arabidopsis images, we label four frames each day. 
While for bean images, we label seven frames each day because of faster leaf movement. 
We develop a Matlab GUI interface for leaf labeling, as shown in Fig~\ref{fig:label}.
A user can open an image to label the two tips and annotate each leaf. 
The results will be automatically saved once a user goes to label the next image. 
This GUI is used to annotate leaves in each frame. 
For consistent annotation of the same leaf over time, we use the labeled results of each frame to find the correspondence according to leaf centers. 
Incorrect correspondence will be manually corrected.

\begin{figure}[h]
\centering
\includegraphics[width=.98\textwidth]{figure/labeling}\\
\caption{Leaf labeling process, including tip labels and leaf annotation.}
\label{fig:label}
\end{figure}

Tip label is implemented by clicking pairs of points on the image. 
The outer tip is always clicked before the inner tip. 
A line connecting each pair of tips will be shown immediately for visualization. 
Inaccurate labels can be deleted and relabeled.

For leaf annotation, we use the idea of merging and splitting super pixels. 
There are six different numbers of super pixels: $100$, $200$, $300$, $500$, $800$, $1000$. 
The user can specify which level to use depending on how well the super pixels can separate the leaves from the background. 
Because one leaf can be covered by several super pixels and one super pixel can across two leaves or the foreground and background. 
We allow merging and splitting super pixels. 
Merging is implemented by drawing a rectangle on the image. 
Every super pixel overlapping with this rectangle will be merged together. 
Splitting is implemented by drawing a line separating a leaf from the background or from another leaf.

As shown in Fig.~\ref{fig:label}, several super pixels that covers one leaf are first merged together to form a large super pixel. 
Since the top part of the super pixel covers some of the background and the bottom part covers another small leaf, two lines are drawn on this super pixel to split it. 
The leaf boundary is overlaid on the image for better visualization to guide the next action. 
This process continues until all leaves have been annotated.

### 2015-04-13 datapaper.tex
labeling section by Xi
Initial commit of creative Senz3D camera component

@@
 
+% For one-column wide figures use
+\begin{figure}
+  \includegraphics[width=9cm,trim=20 240 20 300,clip]{Figures/CameraConfiguration}
+\caption{A plot of the three cameras showing their relative configuration and fields of view as obtained through calibration.
+Units are in mm.
+In the center is the color camera, and its optical center defines the world coordinate system.
+On the right is the depth camera.
+Its points are projected into the world coordinate system.
+On the left is the fluorescent and IR camera.}
+\label{fig:CameraConfiguration} 
+\end{figure}
+
+\subsection{Image Accusation}
+
+\subsection{Image Calibration}
+
+\subsection{Creative Senz3D}
+
+The depth and color images were collected using a Creative Senz3D sensor.
+This section describes characterizes the data from this sensor, particularly the depth data.
+The sensor contains both a $1280 \times 720$ color camera directed parallel to, and separated by roughly 25 mm from, a depth camera which has resolution of $320\times240$ pixels.
+The depth sensor uses a flash near IR illuminator and measures the time-of-flight of the beam at each pixel to obtain dense depth estimates along with an IR reflectance at each pixel.
+
+There are a number of limitations to the depth sensor including sources of depth error.
+The primary measurement limit on the range-to-target is the strength of the reflected beam.
+Hence dark, matt surfaces are measured reliably only at close range on the order of 20 or 30cm.
+Highly reflective surfaces also pose problems with direct reflections leading to saturation and highly unreliable depths.
+In addition reflective surfaces at grazing angles are less reliably measured as little signal is reflected.
+Hence in our data portions of the chamber floor visible in Fig.~\ref{fig:CameraConfiguration} are highly reflective and have incorrect depths.
+Fortunately the primary goal of the depth measurements are to obtain leaf depths, and plants provide good, roughly Lambertian reflections of IR CITE{}.
+Thus For these reasons the non-leaf depth pixels in the 3D data are unreliable and should be ignored.
+Another limitation is that the IR illuminator is slightly offset on the left of the sensor and this results in shadows to the right of some objects, as well as mixed pixels on depth discontinuities.
+Both of these can be readily detected as large standard deviations in the depth image.
+
+\subsubsection{Sensor Calibration}
+
+A checkerboard pattern was used to calibrate all three cameras to obtain both intrinsic and extrinsic parameters.
+While the checkerboard pattern is not visible as variations in depth, it is nevertheless observed as variations in the reflected IR image whose pixels correspond to the depth pixels.
+This enables the use of Zhang's method CITE{} to calculate the intrinsic parameters including a 2-parameter radial distortion of each camera, as well as a calculation of their relative poses.
+The optical center of the color camera is used to define the world coordinates of our data.
+The depth values of the depth camera are projected along their pixel rays and then rotated and translated by the pose of the depth camera, and thus recorded as 3D points in the world coordinate system.
+Hence it is straight forward to project these points onto any of the three camera images.
+
+\subsubsection{Depth Bias and Noise Characterization}
+\label{sec:bias}
+
+We characterized both the bias and the variance of the depth cameras as follows.
+A flat printed checkerboard with a surrounding white board was positioned at a large number of poses [How many?] in front of the sensor.
+The pose of the checkerboard is calculated in each case using the color and IR reflectance images.
+This defines a plane relative to the depth camera which we use to calculate the ground truth depths for each pixel in the depth camera.
+At each pose we collect multiple depth images; this provides both a bias and variance measurement for each pixel at multiple depths.
+
+Next we sought to model the depth bias as a linear function of depth.
+Two parameters were fit for each pixel (a linear coefficient and an offset).
+The results are summarized in Fig.~\ref{fig:Bias}.
+[Need more summary here.]
+
+\begin{figure}
+  %\includegraphics[]{Figures/}
+\caption{Noise and Bias model}
+\label{fig:Bias} 
+\end{figure}
+
+In the recorded 3D data we subtracted our estimated bias, and averaged five depth images for each record.
+Hence the actual depth variance for our data is $1/5$ of the the variances shown in Fig.~\ref{fig:Bias}, and the bias is zero.
+
+Now we noticed that the chamber light shades blocked some of the depth camera field of view, and in doing so reflected some of the IR illumination.
+This resulted in a bias shift of [how much?].
+We removed this bias shift from the depth data.
+
+\subsubsection{Data Description}
+
+The data consist of 5 images per hour taken within 10 minutes of each other.
+These include the fluorescent image, the IR reflectance image with the same camera, the color image, the 3D-depth and a confidence image.
+The 3D-depth image is built from the depth sensor by transforming the points into world coordinates and is expressed in mm.
+The confidence image is the standard deviation of the depths pixels.
+This is useful for identifying pixels at depth discontinuities which are unreliably detected and result in large standard deviations.
+In addition pixels with no response and saturated pixels are marked as high standard deviation.
+[Got to check this].
+
 \subsection{Image Accusation}

### 2015-04-13 datapaper_intro.tex
xm edits

\section{Introduction}
\label{sec:intro}

As the growing of population in the world and the reduction of arable land, there is an increasing desire to improve the yield and quality of various crops, where the undersanding of biology and mechanism of plant growth is a key enabler.
For this purpose, plant biologists create different mutations of the plant, grow them in either indoor chamber or outdoor field, visually observe them during the growth perid, and finally discover the patterns that associate the   key factors (e.g., genre, environments) with the outcome (e.g., visual phenotype, yield)~\cite{}.
While many factors in this research procedure can be assessed quantitatively, which is necessary in order to perform large-scale study, one of the bottleneck is the automatic visual phenotyping.

Plant phenotyping aims to analyze and categorize the visual appearance of plants~\cite{}.
This is typically conducted via manual visual observation.
With the increasing lower cost of imaging sensors and advances of Computer Vision technologies, image-based automatic plant phenotyping is growing into a desirable and viable solution~\cite{}.
In this interdisciplinary solution, computer vision scientists employ various imaging sensors to capture the plants and design advanced algorithms to automatically analyze the plant imagery, with the goal of answering the questions posed by plant biologists.

Plant image analysis is a non-trivial computer vision task, due to diverse variations of leaf appearance, overlapping and dynamics.
In order to develop advanced algorithms, image databases that are well representative of this application domain is highly important.
In fact, computer vision research lives on and advances with databases, as evidenced by the successful databases in the field (e.g., FERET~\cite{Phillips2000}, LFW~\cite{LFW}, Caltech$101$~\cite{Fei-Fei2004}).
However, the publicly available database on plant imagery is very limited, with the only exception of~\cite{scharr2014annotated} and~\cite{haug2014crop}.
Both databases have the limitations in that they only capture RGB images, and are suitable for a small set of tasks.

To facilite future research on plant image analysis, as well as remedy the limitation of existing databases in the field, this paper presents a newly collected multi-modality plant imagery database, termed ``MSU-PID''.
The MSU-PID includes the imagery of two types of plants (Arabidopsis and bean) captured by four types of sensors, Fluorescence, IR, RGB color, and depth.
All four sensors are synchonized to perform the data capturing periodically for multiple days. 
Checkerboard-based camera calibration is perform between the multiple sensors, which results in the explicit correspondence between the pixels of any two modalities.
For a subset of the database, we manually label the ground truth on the leaf identification number, leaf tip locations and leaf segments, using our labeling tool.
To provide a performance baseline for future comparison, we apply our automatic leaf segmentation approach~\cite{yin2014a,yin2014b} to the Arabidopsis imagery and demonstrate the challenge of image analysis on this database.

In summary, this paper and our database have made the following main contribution. 
\begin{itemize}
\item MSU-PID is the first {\it multi-modality} plant image database. 
This allows researchers to study the strength and weakness of individual modality, as well as their fusion in plant image analysis.
\item Our imaging setup and the variety of manu labele make MSU-PID a candidate dataset for a diverse set of plant image analysis tasks, including leaf segementation, leaf counting, leaf alignment, leaf tracking, leaf growth prediction, etc.
\end{itemize}

### 2015-04-13 datapaper.tex
Jeff's content

@@
 
-\title{Data Paper%\thanks{Grants or other notes
+\title{Multi-modality Imagery Database for Plant Phenotyping %\thanks{Grants or other notes
 %about the article that should go on the front page should be
@@
 subject classification numbers as needed.
-\keywords{First keyword \and Second keyword \and More}
+\keywords{Plant Phenotyping  \and Computer Vision \and Plant image \and Leaf segmentation \and Leaf tracking\and Multiple sensors \and Arabidopsis \and Bean}
 % \PACS{PACS code1 \and PACS code2 \and more}
@@
 
-\section{Introduction}\label{intro}
-Text with citations \cite{RefB} and \cite{RefJ}.
+\input{datapaper_intro.tex}
 
-\section{Background} \label{sec:1}
+\input{datapaper_prior.tex}
 
@@
 
+\subsection{Plants}
+
+\input{datapaper_plants.tex}
+
 \subsection{Hardware Setup}
+
+\input{datapaper_hardware.tex}
 
@@
 
-% Non-BibTeX users please use
-\begin{thebibliography}{}
-%
-% and use \bibitem to create references. Consult the Instructions
-% for authors for reference list style.
-%
-\bibitem{RefJ}
-% Format for Journal Reference
-Author, Article title, Journal, Volume, page numbers (year)
-% Format for books
-\bibitem{RefB}
-Author, Book title, page numbers. Publisher, place (year)
-% etc
-\end{thebibliography}
-
+{\small
+\bibliographystyle{springer}
+%\bibliography{/Sharefolder/Dropbox/Bibliographies/abbrev_brief,/Sharefolder/Dropbox/Bibliographies/xl-literature}
+\bibliography{abbrev_brief,xl-literature}
+}
 \end{document}

### 2015-04-13 datapaper_hardware.tex
Jeff's content

Chlorophyll a fluorescence images were captured once per hour during the daylight period in a DEPI chamber [CITE].  A set of 5 images (for averaging) were captured using a Hitachi KP-F145GV CCD (Hitachi Kokusai Electric America Inc., Woodbury, NY)  camera outfitted with an infrared long pass filter (Schott Glass RG-9, Thorlabs, Newton, NJ), during a short period ($<400 msec$) of intense light saturating to photosynthesis ($>10,000 \mu mol~photons~m^{-2} s^{-1}$) provided by an array of white Cree LEDs (XMLAWT, 5700K color temperature, Digi-Key, Thief River Falls, MN) collimated using a 20mm Carclo Lens (10003, LED Supply, Lakewood, CO).
%
Chlorophyll a fluorescence was excited using monochromatic red LEDs (Everlight 625nm, ELSH-F51R1-0LPNM-AR5R6, Digi-Key), collimated using a Ledil reflector optic ($C11347\_REGINA$, Mouser Electronics, Mansfield, TX) and pulsed for $50 \mu s$ during a brief window when the white LEDs were electronically shuttered.  A series of 5 images were also collected in the absence of excitation light for artifact subtraction.

Infrared images were collected once per hour with the same camera and filter used for chlorophyll fluorescence.  Pulses of $940 nm$ light were provided by an array of OSRAM LEDs (SFH 4239, Digi-Key), collimated using a Polymer Optics lens (Part no. 170, Polymer Optics Ltd., Berkshire, England).  Since $940 nm$ light does not influence plant development or drive photosynthesis, images were also collected during the night period.  Sets of 15 images were collected for averaging, in the absence of saturating illumination.   As with chlorophyll a fluorescence, images were captured in the absence of $940 nm$ light for artifact subtraction.

[cite]Cruz, J.A. et al. Dynamic Environmental Photosynthetic Imaging (DEPI) Reveals Emergent Phenotypes Related to the Environmental Repsonses of Photosynthesis. Nature Biotechnology Submitted (2015).

### 2015-04-13 datapaper_plants.tex
Jeff's content

{\it Arabidopsis thaliana} (ecotype Col-0) plants were grown at $20^{\circ}C$, under a 16 hr:8 hr day night cycle with daylight intensity set at $100 \mu mol~photons~m^{-2} s^{-1}$. 
%
Black bean plants ({\it Phaseolus vulgaris L.}), of the cultivar Jaguar, were grown under a 14 hr:10 hr day night cycle with daylight intensity set at $200 \mu mol~photons~m^{-2} s^{-1}$ and night and day temperatures of  $18^{\circ}C$ and $24^{\circ}C$.  
%
Bean plants were watered with half-strength Hoagland’s solution 3 times per week.  In all cases, seeds were planted in soil covered with a black foam mask to minimize fluorescence background from algal growth. 
%
Two-week-old plants ({\it Arabidopsis} or bean) were transferred to imaging chambers and allowed to acclimate for 24 hours to the LED lighting before the start of the experiments. Growth conditions as described above were maintained for each set of plants for the duration of image collection.

### 2015-04-14 datapaper_intro.tex
xm  edits

@@
 In fact, computer vision research lives on and advances with databases, as evidenced by the successful databases in the field (e.g., FERET~\cite{Phillips2000}, LFW~\cite{LFW}, Caltech$101$~\cite{Fei-Fei2004}).
-However, the publicly available database on plant imagery is very limited, with the only exception of~\cite{scharr2014annotated} and~\cite{haug2014crop}.
-Both databases have the limitations in that they only capture RGB images, and are suitable for a small set of tasks.
+However, the publicly available database for plant phenotyping is very limited, with the only exception of LSC database~\cite{scharr2014annotated}.
+The LSC database has the limitations in that it only captures RGB images, and are suitable for a small set of applications.
 
@@
 This allows researchers to study the strength and weakness of individual modality, as well as their fusion in plant image analysis.
-\item Our imaging setup and the variety of manu labele make MSU-PID a candidate dataset for a diverse set of plant image analysis tasks, including leaf segementation, leaf counting, leaf alignment, leaf tracking, leaf growth prediction, etc.
+\item Our imaging setup and the variety of manu labele make MSU-PID an ideal candidate for evaluating a diverse set of plant image analysis tasks, including leaf segementation, leaf counting, leaf alignment, leaf tracking, leaf growth prediction, etc.
 \end{itemize}

### 2015-04-14 datapaper_prior.tex
xm  edits

\section{Prior Work} 
\label{sec:prior}

Databases drive computer vision research.
Hence, it is always important to develop and promopt properly captured databases in the vision community.
While there is a clear desire to apply computer vision to plant imagery, the lack of databases is an obstacle for the further study and development.

 We summarize all existing publicly available databases that are related to plant imagery in Table~\ref{tab:database}.
In terms of potential applications of the databases, they can be categorized into two types.
The first type is for the general purpose of recognizing a particular species of tree or plant.
The Swedish leaf database~\cite{soderkvist2001computer} is probably the first leaf database even though the images are captured by scanners. 
The Flavia database~\cite{wu2007leaf} is consideraly larger and a neural network is used to train a leaf classifier.
The most recent leafsnap project is an impressive effort that includes a very large dataset of $184$ tree types~\cite{kumar2012leafsnap}.
A mobilephone app is also developed to make the leaf classification system portable.
Finally, the crop/weed image database~\cite{haug2014crop} is captured by a robot in the real field, and used for classifying crop vs.~weed.
Note that in this type of databases, normally only a single leaf is imaged and as a result, the challenging problem of leaf segmentation has been bypassed.

The second type of databases is for plant phenotyping where it is important to keep the plant live while imaged.
Thus, no destructive action is taken and an entire plant is imaged.
The LSC database~\cite{scharr2014annotated} is the most similar one to our database.
It captures a large set of RGB images for the Arabidopsis and Tobacco plants.
The provided manual labels allow the evaluation of leaf segmentation and leaf counting.
In comparison, our MSU-PID database utilizes four sensing modalities in the data capturing, each providing different aspects of plant appearance.
Our manual label also enable us to develop algorithm on additional applications such as leaf tracking and alignment.

\begin{table}[t!]
	\centering
	\caption{Plant image databases, where the abbreviation in ``Applications'' column is defined as Leaf Classification (LC), Leaf Segmentation (LS), Leaf Counting (LO), Leaf Alignment (LA), and Leaf Tracking (LT).}
	\resizebox{12cm}{!} {
	%\begin{tabular}{|l@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|}
	\begin{tabular}{l|c|c|c|c|c|c}
		\hline
		\multirow{2}{*}{Database}&  \multirow{2}{*}{Modality}  & Appli-& Plant & Subject/ &Total  &  Labeled   \\ 						
			&         & cations &            Type         &       Classe \#         &  Image \#    & Image \# \\ \hline

Swedish leaf &  Scaned leaf & LC& Swedish trees & $15$ & $1,125$ & $1,125$ \\ \hline
Flavia& RGB  & LC& Leaves & $32$  & $2,120$ & $2,120$ \\ \hline
Leafsnap  & RGB & LC& USA trees & $184$ & $29,107$  &  $29,107$ \\ \hline
Crop/weed &  RGB &Weed det. & Crop/Weed & $2$  & $60$ & $60$ \\ \hline
\multirow{2}{*}{LSC} & \multirow{2}{*}{RGB}  & \multirow{2}{*}{LS, LO} & Arabidopsis &  $43$ & $6287$ & $201$ \\ \cline{4-7}
							    &  & & Tobacco & $80$ & $165,120$ & $83$ \\ \hline
\multirow{2}{*}{MSU-PID}  & Fluorescence,  & LS, LO, & Arabidopsis &  $20$ & $XXX$ & $XXX$ \\ \cline{4-7}
							    & IR, RGB, Depth & LA, LT & Bean & $5$ & $XXX$ & $XXX$ \\ \hline
	       \hline
	\end{tabular}
	}
	\label{tab:database}
\end{table}

### 2015-04-14 datapaper.tex
xm  edits
author list

@@
 \usepackage{epstopdf}
+\usepackage{color}
+\usepackage{multirow}
+\usepackage{tabularx}
 %
@@
 
-\author{First Author         \and
-        Second Author %etc.
-}
+\author{Jeffrey A Cruz$^\star$ \and Xi Yin\footnote{Equal contributor}  \and Xiaoming Liu\footnote{Contact author.
+\email{liuxm@cse.msu.edu}} \and Saif M Imran \and Daniel D Morris \and David M Kramer    \and Jin Chen}
 
-%\authorrunning{Short form of author list} % if too long for running head
+\authorrunning{Cruz {\it et al}} % if too long for running head
 
-\institute{F. Author \at
-              first address \\
-              Tel.: +123-45-678910\\
-              Fax: +123-45-678910\\
-              \email{fauthor@example.com}           %  \\
+\institute{Jeffrey A Cruz, Jin Chen, David M Kramer \at
+              Department of Energy Plant Research Laboratory, Michigan State University\\
+              East Lansing, MI 48824, USA
 %             \emph{Present address:} of F. Author  %  if needed
            \and
-           S. Author \at
-              second address
+           Xi Yin, Xiaoming Liu \at
+              Department of Computer Science and Engineering, Michigan State University\\
+              East Lansing, MI 48824, USA           %  \\
+              \and
+           Saif Imran, Daniel Morris \at
+              Department of Electrical and Computer Engineering, Michigan State University\\
+              East Lansing, MI 48824, USA\\    
 }
@@
 
-\section{Image Labeling}
+%\section{Image Labeling}
+\input{labeling}
 
-\section{Baseline Performance}
+%\section{Baseline Performance}
+\input{baseline}
 
@@
 
-\paragraph{Paragraph headings} Use paragraph headings as needed.
-\begin{equation}
-a^2+b^2=c^2
-\end{equation}
-
-% For one-column wide figures use
-\begin{figure}
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-  \includegraphics{example.eps}
-% figure caption is below the figure
-\caption{Please write your figure caption here}
-\label{fig:1}       % Give a unique label
-\end{figure}
+%\paragraph{Paragraph headings} Use paragraph headings as needed.
+%\begin{equation}
+%a^2+b^2=c^2
+%\end{equation}
 %
-% For two-column wide figures use
-\begin{figure*}
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-  \includegraphics[width=0.75\textwidth]{example.eps}
-% figure caption is below the figure
-\caption{Please write your figure caption here}
-\label{fig:2}       % Give a unique label
-\end{figure*}
-%
-% For tables use
-\begin{table}
-% table caption is above the table
-\caption{Please write your table caption here}
-\label{tab:1}       % Give a unique label
-% For LaTeX tables use
-\begin{tabular}{lll}
-\hline\noalign{\smallskip}
-first & second & third  \\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-number & number & number \\
-number & number & number \\
-\noalign{\smallskip}\hline
-\end{tabular}
-\end{table}
+%% For one-column wide figures use
+%\begin{figure}
+%% Use the relevant command to insert your figure file.
+%% For example, with the graphicx package use
+%  \includegraphics{example.eps}
+%% figure caption is below the figure
+%\caption{Please write your figure caption here}
+%\label{fig:1}       % Give a unique label
+%\end{figure}
+%%
+%% For two-column wide figures use
+%\begin{figure*}
+%% Use the relevant command to insert your figure file.
+%% For example, with the graphicx package use
+%  \includegraphics[width=0.75\textwidth]{example.eps}
+%% figure caption is below the figure
+%\caption{Please write your figure caption here}
+%\label{fig:2}       % Give a unique label
+%\end{figure*}
+%%
+%% For tables use
+%\begin{table}
+%% table caption is above the table
+%\caption{Please write your table caption here}
+%\label{tab:1}       % Give a unique label
+%% For LaTeX tables use
+%\begin{tabular}{lll}
+%\hline\noalign{\smallskip}
+%first & second & third  \\
+%\noalign{\smallskip}\hline\noalign{\smallskip}
+%number & number & number \\
+%number & number & number \\
+%\noalign{\smallskip}\hline
+%\end{tabular}
+%\end{table}
 

### 2015-04-15 datapaper.tex
Added citations

@@
 Hence in our data portions of the chamber floor visible in Fig.~\ref{fig:CameraConfiguration} are highly reflective and have incorrect depths.
-Fortunately the primary goal of the depth measurements are to obtain leaf depths, and plants provide good, roughly Lambertian reflections of IR CITE{}.
+Fortunately the primary goal of the depth measurements are to obtain leaf depths, and plants provide good, roughly Lambertian reflections of IR~\cite{Chelle2006219}.
 Thus For these reasons the non-leaf depth pixels in the 3D data are unreliable and should be ignored.
@@
 While the checkerboard pattern is not visible as variations in depth, it is nevertheless observed as variations in the reflected IR image whose pixels correspond to the depth pixels.
-This enables the use of Zhang's method CITE{} to calculate the intrinsic parameters including a 2-parameter radial distortion of each camera, as well as a calculation of their relative poses.
+This enables the use of Zhang's method~\cite{Zhang2000} to calculate the intrinsic parameters including a 2-parameter radial distortion of each camera, as well as a calculation of their relative poses.
 The optical center of the color camera is used to define the world coordinates of our data.
@@
 %\bibliography{/Sharefolder/Dropbox/Bibliographies/abbrev_brief,/Sharefolder/Dropbox/Bibliographies/xl-literature}
-\bibliography{abbrev_brief,xl-literature}
+\bibliography{abbrev_brief,xl-literature,science}
 }

### 2015-04-16 datapaper.tex
xm's edit
figure
Update to depth camera noise models and figures

@@
 \begin{figure}
-  \includegraphics[width=9cm,trim=20 240 20 300,clip]{Figures/CameraConfiguration}
+  \includegraphics[width=11cm,trim=20 240 20 300,clip]{Figures/CameraConfiguration}
 \caption{A plot of the three cameras showing their relative configuration and fields of view as obtained through calibration.
 Units are in mm.
-In the center is the color camera, and its optical center defines the world coordinate system.
-On the right is the depth camera.
+The optical center of the color camera (on the left) defines the world coordinate system.
+Close to it is the depth camera.
 Its points are projected into the world coordinate system.
-On the left is the fluorescent and IR camera.}
+On the right is the combined fluorescent and IR camera.}
 \label{fig:CameraConfiguration}
@@
 
-\subsection{Image Accusation}
+\subsection{Image Acquisition}
 
@@
 We characterized both the bias and the variance of the depth cameras as follows.
-A flat printed checkerboard with a surrounding white board was positioned at a large number of poses [How many?] in front of the sensor.
+A flat printed checkerboard with a surrounding white board was positioned at a large number of poses in front of the sensor.
 The pose of the checkerboard is calculated in each case using the color and IR reflectance images.
@@
 Two parameters were fit for each pixel (a linear coefficient and an offset).
-The results are summarized in Fig.~\ref{fig:Bias}.
-[Need more summary here.]
+We found that the bias was close to constant as a function of depth, although it varied across the depth image as shown in Fig.~\ref{fig:Bias}.
+The standard deviation of the pixel depth varied as a function of depth and roughly with the distance of the pixel from the optical center.
+Estimates of the noise is shown in Fig.~\ref{fig:Bias}.
 
 \begin{figure}
-  %\includegraphics[]{Figures/}
-\caption{Noise and Bias model}
+\begin{tabular}{ c c }
+  \includegraphics[width=5.5cm,trim=160 260 170 260,clip]{Figures/BiasError} &
+  \includegraphics[width=7.5cm,trim=110 240 50 240,clip]{Figures/SigmaRadius} \\
+  (\emph{a}) & (\emph{b}) \\
+\end{tabular}
+\caption{Noise analysis for a depth camera.
+(\emph{a}) Bias was fit and we found it to be roughly constant as a function of depth.
+This constant offset is shown for the camera pixels with red positive and blue negative offset in mm.
+Inside the chamber, the obstructions around the depth camera altered the bias somewhat and we re-calibrated the bias there.
+In all cases we subtracted the modeled constant bias from the depth images.
+(\emph{b}) The standard deviation of the depth camera depends on depth as well as roughly on radius from the image optical center.
+A radius of 200 pixels corresponds to the corners of the depth camera which can be seen to have large noise.
+}
 \label{fig:Bias}
@@
 In the recorded 3D data we subtracted our estimated bias, and averaged five depth images for each record.
-Hence the actual depth variance for our data is $1/5$ of the the variances shown in Fig.~\ref{fig:Bias}, and the bias is zero.
+Hence the actual depth standard deviations for our data are $1/\sqrt{5}$ of the the standard deviations shown in Fig.~\ref{fig:Bias} and the bias is zero.
 
 Now we noticed that the chamber light shades blocked some of the depth camera field of view, and in doing so reflected some of the IR illumination.
-This resulted in a bias shift of [how much?].
-We removed this bias shift from the depth data.
+This resulted in an additional bias shift which we measured and removed from the depth data.
 
@@
 This is useful for identifying pixels at depth discontinuities which are unreliably detected and result in large standard deviations.
-In addition pixels with no response and saturated pixels are marked as high standard deviation.
-[Got to check this].
+In addition pixels with no response and saturated pixels are given the maximum standard deviation, and should be filtered out.
 
@@
 %\section{Image Labeling}
-\input{labeling}
+\input{datapapr_labeling}
 
 %\section{Baseline Performance}
-\input{baseline}
+\input{datapaper_baseline}
 
@@
 %\bibliography{/Sharefolder/Dropbox/Bibliographies/abbrev_brief,/Sharefolder/Dropbox/Bibliographies/xl-literature}
-\bibliography{abbrev_brief,xl-literature,science}
+\bibliography{abbrev,xl-literature,science}
 }

### 2015-04-17 datapaper_baseline.tex
Xi_baseline

\section{Baseline Performance}
\subsection{Our Framework}
We apply our automatic leaf segmentation, alignment, and tracking framework~\cite{yin2014a,yin2014b} to the Arabidopsis imagery to provide a baseline for future research.
Leaf segmentation aims at finding the correct number of leaves and the corresponding boundary of each leaf in each image.
Leaf alignment is to align the two tips of each leaf.
Leaf tracking is designed to track each leaf over time.

\begin{figure}[h]
\centering
\includegraphics[width=.98\textwidth]{Figures/overview}\\
\caption{Overview of the baseline method.}
\label{fig:methodOverview}
\end{figure}

As shown in Fig~\ref{fig:methodOverview}, the input of this framework is a plant video and a set of predefined templates with various shapes, scales, and orientations.
We also generate the two tips for each template for finding the corresponding tip points of each leaf via Chamfer Matching~\
First, we apply multi-leaf alignment~\cite{yin2014a} approach to find an optimal set of leaf candidates on the last frame of the video, which will provide the information of the number of leaves, tip locations and boundaries of each leaf.
Second, we apply multi-leaf tracking~\cite{yin2014b} approach, which is based on leaf template transformation, to track leaves between continuous two frames.
In the tracking process, we develop a procedure to generate new leaves and delete small leaves. 
For each frame of the video, we can generate a label image with each leaf being labeled with one color and the tip locations for each piece of leaf. 
The label for each leaf in the video maintain the same during tracking process.

\subsection{Performance Evaluation}
To evaluate the performance of leaf segmentation, alignment, and tracking, we use four criteria and provide the Matlab implementations.
Three of them are based on tip-based error, which is defined as average distance of a pair of estimated leaf tips $\hat{\bm{t}}_{1,2}$ with a pair of labeled leaf tips $ \bm{t}_{1,2}$ normalized by the labeled leaf length:

\begin {equation}
e_{la}(\hat{\bm{t}}_{1,2}, \bm{t}_{1,2}) = \frac{||\hat{\bm{t}}_1-{\bm{t}}_1||_2 + ||\hat{\bm{t}}_2-{\bm{t}}_2||_2}{2 ||\bm{t}_1-\bm{t}_2||_2}.
\label{eqn:tipError}
\end{equation}

We build the frame-to-frame and video-to-video correspondence respectively and generate two sets of tip-based errors.
More details can be find in~\cite{};
We define a threshold $\tau$ to operate on the corresponding tip-based errors. 
By varying $\tau$, we compute the first three criteria as:
\begin{itemize}
  \item {\it{Unmatched Leaf Rate(ULR)}}, the percentage of unmatched leaves w.r.t. the total number of labeled leaves. This can attribute to two sources. First, miss detections and false alarms. Second, matched leaves with tip-based errors larger than $\tau$.
  \item {\it{Landmark Error(LE)}}, the average tip-based errors smaller than $\tau$ of all frame-to-frame correspondent leaves.
  \item {\it{Tracking Consistency(TC)}}, the average tip-based errors smaller than $\tau$ of all video-to-video correspondent leaves. 
\end{itemize}

In order to evaluate the leaf segmentation accuracy, we adopt an additional metric~\cite{scharr2014annotated} based on the Dice score of estimated segmentation result and ground truth label:
\begin{itemize}
  \item {\it{Symmetric Best Dice(SBD)}}, the symmetric best Dice among all labeled leaves.
\end{itemize}

The results of our algorithm by varying $\tau$ from 0 to 1 is shown in Fig.XXX.
And the SBD score is XXX by averaging over all plants.

### 2015-04-17 datapapr_labeling.tex
Xi_baseline

--- 2015-04-13 labeling.tex
@@
 Part of the dataset is manually annotated to provide ground truth tip locations, leaf segmentation results and leaf consistency overtime.
-Tip locations are saved in TXT file \textcolor{red}{(TBD)}.
-Leaf segmentation results are stored in PNG images with one color for each leaf.
+Tip locations are saved in a TXT file for each frame. 
+Leaf segmentation results are stored in a PNG image for each frame with one color for each leaf.
 The same color is used to represent the same leaf over a sequence of frames.
 
-We use RGB images for labeling because of better visualization. 
+%We use RGB images for labeling because of better visualization.
 All plants are cropped out from the background and saved as JPG files.
@@
 \centering
-\includegraphics[width=.98\textwidth]{figure/labeling}\\
+\includegraphics[width=.98\textwidth]{Figures/labeling}\\
 \caption{Leaf labeling process, including tip labels and leaf annotation.}
@@
 A line connecting each pair of tips will be shown immediately for visualization.
-Inaccurate labels can be deleted and relabeled.
+Inaccurate labels can be deleted by clicking the right button of the mouse and relabeled by clicking the left button again.
 
-For leaf annotation, we use the idea of merging and splitting super pixels. 
-There are six different numbers of super pixels: $100$, $200$, $300$, $500$, $800$, $1000$. 
-The user can specify which level to use depending on how well the super pixels can separate the leaves from the background. 
-Because one leaf can be covered by several super pixels and one super pixel can across two leaves or the foreground and background. 
-We allow merging and splitting super pixels. 
-Merging is implemented by drawing a rectangle on the image. 
-Every super pixel overlapping with this rectangle will be merged together. 
-Splitting is implemented by drawing a line separating a leaf from the background or from another leaf.
-
-As shown in Fig.~\ref{fig:label}, several super pixels that covers one leaf are first merged together to form a large super pixel. 
-Since the top part of the super pixel covers some of the background and the bottom part covers another small leaf, two lines are drawn on this super pixel to split it. 
+Leaf label is implemented by clicking the boundary of one leaf at each time. 
 The leaf boundary is overlaid on the image for better visualization to guide the next action.
 This process continues until all leaves have been annotated.
+
+%For leaf annotation, we use the idea of merging and splitting super pixels.
+%There are six different numbers of super pixels: $100$, $200$, $300$, $500$, $800$, $1000$.
+%The user can specify which level to use depending on how well the super pixels can separate the leaves from the background.
+%Because one leaf can be covered by several super pixels and one super pixel can across two leaves or the foreground and background.
+%We allow merging and splitting super pixels.
+%Merging is implemented by drawing a rectangle on the image.
+%Every super pixel overlapping with this rectangle will be merged together.
+%Splitting is implemented by drawing a line separating a leaf from the background or from another leaf.
+%
+%As shown in Fig.~\ref{fig:label}, several super pixels that covers one leaf are first merged together to form a large super pixel.
+%Since the top part of the super pixel covers some of the background and the bottom part covers another small leaf, two lines are drawn on this super pixel to split it.
+%The leaf boundary is overlaid on the image for better visualization to guide the next action.
+%This process continues until all leaves have been annotated.

### 2015-04-23 datapapr_labeling.tex
Xi_edit_labeling

@@
 
-%We use RGB images for labeling because of better visualization.
-All plants are cropped out from the background and saved as JPG files.
+We use Fluorescence images for labeling because of clear background. 
+%All plants are cropped out from the background and saved as JPG files.
 For Arabidopsis images, we label four frames each day.
@@
 The results will be automatically saved once a user goes to label the next image.
-This GUI is used to annotate leaves in each frame.
-For consistent annotation of the same leaf over time, we use the labeled results of each frame to find the correspondence according to leaf centers.
-Incorrect correspondence will be manually corrected.
+For consistent annotation of the same leaf over time, we show a number on the center of each leaf indicating the order of labeling from the previous frame. 
+%This GUI is used to annotate leaves in each frame.
+%For consistent annotation of the same leaf over time, we use the labeled results of each frame to find the correspondence according to leaf centers.
+%Incorrect correspondence will be manually corrected.
 
@@
 A line connecting each pair of tips will be shown immediately for visualization.
-Inaccurate labels can be deleted by clicking the right button of the mouse and relabeled by clicking the left button again.
+Inaccurate labels can be deleted by clicking the right button of the mouse near the labeled point and relabeled by clicking the left button again.
 
@@
 The leaf boundary is overlaid on the image for better visualization to guide the next action.
+Incorrect label can be deleted right after the labeling. 
 This process continues until all leaves have been annotated.
+After the labeling of one plant, we visually go through the results and correct inaccurate labels. 
+One example of leaf label result for one plant is shown in Fig.~\ref{fig:LabelExample}, where one color is used to represent one leaf.  
+As we can see, there is leaf showing up and cover up the leaf underneath, which will not be annotated later (transition between day $4$ and day $5$).
+
+%\begin{figure}[h]
+%\centering
+%\includegraphics[width=.98\textwidth]{Figures/labelExamples}\\
+%\caption{Leaf label results for one Arabidopsis plant over nine days with one image per day. }
+%\label{fig:LabelExample}
+%\end{figure}
+
+\begin{figure}[h]
+\begin{centering}
+\begin{tabular}{@{}c@{} c@{} c@{} c@{} c@{} c@{} c@{} c@{} c@{}}
+%\begin{tabular}{lllllllll}
+\includegraphics[width=.11\textwidth]{Figures/labelExample/plant_1_day_1_num_13.png}&
+\includegraphics[width=.11\textwidth]{Figures/labelExample/plant_1_day_2_num_13.png}&
+\includegraphics[width=.11\textwidth]{Figures/labelExample/plant_1_day_3_num_13.png}&
+\includegraphics[width=.11\textwidth]{Figures/labelExample/plant_1_day_4_num_13.png}&
+\includegraphics[width=.11\textwidth]{Figures/labelExample/plant_1_day_5_num_13.png}&
+\includegraphics[width=.11\textwidth]{Figures/labelExample/plant_1_day_6_num_13.png}&
+\includegraphics[width=.11\textwidth]{Figures/labelExample/plant_1_day_7_num_13.png}&
+\includegraphics[width=.11\textwidth]{Figures/labelExample/plant_1_day_8_num_13.png}&
+\includegraphics[width=.11\textwidth]{Figures/labelExample/plant_1_day_9_num_13.png}\\
+  day 1 & day 2 & day 3 & day 4 & day 5 & day 6 & day 7 & day 8 & day 9 \\
+\end{tabular}
+\caption{Leaf label results for one Arabidopsis plant over nine days with one image per day. }
+\label{fig:LabelExample}
+\end{centering}
+\end{figure}
 

### 2015-04-24 datapaper.tex
Xi_baseline
update section 1-3 by jc

@@
 %
+\usepackage{bm}
 \usepackage{graphicx}
@@
 
-\subsection{Image Acquisition}
+%\subsection{Image Acquisition}
 
-\subsection{Image Calibration}
-
-\subsection{Creative Senz3D}
-
-The depth and color images were collected using a Creative Senz3D sensor.
-This section describes characterizes the data from this sensor, particularly the depth data.
-The sensor contains both a $1280 \times 720$ color camera directed parallel to, and separated by roughly 25 mm from, a depth camera which has resolution of $320\times240$ pixels.
-The depth sensor uses a flash near IR illuminator and measures the time-of-flight of the beam at each pixel to obtain dense depth estimates along with an IR reflectance at each pixel.
-
-There are a number of limitations to the depth sensor including sources of depth error.
-The primary measurement limit on the range-to-target is the strength of the reflected beam.
-Hence dark, matt surfaces are measured reliably only at close range on the order of 20 or 30cm.
-Highly reflective surfaces also pose problems with direct reflections leading to saturation and highly unreliable depths.
-In addition reflective surfaces at grazing angles are less reliably measured as little signal is reflected.
-Hence in our data portions of the chamber floor visible in Fig.~\ref{fig:CameraConfiguration} are highly reflective and have incorrect depths.
-Fortunately the primary goal of the depth measurements are to obtain leaf depths, and plants provide good, roughly Lambertian reflections of IR~\cite{Chelle2006219}.
-Thus For these reasons the non-leaf depth pixels in the 3D data are unreliable and should be ignored.
-Another limitation is that the IR illuminator is slightly offset on the left of the sensor and this results in shadows to the right of some objects, as well as mixed pixels on depth discontinuities.
-Both of these can be readily detected as large standard deviations in the depth image.
-
-\subsubsection{Sensor Calibration}
+\subsection{Sensor Calibration}
 
@@
 
-\subsubsection{Data Description}
+%\subsubsection{Data Description}
 
-The data consist of 5 images per hour taken within 10 minutes of each other.
-These include the fluorescent image, the IR reflectance image with the same camera, the color image, the 3D-depth and a confidence image.
-The 3D-depth image is built from the depth sensor by transforming the points into world coordinates and is expressed in mm.
-The confidence image is the standard deviation of the depths pixels.
-This is useful for identifying pixels at depth discontinuities which are unreliably detected and result in large standard deviations.
-In addition pixels with no response and saturated pixels are given the maximum standard deviation, and should be filtered out.
+%\subsection{Image Accusation}
 
-\subsection{Image Accusation}
-
-\subsection{Image Calibration}
+%\subsection{Image Calibration}
 

### 2015-04-24 datapaper_hardware.tex
update section 1-3 by jc

@@
-Chlorophyll a fluorescence images were captured once per hour during the daylight period in a DEPI chamber [CITE].
-A set of 5 images (for averaging) were captured using a Hitachi KP-F145GV CCD (Hitachi Kokusai Electric America Inc., Woodbury, NY)  camera outfitted with an infrared long pass filter (Schott Glass RG-9, Thorlabs, Newton, NJ), during a short period ($<400 msec$) of intense light saturating to photosynthesis ($>10,000 \mu mol~photons~m^{-2} s^{-1}$) provided by an array of white Cree LEDs (XMLAWT, 5700K color temperature, Digi-Key, Thief River Falls, MN) collimated using a 20mm Carclo Lens (10003, LED Supply, Lakewood, CO).
+In this section, we introduce the hardware used for capturing Fluorescence, IR, RGB color, and depth imagery data.
+
+\subsubsection{Fluorescence and IR images}
+Chlorophyll a fluorescence images were captured once per hour during the daylight period in a growth chamber~\cite{cruz2015depi}.
+A set of 5 images were captured using a Hitachi KP-F145GV CCD camera (Hitachi Kokusai Electric America Inc., Woodbury, NY) outfitted with an infrared long pass filter (Schott Glass RG-9, Thorlabs, Newton, NJ), during a short period ($<400 msec$) of intense light saturating to photosynthesis ($>10,000 \mu mol~photons~m^{-2} s^{-1}$) provided by an array of white Cree LEDs (XMLAWT, 5700K color temperature, Digi-Key, Thief River Falls, MN) collimated using a 20mm Carclo Lens (10003, LED Supply, Lakewood, CO).
 %
@@
 
-[cite]Cruz, J.A. et al. Dynamic Environmental Photosynthetic Imaging (DEPI) Reveals Emergent Phenotypes Related to the Environmental Repsonses of Photosynthesis. Nature Biotechnology Submitted (2015).
+\subsubsection{RGB color and depth images} %This section describes characterizes the data from this sensor, particularly the depth data.
+
+The depth and RGB color images were collected using a Creative Senz3D sensor~\cite{nguyen2015vietnamese}.
+The sensor contains both a $1280 \times 720$ color camera directed parallel to, and separated by roughly 25 mm from, a depth camera which has resolution of $320\times240$ pixels.
+The depth sensor uses a flash near IR illuminator and measures the time-of-flight of the beam at each pixel to obtain dense depth estimates along with an IR reflectance at each pixel.
+
+There are a number of limitations to the depth sensor including sources of depth error.
+The primary measurement limit on the range-to-target is the strength of the reflected beam.
+Hence dark, matt surfaces are measured reliably only at close range on the order of $20$ or $30cm$.
+Highly reflective surfaces also pose problems with direct reflections leading to saturation and highly unreliable depths.
+In addition reflective surfaces at grazing angles are less reliably measured as little signal is reflected.
+Hence in our data portions of the chamber floor visible in Fig.~\ref{fig:CameraConfiguration} are highly reflective and have incorrect depths.
+Fortunately the primary goal of the depth measurements are to obtain leaf depths, and plants provide good, roughly Lambertian reflections of IR~\cite{Chelle2006219}.
+Thus For these reasons the non-leaf depth pixels in the 3D data are unreliable and should be ignored.
+Another limitation is that the IR illuminator is slightly offset on the left of the sensor and this results in shadows to the right of some objects, as well as mixed pixels on depth discontinuities.
+Both of these can be readily detected as large standard deviations in the depth image.
+
+The imagery data were collected once per hour. %taken within 10 minutes of each other.  %
+These include the fluorescent image, the IR reflectance image with the same camera, the color image, the 3D-depth and a confidence image.
+The 3D-depth image is built from the depth sensor by transforming the points into world coordinates and is expressed in mm.
+The confidence image is the standard deviation of the depths pixels.
+This is useful for identifying pixels at depth discontinuities which are unreliably detected and result in large standard deviations.
+In addition pixels with no response and saturated pixels are given the maximum standard deviation, and should be filtered out.

### 2015-04-24 datapaper_intro.tex
update section 1-3 by jc

--- 2015-04-13 datapaper_intro.tex
@@
 
-As the growing of population in the world and the reduction of arable land, there is an increasing desire to improve the yield and quality of various crops, where the undersanding of biology and mechanism of plant growth is a key enabler.
-For this purpose, plant biologists create different mutations of the plant, grow them in either indoor chamber or outdoor field, visually observe them during the growth perid, and finally discover the patterns that associate the   key factors (e.g., genre, environments) with the outcome (e.g., visual phenotype, yield)~\cite{}.
-While many factors in this research procedure can be assessed quantitatively, which is necessary in order to perform large-scale study, one of the bottleneck is the automatic visual phenotyping.
+With the rapid growth of world population  and the loss of arable land, there is an increasing desire to improve the yield and quality of crops, where the understanding of the genetic mechanisms to control plant growth is a key enabler~\cite{doos2002population}.
+%
+For this purpose, plant scientists make various genetic mutant strains of plants, grow them either in  growth chambers with simulated environmental conditions or directly in the field, visually observe the plants during the growth period, and finally discover plant morphological or physiological patterns that tightly associate with key growth factors~\cite{houle2010phenomics}.
+%
+While many factors can be assessed quantitatively, which is essential for high-throughput study, one of the bottleneck in this research line is plant visual phenotyping~\cite{walter2015plant}.
 
-Plant phenotyping aims to analyze and categorize the visual appearance of plants~\cite{}.
-This is typically conducted via manual visual observation.
-With the increasing lower cost of imaging sensors and advances of Computer Vision technologies, image-based automatic plant phenotyping is growing into a desirable and viable solution~\cite{}.
-In this interdisciplinary solution, computer vision scientists employ various imaging sensors to capture the plants and design advanced algorithms to automatically analyze the plant imagery, with the goal of answering the questions posed by plant biologists.
+Plant visual phenotyping aims to analyze and categorize the visual appearance of plants~\cite{}.
+In old days, this was conducted via manual visual observation~\cite{Erblichkeit1903}.
+Today, with the increasing lower cost of imaging sensors and advances of computer vision technologies, image-based automatic plant visual phenotyping is growing into a desirable and viable solution~\cite{cruz2015depi}.
+In this interdisciplinary field, scientists employ various imaging sensors to capture plants and design advanced algorithms to automatically analyze the captured plant imagery, with the goal of raising testable biological hypotheses to solve the aforementioned problems.
 
-Plant image analysis is a non-trivial computer vision task, due to diverse variations of leaf appearance, overlapping and dynamics.
+Due to diverse variations of leaf appearance, layout, growth and movement, plant image analysis is a non-trivial computer vision task~\cite{}.
 In order to develop advanced algorithms, image databases that are well representative of this application domain is highly important.
 In fact, computer vision research lives on and advances with databases, as evidenced by the successful databases in the field (e.g., FERET~\cite{Phillips2000}, LFW~\cite{LFW}, Caltech$101$~\cite{Fei-Fei2004}).
-However, the publicly available database on plant imagery is very limited, with the only exception of~\cite{scharr2014annotated} and~\cite{haug2014crop}.
-Both databases have the limitations in that they only capture RGB images, and are suitable for a small set of tasks.
+However, the publicly available database for plant phenotyping is still limited, with the only exception of LSC database \cite{scharr2014annotated}, which, nevertheless, has its own limitations on the type of images (RGB only), and is only suitable for a small set of applications.
 
-To facilite future research on plant image analysis, as well as remedy the limitation of existing databases in the field, this paper presents a newly collected multi-modality plant imagery database, termed ``MSU-PID''.
-The MSU-PID includes the imagery of two types of plants (Arabidopsis and bean) captured by four types of sensors, Fluorescence, IR, RGB color, and depth.
-All four sensors are synchonized to perform the data capturing periodically for multiple days. 
+To facilitate future research on plant image analysis, as well as remedy the limitation of existing databases in the field, this paper presents a newly collected multi-modality plant imagery database, termed ``MSU-PID''.
+The MSU-PID includes the imagery of two types of plants (Arabidopsis and bean), both are widely used in plant research, captured by four types of sensors, i.e.
+Fluorescence, IR, RGB color, and depth.
+%
+All four sensors are synchronized and are programmed to periodically capture data for multiple days.
 Checkerboard-based camera calibration is perform between the multiple sensors, which results in the explicit correspondence between the pixels of any two modalities.
-For a subset of the database, we manually label the ground truth on the leaf identification number, leaf tip locations and leaf segments, using our labeling tool.
+For a subset of the database, we manually label the ground truth on the leaf identification number, leaf tip locations and leaf segments.
 To provide a performance baseline for future comparison, we apply our automatic leaf segmentation approach~\cite{yin2014a,yin2014b} to the Arabidopsis imagery and demonstrate the challenge of image analysis on this database.
 
-In summary, this paper and our database have made the following main contribution. 
+In summary, this paper and our database have made the following main contributions.
 \begin{itemize}
@@
 This allows researchers to study the strength and weakness of individual modality, as well as their fusion in plant image analysis.
-\item Our imaging setup and the variety of manu labele make MSU-PID a candidate dataset for a diverse set of plant image analysis tasks, including leaf segementation, leaf counting, leaf alignment, leaf tracking, leaf growth prediction, etc.
+\item Our imaging setup and the variety of manual label make MSU-PID an ideal candidate for evaluating a diverse set of plant image analysis tasks, including leaf segmentation, leaf counting, leaf alignment, leaf tracking, leaf growth prediction.
 \end{itemize}

### 2015-04-24 datapaper_prior.tex
update section 1-3 by jc

@@
 Databases drive computer vision research.
-Hence, it is always important to develop and promopt properly captured databases in the vision community.
+Hence, it is always important to develop and promote properly captured databases in the vision community.
 While there is a clear desire to apply computer vision to plant imagery, the lack of databases is an obstacle for the further study and development.
@@
 The Swedish leaf database~\cite{soderkvist2001computer} is probably the first leaf database even though the images are captured by scanners.
-The Flavia database~\cite{wu2007leaf} is consideraly larger and a neural network is used to train a leaf classifier.
+The Flavia database~\cite{wu2007leaf} is considerably larger and a neural network is used to train a leaf classifier.
 The most recent leafsnap project is an impressive effort that includes a very large dataset of $184$ tree types~\cite{kumar2012leafsnap}.
-A mobilephone app is also developed to make the leaf classification system portable.
-Finally, the crop/weed image database~\cite{haug2014crop} is captured by a robot in the real field, and used for classifying crop vs.~weed.
+A mobile phone application is also developed to make the leaf classification system portable.
+Finally, the crop/weed image database~\cite{haug2014crop} is captured by a robot in the field, and used for classifying crop vs.~weed.
 Note that in this type of databases, normally only a single leaf is imaged and as a result, the challenging problem of leaf segmentation has been bypassed.
 
-The second type of databases is for plant phenotyping where it is important to keep the plant live while imaged.
-Thus, no destructive action is taken and an entire plant is imaged.
+The second type of databases is for plant phenotyping, where it is important to capture plant images without interfering the growth of plants.
+Thus, non-destructive approaches are taken and the entire plant is imaged.
 The LSC database~\cite{scharr2014annotated} is the most similar one to our database.

### 2015-04-26 datapaper_baseline.tex
Xi edit

@@
-\section{Baseline Performance}
-\subsection{Our Framework}
-We apply our automatic leaf segmentation, alignment, and tracking framework~\cite{yin2014a,yin2014b} to the Arabidopsis imagery to provide a baseline for future research.
+\section{Baseline Method and Performance Evaluation}
+\label{sec:baseline}
+\subsection{Our framework}
+We apply our automatic multi-leaf alignment, segmentation, and tracking framework~\cite{yin2014a,yin2014b} to the testing set of Arabidopsis fluorescence imagery to provide a baseline for future comparison.
 Leaf segmentation aims at finding the correct number of leaves and the corresponding boundary of each leaf in each image.
@@
 As shown in Fig~\ref{fig:methodOverview}, the input of this framework is a plant video and a set of predefined templates with various shapes, scales, and orientations.
-We also generate the two tips for each template for finding the corresponding tip points of each leaf via Chamfer Matching~\
-First, we apply multi-leaf alignment~\cite{yin2014a} approach to find an optimal set of leaf candidates on the last frame of the video, which will provide the information of the number of leaves, tip locations and boundaries of each leaf.
-Second, we apply multi-leaf tracking~\cite{yin2014b} approach, which is based on leaf template transformation, to track leaves between continuous two frames.
+To generate the template set, we first select $10$ templates with different aspect ratios from the labeled images in the training set together with the corresponding tip locations.
+For each template, we scale it to $12$ different sizes in order to cover all size ranges in the database.
+For each scale template, we rotated every $15^{\circ}$ to generate $24$ different directions.
+Tip locations will be scaled and rotated accordingly.
+Finally, we generate $2,880$ leaf templates.
+
+%We also generate the two tips for each template for finding the corresponding tip points of each leaf via Chamfer Matching~\cite{barrow1977parametric}.
+Our work is motivated by Chamfer Matching technique~\cite{barrow1977parametric}, which is used to align two edge maps.
+We extend it to align multiple objects at the same time.
+For each image, we use simple thresholding and edge detection to generate an edge map and mask.
+First, we find the best location of each template in the edge map that has minimal chamfer matching distance, which will result in an over-complete set of leaf candidates.
+Second, we apply multi-leaf alignment~\cite{yin2014a} approach to find an optimal set of leaf candidates on the last frame of the video, which will provide the information of the number of leaves, tip locations and boundaries of each leaf.
+Third, we apply multi-leaf tracking~\cite{yin2014b} approach, which is based on leaf template transformation, to track leaves between continuous two frames.
+
 In the tracking process, we develop a procedure to generate new leaves and delete small leaves.
@@
 
-\subsection{Performance Evaluation}
+\subsection{Evaluation metrics}
 To evaluate the performance of leaf segmentation, alignment, and tracking, we use four criteria and provide the Matlab implementations.
@@
   \item {\it{Landmark Error(LE)}}, the average tip-based errors smaller than $\tau$ of all frame-to-frame correspondent leaves.
-  \item {\it{Tracking Consistency(TC)}}, the average tip-based errors smaller than $\tau$ of all video-to-video correspondent leaves. 
+  \item {\it{Tracking Consistency(TC)}}, the percentage of video-to-video correspondent leaves whos tip-based errors are smaller than $\tau$.
 \end{itemize}
@@
 
-The results of our algorithm by varying $\tau$ from 0 to 1 is shown in Fig.XXX.
-And the SBD score is XXX by averaging over all plants.
+The Matlab function for computing {\it{SBD}} is provided by~\cite{scharr2014annotated}.
+The instruction on how to use the evaluation functions are included within the functions.
+
+\subsection{Performance and analysis}
+The results of our algorithm by varying $\tau$ from 0 to 1 is shown in Fig.~.
+And the {\it{SBD}} score is $0.51$ by averaging over all plants.
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=.98\textwidth]{Figures/performance}\\
+\caption{Performance of the baseline method.}
+\label{fig:performance}
+\end{figure}

### 2015-04-26 datapapr_labeling.tex
Xi edit

@@
-\section{Image Labeling}
+\section{Database and Annotation}
+\subsection{Statistics and protocols}
+MSU-PID includes two plant databases: Arabidopsis and Bean.
+The statistic information of these two databases are summarised in Tab.~\ref{tab:stat}.
+The images were acquired every hour.
+As there is no light at night, plants can not be captured in fluorescence and RGB color images while IR and depth cameras can still capture plants.
+Therefore, in order to make it consistent, we release images captured only in day time, which are $16$ images per day for Arabidopsis and $14$ for bean for all four sensors.
 
-Part of the dataset is manually annotated to provide ground truth tip locations, leaf segmentation results and leaf consistency overtime.
+\begin{table}[h]
+\begin{center}
+\caption{Summary of Arabidopsis and Bean databases.}
+\label{tab:stat}
+\begin{tabular}{c|c|c|c|c|c}
+      \hline
+      % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
+      Database     & Subjects & Days & Images/Day & Total Images & Annotated Images \\
+      \hline
+      Arabidopsis &  16      &  9   &     16     &     2304     &       576    \\
+      %\hline
+      Bean        &   5      &  5   &     14     &     350      &       175 \\
+      \hline
+\end{tabular}
+\end{center}
+\end{table}
+
+The two databases differs in plant resolutions.
+As shown in Fig~\ref{fig:rawIm},  we grow a single bean plant while a whole tray of Arabidopsis are grown at the same time.
+Therefore, the resolution of each Arabidopsis plant is much lower than that of a bean plant.
+We manually crop $16$ Arabidopsis plants, which have been captured by all four sensors.
+Table~\ref{tab:resolution} summaries the resolution of each plant in all four channels.
+
+\begin{figure}[h]
+\begin{centering}
+\begin{tabular}{c c}
+%\begin{tabular}{@{}c@{} c@{}}
+%\begin{tabular}{lllllllll}
+\includegraphics[width=.45\textwidth]{Figures/rawImages/a.png}&
+\includegraphics[width=.45\textwidth]{Figures/rawImages/b.png}\\
+  Arabidopsis & Bean \\
+\end{tabular}
+\caption{Color images of Arabidopsis and bean plants. }
+\label{fig:rawIm}
+\end{centering}
+\end{figure}
+
+\begin{table}[h]
+\begin{center}
+\caption{Plant resolution of Arabidopsis and Bean databases.}
+\label{tab:resolution}
+\begin{tabular}{c|c|c|c|c}
+      \hline
+      % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
+      Database     & Fluorescence       & IR        & RGB      & Depth     \\
+      \hline
+      Arabidopsis &  ~240$\times$240 &  ~240$\times$240 & ~120$\times$120  & NA  \\
+      %\hline
+      Bean        & 1360$\times$1024 & 1360$\times$1024 & 1280$\times$720 & 320$\times$240    \\
+      \hline
+\end{tabular}
+\end{center}
+\end{table}
+
+As shown in Tab.~\ref{tab:database}, MSU-PID can be used for leaf segmentation, leaf alignment, leaf tracking, and leaf counting.
+To facilitate future research, we separate the database into training set and testing set.
+$40\%$ of the data is used for training and $60\%$ for testing.
+Specifically, $6$ plants of Arabidopisis and $2$ plants of bean are selected for training.
+We will provide training and testing data in different folders.
+For fair comparison, both supervised learning and unsupervised learning methods should evaluate the performance on the training and testing sets separately.
+The evaluation metrics will be discussed in Sec.~\ref{sec:baseline}.
+
+\subsection{Manual annotations}
+Part of the database is manually annotated to provide ground truth tip locations, leaf segmentation results and leaf consistency overtime.
 Tip locations are saved in a TXT file for each frame.
@@
 We use Fluorescence images for labeling because of clear background.
-%All plants are cropped out from the background and saved as JPG files.
-For Arabidopsis images, we label four frames each day.
-While for bean images, we label seven frames each day because of faster leaf movement.
-We develop a Matlab GUI interface for leaf labeling, as shown in Fig~\ref{fig:label}.
+For Arabidopsis images, we label $4$ frames each day.
+While for bean images, we label $7$ frames each day because of faster leaf movement.
+A Matlab GUI interface is developed for leaf labeling, as shown in Fig~\ref{fig:label}.
 A user can open an image to label the two tips and annotate each leaf.
@@
 Leaf label is implemented by clicking the boundary of one leaf at each time.
-The leaf boundary is overlaid on the image for better visualization to guide the next action.
+The labeled leaf boundary is overlaid on the image for better visualization to guide the next action.
 Incorrect label can be deleted right after the labeling.
@@
 
+\subsection{File types and name conventions}
+We release training and testing sets in two separate folders.
+In each folder, there are two subfolders named Arabidopsis and Bean.
+The files in each subfolder have the following form:
+\begin{itemize}
+  \item plant$\_$XX$\_$day$\_$X$\_$num$\_$XX$\_$rgb.png: the original RGB color images;
+  \item plant$\_$XX$\_$day$\_$X$\_$num$\_$XX$\_$fmp.png: the original fluorescence images;
+  \item plant$\_$XX$\_$day$\_$X$\_$num$\_$XX$\_$ir.png: the original IR images;
+  \item plant$\_$XX$\_$day$\_$X$\_$num$\_$XX$\_$depth.png: the original depth images;
+  \item plant$\_$XX$\_$day$\_$X$\_$num$\_$XX$\_$label.png: the labeled images;
+  \item plant$\_$XX$\_$day$\_$X$\_$num$\_$XX$\_$tips.txt: the labeled tip locations;
+\end{itemize}
+where $XX$ is an integer number indicating the specific plant information.
+For each image in the database, we provide four channels images in PNG files ($\_$rgb, $\_$fmp, $\_$ir, $\_$depth).
+For annotated images, we have two additional files ($\_$label, $\_$tips) saving the annotation results.
+Leaf segmentation results are encoded as indexed PNG files, where each leaf is assigned a unique and consistent ID over time.
+Leaf ID starts from $1$ and continuously increase.
+And the background is encoded as $0$.
+Tips locations are saved in TXT files where each line has the following format:
+\begin{itemize}
+  \item leaf ID \quad tip1$\_$x \quad tip1$\_$y \quad tip2$\_$x \quad  tip2$\_$y
+\end{itemize}
+where leaf ID is an integer number that is consistent with the segmentation label in the PNG file.
+tip1$\_$x and tip1$\_$y are floating numbers represent the coordinates of the outer tip point.
+tip2$\_$x and tip2$\_$y are floating numbers represent the coordinates of the inner tip point.
+
+In addition to the original images and annotation results, we provide another folder named Matlab with all Matlab functions that will be used for mapping between different image channels and for performance evaluation purpose.
+Note that the annotation is provided based on Fluorescence images.
+In order to evaluate methods developed on other channels, we provide image mapping functions between every two channels.
+
 %For leaf annotation, we use the idea of merging and splitting super pixels.

### 2015-04-28 datapaper.tex
Xi edit
xi_doublecolumn
xm's first edits

@@
 %\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-\documentclass[smallextended]{svjour3}       % onecolumn (second format)
-%\documentclass[twocolumn]{svjour3}          % twocolumn
+%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
+\documentclass[twocolumn]{svjour3}          % twocolumn
 %
@@
 \usepackage{tabularx}
+\usepackage[misc,geometry]{ifsym}
+
+%\usepackage{paralist}
 %
@@
 %
-\begin{document}
+\begin{document}\sloppy
 
-\title{Multi-modality Imagery Database for Plant Phenotyping %\thanks{Grants or other notes
-%about the article that should go on the front page should be
-%placed here. General acknowledgments should be placed at the end of the article.}
+\title{Multi-modality Imagery Database for Plant Phenotyping \thanks{$^\star$ denotes equal contribution by the authors.
+This research was supported by Chemical Sciences, Geosciences and Biosciences Division, Office of Basic Energy Sciences, Office of Science, U.S.
+Department of Energy (award number DE-FG02-91ER20021), and by Center for Advanced Algal and Plant Phenotyping (CAAPP), Michigan State University.
+}
 }
@@
 
-\author{Jeffrey A Cruz$^\star$ \and Xi Yin\footnote{Equal contributor}  \and Xiaoming Liu\footnote{Contact author.
-\email{liuxm@cse.msu.edu}} \and Saif M Imran \and Daniel D Morris \and David M Kramer    \and Jin Chen}
+\author{Jeffrey A Cruz$^\star$ \and Xi Yin\footnote{Equal contributor}  \and Xiaoming Liu \and Saif M Imran \and Daniel~D~Morris \and David M Kramer    \and Jin Chen}
 
@@
 
-\institute{Jeffrey A Cruz, Jin Chen, David M Kramer \at
-              Department of Energy Plant Research Laboratory, Michigan State University\\
-              East Lansing, MI 48824, USA
+\institute{Jeffrey A Cruz $\cdot$ Jin Chen$\cdot$ David M Kramer \at
+              Department of Energy Plant Research Laboratory, Michigan State University, East Lansing, MI 48824, USA  \\
+		E-mail: \{cruzj,jinchen,kramerd8\}@msu.edu		
 %             \emph{Present address:} of F. Author  %  if needed
            \and
-           Xi Yin, Xiaoming Liu \at
-              Department of Computer Science and Engineering, Michigan State University\\
-              East Lansing, MI 48824, USA           %  \\
+           Xi Yin$\cdot$ Xiaoming Liu (\Letter)\at
+              Department of Computer Science and Engineering, Michigan State University,  East Lansing, MI 48824, USA  \\
+		E-mail: \{yinxi1,liuxm\}@cse.msu.edu
+                      %  \\
               \and
-           Saif Imran, Daniel Morris \at
-              Department of Electrical and Computer Engineering, Michigan State University\\
+           Saif Imran$\cdot$Daniel D Morris \at
+              Department of Electrical and Computer Engineering, Michigan State University,
               East Lansing, MI 48824, USA\\  
+		E-mail: \{imransai,dmorris\}@msu.edu
 }
@@
 subject classification numbers as needed.
+Insert your abstract here. Include keywords, PACS and mathematical
+subject classification numbers as needed.
+Insert your abstract here. Include keywords, PACS and mathematical
+subject classification numbers as needed.
+Insert your abstract here. Include keywords, PACS and mathematical
+subject classification numbers as needed.
+Insert your abstract here. Include keywords, PACS and mathematical
+subject classification numbers as needed.
+Insert your abstract here. Include keywords, PACS and mathematical
+subject classification numbers as needed.
+Insert your abstract here. Include keywords, PACS and mathematical
+subject classification numbers as needed.
+Insert your abstract here. Include keywords, PACS and mathematical
+subject classification numbers as needed.
+Insert your abstract here. Include keywords, PACS and mathematical
+subject classification numbers as needed.
+
 \keywords{Plant Phenotyping  \and Computer Vision \and Plant image \and Leaf segmentation \and Leaf tracking\and Multiple sensors \and Arabidopsis \and Bean}
@@
 
-\section{Data Collection}\label{sec:2}
-
-\subsection{Plants}
-
 \input{datapaper_plants.tex}
-
-\subsection{Hardware Setup}
 
@@
 
-% For one-column wide figures use
-\begin{figure}
-  \includegraphics[width=11cm,trim=20 240 20 300,clip]{Figures/CameraConfiguration}
-\caption{A plot of the three cameras showing their relative configuration and fields of view as obtained through calibration.
-Units are in mm.
-The optical center of the color camera (on the left) defines the world coordinate system.
-Close to it is the depth camera.
-Its points are projected into the world coordinate system.
-On the right is the combined fluorescent and IR camera.}
-\label{fig:CameraConfiguration}
-\end{figure}
+\input{datapaper_calibration.tex}
 
-%\subsection{Image Acquisition}
+\input{datapapr_labeling.tex}
 
-\subsection{Sensor Calibration}
+\input{datapaper_baseline.tex}
 
-A checkerboard pattern was used to calibrate all three cameras to obtain both intrinsic and extrinsic parameters.
-While the checkerboard pattern is not visible as variations in depth, it is nevertheless observed as variations in the reflected IR image whose pixels correspond to the depth pixels.
-This enables the use of Zhang's method~\cite{Zhang2000} to calculate the intrinsic parameters including a 2-parameter radial distortion of each camera, as well as a calculation of their relative poses.
-The optical center of the color camera is used to define the world coordinates of our data.
-The depth values of the depth camera are projected along their pixel rays and then rotated and translated by the pose of the depth camera, and thus recorded as 3D points in the world coordinate system.
-Hence it is straight forward to project these points onto any of the three camera images.
-
-\subsubsection{Depth Bias and Noise Characterization}
-\label{sec:bias}
-
-We characterized both the bias and the variance of the depth cameras as follows.
-A flat printed checkerboard with a surrounding white board was positioned at a large number of poses in front of the sensor.
-The pose of the checkerboard is calculated in each case using the color and IR reflectance images.
-This defines a plane relative to the depth camera which we use to calculate the ground truth depths for each pixel in the depth camera.
-At each pose we collect multiple depth images; this provides both a bias and variance measurement for each pixel at multiple depths.
-
-Next we sought to model the depth bias as a linear function of depth.
-Two parameters were fit for each pixel (a linear coefficient and an offset).
-We found that the bias was close to constant as a function of depth, although it varied across the depth image as shown in Fig.~\ref{fig:Bias}.
-The standard deviation of the pixel depth varied as a function of depth and roughly with the distance of the pixel from the optical center.
-Estimates of the noise is shown in Fig.~\ref{fig:Bias}.
-
-\begin{figure}
-\begin{tabular}{ c c }
-  \includegraphics[width=5.5cm,trim=160 260 170 260,clip]{Figures/BiasError} &
-  \includegraphics[width=7.5cm,trim=110 240 50 240,clip]{Figures/SigmaRadius} \\
-  (\emph{a}) & (\emph{b}) \\
-\end{tabular}
-\caption{Noise analysis for a depth camera.
-(\emph{a}) Bias was fit and we found it to be roughly constant as a function of depth.
-This constant offset is shown for the camera pixels with red positive and blue negative offset in mm.
-Inside the chamber, the obstructions around the depth camera altered the bias somewhat and we re-calibrated the bias there.
-In all cases we subtracted the modeled constant bias from the depth images.
-(\emph{b}) The standard deviation of the depth camera depends on depth as well as roughly on radius from the image optical center.
-A radius of 200 pixels corresponds to the corners of the depth camera which can be seen to have large noise.
-}
-\label{fig:Bias}
-\end{figure}
-
-In the recorded 3D data we subtracted our estimated bias, and averaged five depth images for each record.
-Hence the actual depth standard deviations for our data are $1/\sqrt{5}$ of the the standard deviations shown in Fig.~\ref{fig:Bias} and the bias is zero.
-
-Now we noticed that the chamber light shades blocked some of the depth camera field of view, and in doing so reflected some of the IR illumination.
-This resulted in an additional bias shift which we measured and removed from the depth data.
-
-%\subsubsection{Data Description}
-
-%\subsection{Image Accusation}
-
-%\subsection{Image Calibration}
-
-%\section{Image Labeling}
-\input{datapapr_labeling}
-
-%\section{Baseline Performance}
-\input{datapaper_baseline}
-
-\section{Conclusion}
+\input{datapaper_conclusion.tex}
 
@@
 
-{\small
+{%\small
 \bibliographystyle{springer}

### 2015-04-28 datapaper_calibration.tex
xm's first edits

% For one-column wide figures use
\begin{figure}
  \includegraphics[width=8.5cm,trim=20 240 20 300,clip]{Figures/CameraConfiguration}
\caption{A plot of the three cameras showing their relative configuration and fields of view as obtained through calibration.  Units are in mm.  The optical center of the color camera (on the left) defines the world coordinate system.  Close to it is the depth camera.  Its points are projected into the world coordinate system.  On the right is the combined fluorescent and IR camera.}
\label{fig:CameraConfiguration}
\end{figure}

%\subsection{Image Acquisition}

\subsection{Sensor Calibration}

A checkerboard pattern was used to calibrate all three cameras to obtain both intrinsic and extrinsic parameters.  While the checkerboard pattern is not visible as variations in depth, it is nevertheless observed as variations in the reflected IR image whose pixels correspond to the depth pixels.  This enables the use of Zhang's method~\cite{Zhang2000} to calculate the intrinsic parameters including a 2-parameter radial distortion of each camera, as well as a calculation of their relative poses.  The optical center of the color camera is used to define the world coordinates of our data.  The depth values of the depth camera are projected along their pixel rays and then rotated and translated by the pose of the depth camera, and thus recorded as 3D points in the world coordinate system.  Hence it is straight forward to project these points onto any of the three camera images.

\subsubsection{Depth Bias and Noise Characterization}
\label{sec:bias}

We characterized both the bias and the variance of the depth cameras as follows.  A flat printed checkerboard with a surrounding white board was positioned at a large number of poses in front of the sensor.  The pose of the checkerboard is calculated in each case using the color and IR reflectance images.  This defines a plane relative to the depth camera which we use to calculate the ground truth depths for each pixel in the depth camera.  At each pose we collect multiple depth images; this provides both a bias and variance measurement for each pixel at multiple depths.

Next we sought to model the depth bias as a linear function of depth.  Two parameters were fit for each pixel (a linear coefficient and an offset).  We found that the bias was close to constant as a function of depth, although it varied across the depth image as shown in Fig.~\ref{fig:Bias}.  The standard deviation of the pixel depth varied as a function of depth and roughly with the distance of the pixel from the optical center.  Estimates of the noise is shown in Fig.~\ref{fig:Bias}.

\begin{figure*}
\centering
\begin{tabular}{ c c }
  \includegraphics[width=5.5cm,trim=160 260 170 260,clip]{Figures/BiasError} &
  \includegraphics[width=7.5cm,trim=110 240 50 240,clip]{Figures/SigmaRadius} \\
  (\emph{a}) & (\emph{b}) \\
\end{tabular}
\caption{Noise analysis for a depth camera.  (\emph{a}) Bias was fit and we found it to be roughly constant as a function of depth.  This constant offset is shown for the camera pixels with red positive and blue negative offset in mm.  Inside the chamber, the obstructions around the depth camera altered the bias somewhat and we re-calibrated the bias there.  In all cases we subtracted the modeled constant bias from the depth images.  (\emph{b}) The standard deviation of the depth camera depends on depth as well as roughly on radius from the image optical center.  A radius of 200 pixels corresponds to the corners of the depth camera which can be seen to have large noise. }
\label{fig:Bias}
\end{figure*}

In the recorded 3D data we subtracted our estimated bias, and averaged five depth images for each record.  Hence the actual depth standard deviations for our data are $1/\sqrt{5}$ of the the standard deviations shown in Fig.~\ref{fig:Bias} and the bias is zero.

Now we noticed that the chamber light shades blocked some of the depth camera field of view, and in doing so reflected some of the IR illumination.  This resulted in an additional bias shift which we measured and removed from the depth data.

### 2015-04-28 datapaper_intro.tex
xm's first edits

@@
 %
-While many factors can be assessed quantitatively, which is essential for high-throughput study, one of the bottleneck in this research line is plant visual phenotyping~\cite{walter2015plant}.
+While many factors can be assessed quantitatively, which is essential for high-throughput study, one of the bottleneck in this research pipeline is plant visual phenotyping~\cite{walter2015plant}.
 

### 2015-04-28 datapaper_intro.tex
xm's first edits

@@
 
-Plant visual phenotyping aims to analyze and categorize the visual appearance of plants~\cite{}.
-In old days, this was conducted via manual visual observation~\cite{Erblichkeit1903}.
-Today, with the increasing lower cost of imaging sensors and advances of computer vision technologies, image-based automatic plant visual phenotyping is growing into a desirable and viable solution~\cite{cruz2015depi}.
-In this interdisciplinary field, scientists employ various imaging sensors to capture plants and design advanced algorithms to automatically analyze the captured plant imagery, with the goal of raising testable biological hypotheses to solve the aforementioned problems.
+The objective of {\it plant visual phenotyping} is to analyze and categorize the visual appearance of plants. %~\cite{}. 
+In old days, plant phenotyping was conducted through manual visual observation~\cite{Erblichkeit1903}. 
+Today, motivated by the increasing lower cost of imaging sensors and advances of computer vision technologies, image-based automatic plant visual phenotyping is quickly growing into a desirable and viable solution~\cite{cruz2015depi}.
+In this interdisciplinary field, scientists employ various imaging sensors to capture plants and design advanced algorithms to automatically analyze the captured plant imagery, with the purpose of raising testable biological hypotheses to solve the aforementioned problems.
 
-Due to diverse variations of leaf appearance, layout, growth and movement, plant image analysis is a non-trivial computer vision task~\cite{}.
-In order to develop advanced algorithms, image databases that are well representative of this application domain is highly important.
-In fact, computer vision research lives on and advances with databases, as evidenced by the successful databases in the field (e.g., FERET~\cite{Phillips2000}, LFW~\cite{LFW}, Caltech$101$~\cite{Fei-Fei2004}).
-However, the publicly available database for plant phenotyping is still limited, with the only exception of LSC database \cite{scharr2014annotated}, which, nevertheless, has its own limitations on the type of images (RGB only), and is only suitable for a small set of applications.
+\begin{table*}[t!]
+	\centering
+	\caption{Plant image databases, where the abbreviation in ``Applications'' column is defined as Leaf Classification (LC), Leaf Segmentation (LS), Leaf Counting (LO), Leaf Alignment (LA), and Leaf Tracking (LT).}
+	%\resizebox{12cm}{!} {
+	%\begin{tabular}{|l@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|}
+	\begin{tabular}{l|c|c|c|c|c|c}
+		\hline
+		\multirow{2}{*}{Database}&  \multirow{2}{*}{Modality}  & Appli-& Plant & Subject/ &Total  &  Labeled   \\ 						
+			&         & cations &            Type         &       Classe \#         &  Image \#    & Image \# \\ \hline
 
-To facilitate future research on plant image analysis, as well as remedy the limitation of existing databases in the field, this paper presents a newly collected multi-modality plant imagery database, termed ``MSU-PID''.
-The MSU-PID includes the imagery of two types of plants (Arabidopsis and bean), both are widely used in plant research, captured by four types of sensors, i.e.
-Fluorescence, IR, RGB color, and depth.
-%
-All four sensors are synchronized and are programmed to periodically capture data for multiple days.
-Checkerboard-based camera calibration is perform between the multiple sensors, which results in the explicit correspondence between the pixels of any two modalities.
-For a subset of the database, we manually label the ground truth on the leaf identification number, leaf tip locations and leaf segments.
-To provide a performance baseline for future comparison, we apply our automatic leaf segmentation approach~\cite{yin2014a,yin2014b} to the Arabidopsis imagery and demonstrate the challenge of image analysis on this database.
+Swedish leaf &  Scaned leaf & LC& Swedish trees & $15$ & $1,125$ & $1,125$ \\ \hline
+Flavia& RGB  & LC& Leaves & $32$  & $2,120$ & $2,120$ \\ \hline
+Leafsnap  & RGB & LC& USA trees & $184$ & $29,107$  &  $29,107$ \\ \hline
+Crop/weed &  RGB &Weed det. & Crop/weed & $2$  & $60$ & $60$ \\ \hline
+\multirow{2}{*}{LSC} & \multirow{2}{*}{RGB}  & \multirow{2}{*}{LS, LO} & Arabidopsis &  $43$ & $6287$ & $201$ \\ \cline{4-7}
+							    &  & & Tobacco & $80$ & $165,120$ & $83$ \\ \hline
+\multirow{2}{*}{MSU-PID}  & Fluorescence,  & LS, LO, & Arabidopsis &  $20$ & $XXX$ & $XXX$ \\ \cline{4-7}
+							    & IR, RGB, Depth & LA, LT & Bean & $5$ & $XXX$ & $XXX$ \\ \hline
+	       \hline
+	\end{tabular}
+	%}
+	\label{tab:database}
+\end{table*}
+
+Due to diverse variations of leaf shape, appearance, layout, growth and movement, plant image analysis is a non-trivial computer vision task~\cite{Minervini2015}. 
+In order to develop advanced computer vision algorithms, image databases that are well representative of this application domain is highly important. 
+In fact, computer vision research lives on and advances with databases, as evidenced by the successful databases in the field (e.g., FERET~\cite{Phillips2000} and LFW~\cite{LFW}). 
+However, the publicly available database for plant phenotyping is still very limited, with the only exception of LSC database~\cite{scharr2014annotated}, which, nevertheless, has its own limitations on the type of images (RGB only) and is only suitable for a small set of plant image analysis applications.
+
+To facilitate future research on plant image analysis, as well as remedy the limitation of existing databases in the field, this paper presents a newly collected multi-modality plant imagery database at Michigan State University (MSU), termed ``MSU-PID''.
+The MSU-PID includes the imagery of two types of plants (Arabidopsis and bean), both are widely used in plant research, captured by four types of sensors, i.e., Fluorescence, infrared (IR), RGB color, and depth.
+All four sensors are synchronized and are programmed to periodically capture data for multiple consecutive days.
+Checkerboard-based camera calibration is performed between a pair of sensors, which results in the explicit correspondence between the pixels of {\it any} two modalities.
+For a subset of the database, we manually label the ground truth regarding the leaf identification number, locations of leaf tips and leaf segments. 
+To provide a performance baseline for future research and comparison, we apply our automatic leaf segmentation framework~\cite{yin2014a,yin2014b} to the Arabidopsis imagery and demonstrate the unique challenge of image analysis on this database.
 
@@
 \item MSU-PID is the first {\it multi-modality} plant image database.
-This allows researchers to study the strength and weakness of individual modality, as well as their fusion in plant image analysis.
-\item Our imaging setup and the variety of manual label make MSU-PID an ideal candidate for evaluating a diverse set of plant image analysis tasks, including leaf segmentation, leaf counting, leaf alignment, leaf tracking, leaf growth prediction.
+This allows researchers to study the strength and weakness of individual modality, as well as their various combinations in plant image analysis.
+\item Our imaging setup and the variety of manual labels make MSU-PID an ideal candidate for evaluating a diverse set of plant image analysis applications, including leaf segmentation, leaf counting, leaf alignment, leaf tracking, and leaf growth prediction.
 \end{itemize}

### 2015-04-28 datapaper_prior.tex
xi_doublecolumn
xm's first edits

@@
 Hence, it is always important to develop and promote properly captured databases in the vision community. 
-While there is a clear desire to apply computer vision to plant imagery, the lack of databases is an obstacle for the further study and development.
+While there is a clear desire to apply computer vision to plant image analysis, the lack of publicly available plant image databases has been an obstacle for the further study and development.
 
 We summarize all existing publicly available databases that are related to plant imagery in Table~\ref{tab:database}.
-In terms of potential applications of the databases, they can be categorized into two types.
+In terms of potential applications of these databases, they can be categorized into two types.
 The first type is for the general purpose of recognizing a particular species of tree or plant. 
 The Swedish leaf database~\cite{soderkvist2001computer} is probably the first leaf database even though the images are captured by scanners. 
-The Flavia database~\cite{wu2007leaf} is considerably larger and a neural network is used to train a leaf classifier.
-The most recent leafsnap project is an impressive effort that includes a very large dataset of $184$ tree types~\cite{kumar2012leafsnap}.
+The Flavia database~\cite{wu2007leaf} is considerably larger and a neural network is utilized to train a leaf classifier. 
+The most recent leafsnap project is an impressive effort that includes a very large dataset of leaves for $184$ tree types~\cite{kumar2012leafsnap}. 
 A mobile phone application is also developed to make the leaf classification system portable.
-Finally, the crop/weed image database~\cite{haug2014crop} is captured by a robot in the field, and used for classifying crop vs.~weed.
-Note that in this type of databases, normally only a single leaf is imaged and as a result, the challenging problem of leaf segmentation has been bypassed.
+Finally, the crop/weed image database~\cite{haug2014crop} is captured by a robot in the real field, and used for the classification of crop vs.~weed.
+Note that in this type of databases, normally only a {\it single} leaf is imaged in a relatively constrained imaging environment and as a result, the challenging problem of leaf segmentation has been bypassed.
 
 The second type of databases is for plant phenotyping, where it is important to capture plant images without interfering the growth of plants. 
-Thus, non-destructive approaches are taken and the entire plant is imaged.
-The LSC database~\cite{scharr2014annotated} is the most similar one to our database.
+Thus, non-destructive imaging approaches are taken and the entire plant is imaged.
+The LSC database~\cite{scharr2014annotated} is the most relevant one to our database.
 It captures a large set of RGB images for the Arabidopsis and Tobacco plants.
 The provided manual labels allow the evaluation of leaf segmentation and leaf counting.
-In comparison, our MSU-PID database utilizes four sensing modalities in the data capturing, each providing different aspects of plant appearance.
-Our manual label also enable us to develop algorithm on additional applications such as leaf tracking and alignment.
-
-\begin{table}[t!]
-	\centering
-	\caption{Plant image databases, where the abbreviation in ``Applications'' column is defined as Leaf Classification (LC), Leaf Segmentation (LS), Leaf Counting (LO), Leaf Alignment (LA), and Leaf Tracking (LT).}
-	\resizebox{12cm}{!} {
-	%\begin{tabular}{|l@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|}
-	\begin{tabular}{l|c|c|c|c|c|c}
-		\hline
-		\multirow{2}{*}{Database}&  \multirow{2}{*}{Modality}  & Appli-& Plant & Subject/ &Total  &  Labeled   \\ 						
-			&         & cations &            Type         &       Classe \#         &  Image \#    & Image \# \\ \hline
-
-Swedish leaf &  Scaned leaf & LC& Swedish trees & $15$ & $1,125$ & $1,125$ \\ \hline
-Flavia& RGB  & LC& Leaves & $32$  & $2,120$ & $2,120$ \\ \hline
-Leafsnap  & RGB & LC& USA trees & $184$ & $29,107$  &  $29,107$ \\ \hline
-Crop/weed &  RGB &Weed det. & Crop/Weed & $2$  & $60$ & $60$ \\ \hline
-\multirow{2}{*}{LSC} & \multirow{2}{*}{RGB}  & \multirow{2}{*}{LS, LO} & Arabidopsis &  $43$ & $6287$ & $201$ \\ \cline{4-7}
-							    &  & & Tobacco & $80$ & $165,120$ & $83$ \\ \hline
-\multirow{2}{*}{MSU-PID}  & Fluorescence,  & LS, LO, & Arabidopsis &  $20$ & $XXX$ & $XXX$ \\ \cline{4-7}
-							    & IR, RGB, Depth & LA, LT & Bean & $5$ & $XXX$ & $XXX$ \\ \hline
-	       \hline
-	\end{tabular}
-	}
-	\label{tab:database}
-\end{table}
+In comparison, our MSU-PID database utilizes four sensing modalities in the data capturing, each providing different aspects of plant visual appearance.
+Our diverse manual labels also enable us to develop algorithms for additional applications such as leaf tracking and leaf alignment.

### 2015-04-28 datapaper_calibration.tex
xm's first edits

@@
 \begin{figure}
-  \includegraphics[width=8.5cm,trim=20 240 20 300,clip]{Figures/CameraConfiguration}
+  \includegraphics[width=\linewidth,trim=50 230 45 300,clip]{Figures/CameraConfiguration}
 \caption{A plot of the three cameras showing their relative configuration and fields of view as obtained through calibration.
-Units are in mm.
+Units are in $mm$.
 The optical center of the color camera (on the left) defines the world coordinate system.
@@
 While the checkerboard pattern is not visible as variations in depth, it is nevertheless observed as variations in the reflected IR image whose pixels correspond to the depth pixels.
-This enables the use of Zhang's method~\cite{Zhang2000} to calculate the intrinsic parameters including a 2-parameter radial distortion of each camera, as well as a calculation of their relative poses.
+This enables the use of Zhang's method~\cite{Zhang2000} to calculate the intrinsic parameters including a $2$-parameter radial distortion of each camera, as well as a calculation of their relative poses.
 The optical center of the color camera is used to define the world coordinates of our data.
-The depth values of the depth camera are projected along their pixel rays and then rotated and translated by the pose of the depth camera, and thus recorded as 3D points in the world coordinate system.
-Hence it is straight forward to project these points onto any of the three camera images.
+The depth values of the depth camera are projected along their pixel rays and then rotated and translated by the pose of the depth camera, and thus recorded as $3$D points in the world coordinate system.
+Therefore it is straight forward to project these points onto any of the three camera images.
 
@@
 The pose of the checkerboard is calculated in each case using the color and IR reflectance images.  
-This defines a plane relative to the depth camera which we use to calculate the ground truth depths for each pixel in the depth camera.
-At each pose we collect multiple depth images; this provides both a bias and variance measurement for each pixel at multiple depths.
+This defines a plane relative to the depth camera, which we use to calculate the ground truth depths for each pixel in the depth camera.  
+At each pose, we collect multiple depth images; this provides both a bias and variance measurement for each pixel at multiple depths.
 
@@
 Two parameters were fit for each pixel (a linear coefficient and an offset).  
-We found that the bias was close to constant as a function of depth, although it varied across the depth image as shown in Fig.~\ref{fig:Bias}.
+We found that the bias was close to a constant as a function of depth, although it varied across the depth image as shown in Figure~\ref{fig:Bias}.  
 The standard deviation of the pixel depth varied as a function of depth and roughly with the distance of the pixel from the optical center.  
-Estimates of the noise is shown in Fig.~\ref{fig:Bias}.
+Estimates of the noise are shown in Figure~\ref{fig:Bias}.
 
@@
 \begin{tabular}{ c c }
-  \includegraphics[width=5.5cm,trim=160 260 170 260,clip]{Figures/BiasError} &
-  \includegraphics[width=7.5cm,trim=110 240 50 240,clip]{Figures/SigmaRadius} \\
+  \includegraphics[height=5.2cm,trim=160 300 170 310,clip]{Figures/BiasError} &
+  \includegraphics[height=5.2cm,trim=110 240 50 260,clip]{Figures/SigmaRadius} \\
   (\emph{a}) & (\emph{b}) \\
@@
 (\emph{b}) The standard deviation of the depth camera depends on depth as well as roughly on radius from the image optical center.
-A radius of 200 pixels corresponds to the corners of the depth camera which can be seen to have large noise.
+A radius of $200$ pixels corresponds to the corners of the depth camera, which can be seen to have large noise.
 }
@@
 
-In the recorded 3D data we subtracted our estimated bias, and averaged five depth images for each record.
-Hence the actual depth standard deviations for our data are $1/\sqrt{5}$ of the the standard deviations shown in Fig.~\ref{fig:Bias} and the bias is zero.
+In the recorded $3$D data we subtracted our estimated bias, and averaged five depth images for each record.
+Hence the actual depth standard deviations for our data are $1/\sqrt{5}$ of the the standard deviations shown in Figure~\ref{fig:Bias} (b) and the bias is zero.
 
@@
 This resulted in an additional bias shift which we measured and removed from the depth data.
+% FIXME

### 2015-04-28 datapaper_hardware.tex
xm's first edits

--- 2015-04-13 datapaper_hardware.tex
@@
-Chlorophyll a fluorescence images were captured once per hour during the daylight period in a DEPI chamber [CITE].
-A set of 5 images (for averaging) were captured using a Hitachi KP-F145GV CCD (Hitachi Kokusai Electric America Inc., Woodbury, NY)  camera outfitted with an infrared long pass filter (Schott Glass RG-9, Thorlabs, Newton, NJ), during a short period ($<400 msec$) of intense light saturating to photosynthesis ($>10,000 \mu mol~photons~m^{-2} s^{-1}$) provided by an array of white Cree LEDs (XMLAWT, 5700K color temperature, Digi-Key, Thief River Falls, MN) collimated using a 20mm Carclo Lens (10003, LED Supply, Lakewood, CO).
+\subsection{Hardware Setup}
+
+In this section, we introduce the hardware used for capturing Fluorescence, IR, RGB color, and depth imagery data for both plants.
+
+\subsubsection{Fluorescence and IR images}
+Chlorophyll a fluorescence images were captured once every hour during the daylight period in a growth chamber~\cite{cruz2015depi}. 
+A set of $5$ images were captured using a Hitachi KP-F145GV CCD camera (Hitachi Kokusai Electric America Inc., Woodbury, NY) outfitted with an infrared long pass filter (Schott Glass RG-9, Thorlabs, Newton, NJ), during a short period ($<400~ms$) of intense light saturating to photosynthesis ($>10,000~\mu mol~photons~m^{-2} s^{-1}$) provided by an array of white Cree LEDs (XMLAWT, 5700K color temperature, Digi-Key, Thief River Falls, MN) collimated using a $20~mm$ Carclo Lens (10003, LED Supply, Lakewood, CO).
 %
-Chlorophyll a fluorescence was excited using monochromatic red LEDs (Everlight 625nm, ELSH-F51R1-0LPNM-AR5R6, Digi-Key), collimated using a Ledil reflector optic ($C11347\_REGINA$, Mouser Electronics, Mansfield, TX) and pulsed for $50 \mu s$ during a brief window when the white LEDs were electronically shuttered.
-A series of 5 images were also collected in the absence of excitation light for artifact subtraction.
+Chlorophyll a fluorescence was excited using monochromatic red LEDs (Everlight $625~nm$, ELSH-F51R1-0LPNM-AR5R6, Digi-Key), collimated using a Ledil reflector optic ($C11347\_REGINA$, Mouser Electronics, Mansfield, TX) and pulsed for $50~\mu s$ during a brief window when the white LEDs were electronically shuttered.
+In addition, a series of $5$ images were also collected in the absence of the excitation light for artifact subtraction.
 
-Infrared images were collected once per hour with the same camera and filter used for chlorophyll fluorescence.
-Pulses of $940 nm$ light were provided by an array of OSRAM LEDs (SFH 4239, Digi-Key), collimated using a Polymer Optics lens (Part no.
-170, Polymer Optics Ltd., Berkshire, England).
-Since $940 nm$ light does not influence plant development or drive photosynthesis, images were also collected during the night period.
-Sets of 15 images were collected for averaging, in the absence of saturating illumination.
-As with chlorophyll a fluorescence, images were captured in the absence of $940 nm$ light for artifact subtraction.
+Infrared images were collected once every hour with the same camera and filter used for chlorophyll a fluorescence.  
+Pulses of $940~nm$ light were provided by an array of OSRAM LEDs (SFH 4239, Digi-Key), collimated using a Polymer Optics lens (Part no. 170, Polymer Optics Ltd., Berkshire, England).  
+Since $940~nm$ light does not influence plant development or drive photosynthesis, images were also collected during the night period.  
+Sets of $15$ images were collected for averaging, in the absence of saturating illumination.   
+As with chlorophyll a fluorescence, images were captured in the absence of $940~nm$ light for artifact subtraction.
 
-[cite]Cruz, J.A. et al. Dynamic Environmental Photosynthetic Imaging (DEPI) Reveals Emergent Phenotypes Related to the Environmental Repsonses of Photosynthesis. Nature Biotechnology Submitted (2015).
+\subsubsection{RGB color and depth images} %This section describes characterizes the data from this sensor, particularly the depth data.
+
+The RGB color and depth images were collected using a Creative Senz3D sensor~\cite{nguyen2015vietnamese}.
+The sensor contains both a $1280 \times 720$ color camera directed parallel to, and separated by roughly $25~mm$ from, a depth camera which has a resolution of $320\times240$ pixels.
+The depth sensor uses a flash near IR illuminator and measures the time-of-flight of the beam at each pixel to obtain dense depth estimates along with an IR reflectance at each pixel.
+
+There are a number of limitations to the depth sensor that become the sources of depth errors. 
+The primary measurement limitation on the range-to-target is the strength of the reflected beam. 
+As a result, dark, matt surfaces are measured reliably only at a close range on the order of $20$ or $30~cm$.  
+Highly reflective surfaces also pose problems with direct reflections leading to saturation and highly unreliable depths.  
+In addition reflective surfaces at grazing angles are less reliably measured since little signal is reflected. 
+Hence in our data portions of the chamber floor visible in Figure~\ref{fig:CameraConfiguration} are highly reflective and have incorrect depths.  %FIXME
+Fortunately the primary goal of the depth measurements are to obtain leaf depths, and plants provide good, roughly Lambertian reflections of IR~\cite{Chelle2006219}.  
+Therefore for these reasons the non-leaf depth pixels in the $3$D depth data are unreliable and should be ignored in data analysis.  
+Another limitation is that the IR illuminator has a slight offset to the left of the sensor, which results in shadows to the right of some objects, as well as mixed pixels on depth discontinuities.  
+Both of these can be readily detected as large standard deviations in the depth image.
+
+The imagery data were collected once every hour. %taken within 10 minutes of each other.  %
+These include the fluorescent image, the IR reflectance image with the same camera, the color image, the $3$D depth and a confidence image.  
+The $3$D depth image is built from the depth sensor by transforming the points into the world coordinates and is expressed in the unit of $mm$.  
+The confidence image is the standard deviation of the depth pixels.  
+This is useful for identifying pixels at depth discontinuities that are unreliably detected and result in large standard deviations.  
+In addition pixels with no response or saturated pixels are assigned with the maximum standard deviation, and should be filtered out.

### 2015-04-28 datapaper_plants.tex
xm's first edits

@@
-{\it Arabidopsis thaliana} (ecotype Col-0) plants were grown at $20^{\circ}C$, under a 16 hr:8 hr day night cycle with daylight intensity set at $100 \mu mol~photons~m^{-2} s^{-1}$. 
+\section{Data Collection}\label{sec:2}
+
+\subsection{Plants and Growth Conditions}
+
+{\it Arabidopsis thaliana} (ecotype Col-0) plants were grown at $20^{\circ}C$, under a $16$ hr:$8$ hr day night cycle with a daylight intensity set at $100~\mu mol~photons~m^{-2} s^{-1}$.
 %
-Black bean plants ({\it Phaseolus vulgaris L.}), of the cultivar Jaguar, were grown under a 14 hr:10 hr day night cycle with daylight intensity set at $200 \mu mol~photons~m^{-2} s^{-1}$ and night and day temperatures of  $18^{\circ}C$ and $24^{\circ}C$.
+Black bean plants ({\it Phaseolus vulgaris L.}) of the cultivar Jaguar, were grown under a $14$ hr:$10$ hr day night cycle with night and day temperatures of $18^{\circ}C$ and $24^{\circ}C$ respectively, and a daylight intensity set at $200~\mu mol~photons~m^{-2} s^{-1}$.
 %
-Bean plants were watered with half-strength Hoagland’s solution 3 times per week.
-In all cases, seeds were planted in soil covered with a black foam mask to minimize fluorescence background from algal growth.
+Note that the bean plants were watered with half-strength Hoaglands solution three times per week.
+
+In all cases, seeds were planted in soil covered with a black foam mask in order to minimize the fluorescence background from algal growth.
 %
-Two-week-old plants ({\it Arabidopsis} or bean) were transferred to imaging chambers and allowed to acclimate for 24 hours to the LED lighting before the start of the experiments.
+Two-week-old plants ({\it Arabidopsis} or bean) were transferred to imaging chambers and allowed to acclimate for $24$ hours to the LED lighting before the start of the data collection. 
 Growth conditions as described above were maintained for each set of plants for the duration of image collection.

### 2015-04-28 datapaper.tex
xm's first edits

@@
 
-\institute{Jeffrey A Cruz $\cdot$ Jin Chen$\cdot$ David M Kramer \at
+\institute{Jeffrey A Cruz $\cdot$ Jin Chen $\cdot$ David M Kramer \at
               Department of Energy Plant Research Laboratory, Michigan State University, East Lansing, MI 48824, USA  \\
@@
            \and
-           Xi Yin$\cdot$ Xiaoming Liu (\Letter)\at
+           Xi Yin $\cdot$ Xiaoming Liu (\Letter)\at
               Department of Computer Science and Engineering, Michigan State University,  East Lansing, MI 48824, USA  \\
@@
               \and
-           Saif Imran$\cdot$Daniel D Morris \at
+           Saif Imran $\cdot$ Daniel D Morris \at
               Department of Electrical and Computer Engineering, Michigan State University,

### 2015-04-28 datapaper_baseline.tex

@@
 \subsection{Our framework}
-We apply our automatic multi-leaf alignment, segmentation, and tracking framework~\cite{yin2014a,yin2014b} to the testing set of Arabidopsis fluorescence imagery to provide a baseline for future comparison.
+We apply our automatic multi-leaf segmentation and tracking framework~\cite{yin2014a,yin2014b} to the testing set of Arabidopsis fluorescence imagery to provide a baseline for future comparison.
 Leaf segmentation aims at finding the correct number of leaves and the corresponding boundary of each leaf in each image.
@@
 
-\begin{figure}[h]
+\begin{figure*}
 \centering
@@
 \label{fig:methodOverview}
-\end{figure}
+\end{figure*}
 
@@
 \label{fig:performance}
-\end{figure}
+\end{figure*}

### 2015-04-28 datapaper_calibration.tex

@@
 In the recorded $3$D data we subtracted our estimated bias, and averaged five depth images for each record.
-Hence the actual depth standard deviations for our data are $1/\sqrt{5}$ of the the standard deviations shown in Figure~\ref{fig:Bias} (b) and the bias is zero.
+Hence the actual depth standard deviations for our data are $1/\sqrt{5}$ of the standard deviations shown in Figure~\ref{fig:Bias} (b) and the bias is zero.
 

### 2015-04-28 datapaper_intro.tex

@@
 Leafsnap  & RGB & LC& USA trees & $184$ & $29,107$  &  $29,107$ \\ \hline
-Crop/weed &  RGB &Weed det. & Crop/weed & $2$  & $60$ & $60$ \\ \hline
+Crop/weed &  RGB &Weed detection & Crop/weed & $2$  & $60$ & $60$ \\ \hline
 \multirow{2}{*}{LSC} & \multirow{2}{*}{RGB}  & \multirow{2}{*}{LS, LO} & Arabidopsis &  $43$ & $6287$ & $201$ \\ \cline{4-7}
@@
 
-To facilitate future research on plant image analysis, as well as remedy the limitation of existing databases in the field, this paper presents a newly collected multi-modality plant imagery database at Michigan State University (MSU), termed ``MSU-PID''.
-The MSU-PID includes the imagery of two types of plants (Arabidopsis and bean), both are widely used in plant research, captured by four types of sensors, i.e., Fluorescence, infrared (IR), RGB color, and depth.
-All four sensors are synchronized and are programmed to periodically capture data for multiple consecutive days.
+To facilitate future research on plant image analysis, as well as remedy the limitation of existing databases in the field, this paper presents a new multi-modality plant imagery database collected at Michigan State University (MSU), termed ``MSU-PID''.
+The MSU-PID includes the imagery of two types of plants (Arabidopsis and bean), both are widely used in plant research, captured by four types of imaging sensors, i.e., Fluorescence, infrared (IR), RGB color, and depth.
+All four sensors are synchronized and are programmed to periodically capture imagery data for multiple consecutive days.
 Checkerboard-based camera calibration is performed between a pair of sensors, which results in the explicit correspondence between the pixels of {\it any} two modalities.
@@
 This allows researchers to study the strength and weakness of individual modality, as well as their various combinations in plant image analysis.
-\item Our imaging setup and the variety of manual labels make MSU-PID an ideal candidate for evaluating a diverse set of plant image analysis applications, including leaf segmentation, leaf counting, leaf alignment, leaf tracking, and leaf growth prediction.
+\item Our unique imaging setup and the variety of manual labels make MSU-PID an ideal candidate for evaluating a diverse set of plant image analysis applications, including leaf segmentation, leaf counting, leaf alignment, leaf tracking, and potentially leaf growth prediction and $3$D leaf reconstruction.
 \end{itemize}

### 2015-04-28 datapaper_baseline.tex
xm's first edits

@@
-\section{Baseline Method and Performance Evaluation}
+\begin{figure*}[t!]
+\centering
+\includegraphics[width=.98\textwidth]{Figures/overview}\\
+\caption{Overview of the baseline method.}
+\label{fig:methodOverview}
+\end{figure*}
+
+\section{Baseline Method and Performance}
 \label{sec:baseline}
@@
 Leaf tracking is designed to track each leaf over time.
-
-\begin{figure*}
-\centering
-\includegraphics[width=.98\textwidth]{Figures/overview}\\
-\caption{Overview of the baseline method.}
-\label{fig:methodOverview}
-\end{figure*}
 
@@
 
-\subsection{Evaluation metrics}
-To evaluate the performance of leaf segmentation, alignment, and tracking, we use four criteria and provide the Matlab implementations.
-Three of them are based on tip-based error, which is defined as average distance of a pair of estimated leaf tips $\hat{\bm{t}}_{1,2}$ with a pair of labeled leaf tips $ \bm{t}_{1,2}$ normalized by the labeled leaf length:
-
-\begin {equation}
-e_{la}(\hat{\bm{t}}_{1,2}, \bm{t}_{1,2}) = \frac{||\hat{\bm{t}}_1-{\bm{t}}_1||_2 + ||\hat{\bm{t}}_2-{\bm{t}}_2||_2}{2 ||\bm{t}_1-\bm{t}_2||_2}.
-\label{eqn:tipError}
-\end{equation}
-
-We build the frame-to-frame and video-to-video correspondence respectively and generate two sets of tip-based errors.
-More details can be find in~\cite{};
-We define a threshold $\tau$ to operate on the corresponding tip-based errors.
-By varying $\tau$, we compute the first three criteria as:
-\begin{itemize}
-  \item {\it{Unmatched Leaf Rate(ULR)}}, the percentage of unmatched leaves w.r.t.
-the total number of labeled leaves.
-This can attribute to two sources.
-First, miss detections and false alarms.
-Second, matched leaves with tip-based errors larger than $\tau$.
-  \item {\it{Landmark Error(LE)}}, the average tip-based errors smaller than $\tau$ of all frame-to-frame correspondent leaves.
-  \item {\it{Tracking Consistency(TC)}}, the percentage of video-to-video correspondent leaves whos tip-based errors are smaller than $\tau$.
-\end{itemize}
-
-In order to evaluate the leaf segmentation accuracy, we adopt an additional metric~\cite{scharr2014annotated} based on the Dice score of estimated segmentation result and ground truth label:
-\begin{itemize}
-  \item {\it{Symmetric Best Dice(SBD)}}, the symmetric best Dice among all labeled leaves.
-\end{itemize}
-
-The Matlab function for computing {\it{SBD}} is provided by~\cite{scharr2014annotated}.
-The instruction on how to use the evaluation functions are included within the functions.
-
 \subsection{Performance and analysis}

### 2015-04-28 datapapr_labeling.tex
xi_doublecolumn
xm's first edits

--- 2015-04-23 datapapr_labeling.tex
@@
-\section{Image Labeling}
+\section{Annotation, Files and Protocol}
 
-Part of the dataset is manually annotated to provide ground truth tip locations, leaf segmentation results and leaf consistency overtime.
+\begin{table*}
+\begin{center}
+\caption{Summary of Arabidopsis and Bean databases.}
+\label{tab:stat}
+\begin{tabular}{c|c|c|c|c|c}
+      \hline
+      % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
+      Plants     & Subjects & Days & Images/Day & Total Images & Annotated Images \\
+      \hline
+      Arabidopsis &  $16$      &  $9$   &     $16$     &     $2304\times 4$     &       $576\times 4$     \\
+      \hline
+      Bean        &   $5$      &  $5$   &     $14$     &     $350\times 4$       &       $175\times 4$  \\
+      \hline
+\end{tabular}
+\end{center}
+\end{table*}
+
+\subsection{Data statistics}
+MSU-PID includes two subsets, one for each plant type: Arabidopsis and Bean.
+The statistic information of these two subsets are summarised in Table~\ref{tab:stat}.
+The images were acquired every hour.
+As there is no light at night hours, plants can not be imaged by the fluorescence and RGB color sensors while IR and depth cameras can still perform the capturing in the night.
+In order to make sure that all four modalities present at each imaging opportunity, we release the part of images captured only in the day time, which are $16$ images per day for Arabidopsis and $14$ for bean for all four modalities.
+
+\begin{figure*}
+\begin{centering}
+\begin{tabular}{c c}
+%\begin{tabular}{@{}c@{} c@{}}
+%\begin{tabular}{lllllllll}
+\includegraphics[width=.47\textwidth]{Figures/rawImages/a.png}&
+\includegraphics[width=.47\textwidth]{Figures/rawImages/b.png}\\
+  Arabidopsis & Bean \\
+\end{tabular}
+\caption{GRB color images of Arabidopsis and bean plants. }
+\label{fig:rawIm}
+\end{centering}
+\end{figure*}
+
+The two subsets differs in plant image resolutions.
+As shown in Figure~\ref{fig:rawIm},  we grow and image a single bean plant while a whole tray of Arabidopsis are grown at the same time.
+Therefore, the resolution of a Arabidopsis plant is much lower than that of a bean plant.
+We manually crop $16$ Arabidopsis plants, which have been captured by all four sensors simultaneously.
+Table~\ref{tab:resolution} summaries the image resolution of each plant in all four modalities.
+
+\begin{table*}
+\begin{center}
+\caption{Plant image resolution of Arabidopsis and Bean databases.}
+\label{tab:resolution}
+\begin{tabular}{c|c|c|c|c}
+      \hline
+      % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
+      Plants     & Fluorescence       & IR        & RGB      & Depth     \\
+      \hline
+      Arabidopsis &  $\sim$$240\times240$ &  $\sim$$240\times240$  & $\sim$$120\times120$  & NA  \\
+      %\hline
+      Bean        & $1360\times1024$ & $1360\times1024$ & $1280\times720$ & $320\times240$    \\
+      \hline
+\end{tabular}
+\end{center}
+\end{table*}
+
+\subsection{Manual annotations}
+Part of the database is manually annotated to provide ground truth tip locations, leaf segmentation results and leaf consistency overtime.
 Tip locations are saved in a TXT file for each frame.
@@
 
-We use Fluorescence images for labeling because of clear background. 
-%All plants are cropped out from the background and saved as JPG files.
-For Arabidopsis images, we label four frames each day.
-While for bean images, we label seven frames each day because of faster leaf movement.
-We develop a Matlab GUI interface for leaf labeling, as shown in Fig~\ref{fig:label}.
-A user can open an image to label the two tips and annotate each leaf.
-The results will be automatically saved once a user goes to label the next image.
+We use fluorescence images for labeling because of their simple background.
+For Arabidopsis images, we label $4$ frames each day.
+While for bean images, we label $7$ frames each day because of their spontaneous and faster leaf movement.
+A Matlab-based GUI interface is developed for leaf labeling, as shown in Figure~\ref{fig:label}.
+A user can open a plant image to label the two tips and annotate each leaf segment.
+The results will be automatically saved once a user moves onto the next image for labeling.
 For consistent annotation of the same leaf over time, we show a number on the center of each leaf indicating the order of labeling from the previous frame.
@@
 
-\begin{figure}[h]
+\begin{figure*}
 \centering
 \includegraphics[width=.98\textwidth]{Figures/labeling}\\
-\caption{Leaf labeling process, including tip labels and leaf annotation.}
+\caption{Leaf labeling process, including tip labels and leaf segmentation annotation.}
 \label{fig:label}
-\end{figure}
+\end{figure*}
 
-Tip label is implemented by clicking pairs of points on the image.
-The outer tip is always clicked before the inner tip.
-A line connecting each pair of tips will be shown immediately for visualization.
+The labeling of leaf tips is implemented by clicking pairs of points on the image.
+The outer tip is always clicked first before the inner tip.
+For visualization, a line connecting each pair of tips will be shown immediately after clicking the inner tip. 
 Inaccurate labels can be deleted by clicking the right button of the mouse near the labeled point and relabeled by clicking the left button again.
 
-Leaf label is implemented by clicking the boundary of one leaf at each time.
-The leaf boundary is overlaid on the image for better visualization to guide the next action.
+The labeling of the leaf segment is implemented by clicking the boundary of one leaf at each time.
+The labeled leaf boundary is overlaid on the image for better visualization to guide the next action.
 Incorrect label can be deleted right after the labeling.
-This process continues until all leaves have been annotated.
+This process continues until all leaf segments have been annotated.
 After the labeling of one plant, we visually go through the results and correct inaccurate labels.
-One example of leaf label result for one plant is shown in Fig.~\ref{fig:LabelExample}, where one color is used to represent one leaf.  
-As we can see, there is leaf showing up and cover up the leaf underneath, which will not be annotated later (transition between day $4$ and day $5$).
+Note that one alternative approach for labeling leaf segments is to directly label the membership of superpixels instead of drawing a polygon along the boundary.
+Our experience is that since a noticeable percentage of extracted superpixels cover pixels of two neighboring leaves, the extra effort of breaking a superpixel into two makes it a less efficient alternative.
+One example of the labeling results for one plant is shown in Figure~\ref{fig:LabelExample}, where one color is used to represent each specific leaf.
+As we can see during the transition between day $4$ and day $5$, there is one leaf showing up and covering up the leaf underneath, which disappears and will not be annotated later.
 
@@
 
-\begin{figure}[h]
+\begin{figure*}
 \begin{centering}
@@
 \end{tabular}
-\caption{Leaf label results for one Arabidopsis plant over nine days with one image per day. }
+\caption{Leaf labeling results of one Arabidopsis plant over nine days with one image per day. Note that the labels of tips are not shown for visualization clarity. }
 \label{fig:LabelExample}
 \end{centering}
-\end{figure}
+\end{figure*}
+
+\subsection{Name conventions and file types}
+We release training and testing sets in two separate folders.
+In each folder, there are two subfolders named Arabidopsis and Bean.
+The files in each subfolder have the following form:
+\begin{itemize}
+  \item plant$\_$XX$\_$day$\_$X$\_$hour$\_$YY$\_$ID$\_$ZZ$\_$rgb.png: the original RGB color images;
+  \item plant$\_$XX$\_$day$\_$X$\_$hour$\_$YY$\_$ID$\_$ZZ$\_$fmp.png: the original fluorescence images;
+  \item plant$\_$XX$\_$day$\_$X$\_$hour$\_$YY$\_$ID$\_$ZZ$\_$ir.png: the original IR images;
+  \item plant$\_$XX$\_$day$\_$X$\_$hour$\_$YY$\_$ID$\_$ZZ$\_$depth.png: the original depth images;
+  \item plant$\_$XX$\_$day$\_$X$\_$hour$\_$YY$\_$ID$\_$ZZ$\_$label.png: the labeled images of fluorescence modality;
+  \item plant$\_$XX$\_$day$\_$X$\_$hour$\_$YY$\_$ID$\_$ZZ$\_$tips.txt: the labeled tip locations;
+\end{itemize}
+where XX indicates the plant type ("AR" or "BE"), X is an integer indicating the date (e.g., $1-9$ for Arabidopsis), YY represents the image index within a day (e.g., $1-16$ for Arabidopsis), and ZZ is the subject (or plant) ID (e.g., $1-5$ for bean).
+For each combination of day and hour, we provide four modalities in PNG files ($\_$rgb, $\_$fmp, $\_$ir, $\_$depth).
+For annotated images, we have two additional files ($\_$label, $\_$tips) saving the annotation results.
+Leaf segmentation results are encoded as indexed PNG files, where each leaf is assigned a unique and consistent leaf ID over time.
+Leaf ID starts from $1$ and continuously increase till the totoal number of leaves.
+And the background is encoded as $0$.
+Tips locations are saved in TXT files where each line has the following format:
+\begin{itemize}
+  \item leaf ID \quad tip1$\_$x \quad tip1$\_$y \quad tip2$\_$x \quad  tip2$\_$y
+\end{itemize}
+where leaf ID is an integer number that is consistent with the segmentation label in the PNG file.
+tip1$\_$x and tip1$\_$y represent the coordinates of the outer tip point.
+tip2$\_$x and tip2$\_$y represent the coordinates of the inner tip point.
+
+In addition to the original images and annotation results, we provide another folder named Matlab with all Matlab functions that will be used for mapping between different image modalities and for the purpose of performance evaluation.
+Note that the annotation is provided based on fluorescence images.
+In order to evaluate methods developed on other modalities, we provide image mapping functions between every two modalities.
+The total storage of our database is around $XX Mb$, which is convenient for downloading via Internet.
+
+\subsection{Experimental Protocols}
+
+As shown in Tab.~\ref{tab:database}, MSU-PID can be used for leaf segmentation, leaf alignment, leaf tracking, and leaf counting.
+To facilitate future research, we separate the database into training set and testing set.
+$40\%$ of the data is used for training and $60\%$ for testing.
+Specifically, $6$ plants of Arabidopisis and $2$ plants of bean are selected for training.
+We will provide training and testing data in different folders.
+For fair comparison, both supervised learning and unsupervised learning methods should evaluate the performance on the training and testing sets separately.
+The evaluation metrics will be discussed in Sec.~\ref{sec:baseline}.
+
+\paragraph{Performance metric}
+To evaluate the performance of leaf segmentation, alignment, and tracking, we use four criteria and provide the Matlab implementations.
+Three of them are based on tip-based error, which is defined as average distance of a pair of estimated leaf tips $\hat{\bm{t}}_{1,2}$ with a pair of labeled leaf tips $ \bm{t}_{1,2}$ normalized by the labeled leaf length:
+
+\begin {equation}
+e_{la}(\hat{\bm{t}}_{1,2}, \bm{t}_{1,2}) = \frac{||\hat{\bm{t}}_1-{\bm{t}}_1||_2 + ||\hat{\bm{t}}_2-{\bm{t}}_2||_2}{2 ||\bm{t}_1-\bm{t}_2||_2}.
+\label{eqn:tipError}
+\end{equation}
+
+We build the frame-to-frame and video-to-video correspondence respectively and generate two sets of tip-based errors.
+More details can be find in~\cite{};
+We define a threshold $\tau$ to operate on the corresponding tip-based errors.
+By varying $\tau$, we compute the first three criteria as:
+\begin{itemize}
+  \item {\it{Unmatched Leaf Rate(ULR)}}, the percentage of unmatched leaves w.r.t.
+the total number of labeled leaves.
+This can attribute to two sources.
+First, miss detections and false alarms.
+Second, matched leaves with tip-based errors larger than $\tau$.
+  \item {\it{Landmark Error(LE)}}, the average tip-based errors smaller than $\tau$ of all frame-to-frame correspondent leaves.
+  \item {\it{Tracking Consistency(TC)}}, the percentage of video-to-video correspondent leaves whos tip-based errors are smaller than $\tau$.
+\end{itemize}
+
+In order to evaluate the leaf segmentation accuracy, we adopt an additional metric~\cite{scharr2014annotated} based on the Dice score of estimated segmentation result and ground truth label:
+\begin{itemize}
+  \item {\it{Symmetric Best Dice(SBD)}}, the symmetric best Dice among all labeled leaves.
+\end{itemize}
+
+The Matlab function for computing {\it{SBD}} is provided by~\cite{scharr2014annotated}.
+The instruction on how to use the evaluation functions are included within the functions.
 

### 2015-04-28 datapaper_prior.tex

@@
 Our diverse manual labels also enable us to develop algorithms for additional applications such as leaf tracking and leaf alignment.
+
+One of our data modalities is dense depth measurement.
+This has been a component of a number of recent non-plant RGB-D databases designed for object recognition~\cite{Lai2011}, scene segmentation~\cite{Silberman2011}, human analysis~\cite{Sung2011,Barbosa:reid12}, and mapping~\cite{sturm12iros}.
+By including dense depth for a plant database we anticipate enabling development of new 3D plant shape analysis algorithms.

### 2015-04-28 datapaper_calibration.tex
xm's first edits

@@
-% For one-column wide figures use
-\begin{figure}
-  \includegraphics[width=\linewidth,trim=50 230 45 300,clip]{Figures/CameraConfiguration}
-\caption{A plot of the three cameras showing their relative configuration and fields of view as obtained through calibration.
-Units are in $mm$.
-The optical center of the color camera (on the left) defines the world coordinate system.
-Close to it is the depth camera.
-Its points are projected into the world coordinate system.
-On the right is the combined fluorescent and IR camera.}
-\label{fig:CameraConfiguration}
-\end{figure}
-
-%\subsection{Image Acquisition}
-
 \subsection{Sensor Calibration}
@@
 
-\begin{figure*}
-\centering
-\begin{tabular}{ c c }
-  \includegraphics[height=5.2cm,trim=160 300 170 310,clip]{Figures/BiasError} &
-  \includegraphics[height=5.2cm,trim=110 240 50 260,clip]{Figures/SigmaRadius} \\
-  (\emph{a}) & (\emph{b}) \\
-\end{tabular}
-\caption{Noise analysis for a depth camera.
-(\emph{a}) Bias was fit and we found it to be roughly constant as a function of depth.
-This constant offset is shown for the camera pixels with red positive and blue negative offset in mm.
-Inside the chamber, the obstructions around the depth camera altered the bias somewhat and we re-calibrated the bias there.
-In all cases we subtracted the modeled constant bias from the depth images.
-(\emph{b}) The standard deviation of the depth camera depends on depth as well as roughly on radius from the image optical center.
-A radius of $200$ pixels corresponds to the corners of the depth camera, which can be seen to have large noise.
-}
-\label{fig:Bias}
-\end{figure*}
-
 In the recorded $3$D data we subtracted our estimated bias, and averaged five depth images for each record.
@@
 % FIXME
+
+\begin{figure}
+\begin{centering}
+\begin{tabular}{c }
+\includegraphics[width=.47\textwidth]{Figures/rawImages/a.png}\\
+Arabidopsis \\
+\includegraphics[width=.47\textwidth]{Figures/rawImages/b.png}\\
+   Bean \\
+\end{tabular}
+\caption{GRB color images of Arabidopsis and bean plants. }
+\label{fig:rawIm}
+\end{centering}
+\end{figure}
+
+\begin{table*}[t!]
+\begin{center}
+\caption{Summary of Arabidopsis and Bean databases.}
+\label{tab:stat}
+\begin{tabular}{c|c|c|c|c|c}
+      \hline
+      % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
+      Plants     & Subjects & Days & Images/Day & Total Images & Annotated Images \\
+      \hline
+      Arabidopsis &  $16$      &  $9$   &     $16$     &     $2304\times 4$     &       $576\times 4$     \\
+      \hline
+      Bean        &   $5$      &  $5$   &     $14$     &     $350\times 4$       &       $175\times 4$  \\
+      \hline
+\end{tabular}
+\end{center}
+\end{table*}
+
+\begin{table*}
+\begin{center}
+\caption{Plant image resolution of Arabidopsis and Bean databases.}
+\label{tab:resolution}
+\begin{tabular}{c|c|c|c|c}
+      \hline
+      % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
+      Plants     & Fluorescence       & IR        & RGB      & Depth     \\
+      \hline
+      Arabidopsis &  $\sim$$240\times240$ &  $\sim$$240\times240$  & $\sim$$120\times120$  & NA  \\
+      %\hline
+      Bean        & $1360\times1024$ & $1360\times1024$ & $1280\times720$ & $320\times240$    \\
+      \hline
+\end{tabular}
+\end{center}
+\end{table*}

### 2015-04-28 datapaper_hardware.tex
xm's first edits

@@
+\begin{figure}
+  \includegraphics[width=\linewidth,trim=50 200 45 300,clip]{Figures/CameraConfiguration}
+\caption{The hardware setup for our data collection. (Actual figure to be replaced)}
+\label{fig:hardware}
+\end{figure}
+
 \subsection{Hardware Setup}
 
-In this section, we introduce the hardware used for capturing Fluorescence, IR, RGB color, and depth imagery data for both plants.
+In this section, we introduce the hardware used for capturing fluorescence, IR, RGB color, and depth imagery data for both plants.
+Figure~\ref{fig:hardware} illustrates the hardware and imaging setup used in our data collection.
 
@@
 As with chlorophyll a fluorescence, images were captured in the absence of $940~nm$ light for artifact subtraction.
+
+% For one-column wide figures use
+\begin{figure}
+  \includegraphics[width=\linewidth,trim=50 230 45 300,clip]{Figures/CameraConfiguration}
+\caption{A plot of the three cameras showing their relative configuration and fields of view as obtained through calibration.
+Units are in $mm$.
+The optical center of the color camera (on the left) defines the world coordinate system.
+Close to it is the depth camera.
+Its points are projected into the world coordinate system.
+On the right is the combined fluorescent and IR camera.}
+\label{fig:CameraConfiguration}
+\end{figure}
 
@@
 In addition pixels with no response or saturated pixels are assigned with the maximum standard deviation, and should be filtered out.
+
+\begin{figure}[t!]
+\centering
+%\begin{tabular}{ c c}
+%  \includegraphics[height=5.2cm,trim=160 300 170 310,clip]{Figures/BiasError} &
+%  \includegraphics[height=5.2cm,trim=110 240 50 260,clip]{Figures/SigmaRadius} \\
+%  (\emph{a}) & (\emph{b}) \\
+%\end{tabular}
+\begin{tabular}{ c}
+  \includegraphics[height=3.8cm,trim=175 310 140 310,clip]{Figures/BiasError} \\
+   \small{(a)} \\
+  \includegraphics[height=5.9cm,trim=110 250 60 260,clip]{Figures/SigmaRadius} \\
+  \small{(b)}  \\
+\end{tabular}
+\caption{Noise analysis for a depth camera.
+(\emph{a}) Bias was fit and we found it to be roughly constant as a function of depth.
+This constant offset is shown for the camera pixels with red positive and blue negative offset in mm.
+Inside the chamber, the obstructions around the depth camera altered the bias somewhat and we re-calibrated the bias there.
+In all cases we subtracted the modeled constant bias from the depth images.
+(\emph{b}) The standard deviation of the depth camera depends on depth as well as roughly on radius from the image optical center.
+A radius of $200$ pixels corresponds to the corners of the depth camera, which can be seen to have large noise.
+}
+\label{fig:Bias}
+\end{figure}

### 2015-04-28 datapaper_intro.tex
xm's first edits

@@
 							    &  & & Tobacco & $80$ & $165,120$ & $83$ \\ \hline
-\multirow{2}{*}{MSU-PID}  & Fluorescence,  & LS, LO, & Arabidopsis &  $20$ & $XXX$ & $XXX$ \\ \cline{4-7}
-							    & IR, RGB, Depth & LA, LT & Bean & $5$ & $XXX$ & $XXX$ \\ \hline
+\multirow{2}{*}{MSU-PID}  & Fluorescence,  & LS, LO, & Arabidopsis &  $16$ &  $2304\times 4$ & $576\times 4$     \\ \cline{4-7}
+							    & IR, RGB, Depth & LA, LT & Bean & $5$ & $350\times 4$  &  $175\times 4$ \\ \hline
 	       \hline

### 2015-04-28 datapapr_labeling.tex
xm's first edits

@@
 \section{Annotation, Files and Protocol}
-
-\begin{table*}
-\begin{center}
-\caption{Summary of Arabidopsis and Bean databases.}
-\label{tab:stat}
-\begin{tabular}{c|c|c|c|c|c}
-      \hline
-      % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
-      Plants     & Subjects & Days & Images/Day & Total Images & Annotated Images \\
-      \hline
-      Arabidopsis &  $16$      &  $9$   &     $16$     &     $2304\times 4$     &       $576\times 4$     \\
-      \hline
-      Bean        &   $5$      &  $5$   &     $14$     &     $350\times 4$       &       $175\times 4$  \\
-      \hline
-\end{tabular}
-\end{center}
-\end{table*}
 
@@
 
-\begin{figure*}
-\begin{centering}
-\begin{tabular}{c c}
-%\begin{tabular}{@{}c@{} c@{}}
-%\begin{tabular}{lllllllll}
-\includegraphics[width=.47\textwidth]{Figures/rawImages/a.png}&
-\includegraphics[width=.47\textwidth]{Figures/rawImages/b.png}\\
-  Arabidopsis & Bean \\
-\end{tabular}
-\caption{GRB color images of Arabidopsis and bean plants. }
-\label{fig:rawIm}
-\end{centering}
-\end{figure*}
-
 The two subsets differs in plant image resolutions.
@@
 Table~\ref{tab:resolution} summaries the image resolution of each plant in all four modalities.
-
-\begin{table*}
-\begin{center}
-\caption{Plant image resolution of Arabidopsis and Bean databases.}
-\label{tab:resolution}
-\begin{tabular}{c|c|c|c|c}
-      \hline
-      % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
-      Plants     & Fluorescence       & IR        & RGB      & Depth     \\
-      \hline
-      Arabidopsis &  $\sim$$240\times240$ &  $\sim$$240\times240$  & $\sim$$120\times120$  & NA  \\
-      %\hline
-      Bean        & $1360\times1024$ & $1360\times1024$ & $1280\times720$ & $320\times240$    \\
-      \hline
-\end{tabular}
-\end{center}
-\end{table*}
 
@@
 
+\begin{figure*}[t!]
+\centering
+\includegraphics[width=.98\textwidth]{Figures/overview}\\
+\caption{Overview of the baseline method.}
+\label{fig:methodOverview}
+\end{figure*}
+
 \paragraph{Performance metric}

### 2015-04-29 datapapr_labeling.tex
xm's first edits

@@
 
-As shown in Tab.~\ref{tab:database}, MSU-PID can be used for leaf segmentation, leaf alignment, leaf tracking, and leaf counting.
-To facilitate future research, we separate the database into training set and testing set.
+As shown in Table~\ref{tab:database}, MSU-PID can be used for applications such as leaf segmentation, leaf alignment, leaf tracking, and leaf counting.
+To facilitate future research, we separate the database into the training set and the testing set.
 $40\%$ of the data is used for training and $60\%$ for testing.
@@
 We will provide training and testing data in different folders.
-For fair comparison, both supervised learning and unsupervised learning methods should evaluate the performance on the training and testing sets separately.
-The evaluation metrics will be discussed in Sec.~\ref{sec:baseline}.
+For fair comparison, both supervised learning and unsupervised learning methods should evaluate their performances on the training and testing sets separately.
+The user may decide to utilize one or multiple modalities of the plant imagery for training and testing respectively.
+The availability of multiple modalities allows user to design novel experimental setup. 
+For example, using RGB and depth modalities for training and RGB for testing can evaluate an algorithm that can handle a missing modality during the testing.
+%The evaluation metrics will be discussed in Sec.~\ref{sec:baseline}.
 
@@
 \paragraph{Performance metric}
-To evaluate the performance of leaf segmentation, alignment, and tracking, we use four criteria and provide the Matlab implementations.
-Three of them are based on tip-based error, which is defined as average distance of a pair of estimated leaf tips $\hat{\bm{t}}_{1,2}$ with a pair of labeled leaf tips $ \bm{t}_{1,2}$ normalized by the labeled leaf length:
-
+To evaluate the performance of leaf segmentation, alignment, and tracking, we use four performance metrics, whose Matlab implementations will be provided along with the data.
+Three of them are based on the tip-based error, which is defined as the average distance of a pair of estimated leaf tips $\hat{\bm{t}}_{1,2}$ with a pair of labeled leaf tips $ \bm{t}_{1,2}$ normalized by the labeled leaf length:
 \begin {equation}
@@
 We define a threshold $\tau$ to operate on the corresponding tip-based errors.
-By varying $\tau$, we compute the first three criteria as:
+By varying $\tau$, we compute the first three metrics as follows:
 \begin{itemize}
-  \item {\it{Unmatched Leaf Rate(ULR)}}, the percentage of unmatched leaves w.r.t.
-the total number of labeled leaves.
+  \item {\it{Unmatched Leaf Rate (ULR)}}, the percentage of unmatched leaves with respect to the total number of labeled leaves. 
 This can attribute to two sources. 
-First, miss detections and false alarms.
-Second, matched leaves with tip-based errors larger than $\tau$.
-  \item {\it{Landmark Error(LE)}}, the average tip-based errors smaller than $\tau$ of all frame-to-frame correspondent leaves.
-  \item {\it{Tracking Consistency(TC)}}, the percentage of video-to-video correspondent leaves whos tip-based errors are smaller than $\tau$.
+The first is miss detections and false alarms. 
+The second is matched leaves with tip-based errors larger than $\tau$.
+  \item {\it{Landmark Error (LE)}}, the average tip-based errors smaller than $\tau$ of all frame-to-frame correspondent leaves.
+  \item {\it{Tracking Consistency (TC)}}, the percentage of video-to-video correspondent leaves whose tip-based errors are smaller than $\tau$.
 \end{itemize}
 
-In order to evaluate the leaf segmentation accuracy, we adopt an additional metric~\cite{scharr2014annotated} based on the Dice score of estimated segmentation result and ground truth label:
+In order to evaluate the leaf segmentation accuracy, we adopt an additional metric~\cite{scharr2014annotated} based on the Dice score of estimated segmentation results and ground truth labels:
 \begin{itemize}
-  \item {\it{Symmetric Best Dice(SBD)}}, the symmetric best Dice among all labeled leaves.
+  \item {\it{Symmetric Best Dice (SBD)}}, the symmetric best Dice among all labeled leaves.
 \end{itemize}
-
 The Matlab function for computing {\it{SBD}} is provided by~\cite{scharr2014annotated}.
-The instruction on how to use the evaluation functions are included within the functions.
+The instruction on how to use the evaluation functions are included as comments of the function.
 

### 2015-04-29 datapaper_baseline.tex
xm's first edits

@@
-\begin{figure*}[t!]
-\centering
-\includegraphics[width=.98\textwidth]{Figures/overview}\\
-\caption{Overview of the baseline method.}
-\label{fig:methodOverview}
-\end{figure*}
-
 \section{Baseline Method and Performance}
 \label{sec:baseline}
-\subsection{Our framework}
-We apply our automatic multi-leaf segmentation and tracking framework~\cite{yin2014a,yin2014b} to the testing set of Arabidopsis fluorescence imagery to provide a baseline for future comparison.
-Leaf segmentation aims at finding the correct number of leaves and the corresponding boundary of each leaf in each image.
-Leaf alignment is to align the two tips of each leaf.
-Leaf tracking is designed to track each leaf over time.
 
-As shown in Fig~\ref{fig:methodOverview}, the input of this framework is a plant video and a set of predefined templates with various shapes, scales, and orientations.
+To facilitate future research on this database, we provide a baseline approach and its performance by using the fluorescence modality.
+
+\subsection{Multi-leaf segmentation and tracking framework}
+We apply our automatic multi-leaf segmentation and tracking framework~\cite{yin2014a,yin2014b} to the testing set of Arabidopsis fluorescence imagery to provide a baseline.
+As shown in Figure~\ref{fig:methodOverview}, the input of this framework is a plant video and a set of predefined templates with various shapes, scales, and orientations.
 To generate the template set, we first select $10$ templates with different aspect ratios from the labeled images in the training set together with the corresponding tip locations.
-For each template, we scale it to $12$ different sizes in order to cover all size ranges in the database.
-For each scale template, we rotated every $15^{\circ}$ to generate $24$ different directions.
+For each template, we scale it to $12$ different sizes in order to cover the entire range of leaf sizes in the database.
+For each scale template, we rotate every $15^{\circ}$ to generate $24$ templates at different orientations.
 Tip locations will be scaled and rotated accordingly.
 Finally, we generate $2,880$ leaf templates.
-
-%We also generate the two tips for each template for finding the corresponding tip points of each leaf via Chamfer Matching~\cite{barrow1977parametric}.
-Our work is motivated by Chamfer Matching technique~\cite{barrow1977parametric}, which is used to align two edge maps.
-We extend it to align multiple objects at the same time.
-For each image, we use simple thresholding and edge detection to generate an edge map and mask.
-First, we find the best location of each template in the edge map that has minimal chamfer matching distance, which will result in an over-complete set of leaf candidates.
-Second, we apply multi-leaf alignment~\cite{yin2014a} approach to find an optimal set of leaf candidates on the last frame of the video, which will provide the information of the number of leaves, tip locations and boundaries of each leaf.
-Third, we apply multi-leaf tracking~\cite{yin2014b} approach, which is based on leaf template transformation, to track leaves between continuous two frames.
-
-In the tracking process, we develop a procedure to generate new leaves and delete small leaves.
-For each frame of the video, we can generate a label image with each leaf being labeled with one color and the tip locations for each piece of leaf.
-The label for each leaf in the video maintain the same during tracking process.
-
-\subsection{Performance and analysis}
-The results of our algorithm by varying $\tau$ from 0 to 1 is shown in Fig.~.
-And the {\it{SBD}} score is $0.51$ by averaging over all plants.
 
@@
 \end{figure*}
+
+%We also generate the two tips for each template for finding the corresponding tip points of each leaf via Chamfer Matching~\cite{barrow1977parametric}.
+Our work is motivated by Chamfer Matching technique~\cite{barrow1977parametric}, which is used to align two edge maps.
+We extend it to simultaneously align multiple overlapping objects.
+For each image, we use simple thresholding and edge detection to generate an edge map and mask.
+First, we find the best location of each template in the edge map that has the minimal Chamfer matching distance, which will result in an over-completed set of leaf candidates.
+Second, we apply multi-leaf alignment~\cite{yin2014a} approach to find an optimal set of leaf candidates on the last frame of the video, which will provide the information of the number of leaves, tip locations and boundaries of each leaf.
+Third, we apply multi-leaf tracking~\cite{yin2014b} approach, which is based on leaf template transformation, to track leaves between continuous two frames.
+
+In the tracking process, we develop a procedure to generate new leaves and delete small leaves.
+For each frame of the video, we can generate a label image with each leaf being labeled with one color and the tip locations for each estimated leaf.
+The labeled color for each leaf in the video remains the same during the tracking process.
+
+\subsection{Performance and analysis}
+The results of our algorithm by varying $\tau$ from 0 to 1 is shown in Fig.~.
+And the {\it{SBD}} score is $0.51$ by averaging over all plants.

### 2015-04-29 datapaper_intro.tex
xm's first edits

@@
 	\centering
-	\caption{Plant image databases, where the abbreviation in ``Applications'' column is defined as Leaf Classification (LC), Leaf Segmentation (LS), Leaf Counting (LO), Leaf Alignment (LA), and Leaf Tracking (LT).}
+	  \begin{threeparttable}
+	\caption{Plant image databases.}
 	%\resizebox{12cm}{!} {
@@
 		\hline
-		\multirow{2}{*}{Database}&  \multirow{2}{*}{Modality}  & Appli-& Plant & Subject/ &Total  &  Labeled   \\ 						
-			&         & cations &            Type         &       Classe \#         &  Image \#    & Image \# \\ \hline
+		\multirow{2}{*}{Database}&  \multirow{2}{*}{Modality}  &  \multirow{2}{*}{Applications}\tnote{a} & \multirow{2}{*}{Plant Type} & Subject/ &Total  &  Labeled   \\ 						
+			&         &  &                    &       Classe \#         &  Image \#    & Image \# \\ \hline
 
@@
 	%}
+\begin{tablenotes}
+	    \footnotesize	
+            \item[a] The abbreviation in ``Applications'' column is defined as Leaf Classification (LC), Leaf Segmentation (LS), Leaf Counting (LO), Leaf Alignment (LA), and Leaf Tracking (LT).
+        \end{tablenotes}
+     \end{threeparttable}
 	\label{tab:database}
@@
 Checkerboard-based camera calibration is performed between a pair of sensors, which results in the explicit correspondence between the pixels of {\it any} two modalities.
-For a subset of the database, we manually label the ground truth regarding the leaf identification number, locations of leaf tips and leaf segments. 
-To provide a performance baseline for future research and comparison, we apply our automatic leaf segmentation framework~\cite{yin2014a,yin2014b} to the Arabidopsis imagery and demonstrate the unique challenge of image analysis on this database.
+
+The type and amount of manual labels on a datatbase is a critical enabler to the potential applications of the database.
+For a subset of the MSU-PID database, we manually label the ground truth regarding the leaf identification number, locations of leaf tips and leaf segments. 
+As a result,  MSU-PID is suitable for a number of applications, including 1) {\it leaf segmentation} that aims at estimating the correct segmentation mask of each leaf in an image, 2) {\it leaf counting} that estimates the correct number of leaves within a plant, 3) {\it leaf alignment} that aligns the two tips of each leaf -- the cornerstone of the leaf structure, and 4) {\it leaf tracking} that is designed to track each leaf over time.
+Finally, to provide a performance baseline for future research and comparison, we apply our automatic leaf segmentation framework~\cite{yin2014a,yin2014b} to the Arabidopsis imagery and demonstrate the unique challenge of image analysis on this database.
 

### 2015-04-29 datapaper_intro.tex
xm's first edits

@@
 
-To facilitate future research on plant image analysis, as well as remedy the limitation of existing databases in the field, this paper presents a new multi-modality plant imagery database collected at Michigan State University (MSU), termed ``MSU-PID''.
-The MSU-PID includes the imagery of two types of plants (Arabidopsis and bean), both are widely used in plant research, captured by four types of imaging sensors, i.e., Fluorescence, infrared (IR), RGB color, and depth.
+To facilitate future research on plant image analysis, as well as remedy the limitation of existing databases in the field, this paper presents a newly collected multi-modality plant imagery database through an interdisciplinary effort at Michigan State University (MSU), termed ``MSU-PID''.
+The MSU-PID database includes the imagery of two types of plants (Arabidopsis and bean), both are widely used in plant research, captured by four types of imaging sensors, i.e., Fluorescence, infrared (IR), RGB color, and depth.
 All four sensors are synchronized and are programmed to periodically capture imagery data for multiple consecutive days. 

### 2015-04-29 datapaper_conclusion.tex
xm's first edits

\section{Conclusions}

This paper presents a newly collected multi-modality plant imagery database, ``MSU-PID''.
Compared to existing databases in the field, MSU-PID not only has multiple calibrated modalities, but also enables a wide variety of plant image analysis applications.
Therefore, we believe this new database will be benefitial to the research community in terms of algorithm development, performance evaluation, and identifying new research problems in plant image analysis.
Furthmore, we are also open to suggestions and comments from the users of this database to further enhance our imaging setup and capturing protocol, so that we can develop new databases in the future.

### 2015-04-29 datapaper_baseline.tex
performance

@@
 We apply our automatic multi-leaf segmentation and tracking framework~\cite{yin2014a,yin2014b} to the testing set of Arabidopsis fluorescence imagery to provide a baseline.
+We treat all images in $9$ days as a video from first image on the first day to the last image in the last day. 
 As shown in Figure~\ref{fig:methodOverview}, the input of this framework is a plant video and a set of predefined templates with various shapes, scales, and orientations.
-To generate the template set, we first select $10$ templates with different aspect ratios from the labeled images in the training set together with the corresponding tip locations.
-For each template, we scale it to $12$ different sizes in order to cover the entire range of leaf sizes in the database.
+To generate the template set, we first select $12$ templates with different aspect ratios from the labeled images in the training set together with the corresponding tip locations.
+For each template, we scale it to $10$ different sizes in order to cover the entire range of leaf sizes in the database.
 For each scale template, we rotate every $15^{\circ}$ to generate $24$ templates at different orientations.
@@
 We extend it to simultaneously align multiple overlapping objects.
-For each image, we use simple thresholding and edge detection to generate an edge map and mask.
+For plant segmentation, we use simple thresholding and edge detection to generate an edge map and mask.
+The best threshold is learnt from the training set.
+The edge map and mask are used in the alignment and tracking optimization.
+
 First, we find the best location of each template in the edge map that has the minimal Chamfer matching distance, which will result in an over-completed set of leaf candidates.
@@
 
-In the tracking process, we develop a procedure to generate new leaves and delete small leaves.
+In the tracking process, we delete a leaf when it becomes too small. 
+We develop a procedure to generate new leaves when there is a relatively large portion of the mask has not been covered by current leaf candidates.
 For each frame of the video, we can generate a label image with each leaf being labeled with one color and the tip locations for each estimated leaf.
@@
 \subsection{Performance and analysis}
+We apply our algorithm on all $144$ frames of each video and evaluate the performance on labeled $36$ frames.
+Leaf alignment is applied to the last frame of each video. 
+Figure~\ref{fig:alignResult} shows some examples of leaf alignment results. 
+Our framework works very well on segmenting large leaves with no overlap to neighbor leaves. 
+For overlapping leaves, it becomes more challenging as the edges between the overlapping area are more difficult to be detected. 
+However, when the overlapping leaves are further away from the center, they will have a higher chance to be detected as shown in $(3)$ of Fig.~\ref{fig:alignResult}. 
+When the overlapping leaves are close to the center, smaller leaves will be covered by larger leaves as shown in $(1), (4), (5)$ of Fig.~\ref{fig:alignResult}.
+
+Leaf alignment provides the leaf candidates for tracking over time. 
+One example of leaf tracking result is shown in Fig.~\ref{fig:trackExample}.
+
+\begin{figure*}
+\begin{centering}
+\begin{tabular}{c c c c c c}
+%\begin{tabular}{lllllllll}
+\includegraphics[width=.14\textwidth]{Figures/AlignPerformance/9_1}&
+\includegraphics[width=.14\textwidth]{Figures/AlignPerformance/10_1}&
+\includegraphics[width=.14\textwidth]{Figures/AlignPerformance/11_1}&
+\includegraphics[width=.14\textwidth]{Figures/AlignPerformance/12_1}&
+\includegraphics[width=.14\textwidth]{Figures/AlignPerformance/14_1}&
+\includegraphics[width=.14\textwidth]{Figures/AlignPerformance/15_1}\\
+
+\includegraphics[width=.14\textwidth]{Figures/AlignPerformance/9_2}&
+\includegraphics[width=.14\textwidth]{Figures/AlignPerformance/10_2}&
+\includegraphics[width=.14\textwidth]{Figures/AlignPerformance/11_2}&
+\includegraphics[width=.14\textwidth]{Figures/AlignPerformance/12_2}&
+\includegraphics[width=.14\textwidth]{Figures/AlignPerformance/14_2}&
+\includegraphics[width=.14\textwidth]{Figures/AlignPerformance/15_2}\\
+(1) & (2) & (3) & (4) & (5) & (6) \\
+\end{tabular}
+\caption{Leaf alignment results on the last frame of $6$ plant videos. First row shows the original image. Second row shows the alignment result. }
+\label{fig:alignResult}
+\end{centering}
+\end{figure*}
+
+\begin{figure*}
+\begin{centering}
+\begin{tabular}{@{}c@{} c@{} c@{} c@{} c@{} c@{} c@{} c@{} c@{}}
+%\begin{tabular}{lllllllll}
+\includegraphics[width=.11\textwidth]{Figures/trackExample/1_1}&
+\includegraphics[width=.11\textwidth]{Figures/trackExample/1_2}&
+\includegraphics[width=.11\textwidth]{Figures/trackExample/1_3}&
+\includegraphics[width=.11\textwidth]{Figures/trackExample/1_4}&
+\includegraphics[width=.11\textwidth]{Figures/trackExample/1_5}&
+\includegraphics[width=.11\textwidth]{Figures/trackExample/1_6}&
+\includegraphics[width=.11\textwidth]{Figures/trackExample/1_7}&
+\includegraphics[width=.11\textwidth]{Figures/trackExample/1_8}&
+\includegraphics[width=.11\textwidth]{Figures/trackExample/1_9}\\
+
+\includegraphics[width=.11\textwidth]{Figures/trackExample/2_1}&
+\includegraphics[width=.11\textwidth]{Figures/trackExample/2_2}&
+\includegraphics[width=.11\textwidth]{Figures/trackExample/2_3}&
+\includegraphics[width=.11\textwidth]{Figures/trackExample/2_4}&
+\includegraphics[width=.11\textwidth]{Figures/trackExample/2_5}&
+\includegraphics[width=.11\textwidth]{Figures/trackExample/2_6}&
+\includegraphics[width=.11\textwidth]{Figures/trackExample/2_7}&
+\includegraphics[width=.11\textwidth]{Figures/trackExample/2_8}&
+\includegraphics[width=.11\textwidth]{Figures/trackExample/2_9}\\
+
+\includegraphics[width=.11\textwidth]{Figures/trackExample/3_9}&
+\includegraphics[width=.11\textwidth]{Figures/trackExample/3_9}&
+\includegraphics[width=.11\textwidth]{Figures/trackExample/3_9}&
+\includegraphics[width=.11\textwidth]{Figures/trackExample/3_9}&
+\includegraphics[width=.11\textwidth]{Figures/trackExample/3_9}&
+\includegraphics[width=.11\textwidth]{Figures/trackExample/3_9}&
+\includegraphics[width=.11\textwidth]{Figures/trackExample/3_9}&
+\includegraphics[width=.11\textwidth]{Figures/trackExample/3_9}&
+\includegraphics[width=.11\textwidth]{Figures/trackExample/3_9}\\
+
+Day 1 & Day 2 & Day 3 & Day 4 & Day 5 & Day 6 & Day 7 & Day 8 & Day 9 \\
+\end{tabular}
+\caption{Tracking result for one video with one frame for each day.}
+\label{fig:trackExample}
+\end{centering}
+\end{figure*}
+
 The results of our algorithm by varying $\tau$ from 0 to 1 is shown in Fig.~.
-And the {\it{SBD}} score is $0.51$ by averaging over all plants.
+And the {\it{SBD}} score is $0.59$ by averaging over all plants.

### 2015-04-29 datapapr_labeling.tex
xm's first edits
performance

@@
 \section{Annotation, Files and Protocol}
-
 \subsection{Data statistics}
@@
 The two subsets differs in plant image resolutions.
-As shown in Figure~\ref{fig:rawIm},  we grow and image a single bean plant while a whole tray of Arabidopsis are grown at the same time.
+As shown in Figure~\ref{fig:fourmodality},  we grow and image a single bean plant while a whole tray of Arabidopsis are grown at the same time.
 Therefore, the resolution of a Arabidopsis plant is much lower than that of a bean plant.
@@
 As we can see during the transition between day $4$ and day $5$, there is one leaf showing up and covering up the leaf underneath, which disappears and will not be annotated later.
-
-%\begin{figure}[h]
-%\centering
-%\includegraphics[width=.98\textwidth]{Figures/labelExamples}\\
-%\caption{Leaf label results for one Arabidopsis plant over nine days with one image per day. }
-%\label{fig:LabelExample}
-%\end{figure}
 
@@
 
+\begin{figure*}[t!]
+\centering
+\includegraphics[width=.98\textwidth]{Figures/overview}\\
+\caption{Overview of the baseline method.}
+\label{fig:methodOverview}
+\end{figure*}
+
 \subsection{Experimental Protocols}
@@
 
-\begin{figure*}[t!]
-\centering
-\includegraphics[width=.98\textwidth]{Figures/overview}\\
-\caption{Overview of the baseline method.}
-\label{fig:methodOverview}
-\end{figure*}
-
 \paragraph{Performance metric}
@@
 We build the frame-to-frame and video-to-video correspondence respectively and generate two sets of tip-based errors.
-More details can be find in~\cite{};
+More details can be find in~\cite{yin2014b}.
 We define a threshold $\tau$ to operate on the corresponding tip-based errors.

### 2015-04-29 datapaper_baseline.tex
baseline

@@
 One example of leaf tracking result is shown in Fig.~\ref{fig:trackExample}. 
+The leaf template transformation works well for most leaves. 
+As plant grows, younger leaves may grow faster than older leaves and occlude the older leaves. 
+Our backward tracking algorithm tracks leaves from last frame to first frame. 
+Leaves will be deleted when it becomes small and the leaf underneath it will be detected. 
+As shown in Fig,~\ref{}, leaf $X$ replace leaf $X$ at day $X$, which is considered as a tracking failure.
 
@@
 \begin{centering}
-\begin{tabular}{@{}c@{} c@{} c@{} c@{} c@{} c@{} c@{} c@{} c@{}}
+\begin{tabular}{c c@{} c@{} c@{} c@{} c@{} c@{} c@{} c@{} c@{}}
 %\begin{tabular}{lllllllll}
+(1) &
 \includegraphics[width=.11\textwidth]{Figures/trackExample/1_1}&
@@
 \includegraphics[width=.11\textwidth]{Figures/trackExample/1_9}\\
-
+(2)&
 \includegraphics[width=.11\textwidth]{Figures/trackExample/2_1}&
@@
 \includegraphics[width=.11\textwidth]{Figures/trackExample/2_9}\\
-
+(3) &
 \includegraphics[width=.11\textwidth]{Figures/trackExample/3_9}&
@@
 
-Day 1 & Day 2 & Day 3 & Day 4 & Day 5 & Day 6 & Day 7 & Day 8 & Day 9 \\
+ & Day 1 & Day 2 & Day 3 & Day 4 & Day 5 & Day 6 & Day 7 & Day 8 & Day 9 \\
 \end{tabular}
-\caption{Tracking result for one video with one frame for each day.}
+\caption{Tracking result for one video with one frame for each day.
+$(1)$ Example frames in the video.
+$(2)$.
+Leaf label result overlaid with tip locations.
+$(3)$ Leaf tracking result.
+We show one frame for each day.
+}
 \label{fig:trackExample}
@@
 
-The results of our algorithm by varying $\tau$ from 0 to 1 is shown in Fig.~.
-And the {\it{SBD}} score is $0.59$ by averaging over all plants.
+For quantitative evaluation, we vary $\tau$ from 0 to 1 and generate the first three evaluation metrics, as shown in Fig.~\ref{fig:performance}.
+{\it{ULR}} decreases as $\tau$ increases as more leaves are being considered as matched leaves.  
+As $\tau$ keep increasing, {\it{ULR}} approaches a constant value, which is the the diferent number in leaf counting that results from both miss detection and false alarms. 
+{\it{LE}} increases as $\tau$ increases as it includes leaves with larger tip-based errors for averaging. 
+{\it{TC}} increases as $\tau$ increases as more leaves are being considered as correctly tracked leaves. 
+Overall, our method can detect $80\%$ and track $60\%$ of all labeled leaves with $XX$ average tip-based errors.
+
+We generate a label image for each frame based on the leaf segmentation results anc compute the {\it{SBD}} score for each labeled image. 
+The average {\it{SBD}} over all images is $0.59$.

### 2015-04-30 datapaper_calibration.tex
performance
Updates to calibration and hardware

@@
 
-A checkerboard pattern was used to calibrate all three cameras to obtain both intrinsic and extrinsic parameters.
-While the checkerboard pattern is not visible as variations in depth, it is nevertheless observed as variations in the reflected IR image whose pixels correspond to the depth pixels.
-This enables the use of Zhang's method~\cite{Zhang2000} to calculate the intrinsic parameters including a $2$-parameter radial distortion of each camera, as well as a calculation of their relative poses.
-The optical center of the color camera is used to define the world coordinates of our data.
-The depth values of the depth camera are projected along their pixel rays and then rotated and translated by the pose of the depth camera, and thus recorded as $3$D points in the world coordinate system.
-Therefore it is straight forward to project these points onto any of the three camera images.
+A planar checkerboard pattern was used to calibrate all three cameras to obtain both intrinsic and extrinsic parameters.
+While the grid pattern is not visible in the depth image, it is nevertheless observed in the reflected IR image whose pixels correspond to the depth pixels.
+This enables the use of Zhang's method~\cite{Zhang2000} to calculate the intrinsic parameters including a $2$-parameter radial distortion of each camera.
+In this process the poses of all three cameras are also calculated relative to the checkerboard.
+The intrinsic and extrinsic parameters are stored as text files, and a Matlab function is provided that reads the parameters and can plot the camera poses as in Fig.~\ref{fig:CameraConfiguration}.
 
-\subsubsection{Depth Bias and Noise Characterization}
+\subsubsection{Noise Characterization}
 \label{sec:bias}
 
-We characterized both the bias and the variance of the depth cameras as follows.  
-A flat printed checkerboard with a surrounding white board was positioned at a large number of poses in front of the sensor.  
-The pose of the checkerboard is calculated in each case using the color and IR reflectance images.  
-This defines a plane relative to the depth camera, which we use to calculate the ground truth depths for each pixel in the depth camera.  
-At each pose, we collect multiple depth images; this provides both a bias and variance measurement for each pixel at multiple depths.
+The pixel depth measurements have significant noise.
+To characterize the noise variance at a particular depth we collected 300 images of a flat surface facing the camera at this depth and calculated the standard deviation at each pixel.
+We repeated this for increments of 10cm between 30cm and 90cm.
+At each depth we found that the pixel standard deviations were roughly constant at concentric circles around the optical center.
+Hence we can summarize the standard deviation as a function of pixel depth and pixel-radius around the optical center, as shown in Fig.~\ref{fig:Noise}.
+This captures a large fraction of the depth error for pixels on plant leafs, although additional sources of error include individual pixel biases, object specularities, strong variations in object albedo, mixed pixels on object edges, and very-low signal reflection.
 
-Next we sought to model the depth bias as a linear function of depth.  
-Two parameters were fit for each pixel (a linear coefficient and an offset).  
-We found that the bias was close to a constant as a function of depth, although it varied across the depth image as shown in Figure~\ref{fig:Bias}.  
-The standard deviation of the pixel depth varied as a function of depth and roughly with the distance of the pixel from the optical center.  
-Estimates of the noise are shown in Figure~\ref{fig:Bias}.
-
-In the recorded $3$D data we subtracted our estimated bias, and averaged five depth images for each record.
-Hence the actual depth standard deviations for our data are $1/\sqrt{5}$ of the standard deviations shown in Figure~\ref{fig:Bias} (b) and the bias is zero.
+In the recorded $3$D data we averaged five depth images for each record.
+Ideally this leads to reducing the standard deviation by $1/\sqrt{5}$, although the actual benefit is less as some sources of error are not reduced by averaging.
 
@@
 
-\begin{figure}
-\begin{centering}
-\begin{tabular}{c }
-\includegraphics[width=.47\textwidth]{Figures/rawImages/a.png}\\
-Arabidopsis \\
-\includegraphics[width=.47\textwidth]{Figures/rawImages/b.png}\\
-   Bean \\
-\end{tabular}
-\caption{GRB color images of Arabidopsis and bean plants. }
-\label{fig:rawIm}
-\end{centering}
-\end{figure}
+%\begin{figure}
+%\begin{centering}
+%\begin{tabular}{c }
+%\includegraphics[width=.47\textwidth]{Figures/rawImages/a.png}\\
+%Arabidopsis \\
+%\includegraphics[width=.47\textwidth]{Figures/rawImages/b.png}\\
+%   Bean \\
+%\end{tabular}
+%\caption{RGB color images of Arabidopsis and bean plants. }
+%\label{fig:rawIm}
+%\end{centering}
+%\end{figure}
 
@@
       %\hline
-      Bean        & $1360\times1024$ & $1360\times1024$ & $1280\times720$ & $320\times240$    \\
+      Bean        & $1000\times640$ & $1000\times640$ & $380\times720$ & $90\times190$    \\
       \hline

### 2015-04-30 datapaper_hardware.tex
xm's first edits
Updates to calibration and hardware

--- 2015-04-28 datapaper_hardware.tex
@@
+\begin{figure}
+  \includegraphics[width=0.93\linewidth,trim=50 80 200 70,clip]{Figures/hardware}
+\caption{The hardware setup for our data collection.}
+\label{fig:hardware}
+\end{figure}
+
 \subsection{Hardware Setup}
 
-In this section, we introduce the hardware used for capturing Fluorescence, IR, RGB color, and depth imagery data for both plants.
+In this section, we introduce the hardware used for capturing fluorescence, IR, RGB color, and depth imagery data for both plants.
+Figure~\ref{fig:hardware} illustrates the hardware and imaging setup used in our data collection.
 
@@
 In addition pixels with no response or saturated pixels are assigned with the maximum standard deviation, and should be filtered out.
+
+\begin{figure}
+\centering
+  \includegraphics[height=5.9cm,trim=110 250 60 260,clip]{Figures/SigmaRadius} \\
+\caption{Noise analysis for a depth camera obtained by imaging a flat surface at various depths.
+We found that the standard deviation of the pixel depth measurements had a large dependency on both the target depth and the pixel distance from the image optical center.
+A radius of $200$ pixels corresponds to the corners of the depth camera, which can be seen to have far larger noise than at the image center for a given depth.
+}
+\label{fig:Noise}
+\end{figure}

### 2015-05-01 datapaper_calibration.tex
Updates to datapaper_calibration.tex and datapaper_hardware.tex, as well as 2 figures.

@@
 
-The pixel depth measurements have significant noise.
-To characterize the noise variance at a particular depth we collected 300 images of a flat surface facing the camera at this depth and calculated the standard deviation at each pixel.
-We repeated this for increments of 10cm between 30cm and 90cm.
-At each depth we found that the pixel standard deviations were roughly constant at concentric circles around the optical center.
-Hence we can summarize the standard deviation as a function of pixel depth and pixel-radius around the optical center, as shown in Fig.~\ref{fig:Noise}.
-This captures a large fraction of the depth error for pixels on plant leafs, although additional sources of error include individual pixel biases, object specularities, strong variations in object albedo, mixed pixels on object edges, and very-low signal reflection.
+The time of flight depth measurements can have significant noise, and it is useful to both model it and quantify it.
+Doing so can lead to strategies to reduce noise as well as providing guidance to algorithms that use the depth measurements.
+Our goal in this section is to provide a simple noise model that can predict the empirically observed depth noise on smooth, Lambertian surfaces, such as plant leafs.
 
-In the recorded $3$D data we averaged five depth images for each record.
-Ideally this leads to reducing the standard deviation by $1/\sqrt{5}$, although the actual benefit is less as some sources of error are not reduced by averaging.
+The depth noise $\epsilon$ is modeled as the sum of two components, $\epsilon_I$ and $\epsilon_S$: 
+\begin{equation}
+	\epsilon = \epsilon_I + \epsilon_S\label{eq:epsilon}
+\end{equation}
+The term $\epsilon_I$ captures the noise component that varies between images taken from a fixed pose of a static scene.
+On the other hand the term $\epsilon_S$ models noise that is constant between images but varies between pixels.
+The variance of $\epsilon_I$ can be estimated by observing pixels of a fixed scene over multiple images.
+In our experiments we observed a flat, uniform albedo surface perpendicular to the camera at a sequence of depths, and for each depth acquiring 300 images.
+Object depth has a large impact on $\epsilon_I$ likely due to reduced reflected signal.
+For constant depth, we observed that the primary factor affecting the variance is the pixel radius from the image center.
+Physically we expect this dependence is due to a circularly symmetric illuminating beam closely aligned with the optical axis.
+Based on these observations $\sigma_I^2$, the variance of $\epsilon_I$, is empirically estimated as a function of object depth and pixel radius as shown in Fig.~\ref{fig:Noise}.
 
-Now we noticed that the chamber light shades blocked some of the depth camera field of view, and in doing so reflected some of the IR illumination.
-This resulted in an additional bias shift which we measured and removed from the depth data.
-% FIXME
+In addition to image-varying noise, there are pixel depth offsets that are constant for images of the same scene so cannot be removed by averaging over many frames.
+We model these with $\epsilon_S$.
+To estimate its variance, $\sigma_S^2$, we first average over many depth measurement images, in our case 300, to obtain pixel depth estimates that approximately eliminate the effect of $\epsilon_I$.
+Then by calculating true ray depths on a known surface, in our case the observed plane, and assuming that $\epsilon_S$ has the same distribution over all pixels, $\sigma_S^2$ is obtained as the variance of the error between averaged depths and known depths.
+In our experiments we obtained $\sigma_S=6.5mm$, and found that it was insensitive to changes in depth.
+
+Assuming independence of $\epsilon_I$ and $\epsilon_S$, the expected variance of depth measurements in the data collection can be obtained as follows.
+When $N$ images are averaged to obtain a depth image, where $N=5$ for our data collection, the depth variance is predicted to be:
+\begin{equation}
+	\sigma^2 = \frac{\sigma_I^2}{N} + \sigma_S^2.\label{eq:sigma}
+\end{equation}
+
+There are additional sources of noise not captured by this including object specularities, sharp variations in object albedo, mixed-depth pixels on object edges, and cases of very-low signal reflection.
+In addition we noticed that the chamber light shades blocked some of the depth camera field of view, and in doing so reflected some of the IR illumination.
+This resulted in a small constant depth shift for the pixels.
+We measured this shift for each chamber experiment and provide it as an optional correction to the depth images.
 

### 2015-05-01 datapaper_hardware.tex
Updates to datapaper_calibration.tex and datapaper_hardware.tex, as well as 2 figures.

@@
 \begin{figure}
-  \includegraphics[width=\linewidth,trim=50 230 45 300,clip]{Figures/CameraConfiguration}
-\caption{A plot of the three cameras showing their relative configuration and fields of view as obtained through calibration.
-Units are in $mm$.
-The optical center of the color camera (on the left) defines the world coordinate system.
-Close to it is the depth camera.
-Its points are projected into the world coordinate system.
-On the right is the combined fluorescent and IR camera.}
+\begin{tabular}{c}
+  \includegraphics[width=\linewidth,trim=50 200 45 250,clip]{Figures/CameraConfiguration} \\
+  ($a$)\\
+  \includegraphics[width=6cm,trim=100 200 100 200,clip]{Figures/DepthOnBeanRGB} \\
+  ($b$)\\
+\end{tabular}
+\caption{($a$)A plot of the three cameras showing their relative configuration and fields of view as obtained through calibration.
+Units are in $mm$, apart from the size of the images which are scaled and plotted at equal resolution.
+The optical center of the color camera (left-most) defines the world coordinate system.
+Close to it is the depth camera having much lower resolution.
+The right-most camera is the combined fluorescent and IR camera.
+($b$) $3$D points from the depth camera are projected along their rays into the world coordinates and then projected into the color and fluorescent camera images.
+This shows the projection into the color image.
+Only points in a rectangular region around the plant in the depth image are selected, and these are further filtered by eliminating points with high standard deviation.
+An algorithm requiring only $3$D points on the plant could select only those that fall on the leaf pixels.}
 \label{fig:CameraConfiguration}
@@
 In addition reflective surfaces at grazing angles are less reliably measured since little signal is reflected. 
-Hence in our data portions of the chamber floor visible in Figure~\ref{fig:CameraConfiguration} are highly reflective and have incorrect depths.  %FIXME
-Fortunately the primary goal of the depth measurements are to obtain leaf depths, and plants provide good, roughly Lambertian reflections of IR~\cite{Chelle2006219}.  
-Therefore for these reasons the non-leaf depth pixels in the $3$D depth data are unreliable and should be ignored in data analysis.  
-Another limitation is that the IR illuminator has a slight offset to the left of the sensor, which results in shadows to the right of some objects, as well as mixed pixels on depth discontinuities.  
-Both of these can be readily detected as large standard deviations in the depth image.
+Fortunately the primary goal of the depth measurements are to obtain leaf depths, and plants provide good, roughly Lambertian, reflections of IR~\cite{Chelle2006219}.
+Thus the depth pixels that are most reliable and are of most use are those that fall on plant foliage.
 
-The imagery data were collected once every hour. %taken within 10 minutes of each other.  %
+The imagery data were collected once every hour.
 These include the fluorescent image, the IR reflectance image with the same camera, the color image, the $3$D depth and a confidence image.  
@@
 This is useful for identifying pixels at depth discontinuities that are unreliably detected and result in large standard deviations.
-In addition pixels with no response or saturated pixels are assigned with the maximum standard deviation, and should be filtered out.
 
@@
 \caption{Noise analysis for a depth camera obtained by imaging a flat surface at various depths.
-We found that the standard deviation of the pixel depth measurements had a large dependency on both the target depth and the pixel distance from the image optical center.
-A radius of $200$ pixels corresponds to the corners of the depth camera, which can be seen to have far larger noise than at the image center for a given depth.
+We found that the standard deviation, $\sigma_I$ from Eq.
+(\ref{eq:sigma}) of the pixel depth measurements had a large dependency on both the target depth and the pixel distance from the image center, and these are plotted.
+A radius of $0$ pixels is the image center, and of $200$ pixels corresponds to the corners of the depth camera, which can be seen to have far larger standard deviation than at the image center for the same depth.
 }

### 2015-05-01 datapaper_baseline.tex
xm's first edits

@@
 Finally, we generate $2,880$ leaf templates.
-
-\begin{figure*}
-\centering
-\includegraphics[width=.98\textwidth]{Figures/performance}\\
-\caption{Performance of the baseline method.}
-\label{fig:performance}
-\end{figure*}
 
@@
 For overlapping leaves, it becomes more challenging as the edges between the overlapping area are more difficult to be detected. 
-However, when the overlapping leaves are further away from the center, they will have a higher chance to be detected as shown in $(3)$ of Fig.~\ref{fig:alignResult}. 
-When the overlapping leaves are close to the center, smaller leaves will be covered by larger leaves as shown in $(1), (4), (5)$ of Fig.~\ref{fig:alignResult}.
+However, when the overlapping leaves are further away from the center, they will have a higher chance to be detected as shown in $(3)$ of Figure~\ref{fig:alignResult}. 
+When the overlapping leaves are close to the center, smaller leaves will be covered by larger leaves as shown in $(1), (4), (5)$ of Figure~\ref{fig:alignResult}.
 
 Leaf alignment provides the leaf candidates for tracking over time. 
-One example of leaf tracking result is shown in Fig.~\ref{fig:trackExample}. 
+One example of leaf tracking result is shown in Figure~\ref{fig:trackExample}. 
 The leaf template transformation works well for most leaves. 
@@
 Leaves will be deleted when it becomes small and the leaf underneath it will be detected. 
-As shown in Fig,~\ref{}, leaf $X$ replace leaf $X$ at day $X$, which is considered as a tracking failure.
+As shown in Figure~\ref{}, leaf $X$ replace leaf $X$ at day $X$, which is considered as a tracking failure.
 
@@
 
-For quantitative evaluation, we vary $\tau$ from 0 to 1 and generate the first three evaluation metrics, as shown in Fig.~\ref{fig:performance}.
+\begin{figure*}
+\centering
+\includegraphics[width=.98\textwidth]{Figures/performance}\\
+\caption{Performance of the baseline method.}
+\label{fig:performance}
+\end{figure*}
+
+For quantitative evaluation, we vary $\tau$ from $0$ to $1$ and generate the first three evaluation metrics, as shown in Figure~\ref{fig:performance}.
 {\it{ULR}} decreases as $\tau$ increases as more leaves are being considered as matched leaves.  

### 2015-05-01 datapaper_calibration.tex
xm's first edits

@@
 In this process the poses of all three cameras are also calculated relative to the checkerboard.
-The intrinsic and extrinsic parameters are stored as text files, and a Matlab function is provided that reads the parameters and can plot the camera poses as in Fig.~\ref{fig:CameraConfiguration}.
+The intrinsic and extrinsic parameters are stored as text files, and a Matlab function is provided that reads the parameters and can plot the camera poses as in Figure~\ref{fig:CameraConfiguration}.
 
@@
 Physically we expect this dependence is due to a circularly symmetric illuminating beam closely aligned with the optical axis.
-Based on these observations $\sigma_I^2$, the variance of $\epsilon_I$, is empirically estimated as a function of object depth and pixel radius as shown in Fig.~\ref{fig:Noise}.
-
-In addition to image-varying noise, there are pixel depth offsets that are constant for images of the same scene so cannot be removed by averaging over many frames.
-We model these with $\epsilon_S$.
-To estimate its variance, $\sigma_S^2$, we first average over many depth measurement images, in our case 300, to obtain pixel depth estimates that approximately eliminate the effect of $\epsilon_I$.
-Then by calculating true ray depths on a known surface, in our case the observed plane, and assuming that $\epsilon_S$ has the same distribution over all pixels, $\sigma_S^2$ is obtained as the variance of the error between averaged depths and known depths.
-In our experiments we obtained $\sigma_S=6.5mm$, and found that it was insensitive to changes in depth.
-
-Assuming independence of $\epsilon_I$ and $\epsilon_S$, the expected variance of depth measurements in the data collection can be obtained as follows.
-When $N$ images are averaged to obtain a depth image, where $N=5$ for our data collection, the depth variance is predicted to be:
-\begin{equation}
-	\sigma^2 = \frac{\sigma_I^2}{N} + \sigma_S^2.\label{eq:sigma}
-\end{equation}
-
-There are additional sources of noise not captured by this including object specularities, sharp variations in object albedo, mixed-depth pixels on object edges, and cases of very-low signal reflection.
-In addition we noticed that the chamber light shades blocked some of the depth camera field of view, and in doing so reflected some of the IR illumination.
-This resulted in a small constant depth shift for the pixels.
-We measured this shift for each chamber experiment and provide it as an optional correction to the depth images.
-
-%\begin{figure}
-%\begin{centering}
-%\begin{tabular}{c }
-%\includegraphics[width=.47\textwidth]{Figures/rawImages/a.png}\\
-%Arabidopsis \\
-%\includegraphics[width=.47\textwidth]{Figures/rawImages/b.png}\\
-%   Bean \\
-%\end{tabular}
-%\caption{RGB color images of Arabidopsis and bean plants. }
-%\label{fig:rawIm}
-%\end{centering}
-%\end{figure}
+Based on these observations $\sigma_I^2$, the variance of $\epsilon_I$, is empirically estimated as a function of object depth and pixel radius as shown in Figure~\ref{fig:Noise}.
 
@@
 \end{table*}
+
+In addition to image-varying noise, there are pixel depth offsets that are constant for images of the same scene so cannot be removed by averaging over many frames.
+We model these with $\epsilon_S$.
+To estimate its variance, $\sigma_S^2$, we first average over many depth measurement images, in our case 300, to obtain pixel depth estimates that approximately eliminate the effect of $\epsilon_I$.
+Then by calculating true ray depths on a known surface, in our case the observed plane, and assuming that $\epsilon_S$ has the same distribution over all pixels, $\sigma_S^2$ is obtained as the variance of the error between averaged depths and known depths.
+In our experiments we obtained $\sigma_S=6.5mm$, and found that it was insensitive to changes in depth.
+
+Assuming independence of $\epsilon_I$ and $\epsilon_S$, the expected variance of depth measurements in the data collection can be obtained as follows.
+When $N$ images are averaged to obtain a depth image, where $N=5$ for our data collection, the depth variance is predicted to be:
+\begin{equation}
+	\sigma^2 = \frac{\sigma_I^2}{N} + \sigma_S^2.\label{eq:sigma}
+\end{equation}
+
+There are additional sources of noise not captured by this including object specularities, sharp variations in object albedo, mixed-depth pixels on object edges, and cases of very-low signal reflection.
+In addition we noticed that the chamber light shades blocked some of the depth camera field of view, and in doing so reflected some of the IR illumination.
+This resulted in a small constant depth shift for the pixels.
+We measured this shift for each chamber experiment and provide it as an optional correction to the depth images.
+
+%\begin{figure}
+%\begin{centering}
+%\begin{tabular}{c }
+%\includegraphics[width=.47\textwidth]{Figures/rawImages/a.png}\\
+%Arabidopsis \\
+%\includegraphics[width=.47\textwidth]{Figures/rawImages/b.png}\\
+%   Bean \\
+%\end{tabular}
+%\caption{RGB color images of Arabidopsis and bean plants. }
+%\label{fig:rawIm}
+%\end{centering}
+%\end{figure}

### 2015-05-01 datapaper_intro.tex
performance
xm's first edits

@@
 While many factors can be assessed quantitatively, which is essential for high-throughput study, one of the bottleneck in this research pipeline is plant visual phenotyping~\cite{walter2015plant}.
+
+\begin{figure*}
+\begin{centering}
+\begin{tabular}{@{}c c c c}
+%\begin{tabular}{lllllllll}
+\includegraphics[width=.23\textwidth]{Figures/FourModalities/A_rgb}&
+\includegraphics[width=.23\textwidth]{Figures/FourModalities/A_depth}&
+\includegraphics[width=.23\textwidth]{Figures/FourModalities/A_fmp}&
+\includegraphics[width=.23\textwidth]{Figures/FourModalities/A_ir}\\
+Arabidopsis: RGB &  Arabidopsis: Depth & Arabidopsis: Fluorescence & Arabidopsis: IR \\
+\includegraphics[width=.23\textwidth]{Figures/FourModalities/B_rgb}&
+\includegraphics[width=.23\textwidth]{Figures/FourModalities/B_depth}&
+\includegraphics[width=.23\textwidth]{Figures/FourModalities/B_fmp}&
+\includegraphics[width=.23\textwidth]{Figures/FourModalities/B_ir}\\
+Bean: RGB &  Bean: Depth & Bean: Fluorescence & Bean: IR \\
+\end{tabular}
+\caption{The multi-modality plant imagery database of MSU-PID. }
+\label{fig:fourmodality}
+\end{centering}
+\end{figure*}
 
@@
 To facilitate future research on plant image analysis, as well as remedy the limitation of existing databases in the field, this paper presents a newly collected multi-modality plant imagery database through an interdisciplinary effort at Michigan State University (MSU), termed ``MSU-PID''.
-The MSU-PID database includes the imagery of two types of plants (Arabidopsis and bean), both are widely used in plant research, captured by four types of imaging sensors, i.e., Fluorescence, infrared (IR), RGB color, and depth.
+As illustrated in Figure~\ref{fig:fourmodality}, the MSU-PID database includes the imagery of two types of plants (Arabidopsis and bean), both are widely used in plant research, captured by four types of imaging sensors, i.e., Fluorescence, infrared (IR), RGB color, and depth.
 All four sensors are synchronized and are programmed to periodically capture imagery data for multiple consecutive days.

### 2015-05-01 datapaper_intro.tex
revision by Jeff and Jin

@@
 
-With the rapid growth of world population  and the loss of arable land, there is an increasing desire to improve the yield and quality of crops, where the understanding of the genetic mechanisms to control plant growth is a key enabler~\cite{doos2002population}.
+With the rapid growth of world population  and the loss of arable land, there is an increasing desire to improve the yield and quality of crops, where the understanding of the genetic mechanisms to influence plant growth is a key enabler~\cite{doos2002population}.
 %
-For this purpose, plant scientists make various genetic mutant strains of plants, grow them either in  growth chambers with simulated environmental conditions or directly in the field, visually observe the plants during the growth period, and finally discover plant morphological or physiological patterns that tightly associate with key growth factors~\cite{houle2010phenomics}.
+A classic genetics approach is to produce a diverse population of mutant lines, grow them either in growth chambers with simulated environmental conditions or directly in the field, visually observe the plants during the growth period, and finally identify plant morphological or physiological patterns that tightly associate with key growth factors~\cite{houle2010phenomics}.
 %
@@
 In old days, plant phenotyping was conducted through manual visual observation~\cite{Erblichkeit1903}.
-Today, motivated by the increasing lower cost of imaging sensors and advances of computer vision technologies, image-based automatic plant visual phenotyping is quickly growing into a desirable and viable solution~\cite{cruz2015depi}.
+Today, motivated by the increasing lower cost and increasing diversity of imaging sensors and advances of computer vision technologies, image-based automatic plant visual phenotyping is quickly growing into a desirable and viable solution~\cite{furbank2011phenomics,cruz2015depi}.
 In this interdisciplinary field, scientists employ various imaging sensors to capture plants and design advanced algorithms to automatically analyze the captured plant imagery, with the purpose of raising testable biological hypotheses to solve the aforementioned problems.

### 2015-05-02 datapaper_baseline.tex
figure update

@@
 For overlapping leaves, it becomes more challenging as the edges between the overlapping area are more difficult to be detected.
-However, when the overlapping leaves are further away from the center, they will have a higher chance to be detected as shown in $(3)$ of Figure~\ref{fig:alignResult}. 
-When the overlapping leaves are close to the center, smaller leaves will be covered by larger leaves as shown in $(1), (4), (5)$ of Figure~\ref{fig:alignResult}.
+However, when the overlapping leaves are further away from the center, they will have a higher chance to be detected as shown in $(c)$ of Figure~\ref{fig:alignResult}.
+When the overlapping leaves are close to the center, smaller leaves will be covered by larger leaves as shown in $(a), (d), (e)$ of Figure~\ref{fig:alignResult}.
 
@@
 \includegraphics[width=.14\textwidth]{Figures/AlignPerformance/15_2}\\
-(1) & (2) & (3) & (4) & (5) & (6) \\
+(a) & (b) & (c) & (d) & (e) & (f) \\
 \end{tabular}
@@
 %\begin{tabular}{lllllllll}
-(1) &
-\includegraphics[width=.11\textwidth]{Figures/trackExample/1_1}&
-\includegraphics[width=.11\textwidth]{Figures/trackExample/1_2}&
-\includegraphics[width=.11\textwidth]{Figures/trackExample/1_3}&
-\includegraphics[width=.11\textwidth]{Figures/trackExample/1_4}&
-\includegraphics[width=.11\textwidth]{Figures/trackExample/1_5}&
-\includegraphics[width=.11\textwidth]{Figures/trackExample/1_6}&
-\includegraphics[width=.11\textwidth]{Figures/trackExample/1_7}&
-\includegraphics[width=.11\textwidth]{Figures/trackExample/1_8}&
-\includegraphics[width=.11\textwidth]{Figures/trackExample/1_9}\\
-(2)&
-\includegraphics[width=.11\textwidth]{Figures/trackExample/2_1}&
-\includegraphics[width=.11\textwidth]{Figures/trackExample/2_2}&
-\includegraphics[width=.11\textwidth]{Figures/trackExample/2_3}&
-\includegraphics[width=.11\textwidth]{Figures/trackExample/2_4}&
-\includegraphics[width=.11\textwidth]{Figures/trackExample/2_5}&
-\includegraphics[width=.11\textwidth]{Figures/trackExample/2_6}&
-\includegraphics[width=.11\textwidth]{Figures/trackExample/2_7}&
-\includegraphics[width=.11\textwidth]{Figures/trackExample/2_8}&
-\includegraphics[width=.11\textwidth]{Figures/trackExample/2_9}\\
-(3) &
-\includegraphics[width=.11\textwidth]{Figures/trackExample/3_9}&
-\includegraphics[width=.11\textwidth]{Figures/trackExample/3_9}&
-\includegraphics[width=.11\textwidth]{Figures/trackExample/3_9}&
-\includegraphics[width=.11\textwidth]{Figures/trackExample/3_9}&
-\includegraphics[width=.11\textwidth]{Figures/trackExample/3_9}&
-\includegraphics[width=.11\textwidth]{Figures/trackExample/3_9}&
-\includegraphics[width=.11\textwidth]{Figures/trackExample/3_9}&
-\includegraphics[width=.11\textwidth]{Figures/trackExample/3_9}&
-\includegraphics[width=.11\textwidth]{Figures/trackExample/3_9}\\
+(a) &
+\includegraphics[trim= 10 100 20 100, clip, width=.1\textwidth]{Figures/trackExample/1_1}&
+\includegraphics[trim= 50 150 100 200, clip, width=.1\textwidth]{Figures/trackExample/1_2}&
+\includegraphics[trim= 50 150 100 200, clip, width=.1\textwidth]{Figures/trackExample/1_3}&
+\includegraphics[trim= 50 150 100 200, clip, width=.1\textwidth]{Figures/trackExample/1_4}&
+\includegraphics[trim= 50 150 100 200, clip, width=.1\textwidth]{Figures/trackExample/1_5}&
+\includegraphics[trim= 50 150 100 200, clip, width=.1\textwidth]{Figures/trackExample/1_6}&
+\includegraphics[trim= 50 150 100 200, clip, width=.1\textwidth]{Figures/trackExample/1_7}&
+\includegraphics[trim= 50 150 100 200, clip, width=.1\textwidth]{Figures/trackExample/1_8}&
+\includegraphics[trim= 0 100 20 100, clip, width=.1\textwidth]{Figures/trackExample/1_9}\\
+(b)&
+\includegraphics[width=.1\textwidth]{Figures/trackExample/2_1}&
+\includegraphics[width=.1\textwidth]{Figures/trackExample/2_2}&
+\includegraphics[width=.1\textwidth]{Figures/trackExample/2_3}&
+\includegraphics[width=.1\textwidth]{Figures/trackExample/2_4}&
+\includegraphics[width=.1\textwidth]{Figures/trackExample/2_5}&
+\includegraphics[width=.1\textwidth]{Figures/trackExample/2_6}&
+\includegraphics[width=.1\textwidth]{Figures/trackExample/2_7}&
+\includegraphics[width=.1\textwidth]{Figures/trackExample/2_8}&
+\includegraphics[width=.1\textwidth]{Figures/trackExample/2_9}\\
+(c) &
+\includegraphics[width=.1\textwidth]{Figures/trackExample/3_9}&
+\includegraphics[width=.1\textwidth]{Figures/trackExample/3_9}&
+\includegraphics[width=.1\textwidth]{Figures/trackExample/3_9}&
+\includegraphics[width=.1\textwidth]{Figures/trackExample/3_9}&
+\includegraphics[width=.1\textwidth]{Figures/trackExample/3_9}&
+\includegraphics[width=.1\textwidth]{Figures/trackExample/3_9}&
+\includegraphics[width=.1\textwidth]{Figures/trackExample/3_9}&
+\includegraphics[width=.1\textwidth]{Figures/trackExample/3_9}&
+\includegraphics[width=.1\textwidth]{Figures/trackExample/3_9}\\
 
@@
 \centering
-\includegraphics[width=.98\textwidth]{Figures/performance}\\
+\includegraphics[width=.98\textwidth]{Figures/performance.pdf}\\
 \caption{Performance of the baseline method.}
@@
 {\it{TC}} increases as $\tau$ increases as more leaves are being considered as correctly tracked leaves.
-Overall, our method can detect $80\%$ and track $60\%$ of all labeled leaves with $XX$ average tip-based errors.
+Overall, our method can detect $87\%$ and track $50\%$ of all labeled leaves with less than $20\%$ average tip-based errors.
 
 We generate a label image for each frame based on the leaf segmentation results anc compute the {\it{SBD}} score for each labeled image.
-The average {\it{SBD}} over all images is $0.59$.
+The average {\it{SBD}} over all images is $0.61$.

### 2015-05-02 datapapr_labeling.tex
baseline
xm's first edits
figure update

@@
 
-We use fluorescence images for labeling because of their simple background.
+We use the fluorescence images as the input for labeling because of their simple and uniform background.
 For Arabidopsis images, we label $4$ frames each day.
@@
 \end{figure*}
-
-The labeling of leaf tips is implemented by clicking pairs of points on the image.
-The outer tip is always clicked first before the inner tip.
-For visualization, a line connecting each pair of tips will be shown immediately after clicking the inner tip.
-Inaccurate labels can be deleted by clicking the right button of the mouse near the labeled point and relabeled by clicking the left button again.
-
-The labeling of the leaf segment is implemented by clicking the boundary of one leaf at each time.
-The labeled leaf boundary is overlaid on the image for better visualization to guide the next action.
-Incorrect label can be deleted right after the labeling.
-This process continues until all leaf segments have been annotated.
-After the labeling of one plant, we visually go through the results and correct inaccurate labels.
-Note that one alternative approach for labeling leaf segments is to directly label the membership of superpixels instead of drawing a polygon along the boundary.
-Our experience is that since a noticeable percentage of extracted superpixels cover pixels of two neighboring leaves, the extra effort of breaking a superpixel into two makes it a less efficient alternative.
-One example of the labeling results for one plant is shown in Figure~\ref{fig:LabelExample}, where one color is used to represent each specific leaf.
-As we can see during the transition between day $4$ and day $5$, there is one leaf showing up and covering up the leaf underneath, which disappears and will not be annotated later.
 
@@
 
+The labeling of leaf tips is implemented by clicking pairs of points on the image.
+The outer tip is always clicked first before the inner tip.
+For visualization, a line connecting each pair of tips will be shown immediately after clicking the inner tip.
+Inaccurate labels can be deleted by clicking the right button of the mouse near the labeled point and relabeled by clicking the left button again.
+
+The labeling of the leaf segment is implemented by clicking the boundary of one leaf at each time.
+In order to provide more accuracy labeling, we click very dense points ($\sim20$ points on average) on the boundary. 
+The labeled leaf boundary is overlaid on the image for better visualization to guide the next action.
+Incorrect label can be deleted right after the labeling.
+This process continues until all leaf segments have been annotated.
+After the labeling of one plant, we visually go through the results and correct inaccurate labels.
+One example of the labeling results for one plant is shown in Figure~\ref{fig:LabelExample}, where one color is used to represent each specific leaf.
+As we can see during the transition between day $4$ and day $5$, there is one leaf showing up and covering up the leaf underneath, which disappears and will not be annotated later.
+In total, we labeled $5142$ leaves.
+
+Note that one alternative approach for labeling leaf segments is to directly label the membership of superpixels instead of drawing a polygon along the boundary.
+Our experience is that since a noticeable percentage of extracted superpixels cover pixels of two neighboring leaves, the extra effort of breaking a superpixel into two makes it a less efficient alternative.
+
 \subsection{Name conventions and file types}
@@
 The files in each subfolder have the following form:
+
 \begin{itemize}
-  \item plant$\_$XX$\_$day$\_$X$\_$hour$\_$YY$\_$ID$\_$ZZ$\_$rgb.png: the original RGB color images;
-  \item plant$\_$XX$\_$day$\_$X$\_$hour$\_$YY$\_$ID$\_$ZZ$\_$fmp.png: the original fluorescence images;
-  \item plant$\_$XX$\_$day$\_$X$\_$hour$\_$YY$\_$ID$\_$ZZ$\_$ir.png: the original IR images;
-  \item plant$\_$XX$\_$day$\_$X$\_$hour$\_$YY$\_$ID$\_$ZZ$\_$depth.png: the original depth images;
-  \item plant$\_$XX$\_$day$\_$X$\_$hour$\_$YY$\_$ID$\_$ZZ$\_$label.png: the labeled images of fluorescence modality;
-  \item plant$\_$XX$\_$day$\_$X$\_$hour$\_$YY$\_$ID$\_$ZZ$\_$tips.txt: the labeled tip locations;
+  \item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$rgb.png: the original RGB color images;
+  \item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$fmp.png: the original fluorescence images;
+  \item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$ir.png: the original IR images;
+  \item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$depth.png: the original depth images;
+  \item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$label.png: the labeled images of fluorescence modality;
+  \item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$tips.txt: the labeled tip locations;
 \end{itemize}
-where XX indicates the plant type ("AR" or "BE"), X is an integer indicating the date (e.g., $1-9$ for Arabidopsis), YY represents the image index within a day (e.g., $1-16$ for Arabidopsis), and ZZ is the subject (or plant) ID (e.g., $1-5$ for bean).
+where ID indicates the plant ID number ($1$ to $16$ for Arabidopsis, $1$ to $5$ for bean), X is an integer indicating the date ($1-9$ for Arabidopsis, $1$ to $5$ for bean), and YY represents the image index within a day ($1-16$ for Arabidopsis, $1$ to $14$ for bean).
 For each combination of day and hour, we provide four modalities in PNG files ($\_$rgb, $\_$fmp, $\_$ir, $\_$depth).
+%\begin{itemize}
+%  \item plant$\_$XX$\_$day$\_$X$\_$hour$\_$YY$\_$ID$\_$ZZ$\_$rgb.png: the original RGB color images;
+%  \item plant$\_$XX$\_$day$\_$X$\_$hour$\_$YY$\_$ID$\_$ZZ$\_$fmp.png: the original fluorescence images;
+%  \item plant$\_$XX$\_$day$\_$X$\_$hour$\_$YY$\_$ID$\_$ZZ$\_$ir.png: the original IR images;
+%  \item plant$\_$XX$\_$day$\_$X$\_$hour$\_$YY$\_$ID$\_$ZZ$\_$depth.png: the original depth images;
+%  \item plant$\_$XX$\_$day$\_$X$\_$hour$\_$YY$\_$ID$\_$ZZ$\_$label.png: the labeled images of fluorescence modality;
+%  \item plant$\_$XX$\_$day$\_$X$\_$hour$\_$YY$\_$ID$\_$ZZ$\_$tips.txt: the labeled tip locations;
+%\end{itemize}
+%where XX indicates the plant type ("AR" or "BE"), X is an integer indicating the date (e.g., $1-9$ for Arabidopsis), YY represents the image index within a day (e.g., $1-16$ for Arabidopsis), and ZZ is the subject (or plant) ID (e.g., $1-5$ for bean).
+%For each combination of day and hour, we provide four modalities in PNG files ($\_$rgb, $\_$fmp, $\_$ir, $\_$depth).
 For annotated images, we have two additional files ($\_$label, $\_$tips) saving the annotation results.
 Leaf segmentation results are encoded as indexed PNG files, where each leaf is assigned a unique and consistent leaf ID over time.
-Leaf ID starts from $1$ and continuously increase till the totoal number of leaves.
+Leaf ID starts from $1$ and continuously increase till the total number of leaves.
 And the background is encoded as $0$.
@@
 \subsection{Experimental Protocols}
-
 As shown in Table~\ref{tab:database}, MSU-PID can be used for applications such as leaf segmentation, leaf alignment, leaf tracking, and leaf counting.
@@
 Specifically, $6$ plants of Arabidopisis and $2$ plants of bean are selected for training.
-We will provide training and testing data in different folders.
+%We will provide training and testing data in different folders.
 For fair comparison, both supervised learning and unsupervised learning methods should evaluate their performances on the training and testing sets separately.

### 2015-05-02 datapaper_baseline.tex
baseline

@@
 (a) &
-\includegraphics[trim= 10 100 20 100, clip, width=.1\textwidth]{Figures/trackExample/1_1}&
-\includegraphics[trim= 50 150 100 200, clip, width=.1\textwidth]{Figures/trackExample/1_2}&
-\includegraphics[trim= 50 150 100 200, clip, width=.1\textwidth]{Figures/trackExample/1_3}&
-\includegraphics[trim= 50 150 100 200, clip, width=.1\textwidth]{Figures/trackExample/1_4}&
-\includegraphics[trim= 50 150 100 200, clip, width=.1\textwidth]{Figures/trackExample/1_5}&
-\includegraphics[trim= 50 150 100 200, clip, width=.1\textwidth]{Figures/trackExample/1_6}&
-\includegraphics[trim= 50 150 100 200, clip, width=.1\textwidth]{Figures/trackExample/1_7}&
-\includegraphics[trim= 50 150 100 200, clip, width=.1\textwidth]{Figures/trackExample/1_8}&
-\includegraphics[trim= 0 100 20 100, clip, width=.1\textwidth]{Figures/trackExample/1_9}\\
+\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/1_1}&
+\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/1_2}&
+\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/1_3}&
+\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/1_4}&
+\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/1_5}&
+\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/1_6}&
+\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/1_7}&
+\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/1_8}&
+\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/1_9}\\
 (b)&
-\includegraphics[width=.1\textwidth]{Figures/trackExample/2_1}&
-\includegraphics[width=.1\textwidth]{Figures/trackExample/2_2}&
-\includegraphics[width=.1\textwidth]{Figures/trackExample/2_3}&
-\includegraphics[width=.1\textwidth]{Figures/trackExample/2_4}&
-\includegraphics[width=.1\textwidth]{Figures/trackExample/2_5}&
-\includegraphics[width=.1\textwidth]{Figures/trackExample/2_6}&
-\includegraphics[width=.1\textwidth]{Figures/trackExample/2_7}&
-\includegraphics[width=.1\textwidth]{Figures/trackExample/2_8}&
-\includegraphics[width=.1\textwidth]{Figures/trackExample/2_9}\\
+\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/2_1}&
+\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/2_2}&
+\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/2_3}&
+\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/2_4}&
+\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/2_5}&
+\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/2_6}&
+\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/2_7}&
+\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/2_8}&
+\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/2_9}\\
 (c) &
-\includegraphics[width=.1\textwidth]{Figures/trackExample/3_9}&
-\includegraphics[width=.1\textwidth]{Figures/trackExample/3_9}&
-\includegraphics[width=.1\textwidth]{Figures/trackExample/3_9}&
-\includegraphics[width=.1\textwidth]{Figures/trackExample/3_9}&
-\includegraphics[width=.1\textwidth]{Figures/trackExample/3_9}&
-\includegraphics[width=.1\textwidth]{Figures/trackExample/3_9}&
-\includegraphics[width=.1\textwidth]{Figures/trackExample/3_9}&
-\includegraphics[width=.1\textwidth]{Figures/trackExample/3_9}&
-\includegraphics[width=.1\textwidth]{Figures/trackExample/3_9}\\
+\includegraphics[trim= 110 100 170 10, clip, width=.1\textwidth]{Figures/trackExample/3_1.pdf}&
+\includegraphics[trim= 110 100 170 10, clip, width=.1\textwidth]{Figures/trackExample/3_2.pdf}&
+\includegraphics[trim= 110 100 170 10, clip, width=.1\textwidth]{Figures/trackExample/3_3.pdf}&
+\includegraphics[trim= 110 100 170 10, clip, width=.1\textwidth]{Figures/trackExample/3_4.pdf}&
+\includegraphics[trim= 110 100 170 10, clip, width=.1\textwidth]{Figures/trackExample/3_5.pdf}&
+\includegraphics[trim= 110 100 170 10, clip, width=.1\textwidth]{Figures/trackExample/3_6.pdf}&
+\includegraphics[trim= 110 100 170 10, clip, width=.1\textwidth]{Figures/trackExample/3_7.pdf}&
+\includegraphics[trim= 110 100 170 10, clip, width=.1\textwidth]{Figures/trackExample/3_8.pdf}&
+\includegraphics[trim= 110 100 170 10, clip, width=.1\textwidth]{Figures/trackExample/3_9.pdf}\\
 

### 2015-05-02 datapaper_baseline.tex
figure update

@@
 Leaf alignment provides the leaf candidates for tracking over time.
-One example of leaf tracking result is shown in Figure~\ref{fig:trackExample}.
-The leaf template transformation works well for most leaves.
+Figure~\ref{fig:trackExample} shows one leaf tracking result. 
+The leaf template transformation works well for most of the leaves.
 As plant grows, younger leaves may grow faster than older leaves and occlude the older leaves.
-Our backward tracking algorithm tracks leaves from last frame to first frame.
-Leaves will be deleted when it becomes small and the leaf underneath it will be detected.
-As shown in Figure~\ref{}, leaf $X$ replace leaf $X$ at day $X$, which is considered as a tracking failure.
+As shown in Fig.~\ref{fig:trackExample} (b), purple leaf replaces the red leaf at day $6$.
+Our backward tracking algorithm tracks leaves from the last frame to the first frame.
+The two leaves are still being considered as one leaf (ID $8$) in day $4$ and day $3$. 
+Leaf $8$ in day $1$ and $2$ is considered as leaf ID switch and will be not count as consistently tracked leaf. 
+However, it is still been considered as well aligned and segmented leaves. 
+%Leaves will be deleted when it becomes small and the leaf underneath it will be detected.
 
@@
 
-\includegraphics[width=.14\textwidth]{Figures/AlignPerformance/9_2}&
-\includegraphics[width=.14\textwidth]{Figures/AlignPerformance/10_2}&
-\includegraphics[width=.14\textwidth]{Figures/AlignPerformance/11_2}&
-\includegraphics[width=.14\textwidth]{Figures/AlignPerformance/12_2}&
-\includegraphics[width=.14\textwidth]{Figures/AlignPerformance/14_2}&
-\includegraphics[width=.14\textwidth]{Figures/AlignPerformance/15_2}\\
+\includegraphics[trim= 90 60 100 5, clip, width=.14\textwidth]{Figures/AlignPerformance/9_2}&
+\includegraphics[trim= 90 60 100 5, clip, width=.14\textwidth]{Figures/AlignPerformance/10_2}&
+\includegraphics[trim= 90 60 100 5, clip, width=.14\textwidth]{Figures/AlignPerformance/11_2}&
+\includegraphics[trim= 90 60 100 5, clip, width=.14\textwidth]{Figures/AlignPerformance/12_2}&
+\includegraphics[trim= 90 60 100 5, clip, width=.14\textwidth]{Figures/AlignPerformance/14_2}&
+\includegraphics[trim= 90 60 100 5, clip, width=.14\textwidth]{Figures/AlignPerformance/15_2}\\
 (a) & (b) & (c) & (d) & (e) & (f) \\
 \end{tabular}
-\caption{Leaf alignment results on the last frame of $6$ plant videos. First row shows the original image. Second row shows the alignment result. }
+\caption{Leaf alignment results on the last frame of $6$ plant videos.
+First row shows the original image.
+Second row shows the alignment result with red points denote the boundary of the leaf templates in the blue bounding boxes.
+The numbers on the leaves are the leaf IDs representing the order of the leaf being selected and they will be consistent during tracking.}
 \label{fig:alignResult}
@@
 (c) &
-\includegraphics[trim= 110 100 170 10, clip, width=.1\textwidth]{Figures/trackExample/3_1.pdf}&
-\includegraphics[trim= 110 100 170 10, clip, width=.1\textwidth]{Figures/trackExample/3_2.pdf}&
-\includegraphics[trim= 110 100 170 10, clip, width=.1\textwidth]{Figures/trackExample/3_3.pdf}&
-\includegraphics[trim= 110 100 170 10, clip, width=.1\textwidth]{Figures/trackExample/3_4.pdf}&
-\includegraphics[trim= 110 100 170 10, clip, width=.1\textwidth]{Figures/trackExample/3_5.pdf}&
-\includegraphics[trim= 110 100 170 10, clip, width=.1\textwidth]{Figures/trackExample/3_6.pdf}&
-\includegraphics[trim= 110 100 170 10, clip, width=.1\textwidth]{Figures/trackExample/3_7.pdf}&
-\includegraphics[trim= 110 100 170 10, clip, width=.1\textwidth]{Figures/trackExample/3_8.pdf}&
-\includegraphics[trim= 110 100 170 10, clip, width=.1\textwidth]{Figures/trackExample/3_9.pdf}\\
+\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_1.pdf}&
+\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_2.pdf}&
+\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_3.pdf}&
+\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_4.pdf}&
+\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_5.pdf}&
+\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_6.pdf}&
+\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_7.pdf}&
+\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_8.pdf}&
+\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_9.pdf}\\
 
@@
 
-For quantitative evaluation, we vary $\tau$ from $0$ to $1$ and generate the first three evaluation metrics, as shown in Figure~\ref{fig:performance}.
+For quantitative evaluation, we vary $\tau$ from $0$ to $1$ and generate the first three evaluation metrics, as shown in Fig.~\ref{fig:performance}.
 {\it{ULR}} decreases as $\tau$ increases as more leaves are being considered as matched leaves.
-As $\tau$ keep increasing, {\it{ULR}} approaches a constant value, which is the the diferent number in leaf counting that results from both miss detection and false alarms.
+As $\tau$ keep increasing, {\it{ULR}} approaches a constant value, which is the the different number in leaf counting that results from both miss detection and false alarms.
 {\it{LE}} increases as $\tau$ increases as it includes leaves with larger tip-based errors for averaging.
 {\it{TC}} increases as $\tau$ increases as more leaves are being considered as correctly tracked leaves.
+Note that {\it{TC}} is influenced by the length of frames evaluated for each video. 
+As the longer frames we evaluate, the higher chance tracking will be failed. 
 Overall, our method can detect $87\%$ and track $50\%$ of all labeled leaves with less than $20\%$ average tip-based errors.

### 2015-05-02 datapaper_baseline.tex
grammer and typos

@@
 {\it{ULR}} decreases as $\tau$ increases as more leaves are being considered as matched leaves.
-As $\tau$ keep increasing, {\it{ULR}} approaches a constant value, which is the the different number in leaf counting that results from both miss detection and false alarms.
+As $\tau$ keep increasing, {\it{ULR}} approaches a constant value, which is the different number in leaf counting that results from both miss detection and false alarms.
 {\it{LE}} increases as $\tau$ increases as it includes leaves with larger tip-based errors for averaging.
@@
 
-We generate a label image for each frame based on the leaf segmentation results anc compute the {\it{SBD}} score for each labeled image.
+We generate a label image for each frame based on the leaf segmentation results and compute the {\it{SBD}} score for each labeled image.
 The average {\it{SBD}} over all images is $0.61$.

### 2015-05-02 datapaper_intro.tex
grammer and typos

@@
 & & & & Classe \# & Image \# & Image \# \\ \hline
-
 Swedish leaf & Scaned leaf & LC& Swedish trees & $15$ & $1,125$ & $1,125$ \\ \hline
@@
 
-The type and amount of manual labels on a datatbase is a critical enabler to the potential applications of the database.
+The type and amount of manual labels on a database is a critical enabler to the potential applications of the database.
 For a subset of the MSU-PID database, we manually label the ground truth regarding the leaf identification number, locations of leaf tips and leaf segments.

### 2015-05-02 datapapr_labeling.tex
grammer and typos

@@
 MSU-PID includes two subsets, one for each plant type: Arabidopsis and Bean.
-The statistic information of these two subsets are summarised in Table~\ref{tab:stat}.
+The statistic information of these two subsets are summarized in Table~\ref{tab:stat}.
 The images were acquired every hour.
@@
 Note that one alternative approach for labeling leaf segments is to directly label the membership of superpixels instead of drawing a polygon along the boundary.
-Our experience is that since a noticeable percentage of extracted superpixels cover pixels of two neighboring leaves, the extra effort of breaking a superpixel into two makes it a less efficient alternative.
+Our experience is that since a noticeable percentage of extracted superpixels cover pixels of two neighboring leaves. 
+The extra effort of breaking a super pixel into two makes it a less efficient alternative.
 
@@
 Note that the annotation is provided based on fluorescence images.
-In order to evaluate methods developed on other modalities, we provide image mapping functions between every two modalities.
+In order to evaluate methods developed on other modalities, we provide image-mapping functions between every two modalities.
 The total storage of our database is around $XX Mb$, which is convenient for downloading via Internet.
@@
 $40\%$ of the data is used for training and $60\%$ for testing.
-Specifically, $6$ plants of Arabidopisis and $2$ plants of bean are selected for training.
+Specifically, $6$ plants of Arabidopsis and $2$ plants of bean are selected for training.
 %We will provide training and testing data in different folders.
@@
 The Matlab function for computing {\it{SBD}} is provided by~\cite{scharr2014annotated}.
-The instruction on how to use the evaluation functions are included as comments of the function.
+The instructions on how to use the evaluation functions are included as comments of the function.
 

### 2015-05-02 datapaper.tex
xm's first edits

@@
 \usepackage[misc,geometry]{ifsym}
+\usepackage{threeparttable}
 
@@
 \begin{abstract}
-Insert your abstract here. Include keywords, PACS and mathematical
-subject classification numbers as needed.
-Insert your abstract here. Include keywords, PACS and mathematical
-subject classification numbers as needed.
-Insert your abstract here. Include keywords, PACS and mathematical
-subject classification numbers as needed.
-Insert your abstract here. Include keywords, PACS and mathematical
-subject classification numbers as needed.
-Insert your abstract here. Include keywords, PACS and mathematical
-subject classification numbers as needed.
-Insert your abstract here. Include keywords, PACS and mathematical
-subject classification numbers as needed.
-Insert your abstract here. Include keywords, PACS and mathematical
-subject classification numbers as needed.
-Insert your abstract here. Include keywords, PACS and mathematical
-subject classification numbers as needed.
-Insert your abstract here. Include keywords, PACS and mathematical
-subject classification numbers as needed.
+
+Among many applications of machine vision, plant image analysis has recently begin to gain attention due to its potential impact on plant visual phenotyping, particularly in understanding plant growth, assessing the quality/performance of crop plants and improving crop yield.
+Despite its importance, the lack of publicly available research databases containing plant imagery has substantially hindered the advancement of plant image analysis.
+To alleviate this issue, this paper presents a new multi-modality plant imagery database named ``MSU-PID'', with two distinct properties.
+First, MSU-PID is captured using four types of imaging sensors, Fluorescence, infrared (IR), RGB color, and depth.
+Second, the imaging setup and the variety of manual labels allow MSU-PID to be suitable for a diverse set of plant image analysis applications, such as leaf segmentation, leaf counting, leaf alignment, and leaf tracking.
+We provide detailed information on the plants, imaging sensors, calibration, labeling, and baseline performances of this new database.
+%
+%Among many applications of machine vision, plant image analysis has recently begin to gain attentions due to its potential huge impact to plant visual phenotyping, the understanding of plant growth, the quality of crops, and the improvement of the yield.
+%Despite its importance, the pack of publicly available research database of plant imagery has substantially hindered the advancement of plant image analysis.
+%To alleviate this issue, this paper presents a new multi-modality plant imagery database named ``MSU-PID'', with two distinct properties.
+%First, MSU-PID is captured using four types of imaging sensors, Fluorescence, infrared (IR), RGB color, and depth.
+%Second, the imaging setup and the variety of manual labels allow MSU-PID to be suitable for a diverse set of plant image analysis applications, such as leaf segmentation, leaf counting, leaf alignment, and leaf tracking.
+%We provide detailed information on the plants, imaging sensors, calibration, labeling, and baseline performances of this new database.
 

### 2015-05-02 datapaper_baseline.tex

@@
 As plant grows, younger leaves may grow faster than older leaves and occlude the older leaves.
-As shown in Fig.~\ref{fig:trackExample} (b), purple leaf replaces the red leaf at day $6$.
+As shown in Figure ~\ref{fig:trackExample} (b), purple leaf replaces the red leaf at day $6$.
 Our backward tracking algorithm tracks leaves from the last frame to the first frame.
@@
 
-For quantitative evaluation, we vary $\tau$ from $0$ to $1$ and generate the first three evaluation metrics, as shown in Fig.~\ref{fig:performance}.
+For quantitative evaluation, we vary $\tau$ from $0$ to $1$ and generate the first three evaluation metrics, as shown in Figure ~\ref{fig:performance}.
 {\it{ULR}} decreases as $\tau$ increases as more leaves are being considered as matched leaves.

### 2015-05-02 datapaper_hardware.tex

@@
 \begin{figure}
-  \includegraphics[width=0.93\linewidth,trim=50 80 200 70,clip]{Figures/hardware}
+  \includegraphics[width=\linewidth,trim=55 80 200 70,clip]{Figures/hardware}
 \caption{The hardware setup for our data collection.}
@@
 
-% For one-column wide figures use
-\begin{figure}
-\begin{tabular}{c}
-  \includegraphics[width=\linewidth,trim=50 200 45 250,clip]{Figures/CameraConfiguration} \\
-  ($a$)\\
-  \includegraphics[width=6cm,trim=100 200 100 200,clip]{Figures/DepthOnBeanRGB} \\
-  ($b$)\\
-\end{tabular}
-\caption{($a$)A plot of the three cameras showing their relative configuration and fields of view as obtained through calibration.
-Units are in $mm$, apart from the size of the images which are scaled and plotted at equal resolution.
-The optical center of the color camera (left-most) defines the world coordinate system.
-Close to it is the depth camera having much lower resolution.
-The right-most camera is the combined fluorescent and IR camera.
-($b$) $3$D points from the depth camera are projected along their rays into the world coordinates and then projected into the color and fluorescent camera images.
-This shows the projection into the color image.
-Only points in a rectangular region around the plant in the depth image are selected, and these are further filtered by eliminating points with high standard deviation.
-An algorithm requiring only $3$D points on the plant could select only those that fall on the leaf pixels.}
-\label{fig:CameraConfiguration}
-\end{figure}
-
 \subsubsection{RGB color and depth images} %This section describes characterizes the data from this sensor, particularly the depth data.
@@
 Thus the depth pixels that are most reliable and are of most use are those that fall on plant foliage.
+
+% For one-column wide figures use
+\begin{figure}
+\begin{tabular}{c}
+  \includegraphics[width=\linewidth,trim=60 200 45 250,clip]{Figures/CameraConfiguration} \\
+  ($a$)\\
+  \includegraphics[width=0.65\linewidth,trim=175 220 162 180, clip,angle=-90,origin=c]{Figures/DepthOnBeanRGB} \vspace{-10mm} \\ 
+  ($b$)\\
+\end{tabular}
+\caption{($a$)A plot of the three cameras showing their relative configuration and fields of view as obtained through calibration.
+Units are in $mm$, apart from the size of the images which are scaled and plotted at equal resolution.
+The optical center of the color camera (left-most) defines the world coordinate system.
+Close to it is the depth camera having much lower resolution.
+The right-most camera is the combined fluorescent and IR camera.
+($b$) $3$D points from the depth camera are projected along their rays into the world coordinates and then projected into the color and fluorescent camera images.
+This shows the projection into the color image (with $90^{\circ}$ rotation for economical use of space).
+Only points in a rectangular region around the plant in the depth image are selected, and these are further filtered by eliminating points with high standard deviation.
+An algorithm requiring only $3$D points on the plant could select only those that fall on the leaf pixels.}
+\label{fig:CameraConfiguration}
+\end{figure}
 

### 2015-05-03 datapaper_calibration.tex
depth_resolution
grammer and typos
Updates to calibration

@@
 The term $\epsilon_I$ captures the noise component that varies between images taken from a fixed pose of a static scene.
-On the other hand the term $\epsilon_S$ models noise that is constant between images but varies between pixels.
-The variance of $\epsilon_I$ can be estimated by observing pixels of a fixed scene over multiple images.
-In our experiments we observed a flat, uniform albedo surface perpendicular to the camera at a sequence of depths, and for each depth acquiring 300 images.
-Object depth has a large impact on $\epsilon_I$ likely due to reduced reflected signal.
-For constant depth, we observed that the primary factor affecting the variance is the pixel radius from the image center.
+On the other hand the term $\epsilon_S$ models noise is constant between images but varies between pixels.
+The variance of $\epsilon_I$ is estimated for each pixel of a fixed scene observed over multiple images.
+In our experiments we observed a flat, uniform albedo surface perpendicular to the camera at a sequence of depths, and for each depth acquired 300 images.
+Object depth, $d$, has a large impact on $\epsilon_I$ likely due to reduced reflected signal.
+For constant depth, we observed that the primary factor affecting the variance is the pixel radius, $r$, from the image center.
 Physically we expect this dependence is due to a circularly symmetric illuminating beam closely aligned with the optical axis.
-Based on these observations $\sigma_I^2$, the variance of $\epsilon_I$, is empirically estimated as a function of object depth and pixel radius as shown in Figure~\ref{fig:Noise}.
+Based on these observations we model $\sigma_I^2(d,r)$ the variance of $\epsilon_I$, as a function of depth and pixel radius.
+From our experiments we build up a lookup table for this as plotted in Figure~\ref{fig:Noise}.
 
@@
 \hline
-      Arabidopsis &  $\sim$$240\times240$ &  $\sim$$240\times240$  & $\sim$$120\times120$  & NA  \\
+Arabidopsis & $\sim$$240\times240$ & $\sim$$240\times240$ & $\sim$$120\times120$ & $\sim$$25\times25$ \\
 %\hline
@@
 
-In addition to image-varying noise, there are pixel depth offsets that are constant for images of the same scene so cannot be removed by averaging over many frames.
+In addition to repeated-image-varying noise, there are pixel depth offsets that are constant for images of the same scene, and so cannot be removed by averaging over many frames.
 We model these with $\epsilon_S$.
 To estimate its variance, $\sigma_S^2$, we first average over many depth measurement images, in our case 300, to obtain pixel depth estimates that approximately eliminate the effect of $\epsilon_I$.
-Then by calculating true ray depths on a known surface, in our case the observed plane, and assuming that $\epsilon_S$ has the same distribution over all pixels, $\sigma_S^2$ is obtained as the variance of the error between averaged depths and known depths.
+Then by calculating true ray depths on a known surface, in our case the observed plane, and assuming that $\epsilon_S$ has the same distribution over all pixels, $\sigma_S$ is obtained as the standard deviation of the error between averaged depths and known depths.
 In our experiments we obtained $\sigma_S=6.5mm$, and found that it was insensitive to changes in depth.
 
-Assuming independence of $\epsilon_I$ and $\epsilon_S$, the expected variance of depth measurements in the data collection can be obtained as follows.
-When $N$ images are averaged to obtain a depth image, where $N=5$ for our data collection, the depth variance is predicted to be:
+The recorded depth images in the data collection are the result of averaging $N=5$ subsequent depth images.
+Assuming independence of $\epsilon_I$ and $\epsilon_S$, the expected variance of pixel depth measurements for is given by:
 \begin{equation}
-	\sigma^2 = \frac{\sigma_I^2}{N} + \sigma_S^2.\label{eq:sigma}
+\sigma^2(d,r) = \frac{\sigma_I^2(d,r)}{N} + \sigma_S^2.\label{eq:sigma}
 \end{equation}
@@
 There are additional sources of noise not captured by this including object specularities, sharp variations in object albedo, mixed-depth pixels on object edges, and cases of very-low signal reflection.
+One of the utilities of having a modeled expected variance is that it can be compared with the measured variance, and strong disparity is a cue that the surface violates our modeling assumptions, and can be filtered out as not belonging to a plant leaf.
+
 In addition we noticed that the chamber light shades blocked some of the depth camera field of view, and in doing so reflected some of the IR illumination.

### 2015-05-04 datapaper_calibration.tex
noise modeling clarifications

@@
 
-The depth noise $\epsilon$ is modeled as the sum of two components, $\epsilon_I$ and $\epsilon_S$:
+The depth noise, $\varepsilon$, is modeled as the sum of an image dependent term, $\varepsilon_I$, and a sensor dependent term, $\varepsilon_S$:
 \begin{equation}
-\epsilon = \epsilon_I + \epsilon_S\label{eq:epsilon}
+\varepsilon = \varepsilon_I + \varepsilon_S\label{eq:epsilon}
 \end{equation}
-The term $\epsilon_I$ captures the noise component that varies between images taken from a fixed pose of a static scene.
-On the other hand the term $\epsilon_S$ models noise is constant between images but varies between pixels.
-The variance of $\epsilon_I$ is estimated for each pixel of a fixed scene observed over multiple images.
+The term $\varepsilon_I$ is a random variable for each pixel with a value that varies between subsequent images taken from a fixed pose of a static scene.
+On the other hand, $\varepsilon_S$ is a random variable for each pixel that models its depth offset, and its value only changes when the scene changes.
+The variance of $\varepsilon_I$ is estimated for each pixel of a fixed scene observed over multiple images.
 In our experiments we observed a flat, uniform albedo surface perpendicular to the camera at a sequence of depths, and for each depth acquired 300 images.
-Object depth, $d$, has a large impact on $\epsilon_I$ likely due to reduced reflected signal.
+Object depth, $d$, has a large impact on $\varepsilon_I$.
 For constant depth, we observed that the primary factor affecting the variance is the pixel radius, $r$, from the image center.
 Physically we expect this dependence is due to a circularly symmetric illuminating beam closely aligned with the optical axis.
-Based on these observations we model $\sigma_I^2(d,r)$ the variance of $\epsilon_I$, as a function of depth and pixel radius.
+Based on these observations we model $\sigma_I(d,r)$, the standard deviation of $\varepsilon_I$, as a function of depth and pixel radius.
 From our experiments we build up a lookup table for this as plotted in Figure~\ref{fig:Noise}.
@@
 
-In addition to repeated-image-varying noise, there are pixel depth offsets that are constant for images of the same scene, and so cannot be removed by averaging over many frames.
-We model these with $\epsilon_S$.
-To estimate its variance, $\sigma_S^2$, we first average over many depth measurement images, in our case 300, to obtain pixel depth estimates that approximately eliminate the effect of $\epsilon_I$.
-Then by calculating true ray depths on a known surface, in our case the observed plane, and assuming that $\epsilon_S$ has the same distribution over all pixels, $\sigma_S$ is obtained as the standard deviation of the error between averaged depths and known depths.
+Averaging over repeated images of a scene will not remove all the depth error as there are pixel depth offsets that are constant for images of the same scene.
+We model these with $\varepsilon_S$.
+To estimate its standard deviation, $\sigma_S$, we first average over many depth measurement images, in our case 300, to obtain pixel depth estimates that approximately eliminate the effect of $\varepsilon_I$.
+Then by calculating true ray depths on a known surface, in our case the observed plane, and further assuming that $\varepsilon_S$ has the same standard deviation for all pixels, $\sigma_S$ is obtained as the standard deviation of the error between averaged depths and known depths.
 In our experiments we obtained $\sigma_S=6.5mm$, and found that it was insensitive to changes in depth.
@@
 The recorded depth images in the data collection are the result of averaging $N=5$ subsequent depth images.
-Assuming independence of $\epsilon_I$ and $\epsilon_S$, the expected variance of pixel depth measurements for is given by:
+Assuming independence of $\varepsilon_I$ and $\varepsilon_S$, the variance of pixel depth measurements is given by:
 \begin{equation}
@@
 
-There are additional sources of noise not captured by this including object specularities, sharp variations in object albedo, mixed-depth pixels on object edges, and cases of very-low signal reflection.
-One of the utilities of having a modeled expected variance is that it can be compared with the measured variance, and strong disparity is a cue that the surface violates our modeling assumptions, and can be filtered out as not belonging to a plant leaf.
+There are additional sources of noise not modeled by this.
+Object albedo has an impact although this is fairly weak for strong signal reflections.
+Factors with large impact on signal noise include: object specularities, sharp variations in object albedo, mixed-depth pixels on object edges, and cases of very-low signal reflection, all of which can lead to very large variances.
+One of the utilities of having a model for variance is that it can be compared with the measured variance, and the difference used as a cue for portions of the scene that violate our modeling assumptions.
 
-In addition we noticed that the chamber light shades blocked some of the depth camera field of view, and in doing so reflected some of the IR illumination.
+In addition, we noticed that the chamber light shades blocked some of the depth camera field of view, and in doing so reflected some of the IR illumination.
 This resulted in a small constant depth shift for the pixels.

### 2015-05-04 datapaper_hardware.tex
update_Xi
noise modeling clarifications

@@
 \caption{Noise analysis for a depth camera obtained by imaging a flat surface at various depths.
-We found that the standard deviation, $\sigma_I$ from Eq.
-(\ref{eq:sigma}) of the pixel depth measurements had a large dependency on both the target depth and the pixel distance from the image center, and these are plotted.
+We found that the standard deviation, $\sigma_I(d,r)$ from Eq.
+(\ref{eq:sigma}) of the pixel depth measurements had a large dependency on both the target depth, $d$, and the pixel radius, $r$, from the image center, and these are plotted.
 A radius of $0$ pixels is the image center, and of $200$ pixels corresponds to the corners of the depth camera, which can be seen to have far larger standard deviation than at the image center for the same depth.

### 2015-05-04 datapapr_labeling.tex
Updates to calibration
arxiv

@@
 \item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$depth.png: the original depth images;
+\item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$depthSigma.png: the depth standard deviation images;
 \item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$label.png: the labeled images of fluorescence modality;
@@
 In order to evaluate methods developed on other modalities, we provide image-mapping functions between every two modalities.
-The total storage of our database is around $XX Mb$, which is convenient for downloading via Internet.
+The total storage of our database is around $380 Mb$, which is convenient for downloading via Internet.
 
@@
 We build the frame-to-frame and video-to-video correspondence respectively and generate two sets of tip-based errors.
-More details can be find in~\cite{yin2014b}.
+More details can be find in~\cite{yin2015}.
 We define a threshold $\tau$ to operate on the corresponding tip-based errors.

### 2015-05-04 datapaper_baseline.tex
xm's first edits

--- 2015-05-02 datapaper_baseline.tex
@@
 
-\subsection{Multi-leaf segmentation and tracking framework}
+\subsection{Multi-leaf Segmentation and Tracking Framework}
 We apply our automatic multi-leaf segmentation and tracking framework~\cite{yin2014a,yin2014b} to the testing set of Arabidopsis fluorescence imagery to provide a baseline.
@@
 
-\subsection{Performance and analysis}
-We apply our algorithm on all $144$ frames of each video and evaluate the performance on labeled $36$ frames.
-Leaf alignment is applied to the last frame of each video.
-Figure~\ref{fig:alignResult} shows some examples of leaf alignment results.
-Our framework works very well on segmenting large leaves with no overlap to neighbor leaves.
-For overlapping leaves, it becomes more challenging as the edges between the overlapping area are more difficult to be detected.
-However, when the overlapping leaves are further away from the center, they will have a higher chance to be detected as shown in $(c)$ of Figure~\ref{fig:alignResult}.
-When the overlapping leaves are close to the center, smaller leaves will be covered by larger leaves as shown in $(a), (d), (e)$ of Figure~\ref{fig:alignResult}.
-
-Leaf alignment provides the leaf candidates for tracking over time.
-Figure~\ref{fig:trackExample} shows one leaf tracking result. 
-The leaf template transformation works well for most of the leaves.
-As plant grows, younger leaves may grow faster than older leaves and occlude the older leaves.
-As shown in Fig.~\ref{fig:trackExample} (b), purple leaf replaces the red leaf at day $6$.
-Our backward tracking algorithm tracks leaves from the last frame to the first frame.
-The two leaves are still being considered as one leaf (ID $8$) in day $4$ and day $3$. 
-Leaf $8$ in day $1$ and $2$ is considered as leaf ID switch and will be not count as consistently tracked leaf. 
-However, it is still been considered as well aligned and segmented leaves. 
-%Leaves will be deleted when it becomes small and the leaf underneath it will be detected.
-
 \begin{figure*}
@@
 \caption{Leaf alignment results on the last frame of $6$ plant videos.
-First row shows the original image.
-Second row shows the alignment result with red points denote the boundary of the leaf templates in the blue bounding boxes.
+First row shows the original images.
+Second row shows the alignment results with red points denoting the boundary of the leaf templates in the blue bounding boxes.
 The numbers on the leaves are the leaf IDs representing the order of the leaf being selected and they will be consistent during tracking.}
@@
 \end{tabular}
-\caption{Tracking result for one video with one frame for each day.
-$(1)$ Example frames in the video.
-$(2)$.
-Leaf label result overlaid with tip locations.
-$(3)$ Leaf tracking result.
-We show one frame for each day.
-}
+\caption{Tracking result for one video with one frame for each day. $(a)$ Example frames in the video. $(b)$ Leaf label results overlaid with tip locations. $(c)$ Leaf tracking results. }
 \label{fig:trackExample}
@@
 \centering
-\includegraphics[width=.98\textwidth]{Figures/performance.pdf}\\
-\caption{Performance of the baseline method.}
+\includegraphics[width=.81\textwidth]{Figures/performance.pdf}\\
+\caption{Performance of the baseline method on the testing set of the fluorescence modality of Arabidopsis plant.}
 \label{fig:performance}
@@
 
-For quantitative evaluation, we vary $\tau$ from $0$ to $1$ and generate the first three evaluation metrics, as shown in Fig.~\ref{fig:performance}.
+\subsection{Performance and Analysis}
+We apply our algorithm to all $144$ frames of each video and evaluate the performance on labeled $36$ frames.
+Leaf alignment is applied to the last frame of each video.
+Figure~\ref{fig:alignResult} shows some examples of leaf alignment results.
+Our framework works very well on segmenting large leaves with no overlap to neighbor leaves.
+For overlapping leaves, it becomes more challenging as the edges in the overlapping area are more difficult to be detected.
+However, when the overlapping leaves are further away from the center, they will have a higher chance to be detected as shown in $(c)$ of Figure~\ref{fig:alignResult}.
+When the overlapping leaves are close to the center, smaller leaves will be covered by larger leaves as shown in $(a), (d), (e)$ of Figure~\ref{fig:alignResult}.
+
+Leaf alignment provides the leaf candidates for tracking over time. 
+Figure~\ref{fig:trackExample} shows the leaf tracking result of one video.
+The leaf template transformation works well for most of the leaves.
+As plant grows, younger leaves may grow faster than older leaves and occlude the older leaves.
+As shown in Figure~\ref{fig:trackExample} (b), purple leaf replaces the red leaf at day $6$.
+Our backward tracking algorithm tracks leaves from the last frame to the first frame.
+The two leaves are still being considered as one leaf (ID $8$) in day $4$ and day $3$.
+Leaf $8$ in day $1$ and $2$ is a leaf ID switch w.r.t.~the purple ground truth leaf and will not be considered as a consistently tracked leaf.
+However, they are still evaluated as well aligned and segmented leaves.
+%Leaves will be deleted when it becomes small and the leaf underneath it will be detected.
+
+For quantitative evaluation, we vary $\tau$ from $0$ to $1$ and generate the first three evaluation metrics, as shown in Figure~\ref{fig:performance}.
 {\it{ULR}} decreases as $\tau$ increases as more leaves are being considered as matched leaves.
-As $\tau$ keep increasing, {\it{ULR}} approaches a constant value, which is the different number in leaf counting that results from both miss detection and false alarms.
+As $\tau$ keeps increasing, {\it{ULR}} approaches a constant value, which is the different number in leaf counting that results from both miss detection and false alarms.
 {\it{LE}} increases as $\tau$ increases as it includes leaves with larger tip-based errors for averaging.
@@
 Note that {\it{TC}} is influenced by the length of frames evaluated for each video.
-As the longer frames we evaluate, the higher chance tracking will be failed. 
+As the longer frames we evaluate, the higher chance tracking will fail.
 Overall, our method can detect $87\%$ and track $50\%$ of all labeled leaves with less than $20\%$ average tip-based errors.

### 2015-05-04 datapaper_hardware.tex
xm's first edits

@@
 \begin{figure}
-  \includegraphics[width=\linewidth,trim=55 80 200 70,clip]{Figures/hardware}
+  \includegraphics[width=\linewidth,trim=55 100 200 70,clip]{Figures/hardware}
 \caption{The hardware setup for our data collection.}
@@
 
-\subsubsection{Fluorescence and IR images}
+\subsubsection{Fluorescence and IR Images}
 Chlorophyll a fluorescence images were captured once every hour during the daylight period in a growth chamber~\cite{cruz2015depi}.
@@
 
-\subsubsection{RGB color and depth images} %This section describes characterizes the data from this sensor, particularly the depth data.
+\subsubsection{RGB Color and Depth Images} %This section describes characterizes the data from this sensor, particularly the depth data.
 
@@
 \begin{tabular}{c}
-  \includegraphics[width=\linewidth,trim=60 200 45 250,clip]{Figures/CameraConfiguration} \\
+  \includegraphics[width=\linewidth,trim=120 240 80 300,clip]{Figures/CameraConfiguration} \\
   ($a$)\\

### 2015-05-04 datapapr_labeling.tex
xm's first edits

@@
 \section{Annotation, Files and Protocol}
-\subsection{Data statistics}
+\subsection{Data Statistics}
 MSU-PID includes two subsets, one for each plant type: Arabidopsis and Bean.
@@
 Table~\ref{tab:resolution} summaries the image resolution of each plant in all four modalities.
-
-\subsection{Manual annotations}
-Part of the database is manually annotated to provide ground truth tip locations, leaf segmentation results and leaf consistency overtime.
-Tip locations are saved in a TXT file for each frame.
-Leaf segmentation results are stored in a PNG image for each frame with one color for each leaf.
-The same color is used to represent the same leaf over a sequence of frames.
-
-We use the fluorescence images as the input for labeling because of their simple and uniform background.
-For Arabidopsis images, we label $4$ frames each day.
-While for bean images, we label $7$ frames each day because of their spontaneous and faster leaf movement.
-A Matlab-based GUI interface is developed for leaf labeling, as shown in Figure~\ref{fig:label}.
-A user can open a plant image to label the two tips and annotate each leaf segment.
-The results will be automatically saved once a user moves onto the next image for labeling.
-For consistent annotation of the same leaf over time, we show a number on the center of each leaf indicating the order of labeling from the previous frame.
-%This GUI is used to annotate leaves in each frame.
-%For consistent annotation of the same leaf over time, we use the labeled results of each frame to find the correspondence according to leaf centers.
-%Incorrect correspondence will be manually corrected.
 
@@
 
+\subsection{Manual Annotations}
+Part of the database is manually annotated to provide ground truth tip locations, leaf segmentation results and leaf consistency overtime.
+Tip locations are saved in a TXT file for each frame.
+Leaf segmentation results are stored in a PNG image for each frame with one color for each leaf.
+The same color is used to represent the same leaf over a sequence of frames.
+
+We use the fluorescence images as the input for labeling because of their simple and uniform background.
+For Arabidopsis images, we label $4$ frames each day.
+While for bean images, we label $7$ frames each day because of their spontaneous and faster leaf movement.
+A Matlab-based GUI interface is developed for leaf labeling, as shown in Figure~\ref{fig:label}.
+A user can open a plant image to label the two tips and annotate each leaf segment.
+The results will be automatically saved once a user moves onto the next image for labeling.
+For consistent annotation of the same leaf over time, we show a number on the center of each leaf indicating the order of labeling from the previous frame.
+%This GUI is used to annotate leaves in each frame.
+%For consistent annotation of the same leaf over time, we use the labeled results of each frame to find the correspondence according to leaf centers.
+%Incorrect correspondence will be manually corrected.
+
 The labeling of leaf tips is implemented by clicking pairs of points on the image.
@@
 
-\subsection{Name conventions and file types}
+\subsection{Name Conventions and File Types}
 We release training and testing sets in two separate folders.
@@
 \end{itemize}
-where ID indicates the plant ID number ($1$ to $16$ for Arabidopsis, $1$ to $5$ for bean), X is an integer indicating the date ($1-9$ for Arabidopsis, $1$ to $5$ for bean), and YY represents the image index within a day ($1-16$ for Arabidopsis, $1$ to $14$ for bean).
+where ID indicates the plant subject ID number ($1$ to $16$ for Arabidopsis, $1$ to $5$ for bean), X is an integer indicating the date ($1-9$ for Arabidopsis, $1$ to $5$ for bean), and YY represents the image index within a day ($1-16$ for Arabidopsis, $1$ to $14$ for bean).
 For each combination of day and hour, we provide four modalities in PNG files ($\_$rgb, $\_$fmp, $\_$ir, $\_$depth).

### 2015-05-04 datapaper_intro.tex
final edit

@@
 \includegraphics[width=.23\textwidth]{Figures/FourModalities/A_ir}\\
-Arabidopsis: RGB & Arabidopsis: Depth & Arabidopsis: Fluorescence & Arabidopsis: IR \\
+Arabidopsis: RGB & Arabidopsis: depth & Arabidopsis: fluorescence & Arabidopsis: IR \\
 \includegraphics[width=.23\textwidth]{Figures/FourModalities/B_rgb}&
@@
 \includegraphics[width=.23\textwidth]{Figures/FourModalities/B_ir}\\
-Bean: RGB & Bean: Depth & Bean: Fluorescence & Bean: IR \\
+Bean: RGB & Bean: depth & Bean: fluorescence & Bean: IR \\
 \end{tabular}
@@
 & & & Tobacco & $80$ & $165,120$ & $83$ \\ \hline
-\multirow{2}{*}{MSU-PID} & Fluorescence, & LS, LO, & Arabidopsis & $16$ & $2304\times 4$ & $576\times 4$ \\ \cline{4-7}
-& IR, RGB, Depth & LA, LT & Bean & $5$ & $350\times 4$ & $175\times 4$ \\ \hline
+\multirow{2}{*}{MSU-PID} & fluorescence, & LS, LO, & Arabidopsis & $16$ & $2304\times 4$ & $576\times 4$ \\ \cline{4-7}
+& IR, RGB, depth & LA, LT & Bean & $5$ & $350\times 4$ & $175\times 4$ \\ \hline
 \hline
@@
 To facilitate future research on plant image analysis, as well as remedy the limitation of existing databases in the field, this paper presents a newly collected multi-modality plant imagery database through an interdisciplinary effort at Michigan State University (MSU), termed ``MSU-PID''.
-As illustrated in Figure~\ref{fig:fourmodality}, the MSU-PID database includes the imagery of two types of plants (Arabidopsis and bean), both are widely used in plant research, captured by four types of imaging sensors, i.e., Fluorescence, infrared (IR), RGB color, and depth.
+As illustrated in Figure~\ref{fig:fourmodality}, the MSU-PID database includes the imagery of two types of plants (Arabidopsis and bean), both are widely used in plant research, captured by four types of imaging sensors, i.e., fluorescence, infrared (IR), RGB color, and depth.
 All four sensors are synchronized and are programmed to periodically capture imagery data for multiple consecutive days.

### 2015-05-04 datapapr_labeling.tex
final edit

@@
 
-\begin{figure*}
-\begin{centering}
-\begin{tabular}{@{}c@{} c@{} c@{} c@{} c@{} c@{} c@{} c@{} c@{}}
-%\begin{tabular}{lllllllll}
-\includegraphics[width=.11\textwidth]{Figures/labelExample/plant_1_day_1_num_13.png}&
-\includegraphics[width=.11\textwidth]{Figures/labelExample/plant_1_day_2_num_13.png}&
-\includegraphics[width=.11\textwidth]{Figures/labelExample/plant_1_day_3_num_13.png}&
-\includegraphics[width=.11\textwidth]{Figures/labelExample/plant_1_day_4_num_13.png}&
-\includegraphics[width=.11\textwidth]{Figures/labelExample/plant_1_day_5_num_13.png}&
-\includegraphics[width=.11\textwidth]{Figures/labelExample/plant_1_day_6_num_13.png}&
-\includegraphics[width=.11\textwidth]{Figures/labelExample/plant_1_day_7_num_13.png}&
-\includegraphics[width=.11\textwidth]{Figures/labelExample/plant_1_day_8_num_13.png}&
-\includegraphics[width=.11\textwidth]{Figures/labelExample/plant_1_day_9_num_13.png}\\
-day 1 & day 2 & day 3 & day 4 & day 5 & day 6 & day 7 & day 8 & day 9 \\
-\end{tabular}
-\caption{Leaf labeling results of one Arabidopsis plant over nine days with one image per day. Note that the labels of tips are not shown for visualization clarity. }
-\label{fig:LabelExample}
-\end{centering}
-\end{figure*}
+%\begin{figure*}
+%\begin{centering}
+%\begin{tabular}{@{}c@{} c@{} c@{} c@{} c@{} c@{} c@{} c@{} c@{}}
+%%\begin{tabular}{lllllllll}
+%\includegraphics[width=.11\textwidth]{Figures/labelExample/plant_1_day_1_num_13.png}&
+%\includegraphics[width=.11\textwidth]{Figures/labelExample/plant_1_day_2_num_13.png}&
+%\includegraphics[width=.11\textwidth]{Figures/labelExample/plant_1_day_3_num_13.png}&
+%\includegraphics[width=.11\textwidth]{Figures/labelExample/plant_1_day_4_num_13.png}&
+%\includegraphics[width=.11\textwidth]{Figures/labelExample/plant_1_day_5_num_13.png}&
+%\includegraphics[width=.11\textwidth]{Figures/labelExample/plant_1_day_6_num_13.png}&
+%\includegraphics[width=.11\textwidth]{Figures/labelExample/plant_1_day_7_num_13.png}&
+%\includegraphics[width=.11\textwidth]{Figures/labelExample/plant_1_day_8_num_13.png}&
+%\includegraphics[width=.11\textwidth]{Figures/labelExample/plant_1_day_9_num_13.png}\\
+%day 1 & day 2 & day 3 & day 4 & day 5 & day 6 & day 7 & day 8 & day 9 \\
+%\end{tabular}
+%\caption{Leaf labeling results of one Arabidopsis plant over nine days with one image per day. Note that the labels of tips are not shown for visualization clarity. }
+%\label{fig:LabelExample}
+%\end{centering}
+%\end{figure*}
 
@@
 After the labeling of one plant, we visually go through the results and correct inaccurate labels.
-One example of the labeling results for one plant is shown in Figure~\ref{fig:LabelExample}, where one color is used to represent each specific leaf.
-As we can see during the transition between day $4$ and day $5$, there is one leaf showing up and covering up the leaf underneath, which disappears and will not be annotated later.
+One example of the labeling results for one plant is shown in Figure~\ref{fig:trackExample} $(b)$, where one color is used to represent each specific leaf.
+As we can see during the transition between day $5$ and day $6$, there is one leaf showing up and covering up the leaf underneath, which disappears and will not be annotated later.
 In total, we labeled $5142$ leaves.

### 2015-05-04 datapaper_conclusion.tex
typos

@@
 Compared to existing databases in the field, MSU-PID not only has multiple calibrated modalities, but also enables a wide variety of plant image analysis applications.
-Therefore, we believe this new database will be benefitial to the research community in terms of algorithm development, performance evaluation, and identifying new research problems in plant image analysis.
-Furthmore, we are also open to suggestions and comments from the users of this database to further enhance our imaging setup and capturing protocol, so that we can develop new databases in the future.
+Therefore, we believe this new database will be beneficial to the research community in terms of algorithm development, performance evaluation, and identifying new research problems in plant image analysis.
+Furthermore, we are also open to suggestions and comments from the users of this database to further enhance our imaging setup and capturing protocol, so that we can develop new databases in the future.

### 2015-07-14 response/response.tex
xi_edit

\documentclass[11pt,letterpaper]{article}

\usepackage[top=1in,bottom=1in,left=1in,right=1in]{geometry}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{cite}
\usepackage{bm}
\usepackage[usenames]{color}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{textcomp}
\usepackage{times}
\usepackage{url}
\usepackage{xr}

%\externaldocument{../debris}

\newcommand{\eg}{e.g.}
\newcommand{\ie}{i.e.}
\newcommand{\etal}{et~al.~}
\newcommand{\vs}{vs.~}
\newcommand{\cf}{cf.~}
\newcommand{\red}{\color{red}}
\newcommand{\blue}{\color{blue}}
\newcommand{\green}{\color{green}}
\newcommand{\resp}{\textcolor{Blue}}
\renewcommand{\thefigure}{R-\arabic{figure}}

\newcounter{reviewcounter}
\setcounter{reviewcounter}{1}

\newenvironment{review}
{\noindent {\bf Comment~\arabic{reviewcounter}}:\addtocounter{reviewcounter}{1}\itshape}
{\vspace{0.8em}}

\newenvironment{response}
{\noindent {\bf Response}: \color{black}}
{\color{black} \vspace{1.6em}}

\title{Response letter on MVAP-D-15-00159, \\"Multi-modality Imagery Database for Plant Phenotyping"}

\begin{document}

\maketitle

{%\color{blue}
We thank the Guest Editors for the efforts of handling our submission and two reviewers for providing the constructive and valuable feedback.
The detailed comments help us further improve the quality of our manuscript.
%The changes made to the manuscript are highlighted in blue text.
In the following, we list our detailed responses to all the comments.
For your convenience, we add a separate reference list in the end that is used in this response letter.
}

\vspace{2em}
\noindent {\large\textsc{Reviewer~1}}\\
\begin{tabular*}{\textwidth}{c}
\hline
\end{tabular*}

% Reviewer 1: Q1
\begin{review}
The authors should clarify what is intended by "leaf alignment" and why it is important, since this feature is probably less common in plant phenotyping applications than the others that are mentioned.
\end{review}

\begin{response}
Leaf alignment estimates the inner and outer tips of the leaf, which can help understand the leaf structure. 
For example, ~\cite{cerutti2013understanding} uses a polygonal leaf model for leaf segmentation and plant identification.
This leaf structure information can be used to analysis the difference of plant phenotyping within one leaf.  
\\ \textcolor{red}{could not find a reference.}
\end{response}

% Reviewer 1: Q2
\begin{review}
 Figure $1$ should be augmented (or a separate figure should be created) with zoom in details showing how the same plant parts (or scene portions) appear in the different modalities. 
 This would help the reader get a better idea of the contrast and the type of information conveyed by each of the modalities adopted by the authors.
\end{review}

\begin{response}
We have augmented Fig.$1$ by adding one zoom-in view for each image. 
\end{response}

% Reviewer 1: Q3
\begin{review}
Each of the databases mentioned in Table $1$ should be accompanied by a reference.
\end{review}

\begin{response}
We have the corresponding references in the prior work section, which follows the order as they appear in Table $2$. 
Therefore, we do not add the references in Table $2$ for conciseness.
\end{response}

% Reviewer 1: Q4
\begin{review}
The second paragraph of Sec. $2$ begins with "we summarize all existing publicly available databases that are related to plant imagery". 
This is a strong statement, particularly because other plant related image datasets exist (e.g., ImageCLEF, ICL leaf database) which are omitted from the review. 
The authors should adjust language and/or expand the literature review.
\end{review}

\begin{response}
We adjust language by the statement of "we summarize some existing publicly available databases that are related to plant imagery". 
\end{response}

% Reviewer 1: Q5
\begin{review}
In the second paragraph in Sec. $2$, I believe the observation on single leaves imaged in a constrained environment does not apply to the dataset by (Haug and Ostermann, $2014$). 
Please reformulate.
\end{review}

\begin{response}
It is correct that the dataset (Haug and Ostermann, $2014$) is not about single leaves imaged in a constrained environment. 
We still category it in the first type because it does not include leaf segmentation. 
All segmentation tasks are based on plant level. 
We have reformulated this in the second paragraph in Sec. $2$. 
\end{response}

% Reviewer 1: Q6
\begin{review}
At the end of the first paragraph of Sec. $4.4$, p. $8$, the authors envision a use of the multiple modalities in their dataset in which algorithms are developed to handle missing modalities. 
Briefly presenting a use case scenario or citing relevant works may help clarify the importance of this point.
\end{review}

\begin{response}
Here we want to emphasize that it is not necessary to train and test on the same modality. 
For example, if we would like to develop a leaf segmentation algorithm that can work on RGB images, we can still utilize the depth images during training.   
\\ \textcolor{red}{I am not sure if I understand the statement correctly.}
\end{response}

% Reviewer 1: Q7
\begin{review}
In Sec. $5$ no baseline method or result is reported for bean images. Could the authors comment on this?
\end{review}

\begin{response}
The previous developed leaf alignment, segmentation, and tracking algorithm is designed particularly for rosette plants like Arabidopsis and tobacco.
The rosette plant structure is used as a prior in the development of the algorithm.
However, bean plant does not belong to rosette plants.
Therefore, we did not apply the baseline method to bean plants.
We have added this statement in the beginning of Sec $5.1$. 
\end{response}

% Reviewer 1: Q8
\begin{review}
The conclusions (Sec. $6$) should be expanded.
\end{review}

\begin{response}
\textcolor{red}{will expand after everything finished}
\end{response}

% Reviewer 1: Q9
\begin{review}
The acronym "MSU-PID" should be clearly defined when it first appears in text (p. $2$, line $51$)
\end{review}

\begin{response}
Except in the Abstract, the "MSU-PID" first appears in fourth paragraph in Sec $1$. 
We have clearly defined it as short for Michigan State University Plant Image Database. 
\end{response}

% Reviewer 1: Q10
\begin{review}
According to the SI (International System of Units), units of measure should be written in roman type, while italic type is reserved for variables. 
Besides, when they follow a number, a space should be included between numerical value and unit symbol. 
To improve clarity of the manuscript, the authors are therefore advised to adhere to the SI style conventions.
\end{review}

\begin{response}

\end{response}

% Reviewer 1: Q11
\begin{review}
In Sec. $3.2.1$, the "a" of "chlorophyll a" could be italicized to improve clarity.
\end{review}

\begin{response}
We have changed "chlorophyll a" to "chlorophyll {\it a}" all over the paper. 
\end{response}

% Reviewer 1: Q12
\begin{review}
It is not clear on p. $8$, line $15$, if the size of the database is $380$ megabytes (MB) or $380$ megabits (Mb). 
%In the former case "MB" should be used instead of "Mb", while in the latter case the authors should consider reporting the value in megabytes (MB) which is more common.
\end{review}

\begin{response}
It is $380$ MB. 
We have changed it in the text. 
\end{response}

% Reviewer 1: Q13
\begin{review}
In Eq. $3$, p. $8$, the authors should better define the symbols used. In particular, it is not clear if subscripts $1$ and $2$ refer to inner and outer leaf tips respectively, and in which order.
\end{review}

\begin{response}
$t_1$ represents the outer leaf tip and $t_2$ represents the inner leaf tip. 
This representation is the same as the released leaf tip labels as illustrated in the end of the first paragraph in Sec. $4.3$. 
The equation does not rely on the correspondence of inner or outer tips as long as the estimated tips correspond to the labeled tips. 
\end{response}

% Reviewer 1: Q14
\begin{review}
Sec. $5.1$, p. $9$, for completeness the authors should mention the approach they used to find a threshold for plant segmentation.
\end{review}

\begin{response}
We use some training images with groundtruth plant segmentation masks to learn a threshold for binary segmentation. 
The learnt threshold is then applied to both training images and testing images to generate the image mask. 
We have added this statement to the paper. 
\end{response}

\vspace{1em}
\noindent {\large\textsc{Reviewer~2}}\\
\begin{tabular*}{\textwidth}{c}
\hline
\end{tabular*}

% Reviewer 2: Q15
\begin{review}
The authors argue that the most closely related work is that of Scharr et al $2014$. 
They identify as weaknesses that it i) uses only RGB images and ii) can be used for a few vision problems.  
However, upon reading the Scharr paper it is clear that the authors of that work, do mention that they collect additional data to be used in tracking context and for other applications. 
It is not clear if the authors here refer to what is available data from Scharr et al or what is described in the paper?  
Furthermore, the data in Scharr et al appear to originate from different mutants and under different treatments, and also imaged with different cameras. 
Since this work does use only wildtypes and single cultivars this distinction should be made. 
Furthermore, once leaf labeling is available several secondary annotations can be derived so in some sense Table $1$ should be annotated accordingly.
Nevertheless, I recommend the authors for arranging information as in Table $1$.
\end{review}

\begin{response}
We refer to Scharr et al $2014$ that the Leaf Segmentation Challenge datasets only includes independent images without tracking context. 
The reason we do not include mutants is that we assume any computer vision algorithms that work on wildtypes should also work well on mutants as they have similar structure. 
\\ \textcolor{red}{I do not understand what to be added to Table $1$.}
\end{response}

% Reviewer 2: Q16
\begin{review}
Your annotation process is completely interactive. 
Any way to "save interaction" by interactive segmentation approaches?  
I applaud your comment on the difficulty of merging super-pixel results, but I would add at least somewhere that easier ways to annotate will be beneficial.
\end{review}

\begin{response}
Our annotation is not interactive. 
It is totally based on user input without any computer feedback except for visualization. 
Leaf label is implemented by clicking several points along the boundary of the leaf. 
Tip label is implemented by clicking the outer and inner tip points respectively. 
We did explore other options for labeling and found this simple naive way worked the best. 
\end{response}

% Reviewer 2: Q17
\begin{review}
It is unclear if you release this annotation tool? If not, please do... it will be extremely useful for the community.
\end{review}

\begin{response}
We will release the labeling tool together with the dataset. 
\end{response}

% Reviewer 2: Q18
\begin{review}
Does the annotation $\_$hour$\_$YY$\_$label.png  contain a label for each pixel or only for the boundaries?  
If yes, then can you obtain single boundary definition in between overlapping leaves?
\end{review}

\begin{response}
The annotated image is an image the same size as the original image. 
And each pixel is annotated with a number. 
The same number represents the same leaf and $0$ represents the background. 
For overlapping leaves, we can visualize the relative location and annotate accordingly. 
\end{response}

% Reviewer 2: Q19
\begin{review}
Based on your annotations can you find which leaf occludes which?
\end{review}

\begin{response}
During annotation, we can observe which leaf occludes which and annotate the overlapping area to the leaf on top. 
However, it is hard to refer which leaf occludes which from the annotations. 
\end{response}

% Reviewer 2: Q20
\begin{review}
The authors test an algorithm (developed by them) on the fluorescence part of the data. 
Granted this algorithm is presented elsewhere on the same data. 
I was wondering if the authors can either a) use the same algorithm on one of the other modalities, and how it would perform (assuming ground truth labeling obtained via propagation)?  
OR b) if they can apply another benchmark method even from the broad CV literature on one of the CV problems considered in another modality.  
I think doing one of the two, time permitting, will greatly assist the paper.
\end{review}

\begin{response}
\textcolor{red}{to be done: apply to RGB modality if label propagation works fine.}
\end{response}

% Reviewer 2: Q21
\begin{review}
Couple of typos:
\begin{enumerate}
  \item page $6$, line $27$ $2$nd col, please add "are" before present
  \item page $7$, lines $56-69$, left col, the last two sentences should be together and not be separated by a period, but by a comma
  \item page $8$, line $30$, left col, consider using performance instead of performances
\end{enumerate}
\end{review}

\begin{response}
We have corrected those typos. 
\end{response}

%\newpage

{\small
\bibliographystyle{IEEEbib}
\bibliography{references}
}
%\begin{thebibliography}{}
%
%\end{thebibliography}

\clearpage

%\input{../journal.bbl}

\end{document}

### 2015-07-14 datapaper_baseline.tex
xi_edit

@@
 
-To facilitate future research on this database, we provide a baseline approach and its performance by using the fluorescence modality.
+To facilitate future research on this database, we provide a baseline approach and its performance by using the fluorescence modality of Arabidopsis.
 
@@
 We apply our automatic multi-leaf segmentation and tracking framework~\cite{yin2014a,yin2014b} to the testing set of Arabidopsis fluorescence imagery to provide a baseline.
+Note that~\cite{yin2014a,yin2014b} is designed for rosette plants like Arabidopsis. 
+Therefore, it will not be applied to bean plant as it does  not belong to rosette plants. 
 We treat all images in $9$ days as a video from first image on the first day to the last image in the last day.
@@
 For plant segmentation, we use simple thresholding and edge detection to generate an edge map and mask.
-The best threshold is learnt from the training set.
+The best threshold is learnt from the training set, which is done by tuning the threshold in a certain range and find the best one by evaluating the overlap of the segmented masks with the groundtruth label masks.
 The edge map and mask are used in the alignment and tracking optimization.

### 2015-07-14 datapaper_hardware.tex
Update to Figure 3 showing camera configuration, as well as the caption
xi_edit

@@
 \subsubsection{Fluorescence and IR Images}
-Chlorophyll a fluorescence images were captured once every hour during the daylight period in a growth chamber~\cite{cruz2015depi}.
+Chlorophyll {\it a} fluorescence images were captured once every hour during the daylight period in a growth chamber~\cite{cruz2015depi}.
 A set of $5$ images were captured using a Hitachi KP-F145GV CCD camera (Hitachi Kokusai Electric America Inc., Woodbury, NY) outfitted with an infrared long pass filter (Schott Glass RG-9, Thorlabs, Newton, NJ), during a short period ($<400~ms$) of intense light saturating to photosynthesis ($>10,000~\mu mol~photons~m^{-2} s^{-1}$) provided by an array of white Cree LEDs (XMLAWT, 5700K color temperature, Digi-Key, Thief River Falls, MN) collimated using a $20~mm$ Carclo Lens (10003, LED Supply, Lakewood, CO).
 %
-Chlorophyll a fluorescence was excited using monochromatic red LEDs (Everlight $625~nm$, ELSH-F51R1-0LPNM-AR5R6, Digi-Key), collimated using a Ledil reflector optic ($C11347\_REGINA$, Mouser Electronics, Mansfield, TX) and pulsed for $50~\mu s$ during a brief window when the white LEDs were electronically shuttered.
+Chlorophyll {\it a} fluorescence was excited using monochromatic red LEDs (Everlight $625~nm$, ELSH-F51R1-0LPNM-AR5R6, Digi-Key), collimated using a Ledil reflector optic ($C11347\_REGINA$, Mouser Electronics, Mansfield, TX) and pulsed for $50~\mu s$ during a brief window when the white LEDs were electronically shuttered.
 In addition, a series of $5$ images were also collected in the absence of the excitation light for artifact subtraction.
 
-Infrared images were collected once every hour with the same camera and filter used for chlorophyll a fluorescence.
+Infrared images were collected once every hour with the same camera and filter used for chlorophyll {\it a} fluorescence.
 Pulses of $940~nm$ light were provided by an array of OSRAM LEDs (SFH 4239, Digi-Key), collimated using a Polymer Optics lens (Part no. 170, Polymer Optics Ltd., Berkshire, England).
@@
 Sets of $15$ images were collected for averaging, in the absence of saturating illumination.
-As with chlorophyll a fluorescence, images were captured in the absence of $940~nm$ light for artifact subtraction.
+As with chlorophyll {\it a} fluorescence, images were captured in the absence of $940~nm$ light for artifact subtraction.
 
@@
 \caption{($a$)A plot of the three cameras showing their relative configuration and fields of view as obtained through calibration.
-Units are in $mm$, apart from the size of the images which are scaled and plotted at equal resolution.
+Units are in $mm$, and distance to the target bean plant is roughly 620$mm$ in this example.
+The image planes are plotted at depths proportional to the focal lengths.
 The optical center of the color camera (left-most) defines the world coordinate system.

### 2015-07-14 datapaper_intro.tex
xi_edit

@@
 \begin{centering}
-\begin{tabular}{@{}c c c c}
+\begin{tabular}{@{}c c c c c}
 %\begin{tabular}{lllllllll}
+(a) &
 \includegraphics[width=.23\textwidth]{Figures/FourModalities/A_rgb}&
@@
 \includegraphics[width=.23\textwidth]{Figures/FourModalities/A_ir}\\
-Arabidopsis: RGB & Arabidopsis: depth & Arabidopsis: fluorescence & Arabidopsis: IR \\
+(b) &
+\includegraphics[width=.1\textwidth]{Figures/FourModalities/A1_rgb}&
+\includegraphics[width=.1\textwidth]{Figures/FourModalities/A1_depth}&
+\includegraphics[width=.1\textwidth]{Figures/FourModalities/A1_fmp}&
+\includegraphics[width=.1\textwidth]{Figures/FourModalities/A1_ir}\\
+%Arabidopsis: RGB & Arabidopsis: depth & Arabidopsis: fluorescence & Arabidopsis: IR \\
+(c) &
 \includegraphics[width=.23\textwidth]{Figures/FourModalities/B_rgb}&
@@
 \includegraphics[width=.23\textwidth]{Figures/FourModalities/B_ir}\\
-Bean: RGB & Bean: depth & Bean: fluorescence & Bean: IR \\
+(d) &
+\includegraphics[width=.1\textwidth]{Figures/FourModalities/B1_rgb}&
+\includegraphics[width=.1\textwidth]{Figures/FourModalities/B1_depth}&
+\includegraphics[width=.2\textwidth]{Figures/FourModalities/B1_fmp}&
+\includegraphics[width=.2\textwidth]{Figures/FourModalities/B1_ir}\\
+%Bean: RGB & Bean: depth & Bean: fluorescence & Bean: IR \\
+ & RGB & depth & fluorescence & IR\\
 \end{tabular}
-\caption{The multi-modality plant imagery database of MSU-PID. }
+\caption{The multi-modality plant imagery database of MSU-PID.
+(a) four modalities of Arabidopsis; (b) zoom in view of Arabidopsis plant $1$; (c) four modalities of bean; (d) zoom in view of bean plant.}
 \label{fig:fourmodality}
@@
 Swedish leaf & Scaned leaf & LC& Swedish trees & $15$ & $1,125$ & $1,125$ \\ \hline
-Flavia& RGB & LC& Leaves & $32$ & $2,120$ & $2,120$ \\ \hline
+Flavia & RGB & LC& Leaves & $32$ & $2,120$ & $2,120$ \\ \hline
 Leafsnap & RGB & LC& USA trees & $184$ & $29,107$ & $29,107$ \\ \hline
@@
 
-To facilitate future research on plant image analysis, as well as remedy the limitation of existing databases in the field, this paper presents a newly collected multi-modality plant imagery database through an interdisciplinary effort at Michigan State University (MSU), termed ``MSU-PID''.
+To facilitate future research on plant image analysis, as well as remedy the limitation of existing databases in the field, this paper presents a newly collected multi-modality Plant Imagery Database through an interdisciplinary effort at Michigan State University (MSU), termed ``MSU-PID''.
 As illustrated in Figure~\ref{fig:fourmodality}, the MSU-PID database includes the imagery of two types of plants (Arabidopsis and bean), both are widely used in plant research, captured by four types of imaging sensors, i.e., fluorescence, infrared (IR), RGB color, and depth.

### 2015-07-14 datapaper_prior.tex
performance
xi_edit

@@
 
-We summarize all existing publicly available databases that are related to plant imagery in Table~\ref{tab:database}.
+We summarize some existing publicly available databases that are related to plant imagery in Table~\ref{tab:database}. 
 In terms of potential applications of these databases, they can be categorized into two types.
@@
 The Flavia database~\cite{wu2007leaf} is considerably larger and a neural network is utilized to train a leaf classifier.
-The most recent leafsnap project is an impressive effort that includes a very large dataset of leaves for $184$ tree types~\cite{kumar2012leafsnap}. 
+The most recent leafsnap project~\cite{kumar2012leafsnap} is an impressive effort that includes a very large dataset of leaves for $184$ tree types.
 A mobile phone application is also developed to make the leaf classification system portable. 
 Finally, the crop/weed image database~\cite{haug2014crop} is captured by a robot in the real field, and used for the classification of crop vs.~weed.
-Note that in this type of databases, normally only a {\it single} leaf is imaged in a relatively constrained imaging environment and as a result, the challenging problem of leaf segmentation has been bypassed.
+Note that except for~\cite{haug2014crop} where images are captured in the wild for a large area of plant, other databases in this type normally capture only a {\it single} leaf is in a relatively constrained imaging environment.
+Therefore, the challenging problem of leaf segmentation has been bypassed. 
+% Note that in this type of databases, normally only a {\it single} leaf is imaged in a relatively constrained imaging environment and as a result, the challenging problem of leaf segmentation has been bypassed.
 

### 2015-07-14 datapapr_labeling.tex
typos
xi_edit

@@
 As there is no light at night hours, plants can not be imaged by the fluorescence and RGB color sensors while IR and depth cameras can still perform the capturing in the night.
-In order to make sure that all four modalities present at each imaging opportunity, we release the part of images captured only in the day time, which are $16$ images per day for Arabidopsis and $14$ for bean for all four modalities.
+In order to make sure that all four modalities are present at each imaging opportunity, we release the part of images captured only in the day time, which are $16$ images per day for Arabidopsis and $14$ for bean for all four modalities.
 
-The two subsets differs in plant image resolutions.
+The two subsets differ in plant image resolutions.
 As shown in Figure~\ref{fig:fourmodality}, we grow and image a single bean plant while a whole tray of Arabidopsis are grown at the same time.
@@
 While for bean images, we label $7$ frames each day because of their spontaneous and faster leaf movement.
-A Matlab-based GUI interface is developed for leaf labeling, as shown in Figure~\ref{fig:label}.
+A Matlab-based GUI interface is developed for leaf labeling, as shown in Figure~\ref{fig:label}, which will also be available to the public. 
 A user can open a plant image to label the two tips and annotate each leaf segment.
@@
 Note that one alternative approach for labeling leaf segments is to directly label the membership of superpixels instead of drawing a polygon along the boundary.
-Our experience is that since a noticeable percentage of extracted superpixels cover pixels of two neighboring leaves.
-The extra effort of breaking a super pixel into two makes it a less efficient alternative.
+Our experience is that since a noticeable percentage of extracted superpixels cover pixels of two neighboring leaves, the extra effort of breaking a super pixel into two makes it a less efficient alternative.
 
@@
 In order to evaluate methods developed on other modalities, we provide image-mapping functions between every two modalities.
-The total storage of our database is around $380 Mb$, which is convenient for downloading via Internet.
+The total storage of our database is around $380 MB$, which is convenient for downloading via Internet.
 
@@
 %We will provide training and testing data in different folders.
-For fair comparison, both supervised learning and unsupervised learning methods should evaluate their performances on the training and testing sets separately.
+For fair comparison, both supervised learning and unsupervised learning methods should evaluate their performance on the training and testing sets separately.
 The user may decide to utilize one or multiple modalities of the plant imagery for training and testing respectively.

### 2015-07-14 datapaper_hardware.tex
revision - JIN

@@
 Pulses of $940~nm$ light were provided by an array of OSRAM LEDs (SFH 4239, Digi-Key), collimated using a Polymer Optics lens (Part no. 170, Polymer Optics Ltd., Berkshire, England).
-Since $940~nm$ light does not influence plant development or drive photosynthesis, images were also collected during the night period.
+Since $940~nm$ light does not influence plant development or drive photosynthesis, images were also collected during the night period~\cite{eskins1992light}.
+%
+Precisely, phytochromes are the closest photoreceptors that absorb in the far red, near infrared region, but the action spectrum is diminished to zero or near zero ($>800~nm$) in the region where we do IR reflectance ($940~nm$)~\cite{butler1964actton}.
+
 Sets of $15$ images were collected for averaging, in the absence of saturating illumination.

### 2015-07-14 datapaper_intro.tex
revision - JIN

@@
 
-The objective of {\it plant visual phenotyping} is to analyze and categorize the visual appearance of plants. %~\cite{}.
-In old days, plant phenotyping was conducted through manual visual observation~\cite{Erblichkeit1903}.
-Today, motivated by the increasing lower cost and increasing diversity of imaging sensors and advances of computer vision technologies, image-based automatic plant visual phenotyping is quickly growing into a desirable and viable solution~\cite{furbank2011phenomics,cruz2015depi}.
-In this interdisciplinary field, scientists employ various imaging sensors to capture plants and design advanced algorithms to automatically analyze the captured plant imagery, with the purpose of raising testable biological hypotheses to solve the aforementioned problems.
+Plants develop through a complex interaction between genotype and environment.
+This determines their structure and functions and thus performance such as yield or efficient use of resources.
+In order to understand the genetic basis of these economically important parameters, it is essential to quantitatively assess plant phenotypes and then identify the latent relationships to genotypes and environmental factors.
+%
+Plant visual phenotyping has been performed by farmers and breeders for more than 5,000 years.
+In the past, traditional phenotyping is based on experience and intuition, and is laborious~\cite{Erblichkeit1903}.
+Recent progresses in imaging sensor, robotics and automation technologies lead to the development of the ever-increasing new field of highly automated, non-destructive {\it plant visual phenotyping}~\cite{furbank2011phenomics,cruz2015depi}.
+%Modern plant phenotyping is a comprehensive, large-scale assessment of plant traits such as growth, development, tolerance, resistance, architecture, physiology, ecology, yield, and metadata that form the basis for more complex parameters.
+%
+The objective of modern  plant visual phenotyping is to analyze and categorize the morphological  characteristics of plants, thus accurately quantifying plant traits.
+%It advances crop yield improvement and enables the systematic study of the environmental plasticity of plants.
+%
+In this interdisciplinary field, scientists employ various imaging sensors to capture plants and design advanced algorithms to automatically analyze the captured plant imagery, with the purpose of raising testable biological hypotheses to solve problems related to growth, development, stress tolerance, resistance, and so on.
+%
+%In old days, plant phenotyping was conducted through manual visual observation~\cite{Erblichkeit1903}.
+Today, motivated by the increasing lower cost and increasing diversity of imaging sensors technologies, image-based automatic plant visual phenotyping is quickly growing into a desirable and viable solution~\cite{furbank2011phenomics,cruz2015depi}.
+%
+A key advance in visual phenotyping is the capability to non-invasively capture plant traits, enabling continuous measurements that are necessary to monitor plants during growth and/or under stress conditions.
+Vision based phenotyping also increases the throughput of phenotyping experiments by eliminating destructive operations.
+The increased capacity allows more genotypes or biological replicates to be examined under the same environmental conditions~\cite{fahlgren2015lights,walter2015plant}.
 

### 2015-07-14 datapaper_prior.tex
revision - JIN

@@
 
-One of our data modalities is dense depth measurement.
-This has been a component of a number of recent non-plant RGB-D databases designed for object recognition~\cite{Lai2011}, scene segmentation~\cite{Silberman2011}, human analysis~\cite{Sung2011,Barbosa:reid12}, and mapping~\cite{sturm12iros}.
-By including dense depth for a plant database we anticipate enabling development of new 3D plant shape analysis algorithms.
+The four sensing modalities provide unique opportunities to comprehensively characterize plant morphological and physiological phenotypes.
+Chlorophyll fluorescence measurement is an effective method to detect photosynthesis.
+For example, steady-state chlorophyll fluorescence is a relative measure of photosynthetic health in drought stress~\cite{chen2014dissecting}.
+The quantum efficiency of photosystem II can be approximated by comparing chlorophyll fluorescence levels under two light conditions~\cite{baker2008chlorophyll}.
+The dense depth measurement has been a component of a number of recent non-plant RGB-D databases designed for object recognition~\cite{Lai2011}, scene segmentation~\cite{Silberman2011}, human analysis~\cite{Sung2011,Barbosa:reid12}, and mapping~\cite{sturm12iros}.
+By including dense depth for a plant database we anticipate enabling development of new 3D plant canopy analysis algorithms, thus probing the total energy intake and storage.
+The infrared measurement enables researchers to detect chloroplast movements, which have been proposed to optimize light capture and minimize photodamage to the photosynthetic apparatus~\cite{Dutta2015Non}.

### 2015-07-14 datapaper_hardware.tex
revision -JIN v2

@@
 Precisely, phytochromes are the closest photoreceptors that absorb in the far red, near infrared region, but the action spectrum is diminished to zero or near zero ($>800~nm$) in the region where we do IR reflectance ($940~nm$)~\cite{butler1964actton}.
+%
+Note that the other modalities were captured only at day time, so that they will not interfere plant growth.
 
@@
 
-The imagery data were collected once every hour.
-These include the fluorescent image, the IR reflectance image with the same camera, the color image, the $3$D depth and a confidence image.
-The $3$D depth image is built from the depth sensor by transforming the points into the world coordinates and is expressed in the unit of $mm$.
-The confidence image is the standard deviation of the depth pixels.
-This is useful for identifying pixels at depth discontinuities that are unreliably detected and result in large standard deviations.
+\subsubsection{Image collection} 
+The imagery data, including the fluorescent image, the IR reflectance image,  the color image, and the $3$D depth image, were collected once every hour.
+First, the fluorescent image and the IR reflectance image were captured sequentially using the same camera without any delay.
+% 
+After five minutes, the $3$D depth image and the color image were captured using the Creative Senz3D sensor.
+The captured depth points were then transformed into the world coordinates and expressed in the unit of $mm$.
+Since plant leaves do not move quickly, the five minutes gap between the camera operations do not cause severe problems in image calibration.
+
+%A confidence image is the standard deviation of the depth pixels.
+%This is useful for identifying pixels at depth discontinuities that are unreliably detected and result in large standard deviations.
 

### 2015-07-14 datapapr_labeling.tex
final edits

@@
 The availability of multiple modalities allows user to design novel experimental setup.
-For example, using RGB and depth modalities for training and RGB for testing can evaluate an algorithm that can handle a missing modality during the testing.
+For example, using RGB and depth modalities for training and RGB for testing can take advantage of additional information during the learning without incurring extra sensor cost during the testing, which can be implemented via either learning with side information~\cite{chen2013boosting}, or transfering learning with missing modality~\cite{ding2014latent}.
 %The evaluation metrics will be discussed in Sec.~\ref{sec:baseline}.

### 2015-07-14 response/response.tex
final edits

@@
 \begin{response}
-Leaf alignment estimates the inner and outer tips of the leaf, which can help understand the leaf structure. 
+Leaf alignment aims to estimate the structure of a leaf. 
+In the case where the leaf structure is simple (e.g., ellipsoid-shaped leaf), leaf alignment amounts to estimating the inner and outer tips of the leaf.
+For more complex leaf structure (e.g., maple leaf), leaf alignment will estimate additional landmarks on the leaf contour that will consistently appear in all leaves.
+Leaf alignment is important for two reasons:
+First, it goes beyond leaf segmentation and provide structural information of a leaf - a discriminative signature for a leaf.
 For example, ~\cite{cerutti2013understanding} uses a polygonal leaf model for leaf segmentation and plant identification.
-This leaf structure information can be used to analysis the difference of plant phenotyping within one leaf.  
-\\ \textcolor{red}{could not find a reference.}
+Second, plant biologists often hypothesize that different local parts of a leaf may have different photosynthetic efficiency.
+This leaf structure information can be used to quantitatively study this hypothesis and its implication to the overall photosynthetic efficiency of a plant.
+%\\ \textcolor{red}{could not find a reference.}
 \end{response}
@@
 Therefore, we do not add the references in Table $2$ for conciseness.
+
+TBD: pls add reference in Tab.2
 \end{response}
@@
 \begin{response}
-We adjust language by the statement of "we summarize some existing publicly available databases that are related to plant imagery". 
+We adjust language by the statement of ``we summarize existing publicly available databases that are most related to our work".
+
 \end{response}
@@
 \begin{response}
-Here we want to emphasize that it is not necessary to train and test on the same modality. 
-For example, if we would like to develop a leaf segmentation algorithm that can work on RGB images, we can still utilize the depth images during training.   
-\\ \textcolor{red}{I am not sure if I understand the statement correctly.}
+%Here we want to emphasize that it is not necessary to train and test on the same modality. 
+%For example, if we would like to develop a leaf segmentation algorithm that can work on RGB images, we can still utilize the depth images during training.   
+In this use case scenario, the training part of leaf segmentation algorithms may have both the RGB and depth modalities, while during the testing, we may only have the RGB modality available.
+This scenario is useful because it leverages additional information during the training, while does not increase the hardware/sensor cost during the testing.
+Specifically, we may use two types of approachs to implement this scenario.
+One is called learning with side information, which is the depth modality in this example (see~\cite{chen2013boosting}).
+The other is to use transfer learning that handles missing modality in the target domain (see~\cite{ding2014latent}).
+
 \end{response}
@@
 \\ \textcolor{red}{I do not understand what to be added to Table $1$.}
+TBD: Dr. Chen, please add some sentences about mutants in bean data. I recell we plan to capture additional bean data sets that have different mutants. Am I right?
+
 \end{response}
@@
 \bibliographystyle{IEEEbib}
-\bibliography{references}
+\bibliography{abbrev,references}
 }

### 2015-07-14 response/response.tex
xi_reference in table 2

@@
 We have the corresponding references in the prior work section, which follows the order as they appear in Table $2$.
-Therefore, we do not add the references in Table $2$ for conciseness.
-
-TBD: pls add reference in Tab.2
+To make it complete, we also added the reference to Table $2$. 
 \end{response}
@@
 This scenario is useful because it leverages additional information during the training, while does not increase the hardware/sensor cost during the testing.
-Specifically, we may use two types of approachs to implement this scenario.
+Specifically, we may use two types of approaches to implement this scenario.
 One is called learning with side information, which is the depth modality in this example (see~\cite{chen2013boosting}).

### 2015-07-14 datapaper_intro.tex
xi_reference in table 2

@@
 \begin{tabular}{l|c|c|c|c|c|c}
+%\hline
+%\multirow{2}{*}{Database}& \multirow{2}{*}{Modality} & \multirow{2}{*}{Applications}\tnote{a} & \multirow{2}{*}{Plant Type} & Subject/ &Total & Labeled \\
+%& & & & Classe \# & Image \# & Image \# \\ \hline
+%Swedish leaf~\cite{soderkvist2001computer} & Scaned leaf & LC& Swedish trees & $15$ & $1,125$ & $1,125$ \\ \hline
+%Flavia~\cite{wu2007leaf} & RGB & LC& Leaves & $32$ & $2,120$ & $2,120$ \\ \hline
+%Leafsnap~\cite{kumar2012leafsnap} & RGB & LC& USA trees & $184$ & $29,107$ & $29,107$ \\ \hline
+%Crop/weed~\cite{haug2014crop} & RGB &Weed detection & Crop/weed & $2$ & $60$ & $60$ \\ \hline
+%\multirow{2}{*}{LSC~\cite{haug2014crop}} & \multirow{2}{*}{RGB} & \multirow{2}{*}{LS, LO} & Arabidopsis & $43$ & $6287$ & $201$ \\ \cline{4-7}
+%& & & Tobacco & $80$ & $165,120$ & $83$ \\ \hline
+%\multirow{2}{*}{MSU-PID} & fluorescence, & LS, LO, & Arabidopsis & $16$ & $2304\times 4$ & $576\times 4$ \\ \cline{4-7}
+%& IR, RGB, depth & LA, LT & Bean & $5$ & $350\times 4$ & $175\times 4$ \\ \hline
+%\hline
 \hline
@@
 & & & & Classe \# & Image \# & Image \# \\ \hline
-Swedish leaf & Scaned leaf & LC& Swedish trees & $15$ & $1,125$ & $1,125$ \\ \hline
-Flavia & RGB & LC& Leaves & $32$ & $2,120$ & $2,120$ \\ \hline
-Leafsnap & RGB & LC& USA trees & $184$ & $29,107$ & $29,107$ \\ \hline
-Crop/weed & RGB &Weed detection & Crop/weed & $2$ & $60$ & $60$ \\ \hline
-\multirow{2}{*}{LSC} & \multirow{2}{*}{RGB} & \multirow{2}{*}{LS, LO} & Arabidopsis & $43$ & $6287$ & $201$ \\ \cline{4-7}
-& & & Tobacco & $80$ & $165,120$ & $83$ \\ \hline
+Swedish leaf & \multirow{2}{*}{Scaned leaf} & \multirow{2}{*}{LC} & \multirow{2}{*}{Swedish trees} & \multirow{2}{*}{$15$} & \multirow{2}{*}{$1,125$} & \multirow{2}{*}{$1,125$} \\ 
+~\cite{soderkvist2001computer} & & & & & & \\ \hline
+Flavia & \multirow{2}{*}{RGB} & \multirow{2}{*}{LC} & \multirow{2}{*}{Leaves} & \multirow{2}{*}{$32$} & \multirow{2}{*}{$2,120$} & \multirow{2}{*}{$2,120$} \\ 
+~\cite{wu2007leaf} & & & & & & \\ \hline
+Leafsnap & \multirow{2}{*}{RGB} & \multirow{2}{*}{LC} & \multirow{2}{*}{USA trees} & \multirow{2}{*}{$184$} & \multirow{2}{*}{$29,107$} & \multirow{2}{*}{$29,107$} \\ 
+~\cite{kumar2012leafsnap} & & & & & & \\ \hline
+Crop/weed & \multirow{2}{*}{RGB} & \multirow{2}{*}{Weed detection} & \multirow{2}{*}{Crop/weed} & \multirow{2}{*}{$2$} & \multirow{2}{*}{$60$} & \multirow{2}{*}{$60$} \\ 
+~\cite{haug2014crop} & & & & & & \\ \hline
+LSC & \multirow{2}{*}{RGB} & \multirow{2}{*}{LS, LO} & Arabidopsis & $43$ & $6287$ & $201$ \\ \cline{4-7}
+~\cite{haug2014crop} & & & Tobacco & $80$ & $165,120$ & $83$ \\ \hline
 \multirow{2}{*}{MSU-PID} & fluorescence, & LS, LO, & Arabidopsis & $16$ & $2304\times 4$ & $576\times 4$ \\ \cline{4-7}

### 2015-07-15 datapaper_hardware.tex
update for "dense" comment

@@
 The sensor contains both a $1280 \times 720$ color camera directed parallel to, and separated by roughly $25~mm$ from, a depth camera which has a resolution of $320\times240$ pixels.
-The depth sensor uses a flash near IR illuminator and measures the time-of-flight of the beam at each pixel to obtain dense depth estimates along with an IR reflectance at each pixel.
+The depth sensor uses a flash near IR illuminator and measures the time-of-flight~\cite{Hansard2013} of the beam at each pixel to obtain depth estimates along with an IR reflectance at each pixel.
 

### 2015-07-15 response/morrisResponse.tex
Added in my responses

\documentclass[11pt,letterpaper]{article}

\usepackage[top=1in,bottom=1in,left=1in,right=1in]{geometry}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{cite}
\usepackage{bm}
\usepackage[usenames]{color}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{textcomp}
\usepackage{times}
\usepackage{url}
\usepackage{xr}
\usepackage{xcolor}

\newcommand\todo[1]{\textcolor{red}{#1}}

\newcounter{reviewcounter}
\setcounter{reviewcounter}{1}

\newenvironment{review}
{\noindent {\bf Comment~\arabic{reviewcounter}}:\addtocounter{reviewcounter}{1}\itshape}
{\vspace{0.8em}}

\newenvironment{response}
{\noindent {\bf Response}: \color{black}}
{\color{black} \vspace{1.6em}}

\title{Morris Responses}

\begin{document}

\maketitle

\todo{To-do notes are in red}

%B1)
\begin{review}
The authors do a nice work of calibrating the cameras and measuring noise in the depth camera. However, in page 2 introduction say that this calibration allows for the explicit correspondence between pixels of any modality.  The authors rely on this to annotate data in one modality and propagate labels in the other (at least this is what I understand from later on description of methodology).  However, this is a VERY strong assumption and depends completely on the distance between the cameras, the angles, the distance between object and sensors and the actual object arrangement. From our experience even when imaging co-planar plants (such as young arabidopsis) at a distance of ~70cm even when the camera sensors are really close to each other (less than 5cm) some differences in view are there and occlusions are present.  The authors should comment on this and should show as supportive evidence examples of plants at different growth stages in all 4 modalities in raw and
annotated form to show how close this correspondence is matching and how the propagated labels.  Furthermore, additional supporting evidence could be obtained either by arranging for two external and blind annotators
to label some data (different age, different placement in the tray to show the effect of angle) in another modality (e.g., optical) and then measure inter-observer variability. Then they can propagate annotations from fluorescence to images of that modality and measure agreement. If this agreement is better than the in between rater variability then you could argue that propagating annotations is ok to do and actually beneficial.  Nevertheless, you should definitely mention this limitation of your work. 
\end{review}

\begin{response}
\todo{write response}
\end{response}

%C)
\begin{review}
Fig 3 (a) ... From Fig 2 it appears the distance from plant to sensor to be greater than 60mm (6cm) !!! ie., to me it looks close to 60cm, but either Fig 3 has wrong axis range or something else is going on. Can you please explain/update?
Also same figure (3), shouldn't the images overlap? why are shown translated?  
\end{review}

\begin{response}
Yes, the distance to the plant is roughly 620mm.  The image planes are plotted not at the plant location, but at a distance proportional to the focal length of each camera.  We added dashed lines to the figure to make it clearer that these planes do not correspond to the plant depth, and updated the caption to explain it better.
\end{response}

%E1
\begin{review}
On manual annotation process:  Did you use an extra annotator or a supervisor? 
\end{review}

\begin{response}
\todo{What does this question mean -- what is a supervisor?}
\end{response}

%E4
\begin{review}
Again going back to the problem of lack of exact 1-1 correspondence between modalities, how can you guarantee that labels on one are good on the other given such high differences in resolutions among modalities?  Please include at least some visual examples.
\end{review}

\begin{response}
\todo{response similar to above}
\end{response}

%A
\begin{review}
I do not subscribe to the term dense for such low resolution depth cameras. In my book dense refers to high res depth maps. Maybe the authors can reconsider the use of the term.
\end{review}

\begin{response}
We agree and removed the term dense from the depth map image.
\end{response}

\end{document}

### 2015-07-21 datapaper_conclusion.tex
Chen edit

@@
-\section{Conclusions}
+\section{Conclusion and Discussion}
 
@@
 Furthermore, we are also open to suggestions and comments from the users of this database to further enhance our imaging setup and capturing protocol, so that we can develop new databases in the future.
+
+It might be noticed that all plants (respectively for Arabidopsis and bean) in MSU-PID belong to the same genotype and no treatments applied.
+%This would entail that the proposed dataset cannot be used to investigate computer vision algorithms or imaging modalities in relation to group differences.
+Could the authors comment on this?
+This is true.
+We are not comparing group differences, based on morphology (for example).
+This is because we think a fundamental issue with visual phenotyping, i.e.
+accurate and automated identification and tracking of individual leaves over developmental time scales (weeks), which importance has being highlighted in Introduction, needs to be solved before expending our goal to define group differences.
+The inherent challenge in this issue is that as leaves emerge and grow, they change in size, position and shape and they may overlap or be overlapped by other leaves.
+%I think that new text we have added more clearly emphasizes leaf identification and tracking over time rather than developing methods/algorithms to define group differences.

### 2015-07-21 datapaper_hardware.tex
fig2
fig 2
Chen edit

@@
 \begin{figure}
-  \includegraphics[width=\linewidth,trim=55 100 200 70,clip]{Figures/hardware}
+  \includegraphics[width=0.95\linewidth]{Figures/hardware}
 \caption{The hardware setup for our data collection.}
@@
 Infrared images were collected once every hour with the same camera and filter used for chlorophyll {\it a} fluorescence.
-Pulses of $940~nm$ light were provided by an array of OSRAM LEDs (SFH 4239, Digi-Key), collimated using a Polymer Optics lens (Part no. 170, Polymer Optics Ltd., Berkshire, England).
-Since $940~nm$ light does not influence plant development or drive photosynthesis, images were also collected during the night period~\cite{eskins1992light}.
+Pulses of $940nm$ light were provided by an array of OSRAM LEDs (SFH 4239, Digi-Key), collimated using a Polymer Optics lens (Part no. 170, Polymer Optics Ltd., Berkshire, England).
+Since $940nm$ light does not influence plant development or drive photosynthesis, images were also collected during the night period~\cite{eskins1992light}.
 %
-Precisely, phytochromes are the closest photoreceptors that absorb in the far red, near infrared region, but the action spectrum is diminished to zero or near zero ($>800~nm$) in the region where we do IR reflectance ($940~nm$)~\cite{butler1964actton}.
+Precisely, phytochromes are the closest photoreceptors that absorb in the far red, near infrared region, but the action spectrum is diminished to zero or near zero ($>800nm$) in the region where we do IR reflectance ($940nm$)~\cite{butler1964actton}.
 %
@@
 The imagery data, including the fluorescent image, the IR reflectance image,  the color image, and the $3$D depth image, were collected once every hour.
-First, the fluorescent image and the IR reflectance image were captured sequentially using the same camera without any delay.
 %
-After five minutes, the $3$D depth image and the color image were captured using the Creative Senz3D sensor.
-The captured depth points were then transformed into the world coordinates and expressed in the unit of $mm$.
-Since plant leaves do not move quickly, the five minutes gap between the camera operations do not cause severe problems in image calibration.
+Five minutes before the end of each hour, $3$D depth images and the color image were captured using the Creative Senz3D sensor (the depth points were transformed into the world coordinates and expressed in the unit of $mm$), followed by fluorescence and the IR reflectance images collected sequentially at 2 minute intervals by the IR filtered CCD camera.
+%
+No substantial movements or growth were observed within the about four minute period required for image capture using all four modalities, minimizing potential problems in image calibration.
+
+%First, the fluorescent image and the IR reflectance image were captured sequentially using the same camera without any delay.
+%
+%After five minutes, the $3$D depth image and the color image were captured using the Creative Senz3D sensor. 
+%Since plant leaves do not move quickly, the five minutes gap between the camera operations do not cause severe problems in image calibration.
 

### 2015-07-21 datapaper_intro.tex
Chen edit

@@
 
+One practical goal of plant visual phenotyping is to accurately quantify plant traits, particularly those related to photosynthetic performance, growth, yield and resilience to environmental stress.
+For the approach to be of practical use, plants must be monitored continuously, over developmental time scales and under conditions that more closely approximate the native environment (dynamic 'field' conditions)~\cite{fahlgren2015lights,walter2015plant}.
+%
+The capacity to identify and track individual leaves throughout experiments will be important for more clearly defining phenotypic behaviors related to leaf specific factors such as developmental age~\cite{schottler2015photosynthetic} and/or following the application of stress.
+For example, decreases in the average photosynthetic efficiency ($\Phi_{II}$, quantum yield of photochemistry at photosystem II) of an Arabidopsis plant may reflect a heterogeneous distribution of $\Phi_{II}$ values across its entire photosynthetic surface area~\cite{oxborough2004imaging}.
+In this case, mapping distributions to individual leaves can be used to distinguish between a systemic (whole plant) effect and localization of the effect to subset leaves.
+%
+In addition, using more detailed information, such as leaf angle and height/position as well as canopy density/size, it should be possible to improve estimates of total photosynthetic capacity over time (particularly for plants with more complex canopies, like common bean or tobacco), since these factors influence absorption and availability of the light energy used to drive photosynthesis.
+
 \begin{table*}[t!]
@@
 
+%
 The type and amount of manual labels on a database is a critical enabler to the potential applications of the database.

### 2015-07-21 datapaper_prior.tex
final edits
Chen edit

@@
 
-We summarize some existing publicly available databases that are related to plant imagery in Table~\ref{tab:database}.
+We summarize existing publicly available databases that are most related to our work in Table~\ref{tab:database}.
 In terms of potential applications of these databases, they can be categorized into two types.
@@
 The second type of databases is for plant phenotyping, where it is important to capture plant images without interfering the growth of plants.
-Thus, non-destructive imaging approaches are taken and the entire plant is imaged.
-The LSC database~\cite{scharr2014annotated} is the most relevant one to our database.
+Thus, non-destructive imaging approaches are taken and the entire plant is imaged. The LSC database~\cite{scharr2014annotated} is the most relevant one to our database. 
 It captures a large set of RGB images for the Arabidopsis and Tobacco plants. 
@@
 
-The four sensing modalities provide unique opportunities to comprehensively characterize plant morphological and physiological phenotypes.
-Chlorophyll fluorescence measurement is an effective method to detect photosynthesis.
-For example, steady-state chlorophyll fluorescence is a relative measure of photosynthetic health in drought stress~\cite{chen2014dissecting}.
-The quantum efficiency of photosystem II can be approximated by comparing chlorophyll fluorescence levels under two light conditions~\cite{baker2008chlorophyll}.
+%One of our data modalities is dense depth measurement.
+This has been a component of a number of recent non-plant RGB-D databases designed for object recognition~\cite{Lai2011}, scene segmentation~\cite{Silberman2011}, human analysis~\cite{Sung2011,Barbosa:reid12}, and mapping~\cite{sturm12iros}.
+By including dense depth for a plant database we anticipate enabling development of new 3D plant shape analysis algorithms.
+
+The four sensing modalities in MSU-PID provide unique opportunities to comprehensively characterize plant morphological and physiological phenotypes.
+The use of chlorophyll fluorescence at $730$ to $750nm$ as a tool for evaluating photosynthetic performance is well established~\cite{baker2008chlorophyll}, and against non-(chlorophyll)fluorescent background clearly defines photosynthetically active leaf area.
 The dense depth measurement has been a component of a number of recent non-plant RGB-D databases designed for object recognition~\cite{Lai2011}, scene segmentation~\cite{Silberman2011}, human analysis~\cite{Sung2011,Barbosa:reid12}, and mapping~\cite{sturm12iros}.
 By including dense depth for a plant database we anticipate enabling development of new 3D plant canopy analysis algorithms, thus probing the total energy intake and storage.
-The infrared measurement enables researchers to detect chloroplast movements, which have been proposed to optimize light capture and minimize photodamage to the photosynthetic apparatus~\cite{Dutta2015Non}.
+Near infrared (IR) reflectance has been used by others to detect water content in leaves~\cite{chen2014dissecting}.
+However, it may also be useful in determining leaf angle and curvature.
+Furthermore, since imaging occurs at a wavelength that is effectively non-absorbing for photosynthesis or known light receptors~\cite{butler1964actton,eskins1992light} in plants, it can be used for imaging during the night cycle to observe night time leaf expansion or in some cases circadian movements~\cite{mcclung2006plant}.

### 2015-07-21 datapapr_labeling.tex
Chen edit

@@
 %\end{figure*}
+
+It is often argued which is the best setting due to the trade-off between the image resolution and the throughput of phenotyping experiments. 
+We chose to image a whole tray of Arabidopsis at lower resolution rather than an individual at higher resolution, because it better reflects high-throughput protocols, which in practice allows direct comparison of multiple genotypes in the same experiment.
+In contrary, we chose to image a single bean plant because we anticipate enabling development of $3$D plant canopy reconstruction algorithms for bush plants.
 

### 2015-07-22 response/response.tex
Xi_response combined

@@
 \renewcommand{\thefigure}{R-\arabic{figure}}
+
+\newcommand\todo[1]{\textcolor{red}{#1}}
 
@@
 \begin{review}
+The text (including the abstract) contains many typographical and grammatical errors, which are distracting and render the manuscript difficult to read.
+The authors should proofread the document carefully.
+\end{review}
+
+\begin{response}
+\todo{Proofread by everyone}
+\end{response}
+
+% Reviewer 1: Q2
+\begin{review}
+In the introduction, four example applications are mentioned for which the dataset can be used.
+According to the title of the paper the dataset is proposed for phenotyping applications.
+Thus, the authors should elaborate on why and how the computer vision tasks they mention are relevant to plant phenotyping.
+The authors should also include few key references to works that use (or discuss) such features for plant phenotyping.
+\end{review}
+
+\begin{response}
+We have added two paragraphs with related references in the Sec. $1$ to better connect plant phenotyping and computer vision tasks. 
+They are paragraph $2$ and $3$. 
+\end{response}
+
+% Reviewer 1: Q3
+\begin{review}
 The authors should clarify what is intended by "leaf alignment" and why it is important, since this feature is probably less common in plant phenotyping applications than the others that are mentioned.
@@
 This leaf structure information can be used to quantitatively study this hypothesis and its implication to the overall photosynthetic efficiency of a plant.
-%\\ \textcolor{red}{could not find a reference.}
 \end{response}
 
-% Reviewer 1: Q2
+% Reviewer 1: Q4
+\begin{review}
+Since multi-modality is a strength of the proposed dataset, the authors should motivate better their choice of imaging modalities (i.e.
+fluorescence, infrared, RGB color, and depth), highlighting their importance and what information they convey on plant structure and functions.
+Apparently, this is only partly done for depth at the end of Sec. $2$.
+\end{review}
+
+\begin{response}
+We have inserted a brief explanation with references in the last paragraph of Sec. $2$. 
+\end{response}
+
+% Reviewer 1: Q5
 \begin{review}
@@
 \begin{response}
-We have augmented Fig.$1$ by adding one zoom-in view for each image.
+We have augmented Fig.$1$ by adding one zoom-in view for Arabidopsis plant.
+Since bean dataset only includes one plant in the view, we did not provide a zoom-in view.
 \end{response}
 
-% Reviewer 1: Q3
+% Reviewer 1: Q6
 \begin{review}
@@
 
-% Reviewer 1: Q4
+% Reviewer 1: Q7
 \begin{review}
@@
 We adjust language by the statement of ``we summarize existing publicly available databases that are most related to our work".
-
 \end{response}
 
-% Reviewer 1: Q5
+% Reviewer 1: Q8
 \begin{review}
@@
 
-% Reviewer 1: Q6
+% Reviewer 1: Q9
+\begin{review}
+It appears from Sec. $3.1$ that all plant subjects (respectively for Arabidopsis and bean) belong to the same genotype and that no treatments were performed.
+This would entail that the proposed dataset cannot be used to investigate computer vision algorithms or imaging modalities in relation to group differences.
+Could the authors comment on this?
+\end{review}
+
+\begin{response}
+It is true that we did not compare group differences, based on morphology (for example).
+However, we are using these data sets to address a fundamental issue with visual phenotyping; accurate and automated identification and tracking of individual leaves over developmental time scales (weeks).
+The reason this is important is highlighted in other sections, in particular in text we are adding to address point $1$ and $2$.  
+The inherent challenge of course is that as leaves emerge and grow, they change in size, position and shape and they may overlap or be overlapped by other leaves.  
+I think that new text we have added more clearly emphasizes leaf identification and tracking over time rather than developing methods/algorithms to define group differences. 
+We added a paragraph in Conclusion.
+\end{response}
+
+% Reviewer 1: Q10
+\begin{review}
+In Sec. $3.2.1$ the authors remark that light used for night image acquisition does not influence plant development. 
+A reference should be included to support this statement.
+\end{review}
+
+\begin{response}
+We have revised the second paragraph in Sec. $3.2.1$ and added two references to support this statement. 
+\end{response}
+
+% Reviewer 1: Q11
+\begin{review}
+As for the other lighting and imaging protocols adopted by the authors (Sec. $3.2.1$ and $3.2.2$), do they interfere with plant growth?
+\end{review}
+
+\begin{response}
+\todo{Jin}
+\end{response}
+
+% Reviewer 1: Q12
 \begin{review}
@@
 
-% Reviewer 1: Q7
+% Reviewer 1: Q13
 \begin{review}
@@
 
-% Reviewer 1: Q8
+% Reviewer 1: Q14
 \begin{review}
@@
 
-% Reviewer 1: Q9
+% Reviewer 1: Q15
 \begin{review}
@@
 
-% Reviewer 1: Q10
+% Reviewer 1: Q16
 \begin{review}
@@
 \begin{response}
-
+\todo{Xi}
 \end{response}
 
-% Reviewer 1: Q11
+% Reviewer 1: Q17
 \begin{review}
@@
 
-% Reviewer 1: Q12
+% Reviewer 1: Q18
 \begin{review}
@@
 
-% Reviewer 1: Q13
+% Reviewer 1: Q19
 \begin{review}
@@
 
-% Reviewer 1: Q14
+% Reviewer 1: Q20
 \begin{review}
@@
 
-% Reviewer 2: Q15
+% Reviewer 2: Q21
 \begin{review}
@@
 The reason we do not include mutants is that we assume any computer vision algorithms that work on wildtypes should also work well on mutants as they have similar structure.
-\\ \textcolor{red}{I do not understand what to be added to Table $1$.}
-TBD: Dr. Chen, please add some sentences about mutants in bean data. I recell we plan to capture additional bean data sets that have different mutants. Am I right?
-
+\\ %\textcolor{red}{I do not understand what to be added to Table $1$.}
+\todo{TBD: Dr. Chen, please add some sentences about mutants in bean data. I recall we plan to capture additional bean data sets that have different mutants. Am I right?}
 \end{response}
 
-% Reviewer 2: Q16
+% Reviewer 2: Q22
+\begin{review}
+The authors do a nice work of calibrating the cameras and measuring noise in the depth camera. 
+However, in page $2$ introduction says that this calibration allows for the explicit correspondence between pixels of any modality.  
+The authors rely on this to annotate data in one modality and propagate labels in the other (at least this is what I understand from later on description of methodology).  
+However, this is a VERY strong assumption and depends completely on the distance between the cameras, the angles, the distance between object and sensors and the actual object arrangement. 
+From our experience even when imaging co-planar plants (such as young Arabidopsis) at a distance of $\sim 70$cm even when the camera sensors are really close to each other (less than $5$cm) some differences in view are there and occlusions are present.
+The authors should comment on this and should show as supportive evidence examples of plants at different growth stages in all $4$ modalities in raw and annotated form to show how close this correspondence is matching and how the propagated labels.
+Furthermore, additional supporting evidence could be obtained either by arranging for two external and blind annotators to label some data (different age, different placement in the tray to show the effect of angle) in another modality (e.g., optical) and then measure inter-observer variability.
+Then they can propagate annotations from fluorescence to images of that modality and measure agreement. 
+If this agreement is better than the in between rater variability then you could argue that propagating annotations is ok to do and actually beneficial.  
+Nevertheless, you should definitely mention this limitation of your work.
+\end{review}
+
+\begin{response}
+\todo{Daniel}
+\end{response}
+
+% Reviewer 2: Q23
+\begin{review}
+Furthermore, it assumes that cameras are perfectly synchronized which i) is not mentioned and ii) it cannot be done for some modalities since the same camera (with different filter) is used so some delay is expected.
+Granted the plants may not move in between but this should be clarified and mentioned.
+\end{review}
+
+\begin{response}
+\todo{Jin}
+\end{response}
+
+% Reviewer 2: Q24
+\begin{review}
+Fig.
+$3$ (a) ...
+From Fig.
+$2$ it appears the distance from plant to sensor to be greater than $60$mm ($6$cm) !!!
+ie., to me it looks close to $60$cm, but either Fig.
+$3$ has wrong axis range or something else is going on.
+Can you please explain/update?
+Also same Fig. $3$, shouldn't the images overlap? why are shown translated?
+\end{review}
+
+\begin{response}
+Yes, the distance to the plant is roughly $620$mm.  
+The image planes are plotted not at the plant location, but at a distance proportional to the focal length of each camera.  
+We added dashed lines to the figure to make it clearer that these planes do not correspond to the plant depth, and updated the caption to better explain it.
+\end{response}
+
+% Reviewer 2: Q25
+\begin{review}
+On Table $3$ you list resolutions for the acquired image data.  
+This image resolution is much lower than the LSC database of Scharr et al. 
+This limitation should be mentioned.
+\end{review}
+
+\begin{response}
+We added one paragraph in the end of Sec. $4.1$ to address the trade-off between image resolution and experiment throughput.
+\end{response}
+
+% Reviewer 2: Q26
+\begin{review}
+On manual annotation process:  Did you use an extra annotator or a supervisor?
+\end{review}
+
+\begin{response}
+\todo{Yes, we use an extra annotator to estimate the annotation error between different people.}
+\end{response}
+
+% Reviewer 2: Q27
 \begin{review}
@@
 
-% Reviewer 2: Q17
+% Reviewer 2: Q28
 \begin{review}
@@
 
-% Reviewer 2: Q18
+% Reviewer 2: Q29
+\begin{review}
+Again going back to the problem of lack of exact $1-1$ correspondence between modalities, how can you guarantee that labels on one are good on the other given such high differences in resolutions among modalities?
+Please include at least some visual examples.
+\end{review}
+
+\begin{response}
+Please refer to comment $22$.
+\end{response}
+
+% Reviewer 2: Q30
 \begin{review}
@@
 
-% Reviewer 2: Q19
+% Reviewer 2: Q31
 \begin{review}
@@
 
-% Reviewer 2: Q20
+% Reviewer 2: Q32
 \begin{review}
@@
 
-% Reviewer 2: Q21
+% Reviewer 2: Q33
+\begin{review}
+I do not subscribe to the term dense for such low resolution depth cameras. 
+In my book dense refers to high res depth maps. 
+Maybe the authors can reconsider the use of the term.
+\end{review}
+
+\begin{response}
+We agree and have removed the term ``dense" from the depth map image.
+\end{response}
+
+% Reviewer 2: Q34
+\begin{review}
+I am not sure the authors used the correct reference for Erblichkeit $1903$. 
+I think Erblichkeit is part of the title. 
+A google search reveals this: http://caliban.mpipz.mpg.de/johannsen/erblichkeit/
+with the author being: Wilhelm Ludwig Johannsen.
+Please check.
+\end{review}
+
+\begin{response}
+It is right that Erblichkeit is the part of the title and the author name is Wilhelm Ludwig Johannsen.
+We have corrected it. 
+\end{response}
+
+% Reviewer 2: Q35
+\begin{review}
+In page $4$, line $4$, maybe you should put Chlorophyll a either in quotes or italics so a is not confused as an article. 
+\end{review}
+
+\begin{response}
+We have put it in italics to avoid confusion. 
+\end{response}
+
+% Reviewer 2: Q36
+\begin{review}
+Figure $2$ if possible can you please also include an image showing the cameras from the view of the plant (LED off)?
+\end{review}
+
+\begin{response}
+Figure $2$ is updated with extended details. 
+Please refer to the paper. 
+\end{response}
+
+% Reviewer 2: Q37
+\begin{review}
+Collimated ... is a nice special term, but please put in parenthesis the definition to help broad readership.
+\end{review}
+
+\begin{response}
+\todo{Jin}
+\end{response}
+
+% Reviewer 2: Q38
+\begin{review}
+Please also define object albedo again to broaden readership.  
+\end{review}
+
+\begin{response}
+\todo{Daniel}
+\end{response}
+
+% Reviewer 2: Q39
 \begin{review}

### 2015-07-22 datapaper_intro.tex
Xi_response combined

@@
 \includegraphics[width=.23\textwidth]{Figures/FourModalities/B_ir}\\
-(d) &
-\includegraphics[width=.1\textwidth]{Figures/FourModalities/B1_rgb}&
-\includegraphics[width=.1\textwidth]{Figures/FourModalities/B1_depth}&
-\includegraphics[width=.2\textwidth]{Figures/FourModalities/B1_fmp}&
-\includegraphics[width=.2\textwidth]{Figures/FourModalities/B1_ir}\\
+%(d) &
+%\includegraphics[width=.1\textwidth]{Figures/FourModalities/B1_rgb}&
+%\includegraphics[width=.1\textwidth]{Figures/FourModalities/B1_depth}&
+%\includegraphics[width=.2\textwidth]{Figures/FourModalities/B1_fmp}&
+%\includegraphics[width=.2\textwidth]{Figures/FourModalities/B1_ir}\\
 %Bean: RGB & Bean: depth & Bean: fluorescence & Bean: IR \\
@@
 \end{tabular}
-\caption{The multi-modality plant imagery database of MSU-PID.
-(a) four modalities of Arabidopsis; (b) zoom in view of Arabidopsis plant $1$; (c) four modalities of bean; (d) zoom in view of bean plant.}
+\caption{The multi-modality plant imagery database of MSU-PID. (a) four modalities of Arabidopsis; (b) zoom in view of Arabidopsis plant $1$; (c) four modalities of bean.}
 \label{fig:fourmodality}
@@
 Plant visual phenotyping has been performed by farmers and breeders for more than 5,000 years.
-In the past, traditional phenotyping is based on experience and intuition, and is laborious~\cite{Erblichkeit1903}.
+In the past, traditional phenotyping is based on experience and intuition, and is laborious~\cite{johannsenerblichkeit}.
 Recent progresses in imaging sensor, robotics and automation technologies lead to the development of the ever-increasing new field of highly automated, non-destructive {\it plant visual phenotyping}~\cite{furbank2011phenomics,cruz2015depi}.

### 2015-07-22 response/response.tex
xi_response edit

@@
 \begin{response}
-We have added two paragraphs with related references in the Sec. $1$ to better connect plant phenotyping and computer vision tasks. 
-They are paragraph $2$ and $3$. 
+We have added two paragraphs with related references to better connect plant phenotyping and computer vision tasks. 
+Please refer to paragraph $2$ and $3$ in Sec. $1$. 
 \end{response}
@@
 \begin{review}
-The authors should clarify what is intended by "leaf alignment" and why it is important, since this feature is probably less common in plant phenotyping applications than the others that are mentioned.
+The authors should clarify what is intended by ``leaf alignment" and why it is important, since this feature is probably less common in plant phenotyping applications than the others that are mentioned.
 \end{review}
@@
 Leaf alignment is important for two reasons:
-First, it goes beyond leaf segmentation and provide structural information of a leaf - a discriminative signature for a leaf.
+First, it goes beyond leaf segmentation and provides structural information of a leaf - a discriminative signature for a leaf.
 For example, ~\cite{cerutti2013understanding} uses a polygonal leaf model for leaf segmentation and plant identification.
@@
 \begin{review}
- Figure $1$ should be augmented (or a separate figure should be created) with zoom in details showing how the same plant parts (or scene portions) appear in the different modalities.
+Figure $1$ should be augmented (or a separate figure should be created) with zoom in details showing how the same plant parts (or scene portions) appear in different modalities.
 This would help the reader get a better idea of the contrast and the type of information conveyed by each of the modalities adopted by the authors.
@@
 \begin{response}
-We have augmented Fig.$1$ by adding one zoom-in view for Arabidopsis plant.
-Since bean dataset only includes one plant in the view, we did not provide a zoom-in view.
+We have augmented Fig. $1$ by adding one zoom-in view for Arabidopsis plant.
+Since bean dataset only includes one plant with good view, we do not provide a zoom-in view.
 \end{response}
@@
 \begin{review}
-The second paragraph of Sec. $2$ begins with "we summarize all existing publicly available databases that are related to plant imagery".
-This is a strong statement, particularly because other plant related image datasets exist (e.g., ImageCLEF, ICL leaf database) which are omitted from the review.
+The second paragraph of Sec. $2$ begins with ``we summarize all existing publicly available databases that are related to plant imagery".
+This is a strong statement, particularly because other plant related image databases exist (e.g., ImageCLEF, ICL leaf database) which are omitted from the review.
 The authors should adjust language and/or expand the literature review.
@@
 \begin{response}
-We adjust language by the statement of ``we summarize existing publicly available databases that are most related to our work".
+We have adjusted the language by the statement of ``we summarize existing publicly available databases that are most related to our work".
 \end{response}
@@
 \begin{response}
-It is true that we did not compare group differences, based on morphology (for example).
-However, we are using these data sets to address a fundamental issue with visual phenotyping; accurate and automated identification and tracking of individual leaves over developmental time scales (weeks).
-The reason this is important is highlighted in other sections, in particular in text we are adding to address point $1$ and $2$.  
-The inherent challenge of course is that as leaves emerge and grow, they change in size, position and shape and they may overlap or be overlapped by other leaves.  
+It is true that we do not compare group differences, based on morphology (for example).
+However, we are using this database to address a fundamental issue with visual phenotyping: accurate and automated identification and tracking of individual leaves over developmental time scales (weeks).
+The reason this is important is highlighted in other sections, in particular in text we are adding to address Comment $2$ and $4$.  
+The inherent challenge is that leaves change in size, position, and shape as they emerge and grow. 
+Also they may overlap or be overlapped by other leaves.  
 I think that new text we have added more clearly emphasizes leaf identification and tracking over time rather than developing methods/algorithms to define group differences. 
-We added a paragraph in Conclusion.
+We have added one paragraph in Conclusion to better reflect this. 
 \end{response}
@@
 \begin{response}
-We have revised the second paragraph in Sec. $3.2.1$ and added two references to support this statement. 
+We have revised paragraph $2$ in Sec. $3.2.1$ and added $2$ references to support this statement. 
 \end{response}
@@
 The other is to use transfer learning that handles missing modality in the target domain (see~\cite{ding2014latent}).
-
 \end{response}
@@
 \begin{review}
-In Sec. $5$ no baseline method or result is reported for bean images. Could the authors comment on this?
+In Sec. $5$ no baseline method or result is reported for bean images. 
+Could the authors comment on this?
 \end{review}
@@
 \begin{response}
-\textcolor{red}{will expand after everything finished}
+\todo{will expand after everything finished}
 \end{response}
@@
 \begin{response}
-Except in the Abstract, the "MSU-PID" first appears in fourth paragraph in Sec $1$.
+Except in the Abstract, the "MSU-PID" first appears in paragraph $4$ of Sec $1$.
 We have clearly defined it as short for Michigan State University Plant Image Database.
@@
 \begin{review}
-In Eq. $3$, p. $8$, the authors should better define the symbols used. In particular, it is not clear if subscripts $1$ and $2$ refer to inner and outer leaf tips respectively, and in which order.
+In Eq. $3$, p. $8$, the authors should better define the symbols used. 
+In particular, it is not clear if subscripts $1$ and $2$ refer to inner and outer leaf tips respectively, and in which order.
 \end{review}
@@
 \begin{response}
-We refer to Scharr et al $2014$ that the Leaf Segmentation Challenge datasets only includes independent images without tracking context.
+We refer to Scharr et al $2014$ that the Leaf Segmentation Challenge database only includes independent images without tracking context.
 The reason we do not include mutants is that we assume any computer vision algorithms that work on wildtypes should also work well on mutants as they have similar structure.
@@
 Can you please explain/update?
-Also same Fig. $3$, shouldn't the images overlap? why are shown translated?
+Also same Fig. $3$, shouldn't the images overlap? 
+Why are shown translated?
 \end{review}
@@
 \begin{review}
-On manual annotation process:  Did you use an extra annotator or a supervisor?
+On manual annotation process, did you use an extra annotator or a supervisor?
 \end{review}
@@
 \begin{response}
-\todo{Yes, we use an extra annotator to estimate the annotation error between different people.}
+The released label is labeled by one annotator. 
+However, we do use extra annotator to label several images and the annotation error between different annotators is evaluated. 
+\todo{Results?}
 \end{response}
@@
 Your annotation process is completely interactive.
-Any way to "save interaction" by interactive segmentation approaches?
+Any way to ``save interaction" by interactive segmentation approaches?
 I applaud your comment on the difficulty of merging super-pixel results, but I would add at least somewhere that easier ways to annotate will be beneficial.
@@
 \begin{review}
-It is unclear if you release this annotation tool? If not, please do... it will be extremely useful for the community.
+It is unclear if you release this annotation tool? 
+If not, please do. 
+It will be extremely useful for the community.
 \end{review}
@@
 \begin{response}
-We will release the labeling tool together with the dataset.
+We will release the labeling tool together with the database.
 \end{response}
@@
 During annotation, we can observe which leaf occludes which and annotate the overlapping area to the leaf on top.
-However, it is hard to refer which leaf occludes which from the annotations.
+However, it is hard to estimate which leaf occludes which from the annotations.
 \end{response}
@@
 \begin{response}
-\textcolor{red}{to be done: apply to RGB modality if label propagation works fine.}
+\todo{Xi: apply to RGB modality and evaluate the performance with transferred labels. Transferred label is needed!}
 \end{response}
@@
 \begin{response}
-It is right that Erblichkeit is the part of the title and the author name is Wilhelm Ludwig Johannsen.
+It is right that Erblichkeit is part of the title and the author's name is Wilhelm Ludwig Johannsen.
 We have corrected it. 

### 2015-07-22 datapaper_calibration.tex
xm's first edits
final edit
xi_edit paper

@@
 In this process the poses of all three cameras are also calculated relative to the checkerboard. 
-The intrinsic and extrinsic parameters are stored as text files, and a Matlab function is provided that reads the parameters and can plot the camera poses as in Figure~\ref{fig:CameraConfiguration}.
+The intrinsic and extrinsic parameters are stored as text files, and a Matlab function is provided that reads the parameters and can plot the camera poses as in Fig.~\ref{fig:CameraConfiguration}.
 
@@
 Doing so can lead to strategies to reduce noise as well as providing guidance to algorithms that use the depth measurements. 
-Our goal in this section is to provide a simple noise model that can predict the empirically observed depth noise on smooth, Lambertian surfaces, such as plant leafs.
+Our goal in this section is to provide a simple noise model that can predict the empirically observed depth noise on smooth, Lambertian surfaces, such as plant leaves.
 
-The depth noise, $\varepsilon$, is modeled as the sum of an image dependent term, $\varepsilon_I$, and a sensor dependent term, $\varepsilon_S$:
+The depth noise $\varepsilon$ is modeled as the sum of an image dependent term $\varepsilon_I$ and a sensor dependent term $\varepsilon_S$:
 \begin{equation}
-\varepsilon = \varepsilon_I + \varepsilon_S\label{eq:epsilon}
+\varepsilon = \varepsilon_I + \varepsilon_S. \label{eq:epsilon}
 \end{equation}
@@
 The variance of $\varepsilon_I$ is estimated for each pixel of a fixed scene observed over multiple images. 
-In our experiments we observed a flat, uniform albedo surface perpendicular to the camera at a sequence of depths, and for each depth acquired 300 images.
+In our experiments we observed a flat, uniform albedo surface perpendicular to the camera at a sequence of depths, and for each depth acquired $300$ images. 
 Object depth, $d$, has a large impact on $\varepsilon_I$. 
-For constant depth, we observed that the primary factor affecting the variance is the pixel radius, $r$, from the image center.
+For constant depth, we observed that the primary factor affecting the variance is the pixel radius $r$, from the image center. 
 Physically we expect this dependence is due to a circularly symmetric illuminating beam closely aligned with the optical axis. 
 Based on these observations we model $\sigma_I(d,r)$, the standard deviation of $\varepsilon_I$, as a function of depth and pixel radius.  
-From our experiments we build up a lookup table for this as plotted in Figure~\ref{fig:Noise}.
+From our experiments we build up a lookup table for this as plotted in Fig.~\ref{fig:Noise}.
 
@@
 \begin{center}
-\caption{Summary of Arabidopsis and Bean databases.}
+\caption{Summary of Arabidopsis and Bean databases.\todo{last column needs to be updated}}
 \label{tab:stat}
@@
 \begin{center}
-\caption{Plant image resolution of Arabidopsis and Bean databases.}
+\caption{Plant image resolution of Arabidopsis and Bean databases, computed based on the yellow ROIs in Fig.~\ref{fig:fourmodality}.}
 \label{tab:resolution}
@@
 % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
-Plants & Fluorescence & IR & RGB & Depth \\
+Plants & fluorescence & IR & RGB & depth \\
 \hline
@@
 We model these with $\varepsilon_S$. 
-To estimate its standard deviation, $\sigma_S$, we first average over many depth measurement images, in our case 300, to obtain pixel depth estimates that approximately eliminate the effect of $\varepsilon_I$.
+To estimate its standard deviation $\sigma_S$, we first average over many depth measurement images, in our case $300$, to obtain pixel depth estimates that approximately eliminate the effect of $\varepsilon_I$.
 Then by calculating true ray depths on a known surface, in our case the observed plane, and further assuming that $\varepsilon_S$ has the same standard deviation for all pixels, $\sigma_S$ is obtained as the standard deviation of the error between averaged depths and known depths.
-In our experiments we obtained $\sigma_S=6.5mm$, and found that it was insensitive to changes in depth.
+In our experiments we obtained $\sigma_S=6.5mm$ and found that it was insensitive to changes in depth.
 

### 2015-07-22 datapaper_intro.tex
xi_edit paper

@@
 %
-A classic genetics approach is to produce a diverse population of mutant lines, grow them either in growth chambers with simulated environmental conditions or directly in the field, visually observe the plants during the growth period, and finally identify plant morphological or physiological patterns that tightly associate with key growth factors~\cite{houle2010phenomics}.
+A classic genetic approach is to produce a diverse population of mutant lines, grow them either in growth chambers with simulated environmental conditions or directly in the field, visually observe the plants during the growth period, and finally identify plant morphological or physiological patterns that tightly associate with key growth factors~\cite{houle2010phenomics}.
 %
@@
 Plants develop through a complex interaction between genotype and environment. 
-This determines their structure and functions and thus performance such as yield or efficient use of resources.
+This determines their structure, functions, and thus performance such as yield or efficient use of resources. 
 In order to understand the genetic basis of these economically important parameters, it is essential to quantitatively assess plant phenotypes and then identify the latent relationships to genotypes and environmental factors.
 %
-Plant visual phenotyping has been performed by farmers and breeders for more than 5,000 years.
+Plant visual phenotyping has been performed by farmers and breeders for more than $5,000$ years. 
 In the past, traditional phenotyping is based on experience and intuition, and is laborious~\cite{johannsenerblichkeit}. 
@@
 %
-The objective of modern  plant visual phenotyping is to analyze and categorize the morphological  characteristics of plants, thus accurately quantifying plant traits.
+The objective of modern  plant visual phenotyping is to analyze and categorize the morphological characteristics of plants, and thus accurately quantifying plant traits.
 %It advances crop yield improvement and enables the systematic study of the environmental plasticity of plants.
@@
 One practical goal of plant visual phenotyping is to accurately quantify plant traits, particularly those related to photosynthetic performance, growth, yield and resilience to environmental stress.  
-For the approach to be of practical use, plants must be monitored continuously, over developmental time scales and under conditions that more closely approximate the native environment (dynamic 'field' conditions)~\cite{fahlgren2015lights,walter2015plant}.
+For the approaches to be of practical use, plants must be monitored continuously, over developmental time scales and under conditions that more closely approximate the native environment (dynamic 'field' conditions)~\cite{fahlgren2015lights,walter2015plant}.
 %
-The capacity to identify and track individual leaves throughout experiments will be important for more clearly defining phenotypic behaviors related to leaf specific factors such as developmental age~\cite{schottler2015photosynthetic} and/or following the application of stress.
-For example, decreases in the average photosynthetic efficiency ($\Phi_{II}$, quantum yield of photochemistry at photosystem II) of an Arabidopsis plant may reflect a heterogeneous distribution of $\Phi_{II}$ values across its entire photosynthetic surface area~\cite{oxborough2004imaging}.
+The capacity to identify and track individual leaves throughout experiments is important for more clearly defining phenotypic behaviors related to leaf specific factors such as developmental age~\cite{schottler2015photosynthetic} and/or following the application of stress.
+For example, decrease in the average photosynthetic efficiency ($\Phi_{II}$, quantum yield of photochemistry at photosystem II) of an Arabidopsis plant may reflect a heterogeneous distribution of $\Phi_{II}$ values across its entire photosynthetic surface area~\cite{oxborough2004imaging}.
 In this case, mapping distributions to individual leaves can be used to distinguish between a systemic (whole plant) effect and localization of the effect to subset leaves.
 %
-In addition, using more detailed information, such as leaf angle and height/position as well as canopy density/size, it should be possible to improve estimates of total photosynthetic capacity over time (particularly for plants with more complex canopies, like common bean or tobacco), since these factors influence absorption and availability of the light energy used to drive photosynthesis.
+In addition, using more detailed information, such as leaf angle and height/position as well as canopy density/size, it should be possible to improve estimation of total photosynthetic capacity over time (particularly for plants with more complex canopies, like common bean or tobacco), since these factors influence absorption and availability of the light energy used to drive photosynthesis.
 
@@
 
-To facilitate future research on plant image analysis, as well as remedy the limitation of existing databases in the field, this paper presents a newly collected multi-modality Plant Imagery Database through an interdisciplinary effort at Michigan State University (MSU), termed ``MSU-PID''.
-As illustrated in Figure~\ref{fig:fourmodality}, the MSU-PID database includes the imagery of two types of plants (Arabidopsis and bean), both are widely used in plant research, captured by four types of imaging sensors, i.e., fluorescence, infrared (IR), RGB color, and depth.
+To facilitate future research on plant image analysis, as well as remedy the limitation of existing databases in the field, this paper presents a newly collected multi-modality Plant Imagery Database through an interdisciplinary effort at Michigan State University (MSU), which is termed ``MSU-PID''.
+As illustrated in Fig.~\ref{fig:fourmodality}, the MSU-PID database includes the imagery of two types of plants (Arabidopsis and bean, both are widely used in plant research) captured by four types of imaging sensors, i.e., fluorescence, infrared (IR), RGB color, and depth.
 All four sensors are synchronized and are programmed to periodically capture imagery data for multiple consecutive days.
 Checkerboard-based camera calibration is performed between a pair of sensors, which results in the explicit correspondence between the pixels of {\it any} two modalities.
+\todo{Need to be updated about the transformation}
 
-%
 The type and amount of manual labels on a database is a critical enabler to the potential applications of the database.
-For a subset of the MSU-PID database, we manually label the ground truth regarding the leaf identification number, locations of leaf tips and leaf segments.
+For a subset of the MSU-PID database, we manually label the ground truth regarding the leaf identification number, locations of leaf tips, and leaf segments.
 As a result, MSU-PID is suitable for a number of applications, including 1) {\it leaf segmentation} that aims at estimating the correct segmentation mask of each leaf in an image, 2) {\it leaf counting} that estimates the correct number of leaves within a plant, 3) {\it leaf alignment} that aligns the two tips of each leaf -- the cornerstone of the leaf structure, and 4) {\it leaf tracking} that is designed to track each leaf over time.
@@
 This allows researchers to study the strength and weakness of individual modality, as well as their various combinations in plant image analysis.
-\item Our unique imaging setup and the variety of manual labels make MSU-PID an ideal candidate for evaluating a diverse set of plant image analysis applications, including leaf segmentation, leaf counting, leaf alignment, leaf tracking, and potentially leaf growth prediction and $3$D leaf reconstruction.
+\item Our unique imaging setup and the variety of manual labels make MSU-PID an ideal candidate for evaluating a diverse set of plant image analysis applications including leaf segmentation, leaf counting, leaf alignment, leaf tracking, and potentially leaf growth prediction and $3$D leaf reconstruction.
 \end{itemize}

### 2015-07-22 datapaper_plants.tex
xi_edit paper

@@
-\section{Data Collection}\label{sec:2}
+\section{Data Collection}
+\label{sec:2}
 
@@
 
-{\it Arabidopsis thaliana} (ecotype Col-0) plants were grown at $20^{\circ}C$, under a $16$ hr:$8$ hr day night cycle with a daylight intensity set at $100~\mu mol~photons~m^{-2} s^{-1}$.
+{\it Arabidopsis thaliana} (ecotype Col-0) plants were grown at $20^{\circ}C$, under a $16$hr : $8$hr day-night cycle with a daylight intensity set at $100~\mu mol~photons~m^{-2} s^{-1}$.
 %
-Black bean plants ({\it Phaseolus vulgaris L.}) of the cultivar Jaguar, were grown under a $14$ hr:$10$ hr day night cycle with night and day temperatures of $18^{\circ}C$ and $24^{\circ}C$ respectively, and a daylight intensity set at $200~\mu mol~photons~m^{-2} s^{-1}$.
+Black bean plants ({\it Phaseolus vulgaris L.}) of the cultivar Jaguar, were grown under a $14$hr : $10$hr day-night cycle with day and night temperatures of $24^{\circ}C$ and $18^{\circ}C$ respectively, and a daylight intensity set at $200~\mu mol~photons~m^{-2} s^{-1}$.
 %
@@
 %
-Two-week-old plants ({\it Arabidopsis} or bean) were transferred to imaging chambers and allowed to acclimate for $24$ hours to the LED lighting before the start of the data collection. 
+Two-week-old plants ({\it Arabidopsis} and bean) were transferred to imaging chambers and allowed to acclimate for $24$ hours to the LED lighting before the start of the data collection.
 Growth conditions as described above were maintained for each set of plants for the duration of image collection.

### 2015-07-22 datapaper_prior.tex
xi_edit paper

@@
 Hence, it is always important to develop and promote properly captured databases in the vision community.
-While there is a clear desire to apply computer vision to plant image analysis, the lack of publicly available plant image databases has been an obstacle for the further study and development.
+While there is a clear desire to apply computer vision to plant image analysis, the lack of publicly available plant image databases has been an obstacle for further study and development.
 
@@
 The Flavia database~\cite{wu2007leaf} is considerably larger and a neural network is utilized to train a leaf classifier.
-The most recent leafsnap project~\cite{kumar2012leafsnap} is an impressive effort that includes a very large dataset of leaves for $184$ tree types.
+The most recent Leafsnap project~\cite{kumar2012leafsnap} is an impressive effort that includes a very large dataset of leaves for $184$ tree types.
 A mobile phone application is also developed to make the leaf classification system portable.
-Finally, the crop/weed image database~\cite{haug2014crop} is captured by a robot in the real field, and used for the classification of crop vs.~weed.
-Note that except for~\cite{haug2014crop} where images are captured in the wild for a large area of plant, other databases in this type normally capture only a {\it single} leaf is in a relatively constrained imaging environment.
+Finally, the crop/weed image database~\cite{haug2014crop} is captured by a robot in the real field, and used for the classification of crop vs. weed.
+Note that except for~\cite{haug2014crop} where images are captured in the wild for a large area of plant, other databases in this type normally capture only a {\it single} leaf in a relatively constrained imaging environment.
 Therefore, the challenging problem of leaf segmentation has been bypassed.
@@
 The second type of databases is for plant phenotyping, where it is important to capture plant images without interfering the growth of plants.
-Thus, non-destructive imaging approaches are taken and the entire plant is imaged. The LSC database~\cite{scharr2014annotated} is the most relevant one to our database. 
-It captures a large set of RGB images for the Arabidopsis and Tobacco plants. 
+Thus, non-destructive imaging approaches are taken and the entire plant is imaged. 
+The LSC database~\cite{scharr2014annotated} is the most relevant one to our database.
+It captures a large set of RGB images for Arabidopsis and tobacco plants.
 The provided manual labels allow the evaluation of leaf segmentation and leaf counting.
@@
 The four sensing modalities in MSU-PID provide unique opportunities to comprehensively characterize plant morphological and physiological phenotypes. 
-The use of chlorophyll fluorescence at $730$ to $750nm$ as a tool for evaluating photosynthetic performance is well established~\cite{baker2008chlorophyll}, and against non-(chlorophyll)fluorescent background clearly defines photosynthetically active leaf area.
-The dense depth measurement has been a component of a number of recent non-plant RGB-D databases designed for object recognition~\cite{Lai2011}, scene segmentation~\cite{Silberman2011}, human analysis~\cite{Sung2011,Barbosa:reid12}, and mapping~\cite{sturm12iros}.
-By including dense depth for a plant database we anticipate enabling development of new 3D plant canopy analysis algorithms, thus probing the total energy intake and storage.
+The use of chlorophyll fluorescence at $730nm$ to $750nm$ as a tool for evaluating photosynthetic performance is well established~\cite{baker2008chlorophyll}, and against non-(chlorophyll)fluorescent background clearly defines photosynthetically active leaf area.
+The depth measurement has been a component of a number of recent non-plant RGB-D databases designed for object recognition~\cite{Lai2011}, scene segmentation~\cite{Silberman2011}, human analysis~\cite{Sung2011,Barbosa:reid12}, and mapping~\cite{sturm12iros}.
+By including depth map for a plant database, we anticipate enabling development of new $3$D plant canopy analysis algorithms and thus probing the total energy intake and storage.
 Near infrared (IR) reflectance has been used by others to detect water content in leaves~\cite{chen2014dissecting}.  

### 2015-07-22 datapapr_labeling.tex
xi_edit paper

@@
 \subsection{Data Statistics}
-MSU-PID includes two subsets, one for each plant type: Arabidopsis and Bean.
+MSU-PID includes two subsets, one for each plant type: Arabidopsis and bean.
 The statistic information of these two subsets are summarized in Table~\ref{tab:stat}.
 The images were acquired every hour.
-As there is no light at night hours, plants can not be imaged by the fluorescence and RGB color sensors while IR and depth cameras can still perform the capturing in the night.
-In order to make sure that all four modalities are present at each imaging opportunity, we release the part of images captured only in the day time, which are $16$ images per day for Arabidopsis and $14$ for bean for all four modalities.
+As there is no light at night hours, plants can not be imaged by the fluorescence and RGB color sensors while IR and depth cameras can still perform the capturing during the night.
+In order to make sure that all four modalities are present at each imaging modality, we release the part of images captured only in the day time, which are $16$ images per day for Arabidopsis and $14$ for bean for all four modalities.
+\todo{Need to be verified.}
 
 The two subsets differ in plant image resolutions.
-As shown in Figure~\ref{fig:fourmodality}, we grow and image a single bean plant while a whole tray of Arabidopsis are grown at the same time.
+As shown in Fig.~\ref{fig:fourmodality}, we grow and image a single bean plant while a whole tray of Arabidopsis are grown at the same time.
 Therefore, the resolution of a Arabidopsis plant is much lower than that of a bean plant.

### 2015-07-22 response/response.tex
xi_edit paper
response

@@
 Therefore, we did not apply the baseline method to bean plants.
-We have added this statement in the beginning of Sec $5.1$.
+We have added this statement in the beginning of Sec. $5.1$.
 \end{response}
@@
 \begin{response}
-Except in the Abstract, the "MSU-PID" first appears in paragraph $4$ of Sec $1$.
+Except in the Abstract, the "MSU-PID" first appears in paragraph $4$ of Sec. $1$.
 We have clearly defined it as short for Michigan State University Plant Image Database.
@@
 \begin{response}
-\todo{Daniel}
+\todo{Saif and Xi will work on the label transformation and edit the paper. }
 \end{response}
@@
 \begin{response}
-\todo{Jin}
+We have this clarification in the paper. 
+In Sec. $3.2.3$, we describes our image collection process, where the capture of all four modalities takes $4$ minutes. 
+During this short period, no substantial movement or growth were observed. 
 \end{response}

### 2015-07-22 datapapr_labeling.tex
Added label propagation figure.

--- 2015-07-14 datapapr_labeling.tex
@@
 %\end{figure*}
+
+\begin{figure*}
+\begin{centering}
+\begin{tabular}{cccc}
+\includegraphics[width=.18\textwidth]{Figures/LabelAlignment/day_3_hour_23-seg_ir.png}&
+\includegraphics[width=.18\textwidth]{Figures/LabelAlignment/day_3_hour_23-seg_fmp.png}&
+\includegraphics[width=.18\textwidth]{Figures/LabelAlignment/day_3_hour_23-seg_rgb.png}&
+\includegraphics[width=.18\textwidth]{Figures/LabelAlignment/day_3_hour_23-seg_depth.png}\\
+\includegraphics[width=.18\textwidth]{Figures/LabelAlignment/day_5_hour_23-seg_ir.png}&
+\includegraphics[width=.18\textwidth]{Figures/LabelAlignment/day_5_hour_23-seg_fmp.png}&
+\includegraphics[width=.18\textwidth]{Figures/LabelAlignment/day_5_hour_23-seg_rgb.png}&
+\includegraphics[width=.18\textwidth]{Figures/LabelAlignment/day_5_hour_23-seg_depth.png}\\
+\includegraphics[width=.18\textwidth]{Figures/LabelAlignment/day_9_hour_20-seg_ir.png}&
+\includegraphics[width=.18\textwidth]{Figures/LabelAlignment/day_9_hour_20-seg_fmp.png}&
+\includegraphics[width=.18\textwidth]{Figures/LabelAlignment/day_9_hour_20-seg_rgb.png}&
+\includegraphics[width=.18\textwidth]{Figures/LabelAlignment/day_9_hour_20-seg_depth.png}\\
+($a$) & ($b$) & ($c$) & ($d$) \\
+\end{tabular}
+\caption{Label propagation between all four modalities ($a$) infra-red, ($b$) fluorescence, ($c$) color and ($d$) depth, of a sample plant in the Arabidopsis collection for day 3 (top row), day 5 (middle row), and day 9 (bottom row).
+In the dataset the manual segmentation is performed on the fluorescence images and is outlined here as orange lines propagated to all modalities.
+The infra-red image is taken by the same camera and so will have close to exact pixel correspondence.
+To assess the segmented pixel propagation to other modalities, we also manually labeled a subset of the color plant images and propagated this segmentation to all modalities (shown in cyan).
+Comparing these boundaries in each modality gives a measure of the propagation errors due to parallax, and we provide quantitative analysis in table XXX.
+Note that the color and depth images are rotated 90 degrees.}
+\label{fig:LabelAlignment}
+\end{centering}
+\end{figure*}
 

### 2015-07-22 datapaper_hardware.tex
Merge

@@
 Chlorophyll {\it a} fluorescence images were captured once every hour during the daylight period in a growth chamber~\cite{cruz2015depi}.
-A set of $5$ images were captured using a Hitachi KP-F145GV CCD camera (Hitachi Kokusai Electric America Inc., Woodbury, NY) outfitted with an infrared long pass filter (Schott Glass RG-9, Thorlabs, Newton, NJ), during a short period ($<400~ms$) of intense light saturating to photosynthesis ($>10,000~\mu mol~photons~m^{-2} s^{-1}$) provided by an array of white Cree LEDs (XMLAWT, 5700K color temperature, Digi-Key, Thief River Falls, MN) collimated using a $20~mm$ Carclo Lens (10003, LED Supply, Lakewood, CO).
+A set of $5$ images were captured using a Hitachi KP-F145GV CCD camera (Hitachi Kokusai Electric America Inc., Woodbury, NY) outfitted with an infrared long pass filter (Schott Glass RG-$9$, Thorlabs, Newton, NJ), during a short period ($<400~ms$) of intense light saturating to photosynthesis ($>10,000~\mu mol~photons~m^{-2} s^{-1}$) provided by an array of white Cree LEDs (XMLAWT, $5700$K color temperature, Digi-Key, Thief River Falls, MN) collimated using a $20~mm$ Carclo Lens ($10003$, LED Supply, Lakewood, CO).
 %
@@
 Infrared images were collected once every hour with the same camera and filter used for chlorophyll {\it a} fluorescence.
-Pulses of $940nm$ light were provided by an array of OSRAM LEDs (SFH 4239, Digi-Key), collimated using a Polymer Optics lens (Part no. 170, Polymer Optics Ltd., Berkshire, England).
+Pulses of $940nm$ light were provided by an array of OSRAM LEDs (SFH $4239$, Digi-Key), collimated using a Polymer Optics lens (Part no. $170$, Polymer Optics Ltd., Berkshire, England).
 Since $940nm$ light does not influence plant development or drive photosynthesis, images were also collected during the night period~\cite{eskins1992light}.
@@
 The RGB color and depth images were collected using a Creative Senz3D sensor~\cite{nguyen2015vietnamese}. 
-The sensor contains both a $1280 \times 720$ color camera directed parallel to, and separated by roughly $25~mm$ from, a depth camera which has a resolution of $320\times240$ pixels.
+The sensor contains both a $1,280 \times 720$ color camera directed parallel to, and separated by roughly $25mm$ from, a depth camera which has a resolution of $320\times240$ pixels.
 The depth sensor uses a flash near IR illuminator and measures the time-of-flight~\cite{Hansard2013} of the beam at each pixel to obtain depth estimates along with an IR reflectance at each pixel.
 
-There are a number of limitations to the depth sensor that become the sources of depth errors.
+There is a number of limitations to the depth sensor that becomes the sources of depth errors.
 The primary measurement limitation on the range-to-target is the strength of the reflected beam.
-As a result, dark, matt surfaces are measured reliably only at a close range on the order of $20$ or $30~cm$.
+As a result, dark, matt surfaces are measured reliably only at a close range on the order of $20$ or $30cm$.
 Highly reflective surfaces also pose problems with direct reflections leading to saturation and highly unreliable depths.
@@
 \subsubsection{Image collection}
-The imagery data, including the fluorescent image, the IR reflectance image,  the color image, and the $3$D depth image, were collected once every hour.
+The imagery data, including fluorescence, IR reflectance,  RGB color, and the $3$D depth images, is collected once every hour.
 %
-Five minutes before the end of each hour, $3$D depth images and the color image were captured using the Creative Senz3D sensor (the depth points were transformed into the world coordinates and expressed in the unit of $mm$), followed by fluorescence and the IR reflectance images collected sequentially at 2 minute intervals by the IR filtered CCD camera.
+Five minutes before the end of each hour, $3$D depth images and the color image were captured using the Creative Senz3D sensor (the depth points were transformed into the world coordinates and expressed in the unit of $mm$), followed by fluorescence and IR reflectance images collected sequentially at $2$-minute interval by the IR filtered CCD camera.
 %
-No substantial movements or growth were observed within the about four minute period required for image capture using all four modalities, minimizing potential problems in image calibration.
+No substantial movements or growth were observed within the about four-minute period required for image capture using all four modalities, minimizing potential problems in image calibration.
 

### 2015-07-22 datapapr_labeling.tex

@@
 
+It is often argued which is the best setting due to the trade-off between the image resolution and the throughput of phenotyping experiments.
+We chose to image a whole tray of Arabidopsis at lower resolution rather than an individual at higher resolution, because it better reflects high-throughput protocols, which in practice allows direct comparison of multiple genotypes in the same experiment.
+In contrary, we chose to image a single bean plant because we anticipate enabling development of $3$D plant canopy reconstruction algorithms for bush plants.
 \begin{figure*}

### 2015-07-22 datapapr_labeling.tex
xi_edit-figure
Added homography description

@@
 \subsection{Manual Annotations}
-Part of the database is manually annotated to provide ground truth tip locations, leaf segmentation results and leaf consistency overtime.
+Part of the database is manually annotated to provide ground truth tip locations, leaf segmentation results and leaf consistency over time.
 Tip locations are saved in a TXT file for each frame.
@@
 Our experience is that since a noticeable percentage of extracted superpixels cover pixels of two neighboring leaves, the extra effort of breaking a super pixel into two makes it a less efficient alternative.
+
+\subsection{Multimodal Annotations}
+
+The leaf labeling can be propagated to each of the other modalities from the fluorescence images for the Arabidopsis sequence.
+To do this we approximate the plants with a plane, and find homographies that transform the fluorescence images into the other images.
+This provides a direct mapping of the pixel labels between each modality, and is illustrated in Figure~\ref{fig:LabelAlignment}.
+
+This mapping will introduce errors due to depth-based parallax.  [INCLUDE TABLE AND DESCRIPTION HERE].
+
+In the case of the bean plant, the pixel association between modalities is more difficult as the within-plant depth variations are large.
+We found an homography-based mapping performed poorly, and so the manual annotations we supply apply to just the infra-red and fluorescence images which use the same camera.
 

### 2015-07-24 response/response.tex
xi_edit

@@
 We refer to Scharr et al $2014$ that the Leaf Segmentation Challenge database only includes independent images without tracking context.
-The reason we do not include mutants is that we assume any computer vision algorithms that work on wildtypes should also work well on mutants as they have similar structure.
+Please refer to Comment $9$ for the reason we do not include mutants.
+\todo{Are we going to have mutants in bean data?}
+% is that we assume any computer vision algorithms that work on wildtypes should also work well on mutants as they have similar structure.
 \\ %\textcolor{red}{I do not understand what to be added to Table $1$.}
-\todo{TBD: Dr. Chen, please add some sentences about mutants in bean data. I recall we plan to capture additional bean data sets that have different mutants. Am I right?}
+% \todo{TBD: Dr. Chen, please add some sentences about mutants in bean data. I recall we plan to capture additional bean data sets that have different mutants. Am I right?}
 \end{response}
@@
 The released label is labeled by one annotator.
-However, we do use extra annotator to label several images and the annotation error between different annotators is evaluated.
-\todo{Results?}
+However, we do use extra annotator to label several images and the annotation error between different annotators is evaluated, as shown in Table $4$. 
 \end{response}

### 2015-07-24 datapaper.tex
final edit
xi_edit

@@
 
+\newcommand\todo[1]{\textcolor{red}{#1}}
+
 %\usepackage{paralist}
@@
 
-Among many applications of machine vision, plant image analysis has recently begin to gain attention due to its potential impact on plant visual phenotyping, particularly in understanding plant growth, assessing the quality/performance of crop plants and improving crop yield.
+Among many applications of machine vision, plant image analysis has recently began to gain attention due to its potential impact on plant visual phenotyping, particularly in understanding plant growth, assessing the quality/performance of crop plants and improving crop yield.
 Despite its importance, the lack of publicly available research databases containing plant imagery has substantially hindered the advancement of plant image analysis.
 To alleviate this issue, this paper presents a new multi-modality plant imagery database named ``MSU-PID'', with two distinct properties.
-First, MSU-PID is captured using four types of imaging sensors, Fluorescence, infrared (IR), RGB color, and depth.
+First, MSU-PID is captured using four types of imaging sensors, fluorescence, infrared (IR), RGB color, and depth.
 Second, the imaging setup and the variety of manual labels allow MSU-PID to be suitable for a diverse set of plant image analysis applications, such as leaf segmentation, leaf counting, leaf alignment, and leaf tracking.
@@
 \input{datapaper_conclusion.tex}
+
+%\input{calibtable.tex}
 

### 2015-07-24 datapaper_calibration.tex
xi_edit

@@
 \begin{center}
-\caption{Summary of Arabidopsis and Bean databases.\todo{last column needs to be updated}}
+\caption{Summary of Arabidopsis and Bean databases.}%\todo{last column needs to be updated}}
 \label{tab:stat}
@@
 \hline
-Arabidopsis & $16$ & $9$ & $16$ & $2304\times 4$ & $576\times 4$ \\
+Arabidopsis & $16$ & $9$ & $15$ & $2,160\times 4$ & $576\times 4$ \\
 \hline
-Bean & $5$ & $5$ & $14$ & $350\times 4$ & $175\times 4$ \\
+Bean & $5$ & $5$ & $14$ & $350\times 4$ & $175\times 2$ \\
 \hline
@@
 \begin{center}
-\caption{Plant image resolution of Arabidopsis and Bean databases, computed based on the yellow ROIs in Fig.~\ref{fig:fourmodality}.}
+\caption{Plant image resolution of Arabidopsis and bean databases, computed based on the yellow ROIs in Fig.~\ref{fig:fourmodality}.}
 \label{tab:resolution}
@@
 %\hline
-Bean & $1000\times640$ & $1000\times640$ & $380\times720$ & $90\times190$ \\
+Bean & $1,000\times640$ & $1,000\times640$ & $380\times720$ & $90\times190$ \\
 \hline

### 2015-07-24 datapaper_intro.tex
xi_edit

@@
 ~\cite{haug2014crop} & & & & & & \\ \hline
-LSC & \multirow{2}{*}{RGB} & \multirow{2}{*}{LS, LO} & Arabidopsis & $43$ & $6287$ & $201$ \\ \cline{4-7}
+LSC & \multirow{2}{*}{RGB} & \multirow{2}{*}{LS, LO} & Arabidopsis & $43$ & $6,287$ & $201$ \\ \cline{4-7}
 ~\cite{haug2014crop} & & & Tobacco & $80$ & $165,120$ & $83$ \\ \hline
-\multirow{2}{*}{MSU-PID} & fluorescence, & LS, LO, & Arabidopsis & $16$ & $2304\times 4$ & $576\times 4$ \\ \cline{4-7}
-& IR, RGB, depth & LA, LT & Bean & $5$ & $350\times 4$ & $175\times 4$ \\ \hline
+\multirow{2}{*}{MSU-PID} & fluorescence, & LS, LO, & Arabidopsis & $16$ & $2,160\times 4$ & $576\times 4$ \\ \cline{4-7}
+& IR, RGB, depth & LA, LT & Bean & $5$ & $350\times 4$ & $175\times 2$ \\ \hline
 \hline

### 2015-07-24 datapapr_labeling.tex
xi_edit

--- 2015-07-22 datapapr_labeling.tex
@@
 As there is no light at night hours, plants can not be imaged by the fluorescence and RGB color sensors while IR and depth cameras can still perform the capturing during the night.
-In order to make sure that all four modalities are present at each imaging modality, we release the part of images captured only in the day time, which are $16$ images per day for Arabidopsis and $14$ for bean for all four modalities.
-\todo{Need to be verified.}
+In order to make sure that all four modalities are present at each imaging modality, we release the part of images captured only in the day time, which are $15$ images per day for Arabidopsis and $14$ for bean for all four modalities.
 
@@
 \centering
-\includegraphics[width=.98\textwidth]{Figures/labeling}\\
+\includegraphics[width=.90\textwidth]{Figures/labeling}\\
 \caption{Leaf labeling process, including tip labels and leaf segmentation annotation.}
@@
 In contrary, we chose to image a single bean plant because we anticipate enabling development of $3$D plant canopy reconstruction algorithms for bush plants.
+
+\subsection{Manual Annotations}
+Part of the database is manually annotated to provide ground truth tip locations, leaf segmentation results, and leaf consistency overtime.
+Tip locations are saved in a TXT file for each frame.
+Leaf segmentation results are stored in a PNG image for each frame with one color for each leaf.
+The same color is used to represent the same leaf over a sequence of frames.
+
+We use the fluorescence images as the input for labeling because of their simple and uniform background.
+For Arabidopsis images, we label $4$ frames each day.
+While for bean images, we label $7$ frames each day because of their spontaneous and faster leaf movement.
+A Matlab GUI interface is developed for leaf labeling, as shown in Fig.~\ref{fig:label}, which will also be available to the public.
+A user can open a plant image to label the two tips and annotate each leaf segment.
+The results will be automatically saved once a user moves onto the next image for labeling.
+For consistent annotation of the same leaf over time, we show a number on the center of each leaf indicating the order of labeling from the previous frame.
+
+The labeling of leaf tips is implemented by clicking pairs of points on the image.
+The outer tip is always clicked first before the inner tip.
+For visualization, a line connecting each pair of tips will be shown immediately after clicking the inner tip.
+Inaccurate labels can be deleted by clicking the right button of the mouse near the labeled point and relabeled by clicking the left button again immediately after deletion.
+All tips can be deleted by clicking "Clear Tip" and relabel again.
+
+The labeling of the leaf segment is implemented by clicking the boundary of one leaf at each time.
+In order to provide more accuracy labeling, we click very dense points ($\sim20$ points on average) on the boundary.
+The labeled leaf boundary is overlaid on the image for better visualization to guide the next action.
+Incorrect label can be deleted right after the labeling by clicking ``Clear".
+All leaf labels can be deleted by clicking ``Clear All".
+This process continues until all leaf segments have been annotated.
+Once a leaf is invisible due to occlusion, the label can be skipped by clicking ``Invisible". 
+After the labeling of one plant, we visually go through the results and correct inaccurate labels.
+One example of the labeling results for one plant is shown in Fig.~\ref{fig:trackExample} $(b)$, where one color is used to represent each specific leaf.
+As we can see during the transition between day $5$ and day $6$, there is one leaf showing up and covering up the leaf underneath, which disappears and will not be annotated later.
+In total, we labeled $5,142$ leaves.
+
+Note that one alternative approach for labeling leaf segments is to directly label the membership of superpixels instead of drawing a polygon along the boundary.
+Our experience is that since a noticeable percentage of extracted superpixels cover pixels of two neighboring leaves, the extra effort of breaking a super pixel into two makes it a less efficient alternative.
+
+\subsection{Label Propagation}
+\textcolor{red}{input by Dr. Morris on how the transformation is done}
+
 \begin{figure*}
@@
 
-\subsection{Manual Annotations}
-Part of the database is manually annotated to provide ground truth tip locations, leaf segmentation results and leaf consistency overtime.
-Tip locations are saved in a TXT file for each frame.
-Leaf segmentation results are stored in a PNG image for each frame with one color for each leaf.
-The same color is used to represent the same leaf over a sequence of frames.
+%In order to evaluate the performance of label propagation, we use one of our evaluation metric Symmetric Best Dice (SBD), as will describe in Sec.~\ref{sec:protocol}, which is used to evaluate the similarity between two segment masks.
+%Table~\ref{tab:labelError} shows the performance of label propagation vs. the performance of human labels.
+%We compare the label difference between two annotators $L_1$ and $L_2$.
 
-We use the fluorescence images as the input for labeling because of their simple and uniform background.
-For Arabidopsis images, we label $4$ frames each day.
-While for bean images, we label $7$ frames each day because of their spontaneous and faster leaf movement.
-A Matlab-based GUI interface is developed for leaf labeling, as shown in Figure~\ref{fig:label}, which will also be available to the public. 
-A user can open a plant image to label the two tips and annotate each leaf segment.
-The results will be automatically saved once a user moves onto the next image for labeling.
-For consistent annotation of the same leaf over time, we show a number on the center of each leaf indicating the order of labeling from the previous frame.
-%This GUI is used to annotate leaves in each frame.
-%For consistent annotation of the same leaf over time, we use the labeled results of each frame to find the correspondence according to leaf centers.
-%Incorrect correspondence will be manually corrected.
-
-The labeling of leaf tips is implemented by clicking pairs of points on the image.
-The outer tip is always clicked first before the inner tip.
-For visualization, a line connecting each pair of tips will be shown immediately after clicking the inner tip.
-Inaccurate labels can be deleted by clicking the right button of the mouse near the labeled point and relabeled by clicking the left button again.
-
-The labeling of the leaf segment is implemented by clicking the boundary of one leaf at each time.
-In order to provide more accuracy labeling, we click very dense points ($\sim20$ points on average) on the boundary.
-The labeled leaf boundary is overlaid on the image for better visualization to guide the next action.
-Incorrect label can be deleted right after the labeling.
-This process continues until all leaf segments have been annotated.
-After the labeling of one plant, we visually go through the results and correct inaccurate labels.
-One example of the labeling results for one plant is shown in Figure~\ref{fig:trackExample} $(b)$, where one color is used to represent each specific leaf.
-As we can see during the transition between day $5$ and day $6$, there is one leaf showing up and covering up the leaf underneath, which disappears and will not be annotated later.
-In total, we labeled $5142$ leaves.
-
-Note that one alternative approach for labeling leaf segments is to directly label the membership of superpixels instead of drawing a polygon along the boundary.
-Our experience is that since a noticeable percentage of extracted superpixels cover pixels of two neighboring leaves, the extra effort of breaking a super pixel into two makes it a less efficient alternative.
+\begin{table*}[t]
+\centering
+\caption{Human label performance vs. label propagation performance.}
+\begin{tabular}{c|c|c|c|c|c|c}
+\hline
+    & \multicolumn{3}{c|}{fmp modality} & \multicolumn{3}{c}{RGB modality}\\ \hline
+    & $L_1$ vs. $L_1$ & $L_1$ vs. $L_2$  & $L_1$ vs. $L_t$ & $L_1$ vs. $L_1$ & $L_1$ vs. $L_2$ & $L_1$ vs. $L_t$ \\ \hline
+   plant$\_3\_$day$\_3\_$hour$\_23$ & $1$ & $0.750$ & $0.798$ & $1$ & $0.827$ & $0.800$ \\ \hline
+   plant$\_3\_$day$\_5\_$hour$\_23$ & $1$ & $0.793$ & $0.846$ & $1$ & $0.871$ & $0.847$ \\ \hline
+   plant$\_3\_$day$\_9\_$hour$\_20$ & $1$ & $0.837$ & $0.787$ & $1$ & $0.877$ & $0.789$ \\ \hline
+                   average &          $1$ & $0.793$ & $0.810$ & $1$ & $0.858$ & $0.812$ \\ \hline
+\end{tabular}
+\label{tab:labelError}
+\end{table*}
 
@@
 \begin{itemize}
-\item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$rgb.png: the original RGB color images;
-\item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$fmp.png: the original fluorescence images;
-\item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$ir.png: the original IR images;
-\item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$depth.png: the original depth images;
+%\item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$rgb.png: the original RGB color images;
+%\item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$fmp.png: the original fluorescence images;
+%\item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$ir.png: the original IR images;
+%\item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$depth.png: the original depth images;
+\item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$modality.png: the original images in each modality separately;
+%\item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$label.png: the labeled images of fluorescence modality;
+%\item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$tips.txt: the labeled tip locations;
+\item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$label$\_$modality.png: the labeled images of each modality if available;
+\item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$tips$\_$modality.txt: the labeled tip locations of each modality if available;
 \item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$depthSigma.png: the depth standard deviation images;
-\item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$label.png: the labeled images of fluorescence modality;
-\item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$tips.txt: the labeled tip locations;
 \end{itemize}
-where ID indicates the plant subject ID number ($1$ to $16$ for Arabidopsis, $1$ to $5$ for bean), X is an integer indicating the date ($1-9$ for Arabidopsis, $1$ to $5$ for bean), and YY represents the image index within a day ($1-16$ for Arabidopsis, $1$ to $14$ for bean).
+where ID indicates the plant subject ID number ($1$ to $16$ for Arabidopsis, $1$ to $5$ for bean), X is an integer indicating the date ($1-9$ for Arabidopsis, $1$ to $5$ for bean), and YY represents the image index within a day ($1-15$ for Arabidopsis, $1$ to $14$ for bean).
 For each combination of day and hour, we provide four modalities in PNG files ($\_$rgb, $\_$fmp, $\_$ir, $\_$depth).
@@
 
-In addition to the original images and annotation results, we provide another folder named Matlab with all Matlab functions that will be used for mapping between different image modalities and for the purpose of performance evaluation.
-Note that the annotation is provided based on fluorescence images.
-In order to evaluate methods developed on other modalities, we provide image-mapping functions between every two modalities.
+%In addition to the original images and annotation results, we provide another folder named Matlab with all Matlab functions that will be used for mapping between different image modalities and for the purpose of performance evaluation.
+%Note that the annotation is provided based on fluorescence images.
+%In order to evaluate methods developed on other modalities, we provide image-mapping functions between every two modalities.
 The total storage of our database is around $380 MB$, which is convenient for downloading via Internet.
@@
 \subsection{Experimental Protocols}
+\label{sec:protocol}
 As shown in Table~\ref{tab:database}, MSU-PID can be used for applications such as leaf segmentation, leaf alignment, leaf tracking, and leaf counting.
@@
 
-\paragraph{Performance metric}
-To evaluate the performance of leaf segmentation, alignment, and tracking, we use four performance metrics, whose Matlab implementations will be provided along with the data.
+\paragraph{Performance Metric}
+To evaluate the performance of leaf segmentation, alignment, tracking, and counting, we use four performance metrics, whose Matlab implementations will be provided along with the data.
 Three of them are based on the tip-based error, which is defined as the average distance of a pair of estimated leaf tips $\hat{\bm{t}}_{1,2}$ with a pair of labeled leaf tips $ \bm{t}_{1,2}$ normalized by the labeled leaf length:
@@
 The second is matched leaves with tip-based errors larger than $\tau$.
+When $\tau$ is large enough, this value is equal to the leaf counting error.
 \item {\it{Landmark Error (LE)}}, the average tip-based errors smaller than $\tau$ of all frame-to-frame correspondent leaves.
+This is used to measure the leaf tip alignment error. 
 \item {\it{Tracking Consistency (TC)}}, the percentage of video-to-video correspondent leaves whose tip-based errors are smaller than $\tau$.
+This is used to measure leaf tracking error. 
 \end{itemize}
@@
 The Matlab function for computing {\it{SBD}} is provided by~\cite{scharr2014annotated}.
-The instructions on how to use the evaluation functions are included as comments of the function.
+%The instructions on how to use the evaluation functions are included as comments of the function.
 

### 2015-07-25 datapaper_intro.tex
Updated the intro to include homographic warping mention

--- 2015-07-22 datapaper_intro.tex
@@
 
-With the rapid growth of world population and the loss of arable land, there is an increasing desire to improve the yield and quality of crops, where the understanding of the genetic mechanisms to influence plant growth is a key enabler~\cite{doos2002population}.
+With the rapid growth of world population and the loss of arable land, there is an increasing desire to improve the yield and quality of crops.
+Key to increasing yields is gaining understanding of the genetic mechanisms that influence plant growth~\cite{doos2002population}.
 %
@@
 All four sensors are synchronized and are programmed to periodically capture imagery data for multiple consecutive days.
-Checkerboard-based camera calibration is performed between a pair of sensors, which results in the explicit correspondence between the pixels of {\it any} two modalities.
-\todo{Need to be updated about the transformation}
+Checkerboard-based camera calibration is performed on each modality providing intrinsic camera parameters and poses.
+In addition explicit correspondence between the pixels of {\it any} two modalities is obtained using an homographic warping of a plane through the plants.
 

### 2015-07-26 datapapr_labeling.tex
baseline-performance-on-rgb-images

@@
 
-\subsection{Label Propagation}
-\textcolor{red}{input by Dr. Morris on how the transformation is done}
+\subsection{Multimodal Annotations}
+The leaf labeling can be propagated to each of the other modalities from the fluorescence images for the Arabidopsis sequence.
+To do this we approximate the plants with a plane, and find homographies that transform the fluorescence images into the other images.
+This provides a direct mapping of the pixel labels between each modality, and is illustrated in Figure~\ref{fig:LabelAlignment}.
+
+This mapping will introduce errors due to depth-based parallax.  [INCLUDE TABLE AND DESCRIPTION HERE].
+
+In the case of the bean plant, the pixel association between modalities is more difficult as the within-plant depth variations are large.
+We found an homography-based mapping performed poorly, and so the manual annotations we supply apply to just the infra-red and fluorescence images which use the same camera.
 

### 2015-07-26 datapaper_calibration.tex
edit-label-propagation-section

@@
 \begin{center}
-\caption{Summary of Arabidopsis and Bean databases.}%\todo{last column needs to be updated}}
+\caption{Summary of Arabidopsis and Bean databases.}
 \label{tab:stat}
@@
 \begin{center}
-\caption{Plant image resolution of Arabidopsis and bean databases, computed based on the yellow ROIs in Fig.~\ref{fig:fourmodality}.}
+\caption{Plant image resolution of Arabidopsis and Bean databases, computed based on the yellow ROIs in Figure~\ref{fig:fourmodality}.}
 \label{tab:resolution}

### 2015-07-26 datapaper_intro.tex
baseline-performance-on-rgb-images
edit-label-propagation-section

--- 2015-07-24 datapaper_intro.tex
@@
 To facilitate future research on plant image analysis, as well as remedy the limitation of existing databases in the field, this paper presents a newly collected multi-modality Plant Imagery Database through an interdisciplinary effort at Michigan State University (MSU), which is termed ``MSU-PID''.
-As illustrated in Fig.~\ref{fig:fourmodality}, the MSU-PID database includes the imagery of two types of plants (Arabidopsis and bean, both are widely used in plant research) captured by four types of imaging sensors, i.e., fluorescence, infrared (IR), RGB color, and depth.
+As illustrated in Figure~\ref{fig:fourmodality}, the MSU-PID database includes the imagery of two types of plants (Arabidopsis and bean, both are widely used in plant research) captured by four types of imaging sensors, i.e., fluorescence, infrared (IR), RGB color, and depth.
 All four sensors are synchronized and are programmed to periodically capture imagery data for multiple consecutive days.
-Checkerboard-based camera calibration is performed between a pair of sensors, which results in the explicit correspondence between the pixels of {\it any} two modalities.
-\todo{Need to be updated about the transformation}
+Checkerboard-based camera calibration is performed on each modality providing intrinsic camera parameters and poses.
+In addition explicit correspondence between the pixels of {\it any} two modalities is obtained using an homographic warping of a plane through the plants.
 

### 2015-07-26 datapapr_labeling.tex
edit-label-propagation-section

--- 2015-07-24 datapapr_labeling.tex
@@
 The two subsets differ in plant image resolutions.
-As shown in Fig.~\ref{fig:fourmodality}, we grow and image a single bean plant while a whole tray of Arabidopsis are grown at the same time.
+As shown in Figure~\ref{fig:fourmodality}, we grow and image a single bean plant while a whole tray of Arabidopsis are grown at the same time.
 Therefore, the resolution of a Arabidopsis plant is much lower than that of a bean plant.
@@
 \subsection{Manual Annotations}
+\label{sec:annotation}
 Part of the database is manually annotated to provide ground truth tip locations, leaf segmentation results, and leaf consistency overtime.
-Tip locations are saved in a TXT file for each frame.
-Leaf segmentation results are stored in a PNG image for each frame with one color for each leaf.
-The same color is used to represent the same leaf over a sequence of frames.
+We use the fluorescence images as the input for labeling because of their simple and uniform background.
+%Tip locations are saved in a TXT file for each frame.
+%Leaf segmentation results are stored in a PNG image for each frame with one color for each leaf.
+%The same color is used to represent the same leaf over a sequence of frames.
 
-We use the fluorescence images as the input for labeling because of their simple and uniform background.
 For Arabidopsis images, we label $4$ frames each day.
 While for bean images, we label $7$ frames each day because of their spontaneous and faster leaf movement.
-A Matlab GUI interface is developed for leaf labeling, as shown in Fig.~\ref{fig:label}, which will also be available to the public.
+A Matlab GUI interface is developed for leaf labeling, as shown in Figure~\ref{fig:label}, which will also be available to the public.
 A user can open a plant image to label the two tips and annotate each leaf segment.
-The results will be automatically saved once a user moves onto the next image for labeling.
+The results will be automatically saved once a user moves to the next image.
 For consistent annotation of the same leaf over time, we show a number on the center of each leaf indicating the order of labeling from the previous frame.
 
-The labeling of leaf tips is implemented by clicking pairs of points on the image.
-The outer tip is always clicked first before the inner tip.
-For visualization, a line connecting each pair of tips will be shown immediately after clicking the inner tip.
-Inaccurate labels can be deleted by clicking the right button of the mouse near the labeled point and relabeled by clicking the left button again immediately after deletion.
-All tips can be deleted by clicking "Clear Tip" and relabel again.
-
-The labeling of the leaf segment is implemented by clicking the boundary of one leaf at each time.
-In order to provide more accuracy labeling, we click very dense points ($\sim20$ points on average) on the boundary.
+The labeling of the leaf segment (``Leaf Label") is implemented by clicking the boundary of one leaf at each time.
+In order to provide more accuracy labeling, we click very dense points ($\sim20$ points on average for each leaf) on the boundary.
 The labeled leaf boundary is overlaid on the image for better visualization to guide the next action.
@@
 Once a leaf is invisible due to occlusion, the label can be skipped by clicking ``Invisible".
-After the labeling of one plant, we visually go through the results and correct inaccurate labels.
-One example of the labeling results for one plant is shown in Fig.~\ref{fig:trackExample} $(b)$, where one color is used to represent each specific leaf.
+
+The labeling of leaf tips (``Tip Label") is implemented by clicking pairs of points on the image.
+The outer tip is always clicked first before the inner tip.
+For visualization, a line connecting each pair of tips will be shown immediately after clicking the inner tip.
+Inaccurate labels can be deleted by clicking the right button of the mouse near the labeled point and relabeled by clicking the left button again immediately after deletion.
+All tips can be deleted by clicking "Clear Tip" and relabel again.
+The ``Show Tip" option is to select whether to show the tips or not. 
+For relabeling of both leaf segments and leaf tips, press ``Restart".
+
+After the labeling, we visually go through the results and correct inaccurate labels due to human error.
+One example of the labeling results for one plant is shown in Figure~\ref{fig:trackExample} $(b)$, where one color is used to represent each specific leaf.
 As we can see during the transition between day $5$ and day $6$, there is one leaf showing up and covering up the leaf underneath, which disappears and will not be annotated later.
-In total, we labeled $5,142$ leaves.
+% In total, we labeled $5,142$ leaves for fluorescence images.
 
@@
 
-\subsection{Label Propagation}
-\textcolor{red}{input by Dr. Morris on how the transformation is done}
-
-\begin{figure*}
+\subsection{Multimodal Annotations}
+\begin{figure*}[t]
 \begin{centering}
 \begin{tabular}{cccc}
-\includegraphics[width=.18\textwidth]{Figures/LabelAlignment/day_3_hour_23-seg_ir.png}&
-\includegraphics[width=.18\textwidth]{Figures/LabelAlignment/day_3_hour_23-seg_fmp.png}&
-\includegraphics[width=.18\textwidth]{Figures/LabelAlignment/day_3_hour_23-seg_rgb.png}&
-\includegraphics[width=.18\textwidth]{Figures/LabelAlignment/day_3_hour_23-seg_depth.png}\\
-\includegraphics[width=.18\textwidth]{Figures/LabelAlignment/day_5_hour_23-seg_ir.png}&
-\includegraphics[width=.18\textwidth]{Figures/LabelAlignment/day_5_hour_23-seg_fmp.png}&
-\includegraphics[width=.18\textwidth]{Figures/LabelAlignment/day_5_hour_23-seg_rgb.png}&
-\includegraphics[width=.18\textwidth]{Figures/LabelAlignment/day_5_hour_23-seg_depth.png}\\
-\includegraphics[width=.18\textwidth]{Figures/LabelAlignment/day_9_hour_20-seg_ir.png}&
-\includegraphics[width=.18\textwidth]{Figures/LabelAlignment/day_9_hour_20-seg_fmp.png}&
-\includegraphics[width=.18\textwidth]{Figures/LabelAlignment/day_9_hour_20-seg_rgb.png}&
-\includegraphics[width=.18\textwidth]{Figures/LabelAlignment/day_9_hour_20-seg_depth.png}\\
+\includegraphics[width=.15\textwidth]{Figures/LabelAlignment/day_3_hour_23-seg_ir.png}&
+\includegraphics[width=.15\textwidth]{Figures/LabelAlignment/day_3_hour_23-seg_fmp.png}&
+\includegraphics[width=.15\textwidth]{Figures/LabelAlignment/day_3_hour_23-seg_rgb.png}&
+\includegraphics[width=.15\textwidth]{Figures/LabelAlignment/day_3_hour_23-seg_depth.png}\\
+\includegraphics[width=.15\textwidth]{Figures/LabelAlignment/day_5_hour_23-seg_ir.png}&
+\includegraphics[width=.15\textwidth]{Figures/LabelAlignment/day_5_hour_23-seg_fmp.png}&
+\includegraphics[width=.15\textwidth]{Figures/LabelAlignment/day_5_hour_23-seg_rgb.png}&
+\includegraphics[width=.15\textwidth]{Figures/LabelAlignment/day_5_hour_23-seg_depth.png}\\
+\includegraphics[width=.15\textwidth]{Figures/LabelAlignment/day_9_hour_20-seg_ir.png}&
+\includegraphics[width=.15\textwidth]{Figures/LabelAlignment/day_9_hour_20-seg_fmp.png}&
+\includegraphics[width=.15\textwidth]{Figures/LabelAlignment/day_9_hour_20-seg_rgb.png}&
+\includegraphics[width=.15\textwidth]{Figures/LabelAlignment/day_9_hour_20-seg_depth.png}\\
 ($a$) & ($b$) & ($c$) & ($d$) \\
 \end{tabular}
-\caption{Label propagation between all four modalities ($a$) infra-red, ($b$) fluorescence, ($c$) color and ($d$) depth, of a sample plant in the Arabidopsis collection for day 3 (top row), day 5 (middle row), and day 9 (bottom row).
+\caption{Label propagation between all four modalities ($a$) infra-red, ($b$) fluorescence, ($c$) color and ($d$) depth, of a sample plant in the Arabidopsis collection for day $3$ (top row), day $5$ (middle row), and day $9$ (bottom row).
 In the dataset the manual segmentation is performed on the fluorescence images and is outlined here as orange lines propagated to all modalities.
@@
 Comparing these boundaries in each modality gives a measure of the propagation errors due to parallax, and we provide quantitative analysis in table XXX.
-Note that the color and depth images are rotated 90 degrees.}
+Note that the color and depth images are rotated $90$ degrees.}
 \label{fig:LabelAlignment}
@@
 
-%In order to evaluate the performance of label propagation, we use one of our evaluation metric Symmetric Best Dice (SBD), as will describe in Sec.~\ref{sec:protocol}, which is used to evaluate the similarity between two segment masks.
-%Table~\ref{tab:labelError} shows the performance of label propagation vs. the performance of human labels.
-%We compare the label difference between two annotators $L_1$ and $L_2$.
-
 \begin{table*}[t]
 \centering
-\caption{Human label performance vs. label propagation performance.}
+\caption{Human label performance vs. label propagation performance.
+$L_1$ and $L_2$ are the manual label results from two annotators, and $L_t$ is the propagated results.
+The {\it{SBD}} score is averaged over $3$ plants.}
 \begin{tabular}{c|c|c|c|c|c|c}
 \hline
-    & \multicolumn{3}{c|}{fmp modality} & \multicolumn{3}{c}{RGB modality}\\ \hline
+    & \multicolumn{3}{c|}{fluorescence modality} & \multicolumn{3}{c}{RGB modality}\\ \hline
     & $L_1$ vs. $L_1$ & $L_1$ vs. $L_2$  & $L_1$ vs. $L_t$ & $L_1$ vs. $L_1$ & $L_1$ vs. $L_2$ & $L_1$ vs. $L_t$ \\ \hline
-   plant$\_3\_$day$\_3\_$hour$\_23$ & $1$ & $0.750$ & $0.798$ & $1$ & $0.827$ & $0.800$ \\ \hline
-   plant$\_3\_$day$\_5\_$hour$\_23$ & $1$ & $0.793$ & $0.846$ & $1$ & $0.871$ & $0.847$ \\ \hline
-   plant$\_3\_$day$\_9\_$hour$\_20$ & $1$ & $0.837$ & $0.787$ & $1$ & $0.877$ & $0.789$ \\ \hline
-                   average &          $1$ & $0.793$ & $0.810$ & $1$ & $0.858$ & $0.812$ \\ \hline
+   day$\_3\_$hour$\_23$ & $1$ & $0.808$ & $0.804$ & $1$ & $0.827$ & $0.802$ \\ \hline
+   day$\_5\_$hour$\_23$ & $1$ & $0.830$ & $0.836$ & $1$ & $0.871$ & $0.837$ \\ \hline
+   day$\_9\_$hour$\_20$ & $1$ & $0.903$ & $0.886$ & $1$ & $0.877$ & $0.789$ \\ \hline
+                   average &          $1$ & $0.847$ & $0.842$ & $1$ & $0.858$ & $0.809$ \\ \hline
 \end{tabular}
@@
 \end{table*}
+
+The leaf labeling can be propagated to each of the other modalities from the fluorescence images for the Arabidopsis sequence.  
+To do this, we approximate a plant image with a plane, and find homographies that transform the fluorescence images into the other images.  
+This provides a direct mapping of the pixel labels between each modality.
+% and is illustrated in Figure~\ref{fig:LabelAlignment}.
+
+We manually label $3$ images for each of $3$ Arabidopsis plants ($9$ images in total) on fluorescence and RGB modalities. 
+One label propagation results is illustrated in Figure~\ref{fig:LabelAlignment}.
+This mapping will introduce errors due to depth-based parallax.  
+We use {\it{SBD}} score, which will be introduced in Section~\ref{sec:protocol}, to evaluate the similarity between the manual label image and the propagation result. 
+In order to compare the label propagation error with human label error, we ask two different annotators to label the same $9$ images and compute the {\it{SBD}} score. 
+The results are shown in Table~\ref{tab:labelError}.
+
+We can make two conclusion from Table~\ref{tab:labelError}.
+First, the similarity for both manual annotation and label propagation increases as the plant grows.
+This is reasonable because {\it{SBD}} depends on the overlap ratio between two leaves, which is in natural to favor big leaves. 
+Second, the performance of label propagation is only slightly worse than the performance of human annotations. 
+Therefore, we use label propagation to provide the labels for all four modalities for Arabidopsis plants. 
+There are two benefits. 
+First, we will save a lot of human labor. 
+Second, the label is consistent for all four modalities.
+
+In the case of the bean plant, the pixel association between modalities is more difficult as the within-plant depth variations are large.  
+We found a homograph-based mapping performed poorly, and so the manual annotations we supply apply to just the infra-red and fluorescence images which use the same camera.
 
@@
 where leaf ID is an integer number that is consistent with the segmentation label in the PNG file.
-tip1$\_$x and tip1$\_$y represent the coordinates of the outer tip point.
-tip2$\_$x and tip2$\_$y represent the coordinates of the inner tip point.
+tip$1\_$x and tip$1\_$y represent the coordinates of the outer tip point.
+tip$2\_$x and tip$2\_$y represent the coordinates of the inner tip point.
+Any NAN values in the file indicates an invisible leaf.
 
@@
 \label{sec:protocol}
-As shown in Table~\ref{tab:database}, MSU-PID can be used for applications such as leaf segmentation, leaf alignment, leaf tracking, and leaf counting.
+As shown in Table~\ref{tab:database}, MSU-PID can be used for applications such as leaf segmentation, leaf counting, leaf alignment, and leaf tracking.
 To facilitate future research, we separate the database into the training set and the testing set.
@@
 %
-%As shown in Fig.~\ref{fig:label}, several super pixels that covers one leaf are first merged together to form a large super pixel.
+%As shown in Figure ~\ref{fig:label}, several super pixels that covers one leaf are first merged together to form a large super pixel.
 %Since the top part of the super pixel covers some of the background and the bottom part covers another small leaf, two lines are drawn on this super pixel to split it.

### 2015-07-26 datapapr_labeling.tex
label section complete

@@
 tip$2\_$x and tip$2\_$y represent the coordinates of the inner tip point.
-Any NAN values in the file indicates an invisible leaf.
+Any ``nan" value in the file indicates an invisible leaf.
 
@@
 For example, using RGB and depth modalities for training and RGB for testing can take advantage of additional information during the learning without incurring extra sensor cost during the testing, which can be implemented via either learning with side information~\cite{chen2013boosting}, or transfering learning with missing modality~\cite{ding2014latent}.
-%The evaluation metrics will be discussed in Sec.~\ref{sec:baseline}.
 
 \paragraph{Performance Metric}
-To evaluate the performance of leaf segmentation, alignment, tracking, and counting, we use four performance metrics, whose Matlab implementations will be provided along with the data.
+To evaluate the performance of leaf segmentation, alignment, tracking, and counting, we use $4$ performance metrics, whose Matlab implementations will be provided along with the data.
 Three of them are based on the tip-based error, which is defined as the average distance of a pair of estimated leaf tips $\hat{\bm{t}}_{1,2}$ with a pair of labeled leaf tips $ \bm{t}_{1,2}$ normalized by the labeled leaf length:
@@
 \begin{itemize}
-\item {\it{Symmetric Best Dice (SBD)}}, the symmetric best Dice among all labeled leaves.
+\item {\it{Symmetric Best Dice (SBD)}}, the average symmetric best Dice among all labeled leaves.
 \end{itemize}

### 2015-07-26 datapaper_baseline.tex
baseline-performance-on-rgb-images
baseline-first-round-complete

@@
 
-To facilitate future research on this database, we provide a baseline approach and its performance by using the fluorescence modality of Arabidopsis.
+To facilitate future research on this database, we apply our automatic multi-leaf segmentation, alignment, and tracking framework~\cite{yin2014a,yin2014b} to the testing set of Arabidopsis imagery to provide a baseline.
+Specifically, we apply it on fluorescence and RGB modalities. 
+Note that~\cite{yin2014a,yin2014b} is designed for rosette plants like Arabidopsis.
+Therefore, it will not be applied to bean plant as it does not belong to rosette plants.
+%In addition, we also apply it on the RGB modality and use the propagated labels for evaluation.
 
 \subsection{Multi-leaf Segmentation and Tracking Framework}
-We apply our automatic multi-leaf segmentation and tracking framework~\cite{yin2014a,yin2014b} to the testing set of Arabidopsis fluorescence imagery to provide a baseline.
-Note that~\cite{yin2014a,yin2014b} is designed for rosette plants like Arabidopsis. 
-Therefore, it will not be applied to bean plant as it does  not belong to rosette plants. 
-We treat all images in $9$ days as a video from first image on the first day to the last image in the last day.
 As shown in Figure~\ref{fig:methodOverview}, the input of this framework is a plant video and a set of predefined templates with various shapes, scales, and orientations.
+We treat all images in $9$ days as a video from first image on the first day to the last image on the last day.
 To generate the template set, we first select $12$ templates with different aspect ratios from the labeled images in the training set together with the corresponding tip locations.
 For each template, we scale it to $10$ different sizes in order to cover the entire range of leaf sizes in the database.
+The scales for fluorescence images and RGB images are different due to the different image resolutions. 
 For each scale template, we rotate every $15^{\circ}$ to generate $24$ templates at different orientations.
@@
 
-%We also generate the two tips for each template for finding the corresponding tip points of each leaf via Chamfer Matching~\cite{barrow1977parametric}.
-Our work is motivated by Chamfer Matching technique~\cite{barrow1977parametric}, which is used to align two edge maps.
+Our work is motivated by Chamfer Matching (CM) technique~\cite{barrow1977parametric}, which is used to align two edge maps.
 We extend it to simultaneously align multiple overlapping objects.
-For plant segmentation, we use simple thresholding and edge detection to generate an edge map and mask.
+For plant segmentation, we use simple thresholding process and edge detection to generate an image mask and edge map.
 The best threshold is learnt from the training set, which is done by tuning the threshold in a certain range and find the best one by evaluating the overlap of the segmented masks with the groundtruth label masks.
@@
 
-First, we find the best location of each template in the edge map that has the minimal Chamfer matching distance, which will result in an over-completed set of leaf candidates.
+First, we find the best location of each template in the edge map that has the minimal CM distance, which will result in an over-completed set of leaf candidates.
 Second, we apply multi-leaf alignment~\cite{yin2014a} approach to find an optimal set of leaf candidates on the last frame of the video, which will provide the information of the number of leaves, tip locations and boundaries of each leaf.
@@
 %\begin{tabular}{lllllllll}
-\includegraphics[width=.14\textwidth]{Figures/AlignPerformance/9_1}&
-\includegraphics[width=.14\textwidth]{Figures/AlignPerformance/10_1}&
-\includegraphics[width=.14\textwidth]{Figures/AlignPerformance/11_1}&
-\includegraphics[width=.14\textwidth]{Figures/AlignPerformance/12_1}&
-\includegraphics[width=.14\textwidth]{Figures/AlignPerformance/14_1}&
-\includegraphics[width=.14\textwidth]{Figures/AlignPerformance/15_1}\\
+\includegraphics[width=.11\textwidth]{Figures/AlignPerformance/9_1}&
+\includegraphics[width=.11\textwidth]{Figures/AlignPerformance/10_1}&
+\includegraphics[width=.11\textwidth]{Figures/AlignPerformance/11_1}&
+\includegraphics[width=.11\textwidth]{Figures/AlignPerformance/12_1}&
+\includegraphics[width=.11\textwidth]{Figures/AlignPerformance/14_1}&
+\includegraphics[width=.11\textwidth]{Figures/AlignPerformance/15_1}\\
 
-\includegraphics[trim= 90 60 100 5, clip, width=.14\textwidth]{Figures/AlignPerformance/9_2}&
-\includegraphics[trim= 90 60 100 5, clip, width=.14\textwidth]{Figures/AlignPerformance/10_2}&
-\includegraphics[trim= 90 60 100 5, clip, width=.14\textwidth]{Figures/AlignPerformance/11_2}&
-\includegraphics[trim= 90 60 100 5, clip, width=.14\textwidth]{Figures/AlignPerformance/12_2}&
-\includegraphics[trim= 90 60 100 5, clip, width=.14\textwidth]{Figures/AlignPerformance/14_2}&
-\includegraphics[trim= 90 60 100 5, clip, width=.14\textwidth]{Figures/AlignPerformance/15_2}\\
+\includegraphics[trim= 90 60 100 5, clip, width=.11\textwidth]{Figures/AlignPerformance/9_2}&
+\includegraphics[trim= 90 60 100 5, clip, width=.11\textwidth]{Figures/AlignPerformance/10_2}&
+\includegraphics[trim= 90 60 100 5, clip, width=.11\textwidth]{Figures/AlignPerformance/11_2}&
+\includegraphics[trim= 90 60 100 5, clip, width=.11\textwidth]{Figures/AlignPerformance/12_2}&
+\includegraphics[trim= 90 60 100 5, clip, width=.11\textwidth]{Figures/AlignPerformance/14_2}&
+\includegraphics[trim= 90 60 100 5, clip, width=.11\textwidth]{Figures/AlignPerformance/15_2}\\
 (a) & (b) & (c) & (d) & (e) & (f) \\
 \end{tabular}
-\caption{Leaf alignment results on the last frame of $6$ plant videos.
+\caption{Leaf alignment results on the last frame of $6$ fluorescence Arabidopsis videos.
 First row shows the original images.
@@
 
+(d) &
+\includegraphics[width=.09\textwidth]{Figures/trackExample/4_1}&
+\includegraphics[width=.09\textwidth]{Figures/trackExample/4_2}&
+\includegraphics[width=.09\textwidth]{Figures/trackExample/4_3}&
+\includegraphics[width=.09\textwidth]{Figures/trackExample/4_4}&
+\includegraphics[width=.09\textwidth]{Figures/trackExample/4_5}&
+\includegraphics[width=.09\textwidth]{Figures/trackExample/4_6}&
+\includegraphics[width=.09\textwidth]{Figures/trackExample/4_7}&
+\includegraphics[width=.09\textwidth]{Figures/trackExample/4_8}&
+\includegraphics[width=.09\textwidth]{Figures/trackExample/4_9}\\
+
+(e) &
+\includegraphics[trim= 160 100 160 60, clip, width=.1\textwidth]{Figures/trackExample/5_1}&
+\includegraphics[trim= 160 100 160 60, clip, width=.1\textwidth]{Figures/trackExample/5_2}&
+\includegraphics[trim= 160 100 160 60, clip, width=.1\textwidth]{Figures/trackExample/5_3}&
+\includegraphics[trim= 160 100 160 60, clip, width=.1\textwidth]{Figures/trackExample/5_4}&
+\includegraphics[trim= 160 100 160 60, clip, width=.1\textwidth]{Figures/trackExample/5_5}&
+\includegraphics[trim= 160 100 160 60, clip, width=.1\textwidth]{Figures/trackExample/5_6}&
+\includegraphics[trim= 160 100 160 60, clip, width=.1\textwidth]{Figures/trackExample/5_7}&
+\includegraphics[trim= 160 100 160 60, clip, width=.1\textwidth]{Figures/trackExample/5_8}&
+\includegraphics[trim= 160 100 160 60, clip, width=.1\textwidth]{Figures/trackExample/5_9}\\
+
+(f) &
+\includegraphics[trim= 100 90 120 60, clip, width=.1\textwidth]{Figures/trackExample/6_1}&
+\includegraphics[trim= 100 90 120 60, clip, width=.1\textwidth]{Figures/trackExample/6_2}&
+\includegraphics[trim= 100 90 120 60, clip, width=.1\textwidth]{Figures/trackExample/6_3}&
+\includegraphics[trim= 100 90 120 60, clip, width=.1\textwidth]{Figures/trackExample/6_4}&
+\includegraphics[trim= 100 90 120 60, clip, width=.1\textwidth]{Figures/trackExample/6_5}&
+\includegraphics[trim= 100 90 120 60, clip, width=.1\textwidth]{Figures/trackExample/6_6}&
+\includegraphics[trim= 100 90 120 60, clip, width=.1\textwidth]{Figures/trackExample/6_7}&
+\includegraphics[trim= 100 90 120 60, clip, width=.1\textwidth]{Figures/trackExample/6_8}&
+\includegraphics[trim= 100 90 120 60, clip, width=.1\textwidth]{Figures/trackExample/6_9}\\
+
 & Day 1 & Day 2 & Day 3 & Day 4 & Day 5 & Day 6 & Day 7 & Day 8 & Day 9 \\
 \end{tabular}
-\caption{Tracking result for one video with one frame for each day. $(a)$ Example frames in the video. $(b)$ Leaf label results overlaid with tip locations. $(c)$ Leaf tracking results. }
+\caption{Tracking result for plant $16$ with a first frame for each day.
+$(a)$ Example frames in fluorescence modality.
+$(b)$ Manual leaf label results overlaid with tip locations.
+$(c)$ Leaf tracking results on fluorescence images.
+$(d)$ Example frames in RGB modality.
+$(e)$ Label propagation from fluorescence images to RGB images.
+$(f)$ Leaf tracking results on RGB images.}
 \label{fig:trackExample}
@@
 \subsection{Performance and Analysis}
-We apply our algorithm to all $144$ frames of each video and evaluate the performance on labeled $36$ frames.
-Leaf alignment is applied to the last frame of each video.
-Figure~\ref{fig:alignResult} shows some examples of leaf alignment results.
+We apply our algorithm to all $135$ frames of each video and evaluate the performance on labeled $36$ frames.
+Figure~\ref{fig:alignResult} shows some examples of leaf alignment results on the last frame of each video. 
 Our framework works very well on segmenting large leaves with no overlap to neighbor leaves.
@@
 
-Leaf alignment provides the leaf candidates for tracking over time.
-Figure~\ref{fig:trackExample} shows the leaf tracking result of one video.
+%Leaf alignment provides the leaf candidates for tracking over time.
+Figure~\ref{fig:trackExample} shows the leaf tracking result of one Arabidopsis video in both fluorescence and RGB modalities. 
+We can see the high quality leaf label propagation results on this video. 
 The leaf template transformation works well for most of the leaves.
 As plant grows, younger leaves may grow faster than older leaves and occlude the older leaves.
-As shown in Figure~\ref{fig:trackExample} (b), purple leaf replaces the red leaf at day $6$.
-Our backward tracking algorithm tracks leaves from the last frame to the first frame.
-The two leaves are still being considered as one leaf (ID $8$) in day $4$ and day $3$.
-Leaf $8$ in day $1$ and $2$ is a leaf ID switch w.r.t.~the purple ground truth leaf and will not be considered as a consistently tracked leaf.
+As shown in Figure~\ref{fig:trackExample} (b)(e), purple leaf replaces the red leaf at day $6$.
+%Our backward tracking algorithm tracks leaves from the last frame to the first frame.
+The two leaves are still being considered as one leaf (ID $8$) in day $4$ and day $3$ (Figure~\ref{fig:trackExample}(c)).
+Leaf $8$ in day $1$ and $2$ is a leaf ID switch w.r.t.~the purple ground truth leaf and will not be considered as a consistently tracked leaf (Figure~\ref{fig:trackExample}(c)).
 However, they are still evaluated as well aligned and segmented leaves.
-%Leaves will be deleted when it becomes small and the leaf underneath it will be detected.
+\todo{May add more if the final figure updated}
 
 For quantitative evaluation, we vary $\tau$ from $0$ to $1$ and generate the first three evaluation metrics, as shown in Figure~\ref{fig:performance}.
-{\it{ULR}} decreases as $\tau$ increases as more leaves are being considered as matched leaves.
+For both RGB and fluorescence modalities, {\it{ULR}} decreases as $\tau$ increases as more leaves are being considered as matched leaves.
 As $\tau$ keeps increasing, {\it{ULR}} approaches a constant value, which is the different number in leaf counting that results from both miss detection and false alarms.
@@
 We generate a label image for each frame based on the leaf segmentation results and compute the {\it{SBD}} score for each labeled image.
-The average {\it{SBD}} over all images is $0.61$.
+The average {\it{SBD}} is $0.61$ for fluorescence images and $0.56$ for RGB images.

### 2015-07-26 response/response.tex
baseline-performance-on-rgb-images
edit-on-response-letter

@@
 \begin{response}
-\todo{Proofread by everyone}
+We have proofread it very carefully and corrected some typos and grammar errors. 
 \end{response}
@@
 Since multi-modality is a strength of the proposed dataset, the authors should motivate better their choice of imaging modalities (i.e.
-fluorescence, infrared, RGB color, and depth), highlighting their importance and what information they convey on plant structure and functions.
+fluorescence, infrared, RGB color, and depth), highlight their importance and what information they convey on plant structure and functions.
 Apparently, this is only partly done for depth at the end of Sec. $2$.
@@
 \begin{response}
-We have augmented Fig. $1$ by adding one zoom-in view for Arabidopsis plant.
-Since bean dataset only includes one plant with good view, we do not provide a zoom-in view.
+We have augmented Figure $1$ by adding one zoom-in view for one Arabidopsis plant.
+Since bean dataset only contains one plant with good view, we do not provide a zoom-in view.
 \end{response}
@@
 \begin{response}
-We have the corresponding references in the prior work section, which follows the order as they appear in Table $2$.
-To make it complete, we also added the reference to Table $2$.
+We have the corresponding references in Sec. $2$, which follows the order as they appear in Table $2$.
+To make it complete, we also added the references to Table $2$.
 \end{response}
@@
 Also they may overlap or be overlapped by other leaves.
-I think that new text we have added more clearly emphasizes leaf identification and tracking over time rather than developing methods/algorithms to define group differences.
+We emphasize more on leaf identification and tracking rather than developing methods/algorithms to define group differences.
 We have added one paragraph in Conclusion to better reflect this.
@@
 \begin{response}
-%Here we want to emphasize that it is not necessary to train and test on the same modality.
-%For example, if we would like to develop a leaf segmentation algorithm that can work on RGB images, we can still utilize the depth images during training.
 In this use case scenario, the training part of leaf segmentation algorithms may have both the RGB and depth modalities, while during the testing, we may only have the RGB modality available.
@@
 \begin{response}
-\todo{Xi}
+We have changed the inaccurate annotations to adhere to the SI style conventions. 
 \end{response}
@@
 However, this is a VERY strong assumption and depends completely on the distance between the cameras, the angles, the distance between object and sensors and the actual object arrangement.
-From our experience even when imaging co-planar plants (such as young Arabidopsis) at a distance of $\sim 70$cm even when the camera sensors are really close to each other (less than $5$cm) some differences in view are there and occlusions are present.
+From our experience even when imaging co-planar plants (such as young Arabidopsis) at a distance of $\sim 70$ cm even when the camera sensors are really close to each other (less than $5$ cm) some differences in view are there and occlusions are present.
 The authors should comment on this and should show as supportive evidence examples of plants at different growth stages in all $4$ modalities in raw and annotated form to show how close this correspondence is matching and how the propagated labels.
@@
 \begin{response}
-\todo{Saif and Xi will work on the label transformation and edit the paper. }
+We expanded our description of the labeling and the propagation to other modalities in the paper.  
+The data labeling is performed in the fluorescence image modality.  
+The infra-red image is from the same camera and so pixel labeling will be identical.  
+The labels are propagated to the color and depth modalities using planar homographies.  
+The homography between the fluorescence image and the color image is calculated by fitting matching features in these modalities, and the homography to the depth image is found by fitting a plane through the $3$D plant points.
+As the reviewer noted, using these homographies will result in pixel segmentation errors due to parallax for plant regions outside of the modeled planes.  
+We evaluate these errors qualitatively and quantitatively.  
+Figure $6$ illustrates the label propagations from the fluorescence image to the other modalities and from the color image to other modalities with two different line colors.  
+Errors occur where the lines fail to overlap and are due to propagation effects as well as boundary selection variations by the labeler between modalities.  
+We compare the magnitude of these two effects in Table $4$. 
+The performance of label propagation is only slightly worse than the performance of another annotator. 
+Therefore, we propagate the fluorescence labels to other modalities for Arabidopsis plants. 
+As for bean plant, the homograph-based mapping performed poorly due to the large within-plant depth variations. 
+So we only provide the labels for bean plant in fluorescence and IR as they use the same camera. 
+Please refer to Sec. $4.3$ for more details. 
 \end{response}
@@
 The released label is labeled by one annotator.
-However, we do use extra annotator to label several images and the annotation error between different annotators is evaluated, as shown in Table $4$. 
+However, we do use an extra annotator to label several images and the annotation error between different annotators is evaluated.
+As shown in Table $4$, the average annotation similarity in case of {\it{SBD}} score is around $0.847$ for fluorescence and $0.858$ for RGB images. 
+Different annotators have more agreement on the labeling as the plant grows. 
+This is due to the evaluation metric {\it{SBD}}, which favors bigger leaves. 
 \end{response}
@@
 \begin{response}
-\todo{Xi: apply to RGB modality and evaluate the performance with transferred labels. Transferred label is needed!}
+We have applied our algorithm on the RGB images while the groudtruth label is generated via label propagation. 
+The performance on RGB images is shown in Figure $9$ and $10$.  
 \end{response}

### 2015-07-26 datapaper.tex
baseline-performance-on-rgb-images
edit-on-response-letter

@@
 
-Among many applications of machine vision, plant image analysis has recently began to gain attention due to its potential impact on plant visual phenotyping, particularly in understanding plant growth, assessing the quality/performance of crop plants and improving crop yield.
+Among many applications of machine vision, plant image analysis has recently began to gain attention due to its potential impact on plant visual phenotyping, particularly in understanding plant growth, assessing the quality/performance of crop plants, and improving crop yield.
 Despite its importance, the lack of publicly available research databases containing plant imagery has substantially hindered the advancement of plant image analysis.
@@
 \input{datapaper_conclusion.tex}
-
-%\input{calibtable.tex}
 

### 2015-07-26 datapaper_baseline.tex
Edit-Over-Paper-One-Pass

@@
 Specifically, we apply it on fluorescence and RGB modalities. 
+Our work is motivated by Chamfer Matching (CM) technique~\cite{barrow1977parametric}, which is used to align two edge maps.
+We extend it to simultaneously align multiple overlapping objects.
+
 Note that~\cite{yin2014a,yin2014b} is designed for rosette plants like Arabidopsis.
-Therefore, it will not be applied to bean plant as it does not belong to rosette plants.
+Therefore, it will not be applied to bean imagery as it does not belong to rosette plant.
 %In addition, we also apply it on the RGB modality and use the propagated labels for evaluation.
@@
 Tip locations will be scaled and rotated accordingly.
-Finally, we generate $2,880$ leaf templates.
+Finally, we generate $2,880$ leaf templates for each modality.
 
-Our work is motivated by Chamfer Matching (CM) technique~\cite{barrow1977parametric}, which is used to align two edge maps.
-We extend it to simultaneously align multiple overlapping objects.
 For plant segmentation, we use simple thresholding process and edge detection to generate an image mask and edge map.
@@
 
-First, we find the best location of each template in the edge map that has the minimal CM distance, which will result in an over-completed set of leaf candidates.
-Second, we apply multi-leaf alignment~\cite{yin2014a} approach to find an optimal set of leaf candidates on the last frame of the video, which will provide the information of the number of leaves, tip locations and boundaries of each leaf.
+First, we find the best location of each template in the edge map that has the minimal CM distance, which will result in an over-completed set of leaf candidates from all templates.
+Second, we apply multi-leaf alignment~\cite{yin2014a} approach to find an optimal set of leaf candidates on the last frame of the video, which will provide the information of the number of leaves, tip locations, and boundary of each leaf.
 Third, we apply multi-leaf tracking~\cite{yin2014b} approach, which is based on leaf template transformation, to track leaves between continuous two frames.
@@
 In the tracking process, we delete a leaf when it becomes too small.
-We develop a procedure to generate new leaves when there is a relatively large portion of the mask has not been covered by current leaf candidates.
+A new leaf is generated when there is a relatively large portion of the mask that has not been covered by current leaf candidates.
 For each frame of the video, we can generate a label image with each leaf being labeled with one color and the tip locations for each estimated leaf.
@@
 First row shows the original images.
-Second row shows the alignment results with red points denoting the boundary of the leaf templates in the blue bounding boxes.
-The numbers on the leaves are the leaf IDs representing the order of the leaf being selected and they will be consistent during tracking.}
+Second row shows the alignment results with red points denoting the boundaries of the leaf templates in the blue bounding boxes.
+The numbers on the leaves are the leaf IDs representing the order of the leaf being selected and will be consistent during tracking.}
 \label{fig:alignResult}
@@
 \centering
-\includegraphics[width=.81\textwidth]{Figures/performance.pdf}\\
-\caption{Performance of the baseline method on the testing set of the fluorescence modality of Arabidopsis plant.}
+\includegraphics[trim= 10 0 0 10, clip, width=.81\textwidth]{Figures/performance_fmp_rgb.pdf}\\
+\caption{Performance of the baseline method on the testing set of the fluorescence and RGB modalities of Arabidopsis plant.}
 \label{fig:performance}
@@
 \subsection{Performance and Analysis}
-We apply our algorithm to all $135$ frames of each video and evaluate the performance on labeled $36$ frames.
+We apply our algorithm to all frames of each video and evaluate the performance on labeled frames.
 Figure~\ref{fig:alignResult} shows some examples of leaf alignment results on the last frame of each video. 
@@
 For overlapping leaves, it becomes more challenging as the edges in the overlapping area are more difficult to be detected.
-However, when the overlapping leaves are further away from the center, they will have a higher chance to be detected as shown in $(c)$ of Figure~\ref{fig:alignResult}.
-When the overlapping leaves are close to the center, smaller leaves will be covered by larger leaves as shown in $(a), (d), (e)$ of Figure~\ref{fig:alignResult}.
+However, when the overlapping leaves are further away from the center, they will have a higher chance to be detected as shown in Figure~\ref{fig:alignResult} $(c)$.
+When the overlapping leaves are close to the center, smaller leaves will be covered by larger leaves as shown in Figure~\ref{fig:alignResult} $(a), (d), (e)$.
 
@@
 As plant grows, younger leaves may grow faster than older leaves and occlude the older leaves.
-As shown in Figure~\ref{fig:trackExample} (b)(e), purple leaf replaces the red leaf at day $6$.
+As shown in Figure~\ref{fig:trackExample} (b),(e), purple leaf replaces the red leaf at day $6$.
 %Our backward tracking algorithm tracks leaves from the last frame to the first frame.
-The two leaves are still being considered as one leaf (ID $8$) in day $4$ and day $3$ (Figure~\ref{fig:trackExample}(c)).
-Leaf $8$ in day $1$ and $2$ is a leaf ID switch w.r.t.~the purple ground truth leaf and will not be considered as a consistently tracked leaf (Figure~\ref{fig:trackExample}(c)).
+The two leaves are still being considered as one leaf (ID $8$) in day $4$ and day $3$ (Figure~\ref{fig:trackExample} (c)).
+Leaf $8$ in day $1$ and $2$ is a leaf ID switch w.r.t.~the purple ground truth leaf and will not be considered as a consistently tracked leaf (Figure~\ref{fig:trackExample} (c)).
 However, they are still evaluated as well aligned and segmented leaves.
-\todo{May add more if the final figure updated}
 
@@
 As the longer frames we evaluate, the higher chance tracking will fail.
-Overall, our method can detect $87\%$ and track $50\%$ of all labeled leaves with less than $20\%$ average tip-based errors.
+Our method can detect $87\%$ and track $50\%$ of all labeled leaves with less than $20\%$ average tip-based errors on fluorescence images.
 
@@
 The average {\it{SBD}} is $0.61$ for fluorescence images and $0.56$ for RGB images.
+
+Overall, the performance on fluorescence images is better than the performance on RGB images.
+This is due to two reasons. 
+First, the resolution of RGB images is much lower than that of fluorescence images, which will results in the miss detection of small leaves, and more severe leaf occlusions. 
+Second, the label propagation causes some error, which is inevitable with the label homography-based mapping.

### 2015-07-26 datapaper_calibration.tex
Edit-Over-Paper-One-Pass

@@
 In this process the poses of all three cameras are also calculated relative to the checkerboard.
-The intrinsic and extrinsic parameters are stored as text files, and a Matlab function is provided that reads the parameters and can plot the camera poses as in Fig.~\ref{fig:CameraConfiguration}.
+The intrinsic and extrinsic parameters are stored as text files, and a Matlab function is provided that reads the parameters and can plot the camera poses as shown in Figure~\ref{fig:CameraConfiguration}.
 
@@
 The variance of $\varepsilon_I$ is estimated for each pixel of a fixed scene observed over multiple images.
-In our experiments we observed a flat, uniform albedo surface perpendicular to the camera at a sequence of depths, and for each depth acquired $300$ images.
+In our experiments we observed a flat, uniform albedo surface (\todo{Danial: Please define ``albedo" here as from Comment $38$}) perpendicular to the camera at a sequence of depths, and for each depth acquired $300$ images.
 Object depth, $d$, has a large impact on $\varepsilon_I$.
@@
 Based on these observations we model $\sigma_I(d,r)$, the standard deviation of $\varepsilon_I$, as a function of depth and pixel radius.
-From our experiments we build up a lookup table for this as plotted in Fig.~\ref{fig:Noise}.
+From our experiments we build up a lookup table for this as plotted in Figure~\ref{fig:Noise}.
 
@@
 \begin{center}
-\caption{Summary of Arabidopsis and Bean databases.}
+\caption{Summary of Arabidopsis and Bean databases. The ``$\times n$" represents the number of modalities.}
 \label{tab:stat}
@@
 \hline
-Bean & $5$ & $5$ & $14$ & $350\times 4$ & $175\times 2$ \\
+Bean & $5$ & $5$ & $13$ & $325\times 4$ & $175\times 2$ \\
 \hline
@@
 We model these with $\varepsilon_S$.
-To estimate its standard deviation $\sigma_S$, we first average over many depth measurement images, in our case $300$, to obtain pixel depth estimates that approximately eliminate the effect of $\varepsilon_I$.
+To estimate its standard deviation $\sigma_S$, we first average over many depth measurement images, in our case $300$, to obtain pixel depth estimations that approximately eliminate the effect of $\varepsilon_I$.
 Then by calculating true ray depths on a known surface, in our case the observed plane, and further assuming that $\varepsilon_S$ has the same standard deviation for all pixels, $\sigma_S$ is obtained as the standard deviation of the error between averaged depths and known depths.
-In our experiments we obtained $\sigma_S=6.5mm$ and found that it was insensitive to changes in depth.
+In our experiments we obtained $\sigma_S=6.5~mm$ and found that it was insensitive to changes in depth.
 
@@
 
-There are additional sources of noise not modeled by this.
+There are additional sources of noise that are not modeled by this.
 Object albedo has an impact although this is fairly weak for strong signal reflections.

### 2015-07-26 datapaper_hardware.tex
Edit-Over-Paper-One-Pass

@@
 \subsection{Hardware Setup}
-
 In this section, we introduce the hardware used for capturing fluorescence, IR, RGB color, and depth imagery data for both plants.
@@
 Chlorophyll {\it a} fluorescence images were captured once every hour during the daylight period in a growth chamber~\cite{cruz2015depi}.
-A set of $5$ images were captured using a Hitachi KP-F145GV CCD camera (Hitachi Kokusai Electric America Inc., Woodbury, NY) outfitted with an infrared long pass filter (Schott Glass RG-$9$, Thorlabs, Newton, NJ), during a short period ($<400~ms$) of intense light saturating to photosynthesis ($>10,000~\mu mol~photons~m^{-2} s^{-1}$) provided by an array of white Cree LEDs (XMLAWT, $5700$K color temperature, Digi-Key, Thief River Falls, MN) collimated using a $20~mm$ Carclo Lens ($10003$, LED Supply, Lakewood, CO).
-%
+A set of $5$ images were captured using a Hitachi KP-F$145$GV CCD camera (Hitachi Kokusai Electric America Inc., Woodbury, NY) outfitted with an infrared long pass filter (Schott Glass RG-$9$, Thorlabs, Newton, NJ), during a short period ($<400~ms$) of intense light saturating to photosynthesis ($>10,000~\mu mol~photons~m^{-2} s^{-1}$) provided by an array of white Cree LEDs (XMLAWT, $5700$K color temperature, Digi-Key, Thief River Falls, MN) collimated using a $20~mm$ Carclo Lens ($10003$, LED Supply, Lakewood, CO).
 Chlorophyll {\it a} fluorescence was excited using monochromatic red LEDs (Everlight $625~nm$, ELSH-F51R1-0LPNM-AR5R6, Digi-Key), collimated using a Ledil reflector optic ($C11347\_REGINA$, Mouser Electronics, Mansfield, TX) and pulsed for $50~\mu s$ during a brief window when the white LEDs were electronically shuttered.
@@
 Infrared images were collected once every hour with the same camera and filter used for chlorophyll {\it a} fluorescence.
-Pulses of $940nm$ light were provided by an array of OSRAM LEDs (SFH $4239$, Digi-Key), collimated using a Polymer Optics lens (Part no. $170$, Polymer Optics Ltd., Berkshire, England).
-Since $940nm$ light does not influence plant development or drive photosynthesis, images were also collected during the night period~\cite{eskins1992light}.
-%
-Precisely, phytochromes are the closest photoreceptors that absorb in the far red, near infrared region, but the action spectrum is diminished to zero or near zero ($>800nm$) in the region where we do IR reflectance ($940nm$)~\cite{butler1964actton}.
-%
+Pulses of $940~nm$ light were provided by an array of OSRAM LEDs (SFH $4239$, Digi-Key), collimated using a Polymer Optics lens (Part no. $170$, Polymer Optics Ltd., Berkshire, England).
+Since $940~nm$ light does not influence plant development or drive photosynthesis, images were also collected during the night period~\cite{eskins1992light}.
+Precisely, phytochromes are the closest photoreceptors that absorb in the far red, near infrared region, but the action spectrum is diminished to zero or near zero ($>800~nm$) in the region where we do IR reflectance ($940~nm$)~\cite{butler1964actton}.
 Note that the other modalities were captured only at day time, so that they will not interfere plant growth.
@@
 \subsubsection{RGB Color and Depth Images} %This section describes characterizes the data from this sensor, particularly the depth data.
-
 The RGB color and depth images were collected using a Creative Senz3D sensor~\cite{nguyen2015vietnamese}.
-The sensor contains both a $1,280 \times 720$ color camera directed parallel to, and separated by roughly $25mm$ from, a depth camera which has a resolution of $320\times240$ pixels.
+The sensor contains both a $1,280 \times 720$ color camera directed parallel to, and separated by roughly $25~mm$ from, a depth camera which has a resolution of $320\times240$ pixels.
 The depth sensor uses a flash near IR illuminator and measures the time-of-flight~\cite{Hansard2013} of the beam at each pixel to obtain depth estimates along with an IR reflectance at each pixel.
@@
 The primary measurement limitation on the range-to-target is the strength of the reflected beam.
-As a result, dark, matt surfaces are measured reliably only at a close range on the order of $20$ or $30cm$.
+As a result, dark, matt surfaces are measured reliably only at a close range on the order of $20$ or $30~cm$.
 Highly reflective surfaces also pose problems with direct reflections leading to saturation and highly unreliable depths.
@@
 \caption{($a$)A plot of the three cameras showing their relative configuration and fields of view as obtained through calibration.
-Units are in $mm$, and distance to the target bean plant is roughly 620$mm$ in this example.
+Units are in $mm$.
+The distance to the target bean plant is roughly $620~mm$ in this example.
 The image planes are plotted at depths proportional to the focal lengths.
@@
 The imagery data, including fluorescence, IR reflectance,  RGB color, and the $3$D depth images, is collected once every hour.
-%
 Five minutes before the end of each hour, $3$D depth images and the color image were captured using the Creative Senz3D sensor (the depth points were transformed into the world coordinates and expressed in the unit of $mm$), followed by fluorescence and IR reflectance images collected sequentially at $2$-minute interval by the IR filtered CCD camera.
-%
-No substantial movements or growth were observed within the about four-minute period required for image capture using all four modalities, minimizing potential problems in image calibration.
+No substantial movements or growth were observed within the about $4$-minute period required for image capture using all four modalities, which minimize the potential problems in image calibration.
 

### 2015-07-26 datapaper_intro.tex
Edit-Over-Paper-One-Pass

@@
 Plants develop through a complex interaction between genotype and environment.
-This determines their structure, functions, and thus performance such as yield or efficient use of resources.
+This determines their structure, functions, and thus performance such as yield or efficient usage of resources.
 In order to understand the genetic basis of these economically important parameters, it is essential to quantitatively assess plant phenotypes and then identify the latent relationships to genotypes and environmental factors.
@@
 In the past, traditional phenotyping is based on experience and intuition, and is laborious~\cite{johannsenerblichkeit}.
-Recent progresses in imaging sensor, robotics and automation technologies lead to the development of the ever-increasing new field of highly automated, non-destructive {\it plant visual phenotyping}~\cite{furbank2011phenomics,cruz2015depi}.
+Recent progresses in imaging sensor, robotics and automation technologies lead to the development of the ever-increasing new field of highly automated, non-destructive plant visual phenotyping~\cite{furbank2011phenomics,cruz2015depi}.
 %Modern plant phenotyping is a comprehensive, large-scale assessment of plant traits such as growth, development, tolerance, resistance, architecture, physiology, ecology, yield, and metadata that form the basis for more complex parameters.
@@
 
-One practical goal of plant visual phenotyping is to accurately quantify plant traits, particularly those related to photosynthetic performance, growth, yield and resilience to environmental stress.
-For the approaches to be of practical use, plants must be monitored continuously, over developmental time scales and under conditions that more closely approximate the native environment (dynamic 'field' conditions)~\cite{fahlgren2015lights,walter2015plant}.
+One practical goal of plant visual phenotyping is to accurately quantify plant traits, particularly those related to photosynthetic performance, growth, yield, and resilience to environmental stress.
+For the approaches to be of practical, plants must be monitored continuously, over developmental time scales and under conditions that more closely approximate the native environment (dynamic 'field' conditions)~\cite{fahlgren2015lights,walter2015plant}.
 %
-The capacity to identify and track individual leaves throughout experiments is important for more clearly defining phenotypic behaviors related to leaf specific factors such as developmental age~\cite{schottler2015photosynthetic} and/or following the application of stress.
+The capacity to identify and track individual leaves throughout experiments is important to more clearly define phenotypic behaviors related to leaf specific factors such as developmental age~\cite{schottler2015photosynthetic} and/or following the application of stress.
 For example, decrease in the average photosynthetic efficiency ($\Phi_{II}$, quantum yield of photochemistry at photosystem II) of an Arabidopsis plant may reflect a heterogeneous distribution of $\Phi_{II}$ values across its entire photosynthetic surface area~\cite{oxborough2004imaging}.
@@
 \multirow{2}{*}{MSU-PID} & fluorescence, & LS, LO, & Arabidopsis & $16$ & $2,160\times 4$ & $576\times 4$ \\ \cline{4-7}
-& IR, RGB, depth & LA, LT & Bean & $5$ & $350\times 4$ & $175\times 2$ \\ \hline
+& IR, RGB, depth & LA, LT & Bean & $5$ & $325\times 4$ & $175\times 2$ \\ \hline
 \hline
@@
 In fact, computer vision research lives on and advances with databases, as evidenced by the successful databases in the field (e.g., FERET~\cite{Phillips2000} and LFW~\cite{LFW}).
-However, the publicly available database for plant phenotyping is still very limited, with the only exception of LSC database~\cite{scharr2014annotated}, which, nevertheless, has its own limitations on the type of images (RGB only) and is only suitable for a small set of plant image analysis applications.
+However, the publicly available databases for plant phenotyping are still very limited, with the only exception of LSC database~\cite{scharr2014annotated}, which, nevertheless, has its own limitations on the type of images (RGB only) and is only suitable for a small set of plant image analysis applications.
 
@@
 Checkerboard-based camera calibration is performed on each modality providing intrinsic camera parameters and poses.
-In addition explicit correspondence between the pixels of {\it any} two modalities is obtained using an homographic warping of a plane through the plants.
+In addition explicit correspondence between the pixels of {\it any} two modalities is obtained using an homographic warping of a plane through the Arabidopsis plants.
 
 The type and amount of manual labels on a database is a critical enabler to the potential applications of the database.
-For a subset of the MSU-PID database, we manually label the ground truth regarding the leaf identification number, locations of leaf tips, and leaf segments.
-As a result, MSU-PID is suitable for a number of applications, including 1) {\it leaf segmentation} that aims at estimating the correct segmentation mask of each leaf in an image, 2) {\it leaf counting} that estimates the correct number of leaves within a plant, 3) {\it leaf alignment} that aligns the two tips of each leaf -- the cornerstone of the leaf structure, and 4) {\it leaf tracking} that is designed to track each leaf over time.
+For a subset of the MSU-PID database, we manually label the groundtruth regarding the leaf identification number, locations of leaf tips, and leaf segments.
+As a result, MSU-PID is suitable for a number of applications, including $1)$ {\it leaf segmentation} that aims at estimating the correct segmentation mask of each leaf in an image, $2)$ {\it leaf counting} that estimates the correct number of leaves within a plant, $3)$ {\it leaf alignment} that aligns the two tips of each leaf -- the cornerstone of the leaf structure, and $4)$ {\it leaf tracking} that is designed to track each leaf over time.
 Finally, to provide a performance baseline for future research and comparison, we apply our automatic leaf segmentation framework~\cite{yin2014a,yin2014b} to the Arabidopsis imagery and demonstrate the unique challenge of image analysis on this database.

### 2015-07-26 datapaper_plants.tex
Edit-Over-Paper-One-Pass

@@
 
-{\it Arabidopsis thaliana} (ecotype Col-0) plants were grown at $20^{\circ}C$, under a $16$hr : $8$hr day-night cycle with a daylight intensity set at $100~\mu mol~photons~m^{-2} s^{-1}$.
+{\it Arabidopsis thaliana} (ecotype Col-$0$) plants were grown at $20^{\circ}C$, under a $16~hr$ : $8~hr$ day-night cycle with a daylight intensity set at $100~\mu mol~photons~m^{-2} s^{-1}$.
 %
-Black bean plants ({\it Phaseolus vulgaris L.}) of the cultivar Jaguar, were grown under a $14$hr : $10$hr day-night cycle with day and night temperatures of $24^{\circ}C$ and $18^{\circ}C$ respectively, and a daylight intensity set at $200~\mu mol~photons~m^{-2} s^{-1}$.
+Black bean plants ({\it Phaseolus vulgaris L.}) of the cultivar Jaguar, were grown under a $14~hr$ : $10~hr$ day-night cycle with day and night temperatures of $24^{\circ}C$ and $18^{\circ}C$ respectively, and a daylight intensity set at $200~\mu mol~photons~m^{-2} s^{-1}$.
 %
@@
 %
-Two-week-old plants ({\it Arabidopsis} and bean) were transferred to imaging chambers and allowed to acclimate for $24$ hours to the LED lighting before the start of the data collection.
+Two-week-old plants ({\it Arabidopsis} and bean) were transferred to imaging chambers and allowed to acclimate (\todo{Jeff: Please define ``acclimate" as in Comment $37$}) for $24$ hours to the LED lighting before the start of the data collection.
 Growth conditions as described above were maintained for each set of plants for the duration of image collection.

### 2015-07-26 datapaper_prior.tex
Edit-Over-Paper-One-Pass

@@
 Finally, the crop/weed image database~\cite{haug2014crop} is captured by a robot in the real field, and used for the classification of crop vs. weed.
-Note that except for~\cite{haug2014crop} where images are captured in the wild for a large area of plant, other databases in this type normally capture only a {\it single} leaf in a relatively constrained imaging environment.
+Note that except for~\cite{haug2014crop} where images are captured in the wild for a large area of plants, other databases in this type normally capture only a single leaf in a relatively constrained imaging environment.
 Therefore, the challenging problem of leaf segmentation has been bypassed.
@@
 Thus, non-destructive imaging approaches are taken and the entire plant is imaged.
-The LSC database~\cite{scharr2014annotated} is the most relevant one to our database.
+The LSC database~\cite{scharr2014annotated} is the most relevant one to ours.
 It captures a large set of RGB images for Arabidopsis and tobacco plants.
@@
 The four sensing modalities in MSU-PID provide unique opportunities to comprehensively characterize plant morphological and physiological phenotypes.
-The use of chlorophyll fluorescence at $730nm$ to $750nm$ as a tool for evaluating photosynthetic performance is well established~\cite{baker2008chlorophyll}, and against non-(chlorophyll)fluorescent background clearly defines photosynthetically active leaf area.
+The use of chlorophyll fluorescence at $730$ $nm$ to $750$ $nm$ as a tool for evaluating photosynthetic performance is well established~\cite{baker2008chlorophyll}, and against non-(chlorophyll)fluorescent background clearly defines photosynthetically active leaf area.
 The depth measurement has been a component of a number of recent non-plant RGB-D databases designed for object recognition~\cite{Lai2011}, scene segmentation~\cite{Silberman2011}, human analysis~\cite{Sung2011,Barbosa:reid12}, and mapping~\cite{sturm12iros}.

### 2015-07-26 datapapr_labeling.tex
Edit-Over-Paper-One-Pass

--- 2015-07-26 datapapr_labeling.tex
@@
 As there is no light at night hours, plants can not be imaged by the fluorescence and RGB color sensors while IR and depth cameras can still perform the capturing during the night.
-In order to make sure that all four modalities are present at each imaging modality, we release the part of images captured only in the day time, which are $15$ images per day for Arabidopsis and $14$ for bean for all four modalities.
+In order to make sure that all four modalities are present at the same time, we release the part of images captured only in the day hours, which are $15$ images per day for Arabidopsis and $13$ for bean for all four modalities.
 
-The two subsets differ in plant image resolutions.
+The two subsets differ in image resolutions.
 As shown in Figure~\ref{fig:fourmodality}, we grow and image a single bean plant while a whole tray of Arabidopsis are grown at the same time.
-Therefore, the resolution of a Arabidopsis plant is much lower than that of a bean plant.
-We manually crop $16$ Arabidopsis plants, which have been captured by all four sensors simultaneously.
+Therefore, the resolution of a Arabidopsis image is much lower than that of a bean image.
+We manually crop $16$ Arabidopsis plants, which have been captured by all three cameras simultaneously.
 Table~\ref{tab:resolution} summaries the image resolution of each plant in all four modalities.
@@
 \label{sec:annotation}
-Part of the database is manually annotated to provide ground truth tip locations, leaf segmentation results, and leaf consistency overtime.
-We use the fluorescence images as the input for labeling because of their simple and uniform background.
+Part of the database is manually annotated to provide groundtruth tip locations, leaf segmentation results, and leaf consistency overtime.
+We use the fluorescence images as the input for labeling because of their clean and uniform background.
 %Tip locations are saved in a TXT file for each frame.
@@
 For Arabidopsis images, we label $4$ frames each day.
-While for bean images, we label $7$ frames each day because of their spontaneous and faster leaf movement.
+While for bean images, we label $7$ frames each day because of their spontaneous and fast leaf movement.
 A Matlab GUI interface is developed for leaf labeling, as shown in Figure~\ref{fig:label}, which will also be available to the public.
-A user can open a plant image to label the two tips and annotate each leaf segment.
-The results will be automatically saved once a user moves to the next image.
+A user can open a plant image (``Open") to label the two tips and annotate each leaf segment.
+The results will be automatically saved once a user moves to a previous or next image (``Previous", and ``Next").
 For consistent annotation of the same leaf over time, we show a number on the center of each leaf indicating the order of labeling from the previous frame.
@@
 The ``Show Tip" option is to select whether to show the tips or not. 
-For relabeling of both leaf segments and leaf tips, press ``Restart".
+For relabeling of both leaf segments and leaf tips on the current image, click ``Restart".
 
-After the labeling, we visually go through the results and correct inaccurate labels due to human error.
+After the labeling, we visually go through the results and correct inaccurate labels.
 One example of the labeling results for one plant is shown in Figure~\ref{fig:trackExample} $(b)$, where one color is used to represent each specific leaf.
@@
 \end{tabular}
-\caption{Label propagation between all four modalities ($a$) infra-red, ($b$) fluorescence, ($c$) color and ($d$) depth, of a sample plant in the Arabidopsis collection for day $3$ (top row), day $5$ (middle row), and day $9$ (bottom row).
+\caption{Label propagation between all four modalities ($a$) IR, ($b$) fluorescence, ($c$) RGB color, and ($d$) depth, of a sample plant in the Arabidopsis collection for day $3$ (top row), day $5$ (middle row), and day $9$ (bottom row).
 In the dataset the manual segmentation is performed on the fluorescence images and is outlined here as orange lines propagated to all modalities.  
-The infra-red image is taken by the same camera and so will have close to exact pixel correspondence.
+The IR images are taken by the same camera and so will have almost exact pixel correspondence.  
 To assess the segmented pixel propagation to other modalities, we also manually labeled a subset of the color plant images and propagated this segmentation to all modalities (shown in cyan).  
-Comparing these boundaries in each modality gives a measure of the propagation errors due to parallax, and we provide quantitative analysis in table XXX.
+Comparing these boundaries in each modality gives a measure of the propagation errors due to parallax, and we provide quantitative analysis in Table~\ref{tab:labelError}.  
 Note that the color and depth images are rotated $90$ degrees.}
@@
 
-The leaf labeling can be propagated to each of the other modalities from the fluorescence images for the Arabidopsis sequence.  
+The leaf labeling can be propagated to each of the other modalities from the fluorescence images for the Arabidopsis sequences.  
 To do this, we approximate a plant image with a plane, and find homographies that transform the fluorescence images into the other images.  
@@
 We manually label $3$ images for each of $3$ Arabidopsis plants ($9$ images in total) on fluorescence and RGB modalities. 
-One label propagation results is illustrated in Figure~\ref{fig:LabelAlignment}.
+The labels in each modality is propagated on other modalities. 
+The result of one plant is illustrated in Figure~\ref{fig:LabelAlignment}.
 This mapping will introduce errors due to depth-based parallax.  
-We use {\it{SBD}} score, which will be introduced in Section~\ref{sec:protocol}, to evaluate the similarity between the manual label image and the propagation result. 
+We use {\it{SBD}} score, which will be introduced in Section~\ref{sec:protocol}, to evaluate the similarity between the manual labels and the propagation results. 
 In order to compare the label propagation error with human label error, we ask two different annotators to label the same $9$ images and compute the {\it{SBD}} score. 
@@
 
-We can make two conclusion from Table~\ref{tab:labelError}.
+We can make two conclusions from Table~\ref{tab:labelError}.
 First, the similarity for both manual annotation and label propagation increases as the plant grows.
@@
 Second, the performance of label propagation is only slightly worse than the performance of human annotations. 
-Therefore, we use label propagation to provide the labels for all four modalities for Arabidopsis plants. 
+Therefore, we use label propagation to provide the labels for all four modalities for Arabidopsis sequences. 
 There are two benefits. 
@@
 
-In the case of the bean plant, the pixel association between modalities is more difficult as the within-plant depth variations are large.  
-We found a homograph-based mapping performed poorly, and so the manual annotations we supply apply to just the infra-red and fluorescence images which use the same camera.
+In the case of the bean sequences, the pixel association between modalities is more difficult as the within-plant depth variations are large.  
+We found a homograph-based mapping performed poorly, and so the manual annotations we supply apply to just the infrared and fluorescence images which use the same camera.
 
@@
 \end{itemize}
-where ID indicates the plant subject ID number ($1$ to $16$ for Arabidopsis, $1$ to $5$ for bean), X is an integer indicating the date ($1-9$ for Arabidopsis, $1$ to $5$ for bean), and YY represents the image index within a day ($1-15$ for Arabidopsis, $1$ to $14$ for bean).
-For each combination of day and hour, we provide four modalities in PNG files ($\_$rgb, $\_$fmp, $\_$ir, $\_$depth).
+where ID indicates the plant subject ID number ($1$ to $16$ for Arabidopsis, $1$ to $5$ for bean), X is an integer indicating the date ($1-9$ for Arabidopsis, $1$ to $5$ for bean), and YY represents the hour index within a day ($9-23$ for Arabidopsis, $9-21$ for bean).
+For each combination of day and hour, we provide the original images in all four modalities ($\_$rgb, $\_$fmp, $\_$ir, $\_$depth) in PNG files.
 %\begin{itemize}
@@
 %For each combination of day and hour, we provide four modalities in PNG files ($\_$rgb, $\_$fmp, $\_$ir, $\_$depth).
-For annotated images, we have two additional files ($\_$label, $\_$tips) saving the annotation results.
+For annotated modalities, we have two additional files ($\_$label, $\_$tips) saving the annotation results.
 Leaf segmentation results are encoded as indexed PNG files, where each leaf is assigned a unique and consistent leaf ID over time.
-Leaf ID starts from $1$ and continuously increase till the total number of leaves.
+Leaf ID starts from $1$ and continuously increases till the total number of leaves.
 And the background is encoded as $0$.
@@
 \end{itemize}
-where leaf ID is an integer number that is consistent with the segmentation label in the PNG file.
+where leaf ID is an integer number that is consistent with the segmentation label in the $\_$label file.
 tip$1\_$x and tip$1\_$y represent the coordinates of the outer tip point.
 tip$2\_$x and tip$2\_$y represent the coordinates of the inner tip point.
-Any NAN values in the file indicates an invisible leaf.
+Any ``nan" value in the file indicates an invisible leaf.
 
@@
 As shown in Table~\ref{tab:database}, MSU-PID can be used for applications such as leaf segmentation, leaf counting, leaf alignment, and leaf tracking.
-To facilitate future research, we separate the database into the training set and the testing set.
+To facilitate future research, we separate the database into training set and testing set.
 $40\%$ of the data is used for training and $60\%$ for testing.
@@
 For fair comparison, both supervised learning and unsupervised learning methods should evaluate their performance on the training and testing sets separately.
+
 The user may decide to utilize one or multiple modalities of the plant imagery for training and testing respectively.
@@
 For example, using RGB and depth modalities for training and RGB for testing can take advantage of additional information during the learning without incurring extra sensor cost during the testing, which can be implemented via either learning with side information~\cite{chen2013boosting}, or transfering learning with missing modality~\cite{ding2014latent}.
-%The evaluation metrics will be discussed in Sec.~\ref{sec:baseline}.
 
@@
 \item {\it{Tracking Consistency (TC)}}, the percentage of video-to-video correspondent leaves whose tip-based errors are smaller than $\tau$.
-This is used to measure leaf tracking error.
+This is used to measure leaf tracking accuracy.
 \end{itemize}
 
-In order to evaluate the leaf segmentation accuracy, we adopt an additional metric~\cite{scharr2014annotated} based on the Dice score of estimated segmentation results and ground truth labels:
+In order to evaluate the leaf segmentation accuracy, we adopt an additional metric~\cite{scharr2014annotated} based on the Dice score of estimated segmentation results and groundtruth labels:
 \begin{itemize}
-\item {\it{Symmetric Best Dice (SBD)}}, the symmetric best Dice among all labeled leaves.
+\item {\it{Symmetric Best Dice (SBD)}}, the average symmetric best Dice among all labeled leaves.
 \end{itemize}

### 2015-07-27 response/response.tex
go-over-response

@@
 Therefore, we did not apply the baseline method to bean plants.
-We have added this statement in the beginning of Sec. $5.1$.
+We have added this statement in the beginning of Sec. $5$.
 \end{response}
@@
 \begin{response}
-\todo{will expand after everything finished}
+We have expanded the conclusions. 
 \end{response}
@@
 $t_1$ represents the outer leaf tip and $t_2$ represents the inner leaf tip.
-This representation is the same as the released leaf tip labels as illustrated in the end of the first paragraph in Sec. $4.3$.
+This representation is the same as the released leaf tip labels as illustrated in Sec. $4.4$.
 The equation does not rely on the correspondence of inner or outer tips as long as the estimated tips correspond to the labeled tips.
@@
 \begin{response}
-We expanded our description of the labeling and the propagation to other modalities in the paper.  
+We add one more section (Sec. $4.3$) in the paper to describe the labeling and the propagation to other modalities. 
 The data labeling is performed in the fluorescence image modality.
-The infra-red image is from the same camera and so pixel labeling will be identical.  
-The labels are propagated to the color and depth modalities using planar homographies.  
-The homography between the fluorescence image and the color image is calculated by fitting matching features in these modalities, and the homography to the depth image is found by fitting a plane through the $3$D plant points.
+The infrared image is from the same camera and so pixel labeling will be identical.
+The labels are propagated to the RGB color and depth modalities using planar homographies.
+The homography between the fluorescence image and the RGB color image is calculated by fitting matching features in these modalities, and the homography to the depth image is found by fitting a plane through the $3$D plant points.
 As the reviewer noted, using these homographies will result in pixel segmentation errors due to parallax for plant regions outside of the modeled planes.
@@
 From Fig.
-$2$ it appears the distance from plant to sensor to be greater than $60$mm ($6$cm) !!!
-ie., to me it looks close to $60$cm, but either Fig.
+$2$ it appears the distance from plant to sensor to be greater than $60~mm$ ($6~cm$) !!!
+ie., to me it looks close to $60~cm$, but either Fig.
 $3$ has wrong axis range or something else is going on.
@@
 \begin{response}
-Yes, the distance to the plant is roughly $620$mm.
+Yes, the distance to the plant is roughly $620~mm$.
 The image planes are plotted not at the plant location, but at a distance proportional to the focal length of each camera.
@@
 \begin{response}
-Please refer to comment $22$.
+Please refer to Comment $22$.
 \end{response}
@@
 For overlapping leaves, we can visualize the relative location and annotate accordingly.
+Please refer to Fig. $9 (b)$ for examples of the labeled images.  
 \end{response}

### 2015-07-27 response/response.tex
explant conlusion

@@
 \begin{review}
-Fig.
-$3$ (a) ...
-From Fig.
-$2$ it appears the distance from plant to sensor to be greater than $60~mm$ ($6~cm$) !!!
-ie., to me it looks close to $60~cm$, but either Fig.
-$3$ has wrong axis range or something else is going on.
+Figure $3$ (a) ...
+From Figure $2$ it appears the distance from plant to sensor to be greater than $60~mm$ ($6~cm$) !!!
+ie., to me it looks close to $60~cm$, but either Figure $3$ has wrong axis range or something else is going on.
 Can you please explain/update?
-Also same Fig. $3$, shouldn't the images overlap?
+Also same Figure $3$, shouldn't the images overlap?
 Why are shown translated?
@@
 For overlapping leaves, we can visualize the relative location and annotate accordingly.
-Please refer to Fig. $9 (b)$ for examples of the labeled images.  
+Please refer to Figure $9 (b)$ for examples of the labeled images.  
 \end{response}

### 2015-07-27 datapaper_conclusion.tex
explant conlusion

--- 2015-04-29 datapaper_conclusion.tex
@@
-\section{Conclusions}
+\section{Conclusion and Discussion}
 
-This paper presents a newly collected multi-modality plant imagery database, ``MSU-PID''.
-Compared to existing databases in the field, MSU-PID not only has multiple calibrated modalities, but also enables a wide variety of plant image analysis applications.
-Therefore, we believe this new database will be benefitial to the research community in terms of algorithm development, performance evaluation, and identifying new research problems in plant image analysis.
-Furthmore, we are also open to suggestions and comments from the users of this database to further enhance our imaging setup and capturing protocol, so that we can develop new databases in the future.
+This paper presents a newly collected multi-modality plant imagery dataset ``MSU-PID''.
+It has two subsets for Arabidopsis and bean plants respectively. 
+Compared to existing databases in the field, MSU-PID uses multiple calibrated modalities including fluorescence, infrared, RGB color, and depth. 
+Detailed image capture process and camera calibration are studied. 
+We provide our manual labels about leaf tip locations, leaf segments, and leaf consistency over time on fluorescence modality. 
+The labels are propagated to other modalities using homograph mapping for Arabidopsis imagery. 
+Our annotations enable a wide variety of plant image analysis applications.
+
+It might be noticed that all plants in MSU-PID belong to the same genotype and no treatments applied.
+This is because we think a fundamental issue with visual phenotyping, i.e.
+accurate and automated identification and tracking of individual leaves over developmental time scales (weeks), which importance has being highlighted in Introduction, needs to be solved before expending our goal to define group differences.
+The inherent challenge in this issue is that as leaves emerge and grow, they change in size, position and shape and they may overlap or be overlapped by other leaves.
+We emphasize more in leaf identification and tracking rather than developing methods to define group differences.
+
+For others to use our dataset, we have designed an experimental protocol with various evaluation metrics for different applications.  
+To facilitate future research, we apply our automatic multi-leaf segmentation, alignment, and tracking algorithm on the fluorescence and RGB modalities of Arabidopsis imagery, where the labels for RGB modality is provided via label propagation.
+Our methods performs better on fluorescence images than RGB images. 
+This is due to three reasons. 
+First, the algorithm is originally developed for fluorescence images. 
+Second, the resolution of RGB images are much lower than that of fluorescence images. 
+Third, the groudtruth labels for RGB images are generated through the mapping of fluorescence labels, which will cause some error. 
+We recognize our dataset as very challenging dataset.
+
+We believe this new database will be beneficial to the research community in terms of algorithm development, performance evaluation, and identifying new research problems in plant image analysis.
+Furthermore, We are also open to suggestions and comments from the users of this database to further enhance our imaging setup and capturing protocol, so that we can develop new databases in the future.
+
+%This paper presents a newly collected multi-modality plant imagery database, ``MSU-PID''.
+%Compared to existing databases in the field, MSU-PID not only has multiple calibrated modalities, but also enables a wide variety of plant image analysis applications.
+%Therefore, we believe this new database will be beneficial to the research community in terms of algorithm development, performance evaluation, and identifying new research problems in plant image analysis.
+%Furthermore, we are also open to suggestions and comments from the users of this database to further enhance our imaging setup and capturing protocol, so that we can develop new databases in the future.
+%
+%It might be noticed that all plants (respectively for Arabidopsis and bean) in MSU-PID belong to the same genotype and no treatments applied.
+%%This would entail that the proposed dataset cannot be used to investigate computer vision algorithms or imaging modalities in relation to group differences.
+Could the authors comment on this?
+This is true.
+We are not comparing group differences, based on morphology (for example).
+%This is because we think a fundamental issue with visual phenotyping, i.e.
+accurate and automated identification and tracking of individual leaves over developmental time scales (weeks), which importance has being highlighted in Introduction, needs to be solved before expending our goal to define group differences.
+The inherent challenge in this issue is that as leaves emerge and grow, they change in size, position and shape and they may overlap or be overlapped by other leaves.
+%%I think that new text we have added more clearly emphasizes leaf identification and tracking over time rather than developing methods/algorithms to define group differences.
+%
+%

### 2015-07-27 response/response.tex
comments from jeff

@@
 \begin{response}
-\todo{Jin}
+The depth sensor uses a a flash near IR illuminator to obtain depth estimates. 
+The near IR illuminator will not influence the plant growth. 
+The color image does not use any special lighting so it is not harmful as well. 
+The IR and fluorescence images use a saturation light, which will damage the plants only if at high frequency. 
+However, as we are taking images once per hour, the influence is minimal and can be ignored. 
 \end{response}
@@
 Please refer to Comment $9$ for the reason we do not include mutants.
-\todo{Are we going to have mutants in bean data?}
+% \todo{Are we going to have mutants in bean data?} We are not going to have mutants in the bean dataset. 
 % is that we assume any computer vision algorithms that work on wildtypes should also work well on mutants as they have similar structure.
@@
 \begin{response}
-\todo{Jin}
+``Collimated" means to make the light rays parallel. 
+We have added this definition in the paper. 
 \end{response}

### 2015-07-27 datapaper_hardware.tex
comments from jeff

@@
 A set of $5$ images were captured using a Hitachi KP-F$145$GV CCD camera (Hitachi Kokusai Electric America Inc., Woodbury, NY) outfitted with an infrared long pass filter (Schott Glass RG-$9$, Thorlabs, Newton, NJ), during a short period ($<400~ms$) of intense light saturating to photosynthesis ($>10,000~\mu mol~photons~m^{-2} s^{-1}$) provided by an array of white Cree LEDs (XMLAWT, $5700$K color temperature, Digi-Key, Thief River Falls, MN) collimated using a $20~mm$ Carclo Lens ($10003$, LED Supply, Lakewood, CO).
-Chlorophyll {\it a} fluorescence was excited using monochromatic red LEDs (Everlight $625~nm$, ELSH-F51R1-0LPNM-AR5R6, Digi-Key), collimated using a Ledil reflector optic ($C11347\_REGINA$, Mouser Electronics, Mansfield, TX) and pulsed for $50~\mu s$ during a brief window when the white LEDs were electronically shuttered.
+Chlorophyll {\it a} fluorescence was excited using monochromatic red LEDs (Everlight $625~nm$, ELSH-F51R1-0LPNM-AR5R6, Digi-Key), collimated (which means to make the light rays parallel) using a Ledil reflector optic ($C11347\_REGINA$, Mouser Electronics, Mansfield, TX) and pulsed for $50~\mu s$ during a brief window when the white LEDs were electronically shuttered.
 In addition, a series of $5$ images were also collected in the absence of the excitation light for artifact subtraction.

### 2015-07-27 datapaper_plants.tex
comments from jeff

@@
 %
-Two-week-old plants ({\it Arabidopsis} and bean) were transferred to imaging chambers and allowed to acclimate (\todo{Jeff: Please define ``acclimate" as in Comment $37$}) for $24$ hours to the LED lighting before the start of the data collection.
+Two-week-old plants ({\it Arabidopsis} and bean) were transferred to imaging chambers and allowed to acclimate for $24$ hours to the LED lighting before the start of the data collection.
 Growth conditions as described above were maintained for each set of plants for the duration of image collection.

### 2015-07-27 datapaper_conclusion.tex
1st revision edits

@@
 It might be noticed that all plants in MSU-PID belong to the same genotype and no treatments applied.
-This is because we think a fundamental issue with visual phenotyping, i.e.
-accurate and automated identification and tracking of individual leaves over developmental time scales (weeks), which importance has being highlighted in Introduction, needs to be solved before expending our goal to define group differences.
+This is because we think a fundamental issue with visual phenotyping, i.e., accurate and automated identification and tracking of individual leaves over developmental time scales (weeks), whose importance has been highlighted in Section~\ref{sec:intro}, needs to be solved before expending our goal to define group differences.
 The inherent challenge in this issue is that as leaves emerge and grow, they change in size, position and shape and they may overlap or be overlapped by other leaves.
-We emphasize more in leaf identification and tracking rather than developing methods to define group differences.
+We emphasize more in leaf segmentation, alignment and tracking rather than developing methods to discriminate group differences.
 
@@
 To facilitate future research, we apply our automatic multi-leaf segmentation, alignment, and tracking algorithm on the fluorescence and RGB modalities of Arabidopsis imagery, where the labels for RGB modality is provided via label propagation.
-Our methods performs better on fluorescence images than RGB images. 
-This is due to three reasons. 
-First, the algorithm is originally developed for fluorescence images. 
-Second, the resolution of RGB images are much lower than that of fluorescence images. 
-Third, the groudtruth labels for RGB images are generated through the mapping of fluorescence labels, which will cause some error. 
-We recognize our dataset as very challenging dataset.
+The experimental results on fluorescence and RGB images indicate that our dataset is very challenging.
 

### 2015-07-28 datapaper_intro.tex
1st revision edits

@@
 In the past, traditional phenotyping is based on experience and intuition, and is laborious~\cite{johannsenerblichkeit}.
-Recent progresses in imaging sensor, robotics and automation technologies lead to the development of the ever-increasing new field of highly automated, non-destructive plant visual phenotyping~\cite{furbank2011phenomics,cruz2015depi}.
+Recent progresses in imaging sensor and computer vision technologies lead to the development of the ever-increasing new field of highly automated, non-destructive plant visual phenotyping~\cite{furbank2011phenomics,cruz2015depi}.
 %Modern plant phenotyping is a comprehensive, large-scale assessment of plant traits such as growth, development, tolerance, resistance, architecture, physiology, ecology, yield, and metadata that form the basis for more complex parameters.
@@
 A key advance in visual phenotyping is the capability to non-invasively capture plant traits, enabling continuous measurements that are necessary to monitor plants during growth and/or under stress conditions.
-Vision based phenotyping also increases the throughput of phenotyping experiments by eliminating destructive operations.
-The increased capacity allows more genotypes or biological replicates to be examined under the same environmental conditions~\cite{fahlgren2015lights,walter2015plant}.
+It also increases the throughput of phenotyping experiments by eliminating destructive operations, which allows more genotypes or biological replicates to be examined under the same environmental conditions~\cite{fahlgren2015lights,walter2015plant}.
 
-One practical goal of plant visual phenotyping is to accurately quantify plant traits, particularly those related to photosynthetic performance, growth, yield, and resilience to environmental stress.
-For the approaches to be of practical, plants must be monitored continuously, over developmental time scales and under conditions that more closely approximate the native environment (dynamic 'field' conditions)~\cite{fahlgren2015lights,walter2015plant}.
+One goal of plant visual phenotyping is to accurately quantify plant traits, particularly those related to photosynthetic performance, growth, yield, and resilience to environmental stress.
+For the approaches to be of practical, plants must be monitored continuously, over developmental time scales and under conditions that approximate the native environment (dynamic 'field' conditions)~\cite{fahlgren2015lights,walter2015plant}.
 %
-The capacity to identify and track individual leaves throughout experiments is important to more clearly define phenotypic behaviors related to leaf specific factors such as developmental age~\cite{schottler2015photosynthetic} and/or following the application of stress.
+The capacity to identify and track individual leaves over time is important to clearly define phenotypic behaviors related to leaf-specific factors such as developmental age~\cite{schottler2015photosynthetic} and/or following the application of stress.
 For example, decrease in the average photosynthetic efficiency ($\Phi_{II}$, quantum yield of photochemistry at photosystem II) of an Arabidopsis plant may reflect a heterogeneous distribution of $\Phi_{II}$ values across its entire photosynthetic surface area~\cite{oxborough2004imaging}.
-In this case, mapping distributions to individual leaves can be used to distinguish between a systemic (whole plant) effect and localization of the effect to subset leaves.
+In this case, mapping distributions to individual leaves can distinguish between a systemic (whole plant) effect and localization of the effect to subset leaves.
 %
-In addition, using more detailed information, such as leaf angle and height/position as well as canopy density/size, it should be possible to improve estimation of total photosynthetic capacity over time (particularly for plants with more complex canopies, like common bean or tobacco), since these factors influence absorption and availability of the light energy used to drive photosynthesis.
+In addition, using more detailed information, such as leaf angles, height, and position as well as canopy density and size, it is possible to improve the estimation of total photosynthetic capacity over time (particularly for plants with more complex canopies, e.g., common bean or tobacco), since these factors influence absorption and availability of the light energy used to drive photosynthesis.
 

### 2015-07-28 datapapr_labeling.tex
comments from jeff
1st revision edits

@@
 Inaccurate labels can be deleted by clicking the right button of the mouse near the labeled point and relabeled by clicking the left button again immediately after deletion.
-All tips can be deleted by clicking "Clear Tip" and relabel again.
+All tips can be deleted by clicking ``Clear Tip" and relabel again.
 The ``Show Tip" option is to select whether to show the tips or not. 
@@
 \caption{Label propagation between all four modalities ($a$) IR, ($b$) fluorescence, ($c$) RGB color, and ($d$) depth, of a sample plant in the Arabidopsis collection for day $3$ (top row), day $5$ (middle row), and day $9$ (bottom row).
-In the dataset the manual segmentation is performed on the fluorescence images and is outlined here as orange lines propagated to all modalities.  
-The IR images are taken by the same camera and so will have almost exact pixel correspondence.  
-To assess the segmented pixel propagation to other modalities, we also manually labeled a subset of the color plant images and propagated this segmentation to all modalities (shown in cyan).  
+In the dataset the manual segmentation is performed on the fluorescence images and is outlined here as orange lines propagated to all modalities (i.e., the orange lines in (b) are manual labels while these in other three modalities are propagated labels).
+The IR images are taken by the same camera and so will have exact pixel correspondence.  
+To assess the segmented pixel propagation to other modalities, we also manually labeled a subset of the color plant images (shown as cyan in (c)) and propagated this label to other three modalities (i.e., the cyan in (a,b,d) are propagated labels).
 Comparing these boundaries in each modality gives a measure of the propagation errors due to parallax, and we provide quantitative analysis in Table~\ref{tab:labelError}.  
@@
 
-The leaf labeling can be propagated to each of the other modalities from the fluorescence images for the Arabidopsis sequences.  
-To do this, we approximate a plant image with a plane, and find homographies that transform the fluorescence images into the other images.  
+The leaf labeling can be propagated from the fluorescence images to each of the other modalities for the Arabidopsis sequences.  
+To do this, we approximate a plant image with a plane, and estimate homographies that transform the fluorescence images into the images in other modalities.  
 This provides a direct mapping of the pixel labels between each modality.
@@
 
-We manually label $3$ images for each of $3$ Arabidopsis plants ($9$ images in total) on fluorescence and RGB modalities. 
+To quantify the precision of the label propagation, we manually label $3$ images for each of $3$ Arabidopsis plants ($9$ images in total) on fluorescence and RGB modalities. 
 The labels in each modality is propagated on other modalities. 
@@
 This mapping will introduce errors due to depth-based parallax.  
-We use {\it{SBD}} score, which will be introduced in Section~\ref{sec:protocol}, to evaluate the similarity between the manual labels and the propagation results. 
-In order to compare the label propagation error with human label error, we ask two different annotators to label the same $9$ images and compute the {\it{SBD}} score. 
+We use {\it{SBD}} score, which will be introduced in Section~\ref{sec:protocol}, to evaluate the similarity between the manual labels and the propagated labels. 
+In order to compute the inter-annotators variability, we ask two different annotators to label the same $9$ images and compute the {\it{SBD}} score. 
 The results are shown in Table~\ref{tab:labelError}.
@@
 First, the similarity for both manual annotation and label propagation increases as the plant grows.
-This is reasonable because {\it{SBD}} depends on the overlap ratio between two leaves, which is in natural to favor big leaves. 
+This is expected because {\it{SBD}} depends on the overlap ratio between two leaves, which inherently favors larger leaves. 
 Second, the performance of label propagation is only slightly worse than the performance of human annotations. 
-Therefore, we use label propagation to provide the labels for all four modalities for Arabidopsis sequences. 
-There are two benefits. 
-First, we will save a lot of human labor. 
-Second, the label is consistent for all four modalities.
+Therefore, we use label propagation to provide the labels for all four modalities for Arabidopsis sequences, which not only saves laborious human labor, but also provides consistent labels for all four modalities.
 
 In the case of the bean sequences, the pixel association between modalities is more difficult as the within-plant depth variations are large.  
-We found a homograph-based mapping performed poorly, and so the manual annotations we supply apply to just the infrared and fluorescence images which use the same camera.
+We found that a homograph-based mapping performed poorly, and so the manual annotations we supply apply to just the infrared and fluorescence images that use the same camera.
 

### 2015-07-28 datapaper_calibration.tex
explant conlusion
albedo definition

@@
 The variance of $\varepsilon_I$ is estimated for each pixel of a fixed scene observed over multiple images.
-In our experiments we observed a flat, uniform albedo surface (\todo{Danial: Please define ``albedo" here as from Comment $38$}) perpendicular to the camera at a sequence of depths, and for each depth acquired $300$ images.
+In our experiments we observed a flat, uniform albedo (the ratio of reflected light to incident light) surface perpendicular to the camera at a sequence of depths, and for each depth acquired $300$ images.
 Object depth, $d$, has a large impact on $\varepsilon_I$.
@@
 % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
-Plants & fluorescence & IR & RGB & depth \\
+Plants & Fluorescence & IR & RGB & Depth \\
 \hline

### 2015-07-28 response/response.tex
1st revision edits
albedo definition
response update

@@
 \begin{response}
-We have inserted a brief explanation with references in the last paragraph of Sec. $2$.
+We have inserted one paragraph with references to describe the motivation on the choice of image modalities. 
+Please refer to the last paragraph of Sec. $2$.
 \end{response}
@@
 \begin{response}
-We have augmented Figure $1$ by adding one zoom-in view for one Arabidopsis plant.
-Since bean dataset only contains one plant with good view, we do not provide a zoom-in view.
+We have augmented Figure $1$ by adding one row of zoom in view for one Arabidopsis plant.
+Since bean dataset only contains one plant with good view, we do not provide a zoom in view.
 \end{response}
@@
 \begin{response}
-We have adjusted the language by the statement of ``we summarize existing publicly available databases that are most related to our work".
+We have adjusted the language by using the statement of ``we summarize existing publicly available databases that are most related to our work".
 \end{response}
@@
 \begin{response}
-It is correct that the dataset (Haug and Ostermann, $2014$) is not about single leaves imaged in a constrained environment.
-We still category it in the first type because it does not include leaf segmentation.
+It is correct that the dataset by (Haug and Ostermann, $2014$) is not about single leaves imaged in a constrained environment.
+However, we still category it to the first type because it does not consider leaf segmentation.
 All segmentation tasks are based on plant level.
-We have reformulated this in the second paragraph in Sec. $2$.
+We have reformulated the text in the second paragraph of Sec. $2$.
 \end{response}
@@
 Also they may overlap or be overlapped by other leaves.
-We emphasize more on leaf identification and tracking rather than developing methods/algorithms to define group differences.
+We emphasize more on leaf identification and tracking rather than developing methods/algorithms to define group differences, which is not urgent at this point. 
 We have added one paragraph in Conclusion to better reflect this.
@@
 So we only provide the labels for bean plant in fluorescence and IR as they use the same camera.
+Since the labeling tool will be provided together with the database, we expect the interested users to manually label the RGB and depth modalities for the bean plants.
 Please refer to Sec. $4.3$ for more details.

### 2015-07-28 response/response.tex
response proofread one

@@
 \begin{review}
-At the end of the first paragraph of Sec. $4.4$, p. $8$, the authors envision a use of the multiple modalities in their dataset in which algorithms are developed to handle missing modalities.
+At the end of the second paragraph of Sec. $4.5$, the authors envision a use of the multiple modalities in their dataset in which algorithms are developed to handle missing modalities.
 Briefly presenting a use case scenario or citing relevant works may help clarify the importance of this point.
@@
 \begin{review}
-The acronym "MSU-PID" should be clearly defined when it first appears in text (p. $2$, line $51$)
+The acronym "MSU-PID" should be clearly defined when it first appears in text.
 \end{review}
@@
 This representation is the same as the released leaf tip labels as illustrated in Sec. $4.4$.
-The equation does not rely on the correspondence of inner or outer tips as long as the estimated tips correspond to the labeled tips.
+%The equation does not rely on the correspondence of inner or outer tips as long as the estimated tips correspond to the labeled tips.
 \end{response}
@@
 Therefore, we propagate the fluorescence labels to other modalities for Arabidopsis plants.
-As for bean plant, the homograph-based mapping performed poorly due to the large within-plant depth variations.
+As for bean plant, the homography-based mapping performed poorly due to the large within-plant depth variations.
 So we only provide the labels for bean plant in fluorescence and IR as they use the same camera.
@@
 \begin{response}
-We added one paragraph in the end of Sec. $4.1$ to address the trade-off between image resolution and experiment throughput.
+We have added one paragraph in the end of Sec. $4.1$ to address the trade-off between image resolution and experiment throughput.
 \end{response}
@@
 Leaf label is implemented by clicking several points along the boundary of the leaf.
-Tip label is implemented by clicking the outer and inner tip points respectively.
-We did explore other options for labeling and found this simple naive way worked the best.
+Tip label is implemented by clicking the outer and inner tips respectively.
+We did explore other options for labeling and found that this simple naive way worked the best.
 \end{response}
@@
 \begin{review}
-The authors test an algorithm (developed by them) on the fluorescence part of the data.
+The authors test an algorithm on the fluorescence part of the data.
 Granted this algorithm is presented elsewhere on the same data.
@@
 \begin{response}
-\todo{Daniel}
+Albedo is the ratio of reflected light to incident light.
+We have added this definition to the paper.
 \end{response}

### 2015-07-29 response/response.tex
small corrections to response.tex

@@
 {%\color{blue}
-We thank the Guest Editors for the efforts of handling our submission and two reviewers for providing the constructive and valuable feedback.
-The detailed comments help us further improve the quality of our manuscript.
+We thank the Guest Editors for the efforts of handling our submission and two reviewers for providing constructive and valuable feedback.
+The detailed comments helped us improve the quality of our manuscript.
 %The changes made to the manuscript are highlighted in blue text.
@@
 \begin{response}
-We have proofread it very carefully and corrected some typos and grammar errors.
+We have carefully proofread it and corrected typos and grammatical errors.
 \end{response}

### 2015-07-29 datapaper_baseline.tex
baseline performance improved
groundtruth to ground truth

@@
 For plant segmentation, we use simple thresholding process and edge detection to generate an image mask and edge map.
-The best threshold is learnt from the training set, which is done by tuning the threshold in a certain range and find the best one by evaluating the overlap of the segmented masks with the groundtruth label masks.
+The best threshold is learnt from the training set, which is done by tuning the threshold in a certain range and find the best one by evaluating the overlap of the segmented masks with the ground truth label masks.
 The edge map and mask are used in the alignment and tracking optimization.
@@
 We generate a label image for each frame based on the leaf segmentation results and compute the {\it{SBD}} score for each labeled image.
-The average {\it{SBD}} is $0.61$ for fluorescence images and $0.56$ for RGB images.
+The average {\it{SBD}} is $0.61$ for fluorescence images and $0.57$ for RGB images.
 

### 2015-07-29 datapaper_intro.tex
groundtruth to ground truth

@@
 The type and amount of manual labels on a database is a critical enabler to the potential applications of the database.
-For a subset of the MSU-PID database, we manually label the groundtruth regarding the leaf identification number, locations of leaf tips, and leaf segments.
+For a subset of the MSU-PID database, we manually label the ground truth regarding the leaf identification number, locations of leaf tips, and leaf segments.
 As a result, MSU-PID is suitable for a number of applications, including $1)$ {\it leaf segmentation} that aims at estimating the correct segmentation mask of each leaf in an image, $2)$ {\it leaf counting} that estimates the correct number of leaves within a plant, $3)$ {\it leaf alignment} that aligns the two tips of each leaf -- the cornerstone of the leaf structure, and $4)$ {\it leaf tracking} that is designed to track each leaf over time.

### 2015-07-29 datapapr_labeling.tex
groundtruth to ground truth

@@
 \label{sec:annotation}
-Part of the database is manually annotated to provide groundtruth tip locations, leaf segmentation results, and leaf consistency overtime.
+Part of the database is manually annotated to provide ground truth tip locations, leaf segmentation results, and leaf consistency overtime.
 We use the fluorescence images as the input for labeling because of their clean and uniform background.
@@
 
-In order to evaluate the leaf segmentation accuracy, we adopt an additional metric~\cite{scharr2014annotated} based on the Dice score of estimated segmentation results and groundtruth labels:
+In order to evaluate the leaf segmentation accuracy, we adopt an additional metric~\cite{scharr2014annotated} based on the Dice score of estimated segmentation results and ground truth labels:
 \begin{itemize}

### 2015-07-29 datapaper_hardware.tex
Did some corrections in hardware section.

@@
 The sensor contains both a $1,280 \times 720$ color camera directed parallel to, and separated by roughly $25~mm$ from, a depth camera which has a resolution of $320\times240$ pixels.
-The depth sensor uses a flash near IR illuminator and measures the time-of-flight~\cite{Hansard2013} of the beam at each pixel to obtain depth estimates along with an IR reflectance at each pixel.
+The color images are JPEG-compressed coming out of the sensor and so have block artefacts.
+The depth sensor uses a flash near IR illuminator and measures the time-of-flight of the beam at each pixel to obtain depth estimates at each pixel~\cite{Hansard2013}.
 
-There is a number of limitations to the depth sensor that becomes the sources of depth errors.
-The primary measurement limitation on the range-to-target is the strength of the reflected beam.
-As a result, dark, matt surfaces are measured reliably only at a close range on the order of $20$ or $30~cm$.
-Highly reflective surfaces also pose problems with direct reflections leading to saturation and highly unreliable depths.
-In addition reflective surfaces at grazing angles are less reliably measured since little signal is reflected.
-Fortunately the primary goal of the depth measurements are to obtain leaf depths, and plants provide good, roughly Lambertian, reflections of IR~\cite{Chelle2006219}.
-Thus the depth pixels that are most reliable and are of most use are those that fall on plant foliage.
+The depth sensor is limited largely by the strength of the signal returned.
+Low-reflectivity surfaces, such as the foam under the plant leaves, are accurate only at a close range (on the order of $20$ or $30~cm$).
+On the other hand, specular and highly reflective objects, such metal and plastic surfaces in the growth chamber, can saturate the sensor pixels leading to unreliable depths for those pixels.
+Fortunately the primary goal of the depth sensor is to obtain leaf pixel depths, and plants provide good, roughly Lambertian, reflections of IR~\cite{Chelle2006219}.
+As a result the most useful and reliable depth pixels that those that fall on plant foliage, and we usually ignore non-foliage pixel depths.
 

### 2015-07-29 datapaper_hardware.tex
small typo fix in hardware section

@@
 The depth sensor is limited largely by the strength of the signal returned.
-Low-reflectivity surfaces, such as the foam under the plant leaves, are accurate only at a close range (on the order of $20$ or $30~cm$).
+Low-reflectivity surfaces, such as the foam under the plant leaves, are accurate only at close range (on the order of $20$ or $30~cm$).
 On the other hand, specular and highly reflective objects, such metal and plastic surfaces in the growth chamber, can saturate the sensor pixels leading to unreliable depths for those pixels.
-Fortunately the primary goal of the depth sensor is to obtain leaf pixel depths, and plants provide good, roughly Lambertian, reflections of IR~\cite{Chelle2006219}.
-As a result the most useful and reliable depth pixels that those that fall on plant foliage, and we usually ignore non-foliage pixel depths.
+Fortunately the primary goal of the depth sensor is to obtain depths of leaf pixels, and plants provide good, roughly Lambertian, reflections of IR~\cite{Chelle2006219}.
+As a result the most useful and reliable depth pixels are those that fall on plant foliage, and we usually ignore non-foliage pixel depths.
 

### 2015-07-30 datapaper_hardware.tex
add comments from Jeff

@@
 \subsubsection{Fluorescence and IR Images}
-Chlorophyll {\it a} fluorescence images were captured once every hour during the daylight period in a growth chamber~\cite{cruz2015depi}.
+Chlorophyll {\it a} fluorescence images were captured once every hour during the daylight period in a growth chamber~\cite{kramer2015plant}.
 A set of $5$ images were captured using a Hitachi KP-F$145$GV CCD camera (Hitachi Kokusai Electric America Inc., Woodbury, NY) outfitted with an infrared long pass filter (Schott Glass RG-$9$, Thorlabs, Newton, NJ), during a short period ($<400~ms$) of intense light saturating to photosynthesis ($>10,000~\mu mol~photons~m^{-2} s^{-1}$) provided by an array of white Cree LEDs (XMLAWT, $5700$K color temperature, Digi-Key, Thief River Falls, MN) collimated using a $20~mm$ Carclo Lens ($10003$, LED Supply, Lakewood, CO).
-Chlorophyll {\it a} fluorescence was excited using monochromatic red LEDs (Everlight $625~nm$, ELSH-F51R1-0LPNM-AR5R6, Digi-Key), collimated (which means to make the light rays parallel) using a Ledil reflector optic ($C11347\_REGINA$, Mouser Electronics, Mansfield, TX) and pulsed for $50~\mu s$ during a brief window when the white LEDs were electronically shuttered.
+Chlorophyll {\it a} fluorescence was excited using monochromatic red LEDs (Everlight $625~nm$, ELSH-F51R1-0LPNM-AR5R6, Digi-Key), collimated (minimizing the dispersion of light) using a Ledil reflector optic ($C11347\_REGINA$, Mouser Electronics, Mansfield, TX) and pulsed for $50~\mu s$ during a brief window when the white LEDs were electronically shuttered.
 In addition, a series of $5$ images were also collected in the absence of the excitation light for artifact subtraction.
@@
 Since $940~nm$ light does not influence plant development or drive photosynthesis, images were also collected during the night period~\cite{eskins1992light}.
-Precisely, phytochromes are the closest photoreceptors that absorb in the far red, near infrared region, but the action spectrum is diminished to zero or near zero ($>800~nm$) in the region where we do IR reflectance ($940~nm$)~\cite{butler1964actton}.
-Note that the other modalities were captured only at day time, so that they will not interfere plant growth.
+%Precisely, phytochromes are the closest photoreceptors that absorb in the far red, near infrared region, but the action spectrum is diminished to zero or near zero ($>800~nm$) in the region where we do IR reflectance ($940~nm$)~\cite{butler1964actton}.
+Note that the other modalities were captured only at day time, so that they will not interfere with the circadian cycle of the plant.
 

### 2015-07-30 datapaper_intro.tex
add comments from Jeff

@@
 
-Plants develop through a complex interaction between genotype and environment.
-This determines their structure, functions, and thus performance such as yield or efficient usage of resources.
-In order to understand the genetic basis of these economically important parameters, it is essential to quantitatively assess plant phenotypes and then identify the latent relationships to genotypes and environmental factors.
-%
-Plant visual phenotyping has been performed by farmers and breeders for more than $5,000$ years.
-In the past, traditional phenotyping is based on experience and intuition, and is laborious~\cite{johannsenerblichkeit}.
-Recent progresses in imaging sensor and computer vision technologies lead to the development of the ever-increasing new field of highly automated, non-destructive plant visual phenotyping~\cite{furbank2011phenomics,cruz2015depi}.
-%Modern plant phenotyping is a comprehensive, large-scale assessment of plant traits such as growth, development, tolerance, resistance, architecture, physiology, ecology, yield, and metadata that form the basis for more complex parameters.
-%
-The objective of modern plant visual phenotyping is to analyze and categorize the morphological characteristics of plants, and thus accurately quantifying plant traits.
+% Jeff corrected
+The complex interaction between genotype and environment determines how plants will develop physiologically (from the biochemical level to structural morphology), which ultimately influences field performance, for example resource acquisition, resource partitioning and seed yield.
+In order to understand the genetic basis for these economically important parameters, it is essential to quantitatively assess plant phenotypes and then identify the latent relationships between genotype and environmental factors.
+Plant visual phenotyping has been performed by farmers and breeders for more than $5,000$ years to develop plant lines with desirable traits.  
+This traditional method is based on experience and intuition and is both labor intense and time-consuming~\cite{johannsenerblichkeit}.  
+Recent progress in imaging sensor, robotics and automation technologies has recently led to the rapid development of highly-automated, non-destructive, high-throughput methods for visual phenotyping ~\cite{furbank2011phenomics,kramer2015plant}.
+The intent of modern plant visual phenotyping is to accelerate the collection, analysis and categorization visual (e.g.
+morphology, size) and spectral (e.g.
+chlorophyll fluorescence, chlorophyll content, water content, leaf temperature) data sets in order to identify and quantify specific plant traits, especially those related to plant performance.
+This interdisciplinary field requires scientists and engineers to not only develop or employ various image sensors platforms to collect under relevant conditions, but also design advance algorithms for the automated processing and analysis of image data.
+
+%Plants develop through a complex interaction between genotype and environment.
+%This determines their structure, functions, and thus performance such as yield or efficient usage of resources.
+%In order to understand the genetic basis of these economically important parameters, it is essential to quantitatively assess plant phenotypes and then identify the latent relationships to genotypes and environmental factors.
+%Plant visual phenotyping has been performed by farmers and breeders for more than $5,000$ years.
+%In the past, traditional phenotyping is based on experience and intuition, and is laborious~\cite{johannsenerblichkeit}.
+%Recent progresses in imaging sensor and computer vision technologies lead to the development of the ever-increasing new field of highly automated, non-destructive plant visual phenotyping~\cite{furbank2011phenomics,cruz2015depi}.
+%The objective of modern plant visual phenotyping is to analyze and categorize the morphological characteristics of plants, and thus accurately quantifying plant traits.
 %It advances crop yield improvement and enables the systematic study of the environmental plasticity of plants.
 %
-In this interdisciplinary field, scientists employ various imaging sensors to capture plants and design advanced algorithms to automatically analyze the captured plant imagery, with the purpose of raising testable biological hypotheses to solve problems related to growth, development, stress tolerance, resistance, and so on.
-%
-%In old days, plant phenotyping was conducted through manual visual observation~\cite{Erblichkeit1903}.
-Today, motivated by the increasing lower cost and increasing diversity of imaging sensors technologies, image-based automatic plant visual phenotyping is quickly growing into a desirable and viable solution~\cite{furbank2011phenomics,cruz2015depi}.
-%
-A key advance in visual phenotyping is the capability to non-invasively capture plant traits, enabling continuous measurements that are necessary to monitor plants during growth and/or under stress conditions.
-It also increases the throughput of phenotyping experiments by eliminating destructive operations, which allows more genotypes or biological replicates to be examined under the same environmental conditions~\cite{fahlgren2015lights,walter2015plant}.
+%In this interdisciplinary field, scientists employ various imaging sensors to capture plants and design advanced algorithms to automatically analyze the captured plant imagery, with the purpose of raising testable biological hypotheses to solve problems related to growth, development, stress tolerance, resistance, and so on.
+%A key advance in visual phenotyping is the capability to non-invasively capture plant traits, enabling continuous measurements that are necessary to monitor plants during growth and/or under stress conditions.
+%It also increases the throughput of phenotyping experiments by eliminating destructive operations, which allows more genotypes or biological replicates to be examined under the same environmental conditions~\cite{fahlgren2015lights,walter2015plant}.
 
-One goal of plant visual phenotyping is to accurately quantify plant traits, particularly those related to photosynthetic performance, growth, yield, and resilience to environmental stress.
-For the approaches to be of practical, plants must be monitored continuously, over developmental time scales and under conditions that approximate the native environment (dynamic 'field' conditions)~\cite{fahlgren2015lights,walter2015plant}.
-%
+One goal of plant visual phenotyping is to accurately determine genetic components related to photosynthetic performance, growth, yield, and resilience to environmental stress.
+For this approach to be of effective, plants must be monitored continuously, over developmental time scales and under conditions that approximate the native environment (dynamic 'field' conditions)~\cite{fahlgren2015lights,walter2015plant}.
 The capacity to identify and track individual leaves over time is important to clearly define phenotypic behaviors related to leaf-specific factors such as developmental age~\cite{schottler2015photosynthetic} and/or following the application of stress.
@@
 In this case, mapping distributions to individual leaves can distinguish between a systemic (whole plant) effect and localization of the effect to subset leaves.
-%
 In addition, using more detailed information, such as leaf angles, height, and position as well as canopy density and size, it is possible to improve the estimation of total photosynthetic capacity over time (particularly for plants with more complex canopies, e.g., common bean or tobacco), since these factors influence absorption and availability of the light energy used to drive photosynthesis.

### 2015-07-30 datapaper_prior.tex
add comments from Jeff

@@
 The four sensing modalities in MSU-PID provide unique opportunities to comprehensively characterize plant morphological and physiological phenotypes.
-The use of chlorophyll fluorescence at $730$ $nm$ to $750$ $nm$ as a tool for evaluating photosynthetic performance is well established~\cite{baker2008chlorophyll}, and against non-(chlorophyll)fluorescent background clearly defines photosynthetically active leaf area.
+The use of chlorophyll fluorescence at $730$ $nm$ to $750$ $nm$ as a tool for evaluating photosynthetic performance is well established~\cite{baker2008chlorophyll}, and against non-fluorescent background, it clearly defines the chlorophyll-containing (photosynthetically active) leaf area.
 The depth measurement has been a component of a number of recent non-plant RGB-D databases designed for object recognition~\cite{Lai2011}, scene segmentation~\cite{Silberman2011}, human analysis~\cite{Sung2011,Barbosa:reid12}, and mapping~\cite{sturm12iros}.
 By including depth map for a plant database, we anticipate enabling development of new $3$D plant canopy analysis algorithms and thus probing the total energy intake and storage.
-Near infrared (IR) reflectance has been used by others to detect water content in leaves~\cite{chen2014dissecting}.
-However, it may also be useful in determining leaf angle and curvature.
+Near infrared (IR) reflectance at $\sim940~nm$ has been used by others to detect water content in leaves~\cite{chen2014dissecting}.
+However, it may also be useful in determining leaf angle and curvature~\cite{woolley1971reflectance}.
 Furthermore, since imaging occurs at a wavelength that is effectively non-absorbing for photosynthesis or known light receptors~\cite{butler1964actton,eskins1992light} in plants, it can be used for imaging during the night cycle to observe night time leaf expansion or in some cases circadian movements~\cite{mcclung2006plant}.

### 2015-07-30 datapapr_labeling.tex
add comments from Jeff

@@
 
-It is often argued which is the best setting due to the trade-off between the image resolution and the throughput of phenotyping experiments.
-We chose to image a whole tray of Arabidopsis at lower resolution rather than an individual at higher resolution, because it better reflects high-throughput protocols, which in practice allows direct comparison of multiple genotypes in the same experiment.
-In contrary, we chose to image a single bean plant because we anticipate enabling development of $3$D plant canopy reconstruction algorithms for bush plants.
+%It is often argued which is the best setting due to the trade-off between the image resolution and the throughput of phenotyping experiments.
+The trade-off between image resolution and sample throughput is a common conundrum with designing visual phenotyping experiments. 
+We chose to image a whole tray of Arabidopsis at lower resolution rather than an individual at higher resolution, because it better reflects high-throughput protocols, which in practice allow direct comparison of multiple genotypes in the same experiment.
+In contrast, we chose to image a single bean plant because we anticipate enabling development of $3$D plant canopy reconstruction algorithms for bushy plants.
 
@@
 
-For Arabidopsis images, we label $4$ frames each day.
-While for bean images, we label $7$ frames each day because of their spontaneous and fast leaf movement.
-A Matlab GUI interface is developed for leaf labeling, as shown in Figure~\ref{fig:label}, which will also be available to the public.
+For Arabidopsis images, we labeled $4$ frames per day.
+While for bean images, we labeled $7$ frames per day due to the plant's fast and spontaneous leaf movements. 
+A Matlab GUI interface was developed for leaf labeling, as shown in Figure~\ref{fig:label}, which will be available to the public.
 A user can open a plant image (``Open") to label the two tips and annotate each leaf segment.
@@
 The labeling of the leaf segment (``Leaf Label") is implemented by clicking the boundary of one leaf at each time.
-In order to provide more accuracy labeling, we click very dense points ($\sim20$ points on average for each leaf) on the boundary.
+In order to provide more accurate labeling, a fairly high point density ($\sim20$ points on average) is typically used to define the boundary for each leaf. .
 The labeled leaf boundary is overlaid on the image for better visualization to guide the next action.
-Incorrect label can be deleted right after the labeling by clicking ``Clear".
-All leaf labels can be deleted by clicking ``Clear All".
+An incorrect label can be deleted right after the labeling by clicking ``Clear", or all leaf labels can be deleted by clicking ``Clear All".
 This process continues until all leaf segments have been annotated.
@@
 Second, the performance of label propagation is only slightly worse than the performance of human annotations.
-Therefore, we use label propagation to provide the labels for all four modalities for Arabidopsis sequences, which not only saves laborious human labor, but also provides consistent labels for all four modalities.
+Therefore, we use label propagation to provide the labels for all four modalities for Arabidopsis sequences.
+There are two benefits: $1)$ it decreases the need for manual label; $2)$ labeling is consistent for all four modalities. 
+%, which not only saves laborious human labor, but also provides consistent labels for all four modalities.
 

### 2015-09-08 datapaper_intro.tex
revision_Xi

@@
 ~\cite{haug2014crop} & & & & & & \\ \hline
-LSC & \multirow{2}{*}{RGB} & \multirow{2}{*}{LS, LO} & Arabidopsis & $43$ & $6,287$ & $201$ \\ \cline{4-7}
-~\cite{haug2014crop} & & & Tobacco & $80$ & $165,120$ & $83$ \\ \hline
-\multirow{2}{*}{MSU-PID} & fluorescence, & LS, LO, & Arabidopsis & $16$ & $2,160\times 4$ & $576\times 4$ \\ \cline{4-7}
+LSC & \multirow{2}{*}{RGB} & \multirow{2}{*}{LS, LO, LT\tnote{b}} & Arabidopsis & $43$ & $6,287$ & $201$ \\ \cline{4-7}
+~\cite{scharr2014annotated} & & & Tobacco & $80$ & $165,120$ & $83$ \\ \hline
+\multirow{2}{*}{MSU-PID} & fluorescence, & LS, LO & Arabidopsis & $16$ & $2,160\times 4$ & $576\times 4$ \\ \cline{4-7}
 & IR, RGB, depth & LA, LT & Bean & $5$ & $325\times 4$ & $175\times 2$ \\ \hline
@@
 \item[a] The abbreviation in ``Applications'' column is defined as Leaf Classification (LC), Leaf Segmentation (LS), Leaf Counting (LO), Leaf Alignment (LA), and Leaf Tracking (LT).
+\item[b] The data collected in ~\cite{scharr2014annotated} does have temporal images which will allow leaf tracking. However, the dataset that they release does not include any temporal information.
 \end{tablenotes}
@@
 In fact, computer vision research lives on and advances with databases, as evidenced by the successful databases in the field (e.g., FERET~\cite{Phillips2000} and LFW~\cite{LFW}).
-However, the publicly available databases for plant phenotyping are still very limited, with the only exception of LSC database~\cite{scharr2014annotated}, which, nevertheless, has its own limitations on the type of images (RGB only) and is only suitable for a small set of plant image analysis applications.
+However, the publicly available databases for plant phenotyping are still very limited, with the only exception of LSC database~\cite{scharr2014annotated}, which, nevertheless, has its own limitations on the type of images (RGB only) and not having released data related to tracking (although the authors claim in~\cite{scharr2014annotated} that such data is available.)
+% is only suitable for a small set of plant image analysis applications.
 

### 2015-09-09 list of changes/changes.tex
revision_2

\documentclass[11pt,letterpaper]{article}

\usepackage[top=1in,bottom=1in,left=1in,right=1in]{geometry}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{cite}
\usepackage{bm}
\usepackage[usenames]{color}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{textcomp}
\usepackage{times}
\usepackage{url}
\usepackage{xr}

%\externaldocument{../debris}

\newcommand{\eg}{e.g.}
\newcommand{\ie}{i.e.}
\newcommand{\etal}{et~al.~}
\newcommand{\vs}{vs.~}
\newcommand{\cf}{cf.~}
\newcommand{\red}{\color{red}}
\newcommand{\blue}{\color{blue}}
\newcommand{\green}{\color{green}}
\newcommand{\resp}{\textcolor{Blue}}
\renewcommand{\thefigure}{R-\arabic{figure}}

\newcommand\todo[1]{\textcolor{red}{#1}}

\newcounter{reviewcounter}
\setcounter{reviewcounter}{1}

\newenvironment{review}
{\noindent {\bf Comment~\arabic{reviewcounter}}:\addtocounter{reviewcounter}{1}\itshape}
{\vspace{0.8em}}

\newenvironment{response}
{\noindent {\bf Response}: \color{black}}
{\color{black} \vspace{1.6em}}

\title{Response letter on MVAP-D-15-00159R1, \\"Multi-modality Imagery Database for Plant Phenotyping"}

\begin{document}
\date{}
\maketitle

{We thank the Guest Editors and two reviewers for providing feedback and the decision.
Here we prepare the response to the comments and indicate the changes we have made in this revision. 
}
\\

\begin{tabular*}{\textwidth}{c}
\hline
\end{tabular*}

% Comment 1
\begin{review}
In Table $1$, I believe LSC has wrong reference.  
It should be [Scharr et al., $2014$] and not [Haug and Osterman, $2014$].
\end{review}

\begin{response}
We have corrected the wrong reference. 
\end{response}

% Comment 2
\begin{review}
 Also in Table $1$, according to [Scharr et al., $2014$], the data they collected appear to handle at least also Leaf Tracking (maybe also leaf alignment). 
 So the table should be corrected. 
 While, from my understanding, the LSC dataset did not make those available (ie., where not released), from their paper it is clear that this was done. 
 I believe it is best you are explicit on that rather than rely on reader's interpretation.
\end{review}

\begin{response}
We have added ``leaf tracking'' to LSC dataset in Table $1$ with a footnote indicating that the temporal data is not available. 
However, the dataset does not include labels which enables leaf alignment task. 
\end{response}

% Comment 3
\begin{review}
Having said the above, you could potentially edit the part on page $3$, first col, lines $20$ to $24$ to read something along the lines ``with the only exception of LSC database [Scharr et al., $2014$], which has the limitation of including a single modality (RGB only) and not having released with the LSC $2014$, data related to tracking and alignment (although in [Scharr et al., $2014$], the authors claim that such data is available)''
\end{review}

\begin{response}
We have changed the corresponding text to: ``with the only exception of LSC database [Scharr et al., $2014$], which, nevertheless, has its own limitations on the type of images (RGB only) and not having released data related to tracking (although the authors claim in [Scharr et al., $2014$] that such data is available).''
\end{response}

% Comment 4
\begin{review}
Possibly also the text on page $4$, first col, line $25$ to $34$, should be corrected to reflect the comment that [Scharr et al., $2014$] does in fact has data for other vision tasks but they were not included in the LSC. 
This should be clear to the reader, to reflect what is stated in the report.
\end{review}

\begin{response}
We have change the corresponding text to ``The provided manual labels allow the evaluation of leaf segmentation and leaf counting. 
Although it is claimed that they have collected data for leaf tracking, it has not been included in the current LSC dataset''
\end{response}

% Comment 5
\begin{review}
Thank you for your clarification on the Figure $3$a, but i still believe that there is an error on the units of the z axis. 
It shows that cameras are at $60~mm$, but it should $620~mm$ according to your response and caption.
\end{review}

\begin{response}
We have changed the caption slightly to clarify the confusion. 
``The distance to the target bean plant is roughly $620~mm$ in this example. 
For clarity the image planes are plotted not at actual target depth, where they would overlap, but at depths proportional to their focal lengths.''
\end{response}

% Comment 6
\begin{review}
Based on how you made the annotations, I still do not think you can create a single pixel boundary between leaves (at best it will be two pixel thick).
\end{review}

\begin{response}
We annotate each leaf separately. 
For those overlapping leaves, it is possible that we can still get a single pixel boundary if we happen to annotate the same points on the boundary. 
However, it is also likely that they will not share the boundary during annotation. 
So it will be two boundaries for each leaf and they can be connected or not. 
This is an approximation of the boundary and we think the error made by not a single pixel boundary between leaves can be ignored. 
\end{response}

% Comment 7
\begin{review}
Maybe my comment on interaction was not clear. 
Completely interactive in my book means totally with human interaction (not - automated). 
I was asking if you believe that some interactive segmentation algorithms can help.
\end{review}

\begin{response}
Thanks for the clarification. 
We believe that there are some interactive segmentation algorithms, level set for example, can help on the segmentation. 
However, we did not explore the possible segmentation algorithms. 
Instead, we used totally human interaction because it was very accurate and end up without too much labor. 
\end{response}

\end{document}

### 2015-10-19 datapaper.tex
update

@@
 
-Among many applications of machine vision, plant image analysis has recently began to gain attention due to its potential impact on plant visual phenotyping, particularly in understanding plant growth, assessing the quality/performance of crop plants, and improving crop yield.
+Among many applications of machine vision, plant image analysis has recently began to gain more attention due to its potential impact on plant visual phenotyping, particularly in understanding plant growth, assessing the quality/performance of crop plants, and improving crop yield.
 Despite its importance, the lack of publicly available research databases containing plant imagery has substantially hindered the advancement of plant image analysis.

### 2015-10-19 datapaper_baseline.tex
update

@@
 For each scale template, we rotate every $15^{\circ}$ to generate $24$ templates at different orientations.
-Tip locations will be scaled and rotated accordingly.
+Tip locations are scaled and rotated accordingly.
 Finally, we generate $2,880$ leaf templates for each modality.
@@
 A new leaf is generated when there is a relatively large portion of the mask that has not been covered by current leaf candidates.
-For each frame of the video, we can generate a label image with each leaf being labeled with one color and the tip locations for each estimated leaf.
+For each frame of the video, we can generate the tip locations for each estimated leaf and a label image with each leaf being labeled with one color.
 The labeled color for each leaf in the video remains the same during the tracking process.
@@
 This is due to two reasons.
-First, the resolution of RGB images is much lower than that of fluorescence images, which will results in the miss detection of small leaves, and more severe leaf occlusions. 
+First, the resolution of RGB images is much lower than that of fluorescence images, which will results in more miss detections of small leaves, and more severe leaf occlusions.
 Second, the label propagation causes some error, which is inevitable with the label homography-based mapping.

### 2015-10-19 datapapr_labeling.tex
update

@@
 \includegraphics[width=.90\textwidth]{Figures/labeling}\\
-\caption{Leaf labeling process, including tip labels and leaf segmentation annotation.}
+\caption{Leaf annotation process, including leaf tip and leaf segment labels.}
 \label{fig:label}
@@
 While for bean images, we labeled $7$ frames per day due to the plant's fast and spontaneous leaf movements.
-A Matlab GUI interface was developed for leaf labeling, as shown in Figure~\ref{fig:label}, which will be available to the public.
+A Matlab GUI interface was developed for leaf labeling, as shown in Figure~\ref{fig:label}, which will be released to the public.
 A user can open a plant image (``Open") to label the two tips and annotate each leaf segment.
@@
 For consistent annotation of the same leaf over time, we show a number on the center of each leaf indicating the order of labeling from the previous frame.
+The users should follow the order to label leaves.
 
@@
 
-\begin{table*}[t]
-\centering
-\caption{Human label performance vs. label propagation performance.
-$L_1$ and $L_2$ are the manual label results from two annotators, and $L_t$ is the propagated results.
-The {\it{SBD}} score is averaged over $3$ plants.}
-\begin{tabular}{c|c|c|c|c|c|c}
-\hline
-    & \multicolumn{3}{c|}{fluorescence modality} & \multicolumn{3}{c}{RGB modality}\\ \hline
-    & $L_1$ vs. $L_1$ & $L_1$ vs. $L_2$  & $L_1$ vs. $L_t$ & $L_1$ vs. $L_1$ & $L_1$ vs. $L_2$ & $L_1$ vs. $L_t$ \\ \hline
-   day$\_3\_$hour$\_23$ & $1$ & $0.808$ & $0.804$ & $1$ & $0.827$ & $0.802$ \\ \hline
-   day$\_5\_$hour$\_23$ & $1$ & $0.830$ & $0.836$ & $1$ & $0.871$ & $0.837$ \\ \hline
-   day$\_9\_$hour$\_20$ & $1$ & $0.903$ & $0.886$ & $1$ & $0.877$ & $0.789$ \\ \hline
-                   average &          $1$ & $0.847$ & $0.842$ & $1$ & $0.858$ & $0.809$ \\ \hline
-\end{tabular}
-\label{tab:labelError}
-\end{table*}
-
 The leaf labeling can be propagated from the fluorescence images to each of the other modalities for the Arabidopsis sequences.
@@
 First, the similarity for both manual annotation and label propagation increases as the plant grows.
-This is expected because {\it{SBD}} depends on the overlap ratio between two leaves, which inherently favors larger leaves.
+This is expected because {\it{SBD}} depends on the overlap ratio between two leaves, which inherently favors large leaves.
 Second, the performance of label propagation is only slightly worse than the performance of human annotations.
@@
 %, which not only saves laborious human labor, but also provides consistent labels for all four modalities.
+
+\begin{table}[h]
+\centering
+\caption{Human label performance vs. label propagation performance.
+$L_1$ and $L_2$ are the manual label results from two annotators, and $L_t$ is the propagated results.
+The {\it{SBD}} score is averaged over $3$ plants.}
+\begin{tabular}{c|c|c|c|c}
+\hline
+    & \multicolumn{2}{c|}{fluorescence} & \multicolumn{2}{c}{RGB}\\ \hline
+    & $L_1$ vs. $L_2$  & $L_1$ vs. $L_t$ & $L_1$ vs. $L_2$ & $L_1$ vs. $L_t$ \\ \hline
+   day$\_3$ & $0.808$ & $0.804$ & $0.827$ & $0.802$ \\ \hline
+   day$\_5$ & $0.830$ & $0.836$ & $0.871$ & $0.837$ \\ \hline
+   day$\_9$ & $0.903$ & $0.886$ & $0.877$ & $0.789$ \\ \hline
+    average &   $0.847$ & $0.842$ & $0.858$ & $0.809$ \\ \hline
+\end{tabular}
+\label{tab:labelError}
+\end{table}
 

### 2015-10-19 list of changes/changes.tex
update

@@
 \begin{response}
-We have added ``leaf tracking'' to LSC dataset in Table $1$ with a footnote indicating that the temporal data is not available. 
+We have added ``leaf tracking'' to LSC dataset in Table $1$ with a footnote indicating that the temporal data for leaf tracking is not available to the public.
 However, the dataset does not include labels which enables leaf alignment task.
@@
 We have change the corresponding text to ``The provided manual labels allow the evaluation of leaf segmentation and leaf counting.
-Although it is claimed that they have collected data for leaf tracking, it has not been included in the current LSC dataset''
+Although it is claimed that they have collected data for leaf tracking, it has not been included in the current LSC dataset.''
 \end{response}

### 2015-10-20 datapaper_plants.tex
revision edits

@@
 %
-Two-week-old plants ({\it Arabidopsis} and bean) were transferred to imaging chambers and allowed to acclimate for $24$ hours to the LED lighting before the start of the data collection.
-Growth conditions as described above were maintained for each set of plants for the duration of image collection.
+Two-week-old plants ({\it Arabidopsis} and bean) were transferred to imaging chambers and allowed to acclimate for $24$ hours to the LED lighting before starting the data collection.
+Aforementioned growth conditions were maintained for each set of plants for the duration of image collection.

### 2015-10-20 datapaper_prior.tex
revision_Xi
revision edits

@@
 The provided manual labels allow the evaluation of leaf segmentation and leaf counting.
+Although it is claimed that they have collected data for leaf tracking, it has not been included in the current LSC dataset. 
 In comparison, our MSU-PID database utilizes four sensing modalities in the data capturing, each providing different aspects of plant visual appearance.
@@
 By including depth map for a plant database, we anticipate enabling development of new $3$D plant canopy analysis algorithms and thus probing the total energy intake and storage.
-Near infrared (IR) reflectance at $\sim940~nm$ has been used by others to detect water content in leaves~\cite{chen2014dissecting}.
+Near infrared (IR) reflectance at $\sim$~$940~nm$ has been used by others to detect water content in leaves~\cite{chen2014dissecting}.
 However, it may also be useful in determining leaf angle and curvature~\cite{woolley1971reflectance}.

### 2015-10-20 datapapr_labeling.tex
revision edits

@@
 
-\begin{table}[h]
+\begin{table}[t!]
 \centering
@@
 
-In the case of the bean sequences, the pixel association between modalities is more difficult as the within-plant depth variations are large.
+In the case of the bean imagery, the pixel association between modalities is more difficult as the within-plant depth variations are large.
 We found that a homograph-based mapping performed poorly, and so the manual annotations we supply apply to just the infrared and fluorescence images that use the same camera.
@@
 The availability of multiple modalities allows user to design novel experimental setup.
-For example, using RGB and depth modalities for training and RGB for testing can take advantage of additional information during the learning without incurring extra sensor cost during the testing, which can be implemented via either learning with side information~\cite{chen2013boosting}, or transfering learning with missing modality~\cite{ding2014latent}.
+For example, using RGB and depth modalities for training and RGB for testing can take advantage of additional information during the learning without incurring extra sensor cost during the testing, which can be implemented via either learning with side information~\cite{chen2013boosting}, or transfering learning with missing modality~\cite{ding2014latent,Chen2013b}.
 

### 2015-10-20 calibtable.tex
figure size

\begin{table}[t]
\centering
\caption{Image Labelling Errors on Different Modalities.$L1_{fmp}$ refers to the manual annotator 1, $L2_{fmp}$ refers to the manual annotator 2,$L_{e}$ refers to the labelling score error due to the difference in two manual annotations and $P_{e}$ refers to the propagating score errors that occur due to the difference in manual annotator 1 and the mapped annotation from transformation of one modality to another}
\begin{tabular}{c|c|c|c|c|c|c|c|c}
   \hline
    & \multicolumn{4}{|c|}{FMP Modality} & \multicolumn{4}{|c|}{Color Modality}\\
   \hline
    & $L1_{fmp}$ vs $L1_{fmp}$ & $L1_{fmp}$ vs $L2_{fmp}$ & $L_{e}$ & $P_{e}$ & $L1_{rgb}$ vs $L1_{rgb}$ & $L1_{rgb}$ vs $L2_{rgb}$ & $L_{e}$ & $P_{e}$ \\
   \hline
   Day_$3$_hour_$23$ & $1$ & $0.7502$ & $0.2498$ & $0.2019$ & $1$ & $0.8267$ & $0.1733$ & $0.2002$ \\
   \hline
   Day_$5$_hour_$23$ & $1$ & $0.7927$ & $0.2073$ & $0.1541$ & $1$ & $0.8705$ & $0.1295$ & $0.1526$ \\
   \hline
   Day_$9$_hour_$20$ & $1$ & $0.8366$ & $0.1634$ & $0.2134$ & $1$ & $0.8765$ & $0.1235$ & $0.2108$ \\
   \hline
 \end{tabular}
\label{tab:label_errors}
\end{table*}

Table~\ref{tab:label_errors} refers to the BestDice scores and the labelling errors that arise due to the difference in annotations. BestDice scores are calculated based on the percent of pixel overlap between two segmented regions of interest of two images/modalities and selecting the best score amongst all the fits. In our case, two BestDice scores are calculated by interchanging the two modalities and selecting the minimum of the two scores. We select
%\begin{equation}
%\label{Eqn_score_BestDice}
%  score=\min($score1$,$score2$);
%\end{equation}
% where $score1$ refers to the BestDice score of two images and the $score2$ refers to the BestDice score after interchanging the modality.

As can be seen from the table, the propagation errors (errors due to transformation of labelling from one modality to another) is close to the labelling errors (errors due to the difference of scores between two manual annotators), indicating the transformation from one modality to another is reasonable.

### 2015-10-20 datapaper_baseline.tex
figure size

@@
 Note that~\cite{yin2014a,yin2014b} is designed for rosette plants like Arabidopsis.
-Therefore, it will not be applied to bean imagery as it does not belong to rosette plant.
+Therefore, it will not be applied to bean imagery, as it does not belong to rosette plant.
 %In addition, we also apply it on the RGB modality and use the propagated labels for evaluation.
@@
 (c) &
-\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_1.pdf}&
-\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_2.pdf}&
-\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_3.pdf}&
-\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_4.pdf}&
-\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_5.pdf}&
-\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_6.pdf}&
-\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_7.pdf}&
-\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_8.pdf}&
-\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_9.pdf}\\
+\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_1.png}&
+\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_2.png}&
+\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_3.png}&
+\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_4.png}&
+\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_5.png}&
+\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_6.png}&
+\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_7.png}&
+\includegraphics[trim= 100 70 120 10, clip, width=.1\textwidth]{Figures/trackExample/3_8.png}&
+\includegraphics[trim= 100 70 120 10,  clip, width=.1\textwidth]{Figures/trackExample/3_9.png}\\
 
@@
 The two leaves are still being considered as one leaf (ID $8$) in day $4$ and day $3$ (Figure~\ref{fig:trackExample} (c)).
-Leaf $8$ in day $1$ and $2$ is a leaf ID switch w.r.t.~the purple ground truth leaf and will not be considered as a consistently tracked leaf (Figure~\ref{fig:trackExample} (c)).
+Leaf $8$ in day $1$ and $2$ is a leaf ID switch w.r.t. the purple ground truth leaf and will not be considered as a consistently tracked leaf (Figure~\ref{fig:trackExample} (c)).
 However, they are still evaluated as well aligned and segmented leaves.

### 2015-10-20 datapaper_conclusion.tex
figure size

@@
 
-It might be noticed that all plants in MSU-PID belong to the same genotype and no treatments applied.
-This is because we think a fundamental issue with visual phenotyping, i.e., accurate and automated identification and tracking of individual leaves over developmental time scales (weeks), whose importance has been highlighted in Section~\ref{sec:intro}, needs to be solved before expending our goal to define group differences.
-The inherent challenge in this issue is that as leaves emerge and grow, they change in size, position and shape and they may overlap or be overlapped by other leaves.
-We emphasize more in leaf segmentation, alignment and tracking rather than developing methods to discriminate group differences.
+% Jeff's comments
+It should be obvious that all plants in MSU-PID belong to the same genotype and that no treatments were applied to induce phenotypic differences.  
+This is because we have chosen to focus on a fundamental issue with visual phenotyping, i.e.
+accurate and automated identification and tracking of individual leaves over developmental time scales (days to weeks).
+The inherent challenge is that as leaves emerge and grow they change in size, position and shape and they may overlap or be overlapped by other leaves.  
+Yet, as emphasized in the introduction, these factors may be important determinants for defining phenotypic differences between/among groups.  
+In addition, development of these methods would invaluable for providing data to refine models of photosynthesis in plants with more complex canopies and in canopy systems.  
+%It might be noticed that all plants in MSU-PID belong to the same genotype and no treatments applied.
+%This is because we think a fundamental issue with visual phenotyping, i.e., accurate and automated identification and tracking of individual leaves over developmental time scales (weeks), whose importance has been highlighted in Section~\ref{sec:intro}, needs to be solved before expending our goal to define group differences.
+%The inherent challenge in this issue is that as leaves emerge and grow, they change in size, position and shape and they may overlap or be overlapped by other leaves.
+%We emphasize more in leaf segmentation, alignment and tracking rather than developing methods to discriminate group differences.
 

### 2015-10-20 datapaper_hardware.tex
revision_2
figure size

@@
 %Precisely, phytochromes are the closest photoreceptors that absorb in the far red, near infrared region, but the action spectrum is diminished to zero or near zero ($>800~nm$) in the region where we do IR reflectance ($940~nm$)~\cite{butler1964actton}.
-Note that the other modalities were captured only at day time, so that they will not interfere with the circadian cycle of the plant.
+Note that the other modalities were captured only at daytime, so that they will not interfere with the circadian cycle of the plant.
 
@@
 The sensor contains both a $1,280 \times 720$ color camera directed parallel to, and separated by roughly $25~mm$ from, a depth camera which has a resolution of $320\times240$ pixels.
-The color images are JPEG-compressed coming out of the sensor and so have block artefacts.
+The color images are JPEG-compressed coming out of the sensor and so have block artifacts.
 The depth sensor uses a flash near IR illuminator and measures the time-of-flight of the beam at each pixel to obtain depth estimates at each pixel~\cite{Hansard2013}.
@@
 The distance to the target bean plant is roughly $620~mm$ in this example.
-The image planes are plotted at depths proportional to the focal lengths.
+For clarity the image planes are plotted not at actual target depth, where they would overlap, but at depths proportional to their focal lengths.
 The optical center of the color camera (left-most) defines the world coordinate system.
@@
 This shows the projection into the color image (with $90^{\circ}$ rotation for economical use of space).
-Only points in a rectangular region around the plant in the depth image are selected, and these are further filtered by eliminating points with high standard deviation.
+Only points in a rectangular region around the plant in the depth image are selected, and it is further filtered by eliminating points with high standard deviation.
 An algorithm requiring only $3$D points on the plant could select only those that fall on the leaf pixels.}

### 2015-10-20 datapapr_labeling.tex
figure size

@@
 The images were acquired every hour.
-As there is no light at night hours, plants can not be imaged by the fluorescence and RGB color sensors while IR and depth cameras can still perform the capturing during the night.
+As there is no light at night hours, plants cannot be imaged by the fluorescence and RGB color sensors while IR and depth cameras can still perform the capturing during the night.
 In order to make sure that all four modalities are present at the same time, we release the part of images captured only in the day hours, which are $15$ images per day for Arabidopsis and $13$ for bean for all four modalities.
@@
 Note that one alternative approach for labeling leaf segments is to directly label the membership of superpixels instead of drawing a polygon along the boundary.
-Our experience is that since a noticeable percentage of extracted superpixels cover pixels of two neighboring leaves, the extra effort of breaking a super pixel into two makes it a less efficient alternative.
+Our experience is that since a noticeable percentage of extracted superpixels cover pixels of two neighboring leaves; the extra effort of breaking a super pixel into two makes it a less efficient alternative.
 
@@
 To quantify the precision of the label propagation, we manually label $3$ images for each of $3$ Arabidopsis plants ($9$ images in total) on fluorescence and RGB modalities.
-The labels in each modality is propagated on other modalities.
+The label in each modality is propagated on other modalities.
 The result of one plant is illustrated in Figure~\ref{fig:LabelAlignment}.
@@
 The availability of multiple modalities allows user to design novel experimental setup.
-For example, using RGB and depth modalities for training and RGB for testing can take advantage of additional information during the learning without incurring extra sensor cost during the testing, which can be implemented via either learning with side information~\cite{chen2013boosting}, or transfering learning with missing modality~\cite{ding2014latent,Chen2013b}.
+For example, using RGB and depth modalities for training and RGB for testing can take advantage of additional information during the learning without incurring extra sensor cost during the testing, which can be implemented via either learning with side information~\cite{chen2013boosting}, or transferring learning with missing modality~\cite{ding2014latent,Chen2013b}.
 
@@
 \item {\it{Tracking Consistency (TC)}}, the percentage of video-to-video correspondent leaves whose tip-based errors are smaller than $\tau$.
-This is used to measure leaf tracking accuracy.
+This is used to measure leaf-tracking accuracy.
 \end{itemize}

### 2015-10-20 response/response.tex
groundtruth to ground truth
all

@@
 \begin{response}
-The depth sensor uses a a flash near IR illuminator to obtain depth estimates.
-The near IR illuminator will not influence the plant growth.
-The color image does not use any special lighting so it is not harmful as well.
-The IR and fluorescence images use a saturation light, which will damage the plants only if at high frequency.
-However, as we are taking images once per hour, the influence is minimal and can be ignored.
+RGB images are collected without additional light sources and only when the growth illumination is turned on, while the distance measurements uses a near IR ($\sim900~nm$) light sources.  
+These modalities should not influence photosynthesis, growth or development.  
+Both IR imaging and chlorophyll fluorescence imaging collect data during a very short dark interval when the growth light is electronically shuttered ($\sim100~microseconds/image$).  
+This should have minimal impact on photosynthesis and presumably growth.  
+Two saturating light flashes ($300~msec$ duration) in rapid succession ($\sim600~msec$ apart) are used during chlorophyll fluorescence imaging.  
+At high frequency ($4$ or more image sets per hour), this modality can be damaging to photosynthesis and growth, especially at low growth light intensities when photoprotection is minimally induced.  
+We have limited image collection to $1$ data set per hour.
 \end{response}
@@
 \begin{response}
-We use some training images with groundtruth plant segmentation masks to learn a threshold for binary segmentation.
+We use some training images with ground truth plant segmentation masks to learn a threshold for binary segmentation.
 The learnt threshold is then applied to both training images and testing images to generate the image mask.
@@
 \begin{response}
-``Collimated" means to make the light rays parallel.
+``Collimated" means to make the light rays parallel in order to minimize dispersion of light.
 We have added this definition in the paper.

### 2015-10-20 response/morrisResponse.tex
all

@@
 \begin{response}
-\todo{write response}
+We expanded our description of the labeling and the propagation to other modalities in the paper.
+The data labeling is performed in the fluorescence image modality.
+The infra-red image is from the same camera and so pixel labeling will be identical.
+The labels are propagated to the color and depth modalities using planar homographies.
+The homography between the fluorescence image and the color image is calculated by fitting matching features in these modalities, and the homography to the depth image is found by fitting a plane through the 3D plant points.
+As the reviewer noted, using these homographies will result in pixel segmentation errors due to parallax for plant regions outside of the modeled planes.
+We evaluate these errors qualitatively and quantitatively.
+Figure~\ref{fig:LabelAlignment} illustrates the label propagations from the fluorescence image to the other modalities and from the color image to other modalities with two different line colors.
+Errors occur where the lines fail to overlap and are due to propagation effects as well as boundary selection variations by the labeler between modalities.
+We compare the magnitude of these two effects in table \todo{XXX}.
+\todo{ADD TABLE RESULTS}
+
+\begin{figure*}
+\begin{centering}
+\begin{tabular}{cccc}
+\includegraphics[width=.18\textwidth]{../Figures/LabelAlignment/day_3_hour_23-seg_ir.png}&
+\includegraphics[width=.18\textwidth]{../Figures/LabelAlignment/day_3_hour_23-seg_fmp.png}&
+\includegraphics[width=.18\textwidth]{../Figures/LabelAlignment/day_3_hour_23-seg_rgb.png}&
+\includegraphics[width=.18\textwidth]{../Figures/LabelAlignment/day_3_hour_23-seg_depth.png}\\
+\includegraphics[width=.18\textwidth]{../Figures/LabelAlignment/day_5_hour_23-seg_ir.png}&
+\includegraphics[width=.18\textwidth]{../Figures/LabelAlignment/day_5_hour_23-seg_fmp.png}&
+\includegraphics[width=.18\textwidth]{../Figures/LabelAlignment/day_5_hour_23-seg_rgb.png}&
+\includegraphics[width=.18\textwidth]{../Figures/LabelAlignment/day_5_hour_23-seg_depth.png}\\
+\includegraphics[width=.18\textwidth]{../Figures/LabelAlignment/day_9_hour_20-seg_ir.png}&
+\includegraphics[width=.18\textwidth]{../Figures/LabelAlignment/day_9_hour_20-seg_fmp.png}&
+\includegraphics[width=.18\textwidth]{../Figures/LabelAlignment/day_9_hour_20-seg_rgb.png}&
+\includegraphics[width=.18\textwidth]{../Figures/LabelAlignment/day_9_hour_20-seg_depth.png}\\
+($a$) & ($b$) & ($c$) & ($d$) \\
+\end{tabular}
+\caption{Label propagation between all four modalities ($a$) infra-red, ($b$) fluorescence, ($c$) color and ($d$) depth, of a sample plant in the Arabidopsis collection for day 3 (top row), day 5 (middle row), and day 9 (bottom row).
+In the dataset the manual segmentation is performed on the fluorescence images and is outlined here as orange lines propagated to all modalities.
+The infra-red image is taken by the same camera and so will have close to exact pixel correspondence.
+To assess the segmented pixel propagation to other modalities, we also manually labeled a subset of the color plant images and propagated this segmentation to all modalities (shown in cyan).
+Comparing these boundaries in each modality gives a measure of the propagation errors due to parallax, and we provide quantitative analysis in table XXX.
+Note that the color and depth images are rotated 90 degrees.}
+\label{fig:LabelAlignment}
+\end{centering}
+\end{figure*}
+
 \end{response}
@@
 \begin{response}
-\todo{What does this question mean -- what is a supervisor?}
+We used an extra annotator. \todo{is this correct?}
 \end{response}
@@
 \begin{response}
-\todo{response similar to above}
+The pixel correspondence accuracy evaluation is explained in a response above, and a figure has been added to illustrate it, (Figure~\ref{fig:LabelAlignment}). 
 \end{response}
